---
title: "Religious Change is a Simpson's Paradox"
description: ""
author:
  - name: Joseph Bulbulia
    url: https://josephbulbulia.netlify.app
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: 0000-0002-5861-2056
  - name          : Chris G. Sibley
    affiliation   : School of Psychology, University of Auckland
    orcid_id: 0000-0002-4064-8800
date: 2021-JAN-10
output:
  distill::distill_article:
    self_contained: true
    toc: true
    code_folding: true
bibliography: r-references.bib
editor_options: 
  markdown: 
    wrap: 60
---

```{r setup, include=FALSE}
# setup
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  layout = "l-body-outset",
  fig.width = 16,
  fig.height = 9,
  collapse = TRUE,
  R.options = list(width = 60
)
  )

# packages
library("tidyverse") # data wrangling 
library("here") # setting directories
library("ggplot2") # graph 
library("ggthemes") # themes
library("table1") # tables
library("msm") # alluvial graphs
library("markovchain") # Graphs
library("diagram")# Graphs
library("seqHMM")
library("igraph")
library("TraMineR")
library("xtable")
```

## Religious change at a societial level indicates "clocklike" decline

```{r  poprelchange, fig.cap= "Clock-like Decline in Proportion of Christian Affiliation since 1966 at about 1%-2% per year", cache = TRUE, code_folding=TRUE, include = FALSE}
# Show decline in religion at the Society Level, using census data
# religious decline in new Zealand

# import census data
declineUSE <-
  as.data.frame(read.csv(
    here::here("data", "declineUSE.csv")
    ))
# select only religious people

decline <- declineUSE %>%
  select(-"NoReligion") 

# decline  NZ census counts for Christians as a percentage of the total population


library(ggplot2)

pr <- ggplot(decline, aes(y = PercentagePopulation, x = Years)) + theme_bw() +
  geom_smooth(method = "glm") +
  geom_point(
    stat = "identity",
    colour = "red",
    fill = "white",
    size = 2,
    stroke = 1
  ) + labs(x = "Time", y = "Percentage Christians") +
  labs(title = "Aggregate proportional decline in Christian affiliation: New Zealand years 1966-2018")  +
  scale_y_continuous(limits = c(0, 1)) +
  theme_bw()
pr

```

Figure \@ref(fig:hmmchange) a. presents New Zealand Census
data for society-level religious affiliation. The census
data show a clock-like decline in religious affiliation at
the level of the New Zealand population since 1966 of about
1% loss in religious affiliation per year, and more
recently, closer to 2% loss. This suggests that people are
becoming less religious over time.

## Religious change at the individual level consists of opposing processes

However, society-level change is the average of two opposing
processes that occur at the level of individuals:

-   **religious affiliation**: people might affiliate from a
    position of no-affiliation.
-   **religious disaffiliation**: people might disaffiliate
    from a position of affiliation.

These two opposing processes occur against a background of
stability - most people remain constant in their religious
affiliation or disaffiliation.

Here, we use a Hidden Markov Model to estimate rates of
religious affiliation and disaffiliation across the New
Zealand population from 2009/10 -- 2020 in a sample of
respondents who completed at least two NZAVS waves ($N$ =
48272).

We find that, annually, the society-level rate of religious
disaffiliation in New Zealand is .02%. That is the
difference between the disaffiliation rate (Pr = .03) and
the religious affiliation rate (Pr = .01). NZAVS data do not
capture fluctuations from migration, hence, the NZAVS
closely approximates the national census estimate for net
religious change at the society level.

```{r  msm, cache = TRUE, include = TRUE}
# Using markov models, show that change within people as they age differs from the society-wide trend
df <- readRDS(here::here("data", "df"))

te <- df %>%
  filter (Wave == 2019) %>%
  filter(YearMeasured==1)



  length(unique(te$Id))

#create dataframe
dat  <- df %>%
  dplyr::filter(YearMeasured == 1) %>% # filtering only people who have responded in a year
  dplyr::select(Wave, Age, Wave, Religious1 , Id, Relid, years) %>%
  dplyr::mutate(yearW  = as.numeric(Wave) - 1) %>%
  # filter(!is.na(Religious1))%>%
  group_by(Id) %>% filter(n() > 1) %>% # have responded to at least 2 x waves
  filter(n() != 0) %>%
  ungroup(Id) %>%
  group_by(Wave) %>%
  filter(!is.na(Religious1)) %>%
  ungroup() %>%
  arrange(Id, yearW)
#nrow(df)

# unique ids
length(unique(dat$Id)) #48165

```

MSM Analysis

```{r  msm2, cache = TRUE, eval = FALSE}
### MSM ANALYIS BELOW ###
# commenting out model to save time (which I've saved in a file, below)
# initial matrix for transitions
library("msm")

Q0 <- rbind(c(.9, .1),
            c(.1, .9))

# intensity matrix
Q0

# Initialise
crudeinR <-
  msm::crudeinits.msm(Religious1 ~ yearW, Id, # Id = identifier
                      data = dat,
                      qmatrix = Q0)

m1a  <- msm(
  Religious1 ~ yearW,
  Id,
  data = dat,
  covariates =  ~ Age,
  qmatrix = crudeinR,
  ematrix = rbind(c(.1,.1),c(.1,.1)),
  est.initprobs = TRUE,
  exacttimes = TRUE,# Not running without this assumption.
  gen.inits = TRUE
)
#saveRDS(m1, here::here( "models","mnm-simpson-paradox-religious-change" ))

# 
m2  <- msm(
  Religious1 ~ yearW,
  Id,
  data = dat,
  covariates =  ~ Age,
  qmatrix = crudeinR,
  ematrix = rbind(c(.1,.1),c(.1,.1)),
  est.initprobs = TRUE,
  exacttimes = TRUE,# Not running without this assumption.
  gen.inits = TRUE
)
#saveRDS(m2, here::here( "models","mnm-simpson-paradox-religious-change-2" ))

```


```{r eval = FALSE}
m1 <-readRDS(here::here( "models","mnm-simpson-paradox-religious-change" ))
m2 <-readRDS(here::here( "models","mnm-simpson-paradox-religious-change-2" ))

#probability matrix
# m1
msm::pmatrix.msm( m1a ) 
msm::pmatrix.msm( m1 ) 
msm::pmatrix.msm( m2 ) # Matches 1
```


We can compare this with the raw (un-modelled) state transition, which overstates overall change.

```{r}

# example change in wave 2018/ wave 2019
dat$yearW
dat2 <- dat %>%
  filter(yearW == 09 | yearW == 10)

raw <-msm::statetable.msm(Religious1, Id, data = dat2)
# calculates proportions by rows
out<- prop.table(raw, 1)


# latex
xtable(out)



raw2 <- msm::statetable.msm(Religious1, Id, data = dat)
out2 <- prop.table(raw2, 1)
xtable(out2)

```



```{r  hmmchange, fig.cap="Hidden Markov Model reveals religious change within people differs from the society wide-aggregate trend. As people age, they are more likely to affiliate and less likely to disaffiliate. The population gap comes from greater disaffiliation among young people than affiliation.", echo =FALSE}


#m1 <-readRDS(here::here( "models","mnm-simpson-paradox-religious-change" ))

# Graph
oz<- as.matrix( msm::pmatrix.msm( m1 ) )
oz <- round(oz, digits = 3)


stateNames <- c("Secular (.63)","Religious (.37)")
row.names(oz) <- stateNames; colnames(oz) <- stateNames
oz
## need to transpose or else arrows go in the wrong direction
toz <- t(oz) 

#library(pracma)
plotmat(toz,
       # pos = c(1,2), 
       # lwd = 1, 
       # box.lwd = 2, 
        cex.txt = 0.9, 
        box.size = 0.09, 
       # box.type = "circle", 
        box.prop = 0.5,
        arr.pos =  0.4, 
        shadow.size = 0.001,
        box.col = c("lightgreen","lightblue","orange"),
       # arr.length=.1,
       # arr.width=.1,
        self.cex = .4,
        self.shifty = -.01,
        self.shiftx = .12,
        main = "Hidden Markov Model reveals religious switching
       New Zealand: years 2009-2020")

```


## Graph 


```{r  hmmchange2, cache = TRUE, fig.cap="Hidden Markov Model reveals religious change within people differs from the society wide-aggregate trend. As people age, they are more likely to affiliate and less likely to disaffiliate. The population gap comes from much greater disaffiliation among young people than affiliation.", include = TRUE, code_folding=TRUE}

# note to self, this code can be improved
### CREATE PLOT  ###  CONVERSION AGE PLOT
## 20 year olds

#m1 <-readRDS(here::here( "models","mnm-simpson-paradox-religious-change" ))

p20 <-
  pmatrix.msm(m1, covariates = list(Age = 20), ci = "normal")
p20.Convert <- p20$estimates[1, 2]
p20.Convert.L <- p20$L[1, 2]
# get upper bound
p20.Convert.U <- p20$U[1, 2]
con.20 <- c(20, p20.Convert, p20.Convert.L, p20.Convert.U)
## 30 year olds
p30 <-
  pmatrix.msm(m1, covariates = list(Age = 30), ci = "normal")
p30.Convert <- p30$estimates[1, 2]
# set lower bound
p30.Convert.L <- p30$L[1, 2]
# get upper bound
p30.Convert.U <- p30$U[1, 2]
#combine
con.30 <- c(30, p30.Convert, p30.Convert.L, p30.Convert.U)
## 40 year old
p40 <-
  pmatrix.msm(m1, covariates = list(Age = 40), ci = "normal")
# Get Transition to Relid Estimate
p40.Convert <- p40$estimates[1, 2]
# set lower bound
p40.Convert.L <- p40$L[1, 2]
# get upper bound
p40.Convert.U <- p40$U[1, 2]
con.40 <- c(40, p40.Convert, p40.Convert.L, p40.Convert.U)
## 50 year old
p50 <-
  pmatrix.msm(m1, covariates = list(Age = 50), ci = "normal")
# Get Transition to Relid Estimate
p50.Convert <- p50$estimates[1, 2]
# set lower bound
p50.Convert.L <- p50$L[1, 2]
# get upper bound
p50.Convert.U <- p50$U[1, 2]
con.50 <- c(50, p50.Convert, p50.Convert.L, p50.Convert.U)
## 60 year olds
p60 <-
  pmatrix.msm(m1, covariates = list(Age = 60), ci = "normal")
# Get Transition to Relid Estimate
p60.Convert <- p60$estimates[1, 2]
# set lower bound
p60.Convert.L <- p60$L[1, 2]
# get upper bound
p60.Convert.U <- p60$U[1, 2]
con.60 <- c(60, p60.Convert, p60.Convert.L, p60.Convert.U)
## 70 year olds
p70 <-
  pmatrix.msm(m1, covariates = list(Age = 70), ci = "normal")
# Get Transition to Relid Estimate
p70.Convert <- p70$estimates[1, 2]
# set lower bound
p70.Convert.L <- p70$L[1, 2]
# get upper bound
p70.Convert.U <- p70$U[1, 2]
con.70 <- c(70, p70.Convert, p70.Convert.L, p70.Convert.U)
### ## 80 year olds
p80 <-
  pmatrix.msm(m1, covariates = list(Age = 80), ci = "normal")
# Get Transition to Relid Estimate
p80.Convert <- p80$estimates[1, 2]
# set lower bound
p80.Convert.L <- p80$L[1, 2]
# get upper bound
p80.Convert.U <- p80$U[1, 2]
con.80 <- c(80, p80.Convert, p80.Convert.L, p80.Convert.U)
# ### ## 90 year olds
p90 <-
  pmatrix.msm(m1, covariates = list(Age = 90), ci = "normal")
# # Get Transition to Relid Estimate
p90.Convert <- p90$estimates[1, 2]
# # set lower bound
p90.Convert.L <- p90$L[1, 2]
p90.Convert.U <- p90$U[1, 2]
con.90 <- c(90, p90.Convert, p90.Convert.L, p90.Convert.U)
# ### create data frame for conversion plot
conplot <-
  data.frame(rbind(con.20, con.30, con.40, con.50, con.60, con.70, con.80, con.90))
colnames(conplot) <-
  c("age", "conv_probability", "conv_lower", "conv_upper")
library(ggplot2)
#library(wesanderson)
#wes_palette("Zissou1", type = c("discrete"))
#library("ggsci")

plot.con <-
  ggplot(aes(
    x = age,
    y = conv_probability,
    ymin = conv_lower,
    ymax = conv_upper
  ),
  data = conplot) + geom_point(stroke = 2, colour = "#d1495b")  +
  geom_linerange(alpha =   1, colour = "#d1495b") +
  geom_smooth(colour = "#d1495b",
              method = "loess",
              se = FALSE)  +
  scale_y_continuous(limits = c(0, .1)) +
  labs(x = "Age", y = "Religious Affiliation Transition Probability w/ 95% CI") + theme_bw() + labs(title = "Religious (Dis)affiliation Dynamics in New Zealand: years 2009-2020")

#plot.con
#m1

##### CREAT PLOT FOR DECONVERSION
## 20 year olds
p20 <-
  pmatrix.msm(m1, covariates = list(Age = 20), ci = "normal")
# Get Transition to Relid Estimate
p20.decon <- p20$estimates[2, 1]
p20.decon.L <- p20$L[2, 1]
p20.decon.U <- p20$U[2, 1]
decon.20 <- c(20, p20.decon, p20.decon.L, p20.decon.U)
p30 <-
  pmatrix.msm(m1, covariates = list(Age = 30), ci = "normal")
p30.decon <- p30$estimates[2, 1]
p30.decon.L <- p30$L[2, 1]
p30.decon.U <- p30$U[2, 1]
decon.30 <- c(30, p30.decon, p30.decon.L, p30.decon.U)
p40 <-
  pmatrix.msm(m1, covariates = list(Age = 40), ci = "normal")
p40.decon <- p40$estimates[2, 1]
p40.decon.L <- p40$L[2, 1]
p40.decon.U <- p40$U[2, 1]
decon.40 <- c(40, p40.decon, p40.decon.L, p40.decon.U)
p50 <-
  pmatrix.msm(m1, covariates = list(Age = 50), ci = "normal")
p50.decon <- p50$estimates[2, 1]
p50.decon.L <- p50$L[2, 1]
p50.decon.U <- p50$U[2, 1]
decon.50 <- c(50, p50.decon, p50.decon.L, p50.decon.U)
p60 <-
  pmatrix.msm(m1, covariates = list(Age = 60), ci = "normal")
p60.decon <- p60$estimates[2, 1]
p60.decon.L <- p60$L[2, 1]
p60.decon.U <- p60$U[2, 1]
decon.60 <- c(60, p60.decon, p60.decon.L, p60.decon.U)
p70 <-
  pmatrix.msm(m1, covariates = list(Age = 70), ci = "normal")
p70.decon <- p70$estimates[2, 1]
p70.decon.L <- p70$L[2, 1]
p70.decon.U <- p70$U[2, 1]
decon.70 <- c(70, p70.decon, p70.decon.L, p70.decon.U)
p80 <-
  pmatrix.msm(m1, covariates = list(Age = 80), ci = "normal")
p80.decon <- p80$estimates[2, 1]
p80.decon.L <- p80$L[2, 1]
p80.decon.U <- p80$U[2, 1]
decon.80 <- c(80, p80.decon, p80.decon.L, p80.decon.U)
p90 <-
  pmatrix.msm(m1, covariates = list(Age = 90), ci = "normal")
p90.decon <- p90$estimates[2, 1]
p90.decon.L <- p90$L[2, 1]
p90.decon.U <- p90$U[2, 1]
decon.90 <- c(90, p90.decon, p90.decon.L, p90.decon.U)

### create data frame for conversion plot
deconplot <-
  data.frame(rbind(
    decon.20,
    decon.30,
    decon.40,
    decon.50,
    decon.60,
    decon.70,
    decon.80,
    decon.90
  ))
colnames(deconplot) <-
  c("age", "decon_probability", "decon_lower", "decon_upper")
library(ggplot2)
plot.decon <-
  ggplot(aes(
    x = age,
    y = decon_probability,
    ymin = decon_lower,
    ymax = decon_upper
  ),
  data = deconplot) +
  geom_point(alpha = 1,
             colour = "#00798c",
             stroke = 2) +   geom_linerange(alpha = 1, colour = "#00798c") +
  #scale_y_continuous(limits=c(0,.1))    +
  geom_smooth(colour = "#00798c", se = T) +
  labs(x = "Age", y = "Religious Disaffiliation Transition Probability w/ 95% CI") +
  theme_bw() +
  labs(title = "Religious (Dis)affiliation Dynamics")  +
  theme(legend.position = "bottom")

library(gridExtra)

#grid.arrange(plot.con,plot.decon, ncol=2)
### SUPERIMPOSE
deconplot$Group <- as.factor(rep("Disaffiliation", nrow(deconplot)))
conplot$Group <- as.factor(rep("Affiliation", nrow(conplot)))
deconplot2 <- deconplot %>%
  dplyr::mutate(
    conv_probability = decon_probability,
    conv_lower = decon_lower,
    conv_upper = decon_upper
  ) %>%
  dplyr::select(-c(decon_probability, decon_upper, decon_lower))

comboplot <- rbind(conplot, deconplot2)
#comboplot
# get initial probabilities for title label
#pmatrix.msm(m1)

library(ggplot2)

# plot.combo <-
#   ggplot(
#     aes(
#       x = age,
#       y = conv_probability,
#       ymin = conv_lower,
#       ymax = conv_upper,
#       colour = Group
#     ),
#     data = comboplot
#   ) +
#   geom_point(alpha = 1, stroke = 2) +
#   geom_linerange(alpha = 1) +
#   geom_smooth(se = F) +
#   scale_y_continuous(limits = c(0, .96))  +
#   labs(x = "Age", y = "Annual Probability of Religious (Dis)affiliation w/ 95 CI: range: Pr = 0 to Pr = 1 ") + theme_bw() + labs(title = "Religious (Dis)affiliation Dynamics in New Zealand: years 2020 -- 2020") +
#   #scale_colour_manual(values=c( "#E69F00", "#56B4E9")) +
#   scale_colour_manual(values = c("#d1495b", "#00798c")) +
#   theme(legend.position = "bottom")
# plot.combo


plotindividual <-
  ggplot(
    aes(
      x = age,
      y = conv_probability,
      ymin = conv_lower,
      ymax = conv_upper,
      colour = Group
    ),
    data = comboplot
  ) +
  geom_point(alpha = 1, stroke = 2) +
  geom_linerange(alpha = 1) +
  geom_smooth(se = F) +
  scale_y_continuous(limits = c(0, 1))  +
  labs(x = "Age", y = "Annual Probability of Religious (Dis)affiliation w/ 95 CI ") + theme_bw() + labs(title = "Religious (Dis)affiliation Dynamics in New Zealand: years 2009-2020") +
  #scale_colour_manual(values=c( "#E69F00", "#56B4E9")) +
  scale_colour_manual(values = c("#d1495b", "#00798c")) +
  theme(legend.position = "bottom")

library(patchwork)
pr + plotindividual  + 
  plot_annotation(title = 'Aggregated society-level change (a) differs from Individual-level religious change (b)', tag_levels = "a")


#pr / plot.combo + plot_annotation(title = "Religious Change over Time",
#         subtitle = "(i) Society-level aggregate change (ii) Individual-level process: affiliation vs. disaffiliation",
#tag_levels = "i")
```

However, as evident in Figure \@ref(fig:hmmchange),
individual-level NZAVS data reveal that as people age, the
religious affiliation rate gradually increases. Likewise, as
people age, the religious disaffiliation rate gradually
decreases. The age at which religious affiliation exceeds
disaffiliation is about 70 years old. The society-level
trend and individual-level trends run in the opposite
directions because there is higher relative religious
disaffiliation among young people. This example illustrates
what is called a "Simpson's Paradox." Wherever there is
potential for switching between states at an individual
level, there is on opportunity for a Simpson's Paradox. Most
facts of interest about the role of religion in a persons
life are subject to switching.

## Religious change is a Simpson's Paradox

```{r hmmchangeI, cache = TRUE, fig.cap="Close up of opposing processes within indiviuals (scale pr = 0 to pr = .1). Hidden Markov Model reveals that as people age, they are more likely to affiliate and less likely to disaffiliate. The population gap comes from much greater disaffiliation among young people than affiliation.", include = TRUE, code_folding=TRUE}
plotI <-
  ggplot(
    aes(
      x = age,
      y = conv_probability,
      ymin = conv_lower,
      ymax = conv_upper,
      colour = Group
    ),
    data = comboplot
  ) +
  geom_point(alpha = 1, stroke = 2) +
  geom_linerange(alpha = 1) +
  geom_smooth(se = F) +
  scale_y_continuous(limits = c(0, .1))  +
  labs(x = "Age", y = "Annual Probability of Religious (Dis)affiliation w/ 95 CI: range: Pr = 0 to Pr = 1 ") + theme_bw() + labs(title = "Religious (Dis)affiliation Dynamics in New Zealand: years 2020 -- 2020") +
  #scale_colour_manual(values=c( "#E69F00", "#56B4E9")) +
  scale_colour_manual(values = c("#d1495b", "#00798c")) +
  theme(legend.position = "bottom")
plotI
```

Appreciating that religious change is a Simpson's paradox
helps to build an intuition for why panel data are so
powerful. Sociologists have documented persistent declines
in religious affiliation across western societies, a process
Max Weber called "the disenchantment of the world"
[@Weber1946-zp]. This disenchantment theory is a central
dogma in the sociology of religion [@Norris2004-gu]. The
theory is accurate for describing society-level dynamics.
Indeed, NZAVS data confirm the society-level
"disenchantment." However, this central dogma is poorly
suited for understanding how religion and spirituality take
shape within the lives of individuals.


## Appendix

## Raw Trajectories

```{r}
library(LMest)
relwidelong<-  df %>%
  dplyr::mutate(Religious = Religious1-1)%>%
  dplyr::select(Id,Religious,Wave)

##THIS HANGS
#out <- with(relwidelong, long2matrices(id = Id, X = Age, Y = Religious))

relwide<- spread(relwidelong,Wave,Religious)
head(relwide)

#relwide<-relwide[complete.cases(relwide), ]


Relidwide<-  df %>%
  dplyr::filter(YearMeasured==1)%>%
  dplyr::select(Id,Relid,Wave)%>%
  group_by(Id) %>% filter(n() > 5)%>%
  filter(n() !=0)%>% 
  ungroup(Id)%>%
  spread(Wave,Relid)

Relidwide<-Relidwide[complete.cases(Relidwide), ]
head(Relidwide)

x_var_list<-names(relwide[,2:11])
x_var_list
library(lcsm)
plot_trajectories(data = relwide,
                 id_var = "Id", 
                 var_list = x_var_list,
                 xlab = "Time", ylab = "Value",
                 connect_missing = F, 
                 random_sample_frac = 0.1, 
                 title_n = TRUE)  +
  facet_wrap(~Id)

plot_trajectories(data = Relidwide,
                  id_var = "Id", 
                  var_list = x_var_list,
                  xlab = "Time", ylab = "Value",
                  connect_missing = F, 
                  random_sample_frac = 0., 
                  title_n = TRUE)  +
  facet_wrap(~Id)
# SAVED random_selection_RELID 2k x 2k
```




# Notes

### Graph of states 

```{r}

# Graph
oz_20<- as.matrix( msm::pmatrix.msm(m1, covariates = list(Age = 30)))
oz_20 <- round(oz_20, digits = 3)


stateNames <- c("Secular ","Religious")
row.names(oz_20) <- stateNames; colnames(oz_20) <- stateNames
oz_20
## need to transpose or else arrows go in the wrong direction
toz_20 <- t(oz_20) 

#library(pracma)
plotmat(toz_20,
       # pos = c(1,2), 
       # lwd = 1, 
       # box.lwd = 2, 
        cex.txt = 0.9, 
        box.size = 0.09, 
       # box.type = "circle", 
        box.prop = 0.5,
        arr.pos =  0.4, 
        shadow.size = 0.001,
        box.col = c("lightgreen","lightblue","orange"),
       # arr.length=.1,
       # arr.width=.1,
        self.cex = .4,
        self.shifty = -.01,
        self.shiftx = .12,
        main = "Hidden Markov Model reveals religious switching
       New Zealand: years 2009-2020, Age = 20")



# Graph
oz_70<- as.matrix( msm::pmatrix.msm(m1, covariates = list(Age = 70)))
oz_70 <- round(oz_70, digits = 3)
oz_70

stateNames <- c("Secular ","Religious")
row.names(oz_70) <- stateNames; colnames(oz_70) <- stateNames
oz_70
## need to transpose or else arrows go in the wrong direction
toz_70 <- t(oz_70) 

#library(pracma)
dev.off()
par(mfrow=c(1,2))

plotmat(toz_20,
       # pos = c(1,2), 
       # lwd = 1, 
       # box.lwd = 2, 
        cex.txt = 0.9, 
        box.size = 0.09, 
       # box.type = "circle", 
        box.prop = 0.5,
        arr.pos =  0.4, 
        shadow.size = 0.001,
        box.col = c("lightgreen","lightblue","orange"),
       # arr.length=.1,
       # arr.width=.1,
        self.cex = .4,
        self.shifty = -.01,
        self.shiftx = .12,
        main = "Hidden Markov Model reveals religious switching
       New Zealand: years 2009-2020, Age = 20")


plotmat(toz_70,
       # pos = c(1,2), 
       # lwd = 1, 
       # box.lwd = 2, 
        cex.txt = 0.9, 
        box.size = 0.09, 
       # box.type = "circle", 
        box.prop = 0.5,
        arr.pos =  0.4, 
        shadow.size = 0.001,
        box.col = c("lightgreen","lightblue","orange"),
       # arr.length=.1,
       # arr.width=.1,
        self.cex = .4,
        self.shifty = -.01,
        self.shiftx = .12,
        main = "Hidden Markov Model reveals religious switching
       New Zealand: years 2009-2020, Age = 70")

```





### Three state model 


```{r}
q3 <-rbind(c(.1,.1,.1),
           c(.1,.1,.1),
           c(.1,.1,.1)) #  Allow permitted transitions


# standardise age
# dat2 <- dat %>%
#   mutate(age_s = scale(Age))

#three state emissions model
m3  <- msm(
  Religious1 ~ yearW,
  Id,
  data = dat,
  covariates = ~ Age,
  est.initprobs = TRUE,
  exacttimes = TRUE,# Not running without this assumption.
  gen.inits = TRUE,
  qmatrix = q3,
  ematrix = rbind(c(.1, .1, .1),
                  c(.1, .1, .1),
                  c(.1, .1, .1)
))


saveRDS(m3, here::here("models","simpsons-paradox-religion-three-state"))

# saved to save time

m3 <- readRDS(here::here("models", "simpsons-paradox-religion-three-state"))

qmatrix.msm(m3)
pmatrix.msm(m3) # works


## 
options(scipen = 100)
pmatrix.msm(m3, covariates = list(Age = 30))
pmatrix.msm(m3, covariates = list(Age = 60))
pmatrix.piecewise.msm(m3)
round( pmatrix.msm(m3, covariates = list(Age = 20)), 2)
pmatrix.msm(m3, covariates = "mean" )




# Graph
hoz_70<- as.matrix( msm::pmatrix.msm(m3, covariates = list(Age = 70)))
hoz_70 <- round(hoz_70, digits = 2)
hoz_70

stateNames <- c("Secular ","Religious")
row.names(oz_70) <- stateNames; colnames(oz_70) <- stateNames
oz_70
## need to transpose or else arrows go in the wrong direction
toz_70 <- t(oz_70) 

#library(pracma)
dev.off()
par(mfrow=c(1,2))

plotmat(toz_20,
       # pos = c(1,2), 
       # lwd = 1, 
       # box.lwd = 2, 
        cex.txt = 0.9, 
        box.size = 0.09, 
       # box.type = "circle", 
        box.prop = 0.5,
        arr.pos =  0.4, 
        shadow.size = 0.001,
        box.col = c("lightgreen","lightblue","orange"),
       # arr.length=.1,
       # arr.width=.1,
        self.cex = .4,
        self.shifty = -.01,
        self.shiftx = .12,
        main = "Hidden Markov Model reveals religious switching
       New Zealand: years 2009-2020, Age = 20")

# 
# 
# # Reduce data
# 
# dat2  <- df %>%
#   dplyr::filter(YearMeasured == 1 )%>% # filtering only people who have responded in a year
#   dplyr::select(Wave, Age, Wave, Religious1 ,Id, Relid, years)%>%
#   dplyr::mutate(yearW  = as.numeric(Wave)-1) %>%
#  # filter(!is.na(Religious1))%>%
#   group_by(Id) %>% filter(n() > 3)%>% # have responded to at least 4 x waves
#   filter(n() !=0)%>%
#   ungroup(Id)%>%
#   group_by(Wave) %>%
#   filter(!is.na(Religious1)) %>%
#   ungroup()%>%
#   arrange(Id,yearW)
# 
# # # 19,486
# 
# length(unique(dat2$Id))
# 

# standardise 
summary(df$Cohort)
dat2 <- df %>%
  dplyr::filter(YearMeasured == 1 )%>% # filtering only people who have responded in a year
  dplyr::select(Wave, Age, Wave, Religious1 ,Id, Relid, years, Cohort.WideBand,GenCohort, Cohort)%>%
  dplyr::mutate(yearW  = as.numeric(Wave)-1) %>%
 # filter(!is.na(Religious1))%>%
  group_by(Id) %>% filter(n() > 1)%>% # have responded to at least 2 x waves
  filter(n() !=0)%>%
  ungroup(Id)%>%
  group_by(Wave) %>%
  filter(!is.na(Religious1)) %>%
  filter(!is.na(GenCohort)) %>%
  ungroup()%>%
 mutate(age2009 = 2019 - Cohort) %>%
mutate(Cohort_WideBand = as.numeric(Cohort.WideBand)) %>%
  arrange(Id,yearW)

relwidelong<-  df %>%
  dplyr::mutate(Religious = Religious1-1)%>%
  dplyr::select(Id,Religious,Wave)


GenCohortwidelong<-  df %>%
  dplyr::select(Id,GenCohort,Wave)
##THIS HANGS
#out <- with(relwidelong, long2matrices(id = Id, X = Age, Y = Religious))

relwide<- spread(relwidelong,Wave,Religious)
relwide
genwide<- spread(GenCohortwidelong,Wave,GenCohort)

Genwide = as.data.frame(genwide$`2019`)
head(Genwide)

colnames(Genwide)<-"GenCohort"

str(Genwide$GenCohort)




m3b  <- msm(
  Religious1 ~ yearW,
  Id,
  data = dat2,
  covariates = ~ Cohort_WideBand,
  est.initprobs = TRUE,
  exacttimes = TRUE,# Not running without this assumption.
 # gen.inits = TRUE,
  qmatrix = q3,
  ematrix = rbind(c(.1, .1, .1),
                  c(.1, .1, .1),
                  c(.1, .1, .1))
)

# saveRDS(m3b, here::here("models","simpsons-paradox-religion-three-state-cohortwide"))


# options(scipen = 100)
m3b
covariates=list(sex=0))

pmatrix.msm(m3b)
pmatrix.msm(m3b, covariates = list(Cohort_WideBand = 1))
pmatrix.msm(m3b, covariates = list(Cohort_WideBand = 5))

m1
str(m3b)

m3b$hmodel$initprobs  


# 
# round( pmatrix.msm(m3b, covariates = list(Age = 20)), 2)
# rouncd( pmatrix.msm(m3b, covariates = list(Age = 40)), 2)
# 
# pmatrix.msm(m3, covariates = "mean" )
# 
# 
# 
saveRDS(m3b, here::here("models","simpsons-paradox-religion-three-state-cohortwide"))


# Graph
hoz_70<- as.matrix( msm::pmatrix.msm(m3b, covariates = list(Cohort_WideBand = 8)))
hoz_70 <- round(hoz_70, digits = 2)
hoz_70

stateNames <- c("Secular ","Religious", "Liminal")
row.names(hoz_70) <- stateNames; colnames(hoz_70) <- stateNames
hoz_70
## need to transpose or else arrows go in the wrong direction
hoz_70 <- t(hoz_70) 


plotmat(hoz_70,
       # pos = c(1,2), 
       # lwd = 1, 
       # box.lwd = 2, 
        cex.txt = 0.9, 
        box.size = 0.09, 
       # box.type = "circle", 
        box.prop = 0.5,
        arr.pos =  0.4, 
        shadow.size = 0.001,
        box.col = c("lightgreen","lightblue","orange"),
       # arr.length=.1,
       # arr.width=.1,
        self.cex = .4,
        self.shifty = -.01,
        self.shiftx = .12,
        main = "Hidden Markov Model reveals religious switching
       New Zealand: years 2009-2020, Age = 70")

```


```{r}
# Graph
table(dat2$Cohort_WideBand)
hoz_20<- as.matrix( msm::pmatrix.msm(m3b, covariates = list(Cohort_WideBand = 3)))
hoz_20 <- round(hoz_20, digits = 2)
hoz_20

stateNames <- c("Secular ","Religious", "Liminal")
row.names(hoz_20) <- stateNames; colnames(hoz_20) <- stateNames
hoz_20
## need to transpose or else arrows go in the wrong direction
hoz_20 <- t(hoz_20) 


plotmat(hoz_20,
       # pos = c(1,2), 
       # lwd = 1, 
       # box.lwd = 2, 
        cex.txt = 0.9, 
        box.size = 0.09, 
       # box.type = "circle", 
        box.prop = 0.5,
        arr.pos =  0.4, 
        shadow.size = 0.001,
        box.col = c("lightgreen","lightblue","orange"),
       # arr.length=.1,
       # arr.width=.1,
        self.cex = .4,
        self.shifty = -.01,
        self.shiftx = .12,
        main = "Hidden Markov Model reveals religious switching
       New Zealand: years 2009-2020, Cohort = 3")

```


```{r}
# Graph
table(dat2$Cohort_WideBand)
hoz_90<- as.matrix( msm::pmatrix.msm(m3b, covariates = list(Cohort_WideBand = 9)))
hoz_90 <- round(hoz_90, digits = 2)
hoz_90

stateNames <- c("Secular ","Religious", "Liminal")
row.names(hoz_90) <- stateNames; colnames(hoz_90) <- stateNames
hoz_90
## need to transpose or else arrows go in the wrong direction
hoz_90 <- t(hoz_90) 


plotmat(hoz_90,
       # pos = c(1,2), 
       # lwd = 1, 
       # box.lwd = 2, 
        cex.txt = 0.9, 
        box.size = 0.09, 
       # box.type = "circle", 
        box.prop = 0.5,
        arr.pos =  0.4, 
        shadow.size = 0.001,
        box.col = c("lightgreen","lightblue","orange"),
       # arr.length=.1,
       # arr.width=.1,
        self.cex = .4,
        self.shifty = -.01,
        self.shiftx = .12,
        main = "Hidden Markov Model reveals religious switching
       New Zealand: years 2009-2020, Cohort = 9")

```



```{r}
# Graph
table(dat2$Cohort_WideBand)
hoz_50<- as.matrix( msm::pmatrix.msm(m3b, covariates = list(Cohort_WideBand = 5)))
hoz_50 <- round(hoz_50, digits = 2)
hoz_50

stateNames <- c("Secular ","Religious", "Liminal")
row.names(hoz_50) <- stateNames; colnames(hoz_50) <- stateNames
hoz_50
## need to transpose or else arrows go in the wrong direction
hoz_50 <- t(hoz_50) 


plotmat(hoz_50,
       # pos = c(1,2), 
       # lwd = 1, 
       # box.lwd = 2, 
        cex.txt = 0.9, 
        box.size = 0.09, 
       # box.type = "circle", 
        box.prop = 0.5,
        arr.pos =  0.4, 
        shadow.size = 0.001,
        box.col = c("lightgreen","lightblue","orange"),
       # arr.length=.1,
       # arr.width=.1,
        self.cex = .4,
        self.shifty = -.01,
        self.shiftx = .12,
        main = "Hidden Markov Model reveals religious switching
       New Zealand: years 2009-2020, Cohort = 5")

```


```{r}
 Graph
table(dat2$Cohort_WideBand)
hoz_m<- as.matrix( msm::pmatrix.msm(m3b, covariates = "mean"))
hoz_m <- round(hoz_m, digits = 2)
hoz_m

stateNames <- c("Secular ","Religious", "Liminal")
row.names(hoz_m) <- stateNames; colnames(hoz_m) <- stateNames
hoz_m
## need to transpose or else arrows go in the wrong direction
hoz_m <- t(hoz_m) 


plotmat(hoz_m,
       # pos = c(1,2), 
       # lwd = 1, 
       # box.lwd = 2, 
        cex.txt = 0.9, 
        box.size = 0.09, 
       # box.type = "circle", 
        box.prop = 0.5,
        arr.pos =  0.4, 
        shadow.size = 0.001,
        box.col = c("lightgreen","lightblue","orange"),
       # arr.length=.1,
       # arr.width=.1,
        self.cex = .4,
        self.shifty = -.01,
        self.shiftx = .12,
        main = "Hidden Markov Model reveals religious switching
       New Zealand: years 2009-2020, Cohort = average")

```


```{r}
# Graph
table(dat2$Cohort_WideBand)
hoz_70<- as.matrix( msm::pmatrix.msm(m3b, covariates = list(Cohort_WideBand = 7)))
hoz_70 <- round(hoz_70, digits = 2)
hoz_70

stateNames <- c("Secular ","Religious", "Liminal")
row.names(hoz_70) <- stateNames; colnames(hoz_70) <- stateNames
hoz_70
## need to transpose or else arrows go in the wrong direction
hoz_70 <- t(hoz_70) 


plotmat(hoz_70,
       # pos = c(1,2), 
       # lwd = 1, 
       # box.lwd = 2, 
        cex.txt = 0.9, 
        box.size = 0.09, 
       # box.type = "circle", 
        box.prop = 0.5,
        arr.pos =  0.4, 
        shadow.size = 0.001,
        box.col = c("lightgreen","lightblue","orange"),
       # arr.length=.1,
       # arr.width=.1,
        self.cex = .4,
        self.shifty = -.01,
        self.shiftx = .12,
        main = "Hidden Markov Model reveals religious switching
       New Zealand: years 2009-2020, Cohort = 7")

```

We can estimate a Hidden Markov Model using the seqHMM package.  

```{r}
# 
# library(seqHMM)
# #check to pull right data
# library(LMest)
# relwidelong<-  df %>%
#   dplyr::mutate(Religious = Religious1-1)%>%
#   dplyr::select(Id,Religious,Wave)
# 
# 
# GenCohortwidelong<-  df %>%
#   dplyr::select(Id,GenCohort,Wave)
# ##THIS HANGS
# #out <- with(relwidelong, long2matrices(id = Id, X = Age, Y = Religious))
# 
# relwide<- spread(relwidelong,Wave,Religious)
# relwide
# genwide<- spread(GenCohortwidelong,Wave,GenCohort)
# 
# Genwide = as.data.frame(genwide$`2019`)
# head(Genwide)
# 
# colnames(Genwide)<-"GenCohort"
# 
# str(Genwide$GenCohort)
# 
# #cohort_wideband = as.numeric(df$Cohort.WideBand)
# cohort_wideband = as.numeric(df$Cohort.WideBand)
# 
# 
# relwide2 = cbind(relwide, Genwide)
# head(relwide2)
# 
# #relwide<-relwide[complete.cases(relwide), ]
# 
# 
# 
# relw <- relwide2[, 2:12]
# relw
# #####
# relseq2 <- seqdef(relw,label = c("Rel-","Rel+"))
# relseq2
# nrow(relseq2)
# 
# 
# ## 2 state model in  this package
# sc_initmod_random <- build_hmm(observations = relseq2, n_states = 3)
# sc_initmod_random
# 
# 
# nrow(GenCohort)
# listdat<-list(relwide2)
# 
# listdat$covariates$cohort<-factor(Genwide$GenCohort, labels = c("silent","boomers","genx","geny","genz"))
# 
# listdat$covariates$cohort
# # 
# 
# 
# 
# sc_initmod <- build_hmm(
#   observations = relseq2,
#   initial_probs = sc_initmod_random$initial_probs,
#   transition_probs = sc_initmod_random$transition_probs,
#   emission_probs = sc_initmod_random$emission_probs,
#   formula = ~ cohort, 
#   data = listdat$covariates
# )
# 
# sc_initmod
# 
# sc_fit <- fit_model(sc_initmod)
# 
# #saveRDS(sc_fit, here::here("models","hmm_threestate_cohort"))
# 
# sc_fit<- readRDS(here::here("models","hmm_threestate_cohort"))
# fm<- sc_fit$model
# 
# 
# summary(fm, conditional_se = FALSE)
# str(fm)
# fm
# 
# library(igraph)
# plot(sc_fit$model,
#      layout = layout_nicely, 
#      # vertex.label = "names"
#      title ="Hidtden States Religious Identification",
#     legend.prop =.3)
# dev.off()
# 
# transprob<-as.matrix(
#   fm$transition_probs
#   )
# transprob

```



```{r}
library(seqHMM)
####  ## Mixed clusters ### THIS WORKS AS FOLLOWS...  
dat2 <- df %>%
  dplyr::filter(YearMeasured == 1 )%>% # filtering only people who have responded in a year
  dplyr::select(Wave, Age, Wave, Religious1 ,Id, Relid, years, Cohort.WideBand,GenCohort, Cohort)%>%
  dplyr::mutate(yearW  = as.numeric(Wave)-1) %>%
 # filter(!is.na(Religious1))%>%
  group_by(Id) %>% filter(n() > 1)%>% # have responded to at least 2 x waves
  filter(n() !=0)%>%
  ungroup(Id)%>%
  group_by(Wave) %>%
  filter(!is.na(Religious1)) %>%
  filter(!is.na(Cohort.WideBand)) %>%
  ungroup()%>%
  tidyr::fill(Cohort.WideBand) %>%
 mutate(age2009 = 2019 - Cohort) %>%
mutate(Cohort_WideBand = as.factor(Cohort.WideBand)) %>%
  arrange(Id,yearW)

relwidelong<-  dat2 %>%
  dplyr::mutate(Religious = Religious1-1)%>%
  dplyr::select(Id,Religious,Wave)




GenCohortwidelong<-  dat2 %>%
  dplyr::select(Id,GenCohort,Wave) 



#out <- with(relwidelong, long2matrices(id = Id, X = Age, Y = Religious))
GenCohortwidelong
relwide<- spread(relwidelong,Wave,Religious)
relwide
nrow(relwide)

genwide<- spread(GenCohortwidelong,Wave,GenCohort) %>%
  gather(key, val, -Id) %>%
    group_by(Id) %>% 
    fill(val) %>% 
    spread(key, val)


length(unique(genwide$Id))

Genwide<- as.data.frame(as.factor(genwide$`2019`))
Genwide

colnames(Genwide)<-"GenCohort"

str(Genwide$GenCohort)

listdat <-list(relwide)

str(listdat )

listdat$covariates$GenCohort <- factor(Genwide$GenCohort, labels = c("silent","boomers","genx","geny","genz"))

length(listdat$covariates$GenCohort)

relw <- relwide[, 2:12]
relw
#####
relseq <- seqdef(relw,label = c("Rel-","Rel+"))
relseq

# check rows same
nrow(relseq)== nrow(Genwide)



# Plotting state distribution plots of observations
ssplot(mc_obs, title = "State distribution plots")


#
hmm_initmod <- build_hmm(observations = relseq, n_states = 3)
hmm_initmod

## 3 states 2 clusters
initial_probs<-hmm_initmod$initial_probs

initial_probs
transition_probs<-hmm_initmod$transition_probs
transition_probs
em_probs<-hmm_initmod$emission_probs
em_probs

mhmm_init <- list(initial_probs,initial_probs)
mhmm_init

mhmm_trans <- list(transition_probs,transition_probs)
mhmm_trans

mhmm_em <- list(em_probs,em_probs)
mc_obs<- list(relseq)
mc_obs

mhmm_trans
mhmm_init
mhmm_em



init_mhmm<-build_mhmm(observations = mc_obs, 
                      initial_probs = mhmm_init,
                      transition_probs = mhmm_trans, 
                      emission_probs = mhmm_em, 
                      formula = ~ GenCohort, 
                      data = listdat$covariates,
                      n=3,
                      n_clusters=2)

str(init_mhmm)





# Run 3 times

#mhmm_fit <- fit_model(init_mhmm, threads = 4)

saveRDS(mhmm_fit,"mhmm_fit")

#saveRDS(mhmm_fit, here::here( "mhmm_fit_relid_cohort"))

# 
# # control_em = list(restart = list(times = 10)))
# 
# mhmm_fit.v3 <- fit_model(init_mhmm, threads = 4)
# saveRDS(mhmm_fit.v3,"mhmm_fit")

options(scipen=999)

mhmm <- mhmm_fit$model
# mhmm <- mhmm_fit.run2$model
# mhmm <- mhmm_fit.v3$model

Summary
mhmm 

require("igraph")
require(TraMineR)

mhmm

plogis(0.0123 -2.3053)

plot(mhmm,interactive = F, ask = FALSE,
    # layout = layout_nicely,
     legend.prop =.4,
     ncol.legend = 6,
    label.max.length = 15,
    vertex.size = 40)



dev.off()
plogis( 1.8009 +(-0.0201)*60)




dev.off()
str(mhmm)
plot(mhmm,
     interact = F,
   #  layout = layout_nicely,
     # vertex.label = c("ReligiousZeroVolunteer","ReligiousVolunteeer","ZeroReligiousZeroVolunteer","ZeroReligiousVolunteer"),
     main ="Hidden States Religious Change",
     legend.prop =.2,
     ncol.legend = 3)

sep_hmm <- separate_mhmm(mhmm)
plot(sep_hmm[[1]], 
     loops=T, 
     layout =layout_nicely, 
     legend.prop =.1,
     ncol.legend = 3)
dev.off()
plot(sep_hmm[[2]], 
    loops=T, 
     layout =layout_nicely, 
     #layout =layout_nicely, 
     legend.prop =.2,
     ncol.legend = 3,sortv = "mds.hidden")


str(sc_hmm)
sc_hmm <- mc_to_sc(mhmm)

dev.off()  
png(file=here::here("figs", "test_hmm.png"), width = 500, height = 500, units = "px", pointsize = 12)

ssplot(sep_hmm[[2]], type = "I", sortv = "from.end", sort.channel = 0, 
    legend.prop = 0.5)
dev.off()  


ssplot(
  mhmm, 
#  type = "I", 
 # plots = "both",
  # Sorting subjects according to multidimensional
  # scaling scores of the most probable hidden state paths
  #sortv = "mds.hidden", 
  # Naming the channels
#  ylab = c("Religious", "Secular", "Mixed"), 
  # Title for the plot
  title = "Observed sequences and the 
most probable paths of hidden states",
  # Labels for hidden states (most common states)
#  hidden.states.labels = c("1: Childless single, with parents", 
 #                          "2: Childless single, left home",
 #                          "3: Married without children"),
  # Colours for hidden states
#  hidden.states.colors = c("olivedrab", "bisque", "indianred"),
  # Labels for x axis
 # xtlab = 15:30,   
  xlab = "Age",
  # Proportion for legends
  legend.prop = 0.45)
```


```{r}
######### Next with just two states and two clust 

#
hmm_initmod <- build_hmm(observations = relseq, n_states = 2)
hmm_initmod

## 2 states 2 clusters
initial_probs<-hmm_initmod$initial_probs

initial_probs
transition_probs<-hmm_initmod$transition_probs
transition_probs
em_probs<-hmm_initmod$emission_probs
em_probs

mhmm_init <- list(initial_probs,initial_probs)
mhmm_init

mhmm_trans <- list(transition_probs,transition_probs)
mhmm_trans

mhmm_em <- list(em_probs,em_probs)
mc_obs<- list(relseq)



init_mhmm_2 <-build_mhmm(observations = mc_obs, 
                      initial_probs = mhmm_init,
                      transition_probs = mhmm_trans, 
                      emission_probs = mhmm_em, 
                      formula = ~ GenCohort, 
                      data = listdat$covariates,
                      n = 2,
                      n_clusters = 2)

init_mhmm_2

# Run 3 times

mhmm_fit_2 <- fit_model(init_mhmm_2)


saveRDS(mhmm_fit_2, here::here( "mhmm_fit_relid_cohort-2"))

# 
# # control_em = list(restart = list(times = 10)))
# 
# mhmm_fit.v3 <- fit_model(init_mhmm, threads = 4)
# saveRDS(mhmm_fit.v3,"mhmm_fit")

options(scipen=999)

mhmm2 <- mhmm_fit_2$model

mhmm2


plot(mhmm2,interactive = F, ask = FALSE,
    # layout = layout_nicely,
     legend.prop =.4,
     ncol.legend = 6,
    label.max.length = 15,
    vertex.size = 40)






dev.off()

plot(mhmm2,
     interact = F,
   #  layout = layout_nicely,
     # vertex.label = c("ReligiousZeroVolunteer","ReligiousVolunteeer","ZeroReligiousZeroVolunteer","ZeroReligiousVolunteer"),
     main ="Hidden States Religious Change",
     legend.prop =.2,
     ncol.legend = 3)

sep_hmm <- separate_mhmm(mhmm2)
plot(sep_hmm[[1]], 
     loops=T, 
     layout =layout_nicely, 
     legend.prop =.1,
     ncol.legend = 3)
dev.off()
plot(sep_hmm[[2]], 
    loops=T, 
     layout =layout_nicely, 
     #layout =layout_nicely, 
     legend.prop =.2,
     ncol.legend = 3,sortv = "mds.hidden")


# 
# 
# png(file=here::here("figs", "test_hmm.png"), width = 500, height = 500, units = "px", pointsize = 12)
# 
# ssplot(sep_hmm[[2]], type = "I", sortv = "from.end", sort.channel = 0, 
#     legend.prop = 0.5)
# dev.off()  


ssplot(
  mhmm, 
#  type = "I", 
 # plots = "both",
  # Sorting subjects according to multidimensional
  # scaling scores of the most probable hidden state paths
  #sortv = "mds.hidden", 
  # Naming the channels
#  ylab = c("Religious", "Secular", "Mixed"), 
  # Title for the plot
  title = "Observed sequences and the 
most probable paths of hidden states",
  # Labels for hidden states (most common states)
#  hidden.states.labels = c("1: Childless single, with parents", 
 #                          "2: Childless single, left home",
 #                          "3: Married without children"),
  # Colours for hidden states
#  hidden.states.colors = c("olivedrab", "bisque", "indianred"),
  # Labels for x axis
 # xtlab = 15:30,   
  xlab = "Age",
  # Proportion for legends
  legend.prop = 0.45)


## One chanel


hmm_initmod <- build_hmm(observations = relseq, n_states = 2)
hmm_initmod

## 2 states 2 clusters
initial_probs<-hmm_initmod$initial_probs

initial_probs
transition_probs<-hmm_initmod$transition_probs
transition_probs
em_probs<-hmm_initmod$emission_probs
em_probs


## 2 state model in  this package
sc_initmod_random <- build_hmm(observations = relseq, n_states = 2)
sc_initmod_random


listdat$covariates$cohort<-factor(Genwide$GenCohort, labels = c("silent","boomers","genx","geny","genz"))

length(listdat$covariates$cohort)
nrow(relseq)



sc_initmod <- build_hmm(
  observations = relseq,
  initial_probs = initial_probs,
  transition_probs = transition_probs,
  emission_probs = em_probs,
  formula = ~ cohort, # won't work
  data = listdat$covariates
)


#sc_fit <- fit_model(sc_initmod)

#saveRDS(sc_fit, here::here("models","hmm_twostate_cohort"))

sc_fit<- readRDS(here::here("models","hmm_twostate_cohort"))
fm<- sc_fit$model


summary(fm, conditional_se = FALSE)
str(fm)
fm

library(igraph)
plot(sc_fit$model,
     layout = layout_nicely,
     # vertex.label = "names"
     title ="Hidtden States Religious Identification",
    legend.prop =.3)
dev.off()

transprob<-as.matrix(
  fm$transition_probs
  )
transprob


```


```{r}
##### MSM

#
q0
q0 <-rbind(c(.1,.1,.1),c(.1,.1,.1),c(.1,.1,.1)) #  Allow permitted transitions

## THIS WORKED! :)c 
gh.mod.mnm.2  <- msm(Religious1 ~ years,
                     Id,
                     data=ldf.5,
                     covariates = ~Age,
                     est.initprobs = TRUE,
                     qmatrix =q0,
                     ematrix = rbind(c(.1,.1,.1),
                                      c(.1,.1,.1),
                                      c(.1,.1,.1)))


qmatrix.msm(gh.mod.mnm.2)

pmatrix.msm(gh.mod.mnm.2) # This worked!
#saveRDS(gh.mod.mnm.2,"gh.mod.mnm.2")
gh.mod.mnm.2<-readRDS("gh.mod.mnm.2")
## Big and sharp shift at 50 
pmatrix.msm(gh.mod.mnm.2, covariates = list(Age =50))
pmatrix.msm(gh.mod.mnm.2,covariates = "mean")


q0 <-rbind(c(1,1,1),c(1,1,1),c(1,1,1)) #  Allow permitted transitions

#### nonsense
# gh.mod.mnm.3  <- msm(Religious1 ~ years,
#                       Id,
#                       data=ldf.5,
#                       covariates = ~Age,
#                       qmatrix =q0,
#                       ematrix = rbind(c(.1,.1,.1),
#                                       c(.1,.1,.1),
#                                       c(.1,.1,.1)),
#                      est.initprobs=TRUE)
#  
# 
# pmatrix.msm(gh.mod.mnm.3)
# ppass.msm(gh.mod.mnm.3)
# odds.msm(gh.mod.mnm.3)
# plot(gh.mod.mnm.3)
# saveRDS(gh.mod.mnm.3,"gh.mod.mnm.3")



```

