---
title: "Ethnicity Analysis"
description: "Intial work for Hedwig"
author:
  - name: Joseph Bulbulia
    url: https://josephbulbulia.netlify.app
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: 0000-0002-5861-2056
date: 2021-JUN-21
output:
  distill::distill_article:
    self_contained: true
    toc: true
    code_folding: true
---

```{r setup, include=FALSE}
# setup
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  layout = "l-body-outset",
  fig.width = 12,
  fig.height = 15,
  collapse = TRUE,
  R.options = list(width = 60
  )
)
```

```{r libs, include=FALSE}
library("tidyverse")
library("here")
library("equatiomatic")
library("lubridate")
library("ggplot2")
library("ggthemes") #themes
library("ggpubr")
library("viridis")
library("patchwork")
library("ggforce")
library("kableExtra")
library("lme4")
library("ggplot2")
library("ggeffects")
library("sjPlot")
library("kableExtra")
library("easystats")
library("brms")
library("rstan")
library("rstanarm")
library("bayesplot")
library("easystats")
library("kableExtra")
library("broom")
library("tidybayes")
library("bmlm")
# rstan options
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores ())
theme_set(theme_classic())
```

```{r cache = FALSE, include = FALSE}
#import data
df<-read.csv(here::here("data_raw","data_emapaccept_210614.csv"))

# check format
#str(df)


# select variables
library(tidyverse)

dat <- df %>%
  select(
    CASE,
    ET06_01_NZEuropean,
    ET06_02_Maori,
    ET06_03_Pasifica,
    ET06_04_Chinese,
    ET06_05_Indian,
    ET06_06_African,
    ET06_07_NA,
    ET06_08_SA,
    ET06_09_European,
    ET06_11_EA,
    ET06_12_SA,
    ET06_13_SeA,
    ET06_14_WA,
    DE02_Gender_Identify_Most,
    Age,
    DE04_Highest_Ed
  ) %>%
  mutate(
    id = as.factor(CASE),
    nzeuro = as.integer(ET06_01_NZEuropean - 1),
    maori = as.integer(ET06_02_Maori - 1),
    pacific = as.integer(ET06_03_Pasifica - 1),
    chinese  = as.integer(ET06_04_Chinese - 1) ,
    indian  = as.integer(ET06_05_Indian - 1),
    african = as.integer(ET06_06_African - 1),
    missing = as.integer(ET06_07_NA - 1),
    euro = as.integer(ET06_09_European - 1),
    ea =  as.integer(ET06_11_EA - 1) ,
    # check with Hedwig what these mean
    sa08 = as.integer(ET06_08_SA - 1),
    # check with Hedwig what these mean
    se12 = as.integer(ET06_12_SA - 1),
    # check with Hedwig what these mean
    sea = as.integer(ET06_13_SeA - 1),
    # check with Hedwig what these mean
    wa = as.integer(ET06_14_WA - 1),
    # check with Hedwig what these mean
    gender_id = as.factor(DE02_Gender_Identify_Most),
    # male or female?
    age = as.numeric(Age),
    edu = DE04_Highest_Ed
  ) %>%
  na_if(-9) %>%
  select(
    id,
    gender_id,
    age,
    edu,
    nzeuro,
    maori,
    pacific,
    chinese,
    indian,
    african,
    missing,
    euro,
    ea,
    sa08,
    se12,
    sea,
    wa
  ) 
glimpse(dat)
dt <- dat %>% rowwise(id)
glimpse(dt)


dt_1 <- dt %>%
  mutate(total = sum(
    c(nzeuro,
      maori,
      pacific,
      chinese,
      indian,
      african,
      missing,
      euro,
      ea,
      sa08,
      se12,
      sea,
      wa
    )
  ),
  diversity = 
  sum(
    c(nzeuro,
      maori,
      pacific,
      chinese,
      indian,
      african,
      missing,
      euro,
      ea,
      sa08,
      se12,
      sea,
      wa
    ) != 0
  )) %>%
  group_by(id) %>%
  mutate(max_ethnic = max(
    c(
      nzeuro,
      maori,
      pacific,
      chinese,
      indian,
      african,
      missing,
      euro,
      ea,
      sa08,
      se12,
      sea,
      wa
    )
  )) %>%
  mutate(
    proportion_maori = as.numeric(maori / total),
    proportion_nzeuro = as.numeric(nzeuro / total),
    proportion_pacific = as.numeric(pacific / total),
    proportion_indian = as.numeric(indian / total),
    proportion_chinese = as.numeric(chinese / total)
  ) %>%
  mutate(superidentified = as.integer(ifelse(total >= 120, 1, 0))) %>%
  mutate(underidentified = as.integer(ifelse(total <=80, 1, 0))) %>%
  ungroup()

nrow(dt_1)


nm1<- c("nzeuro",
      "maori",
      "pacific",
      "chinese",
      "indian",
      "african",
      "missing",
      "euro",
      "ea",
      "sa08",
      "se12",
      "sea",
      "wa")


dtt <- dt_1 %>%
  mutate(mak = pmax(!!!rlang::syms(nm1))) 

nrow(dtt)

# dtt<- dtt%>% 
#   mutate(max_eth = ifelse(maori == mak & across(nzeuro:wa) != mak, "maori_max", 
#                            ifelse(nzeuro == mak &  across(nzeuro:wa) != mak, "nzeuro_max", 
#                                   ifelse(indian == mak & across(nzeuro:wa) != mak, "indian_max", 
#                                           ifelse(pacific == mak & across(nzeuro:wa) != mak, "pacific_max", 
#                                                  ifelse (chinese == mak & across(nzeuro:wa) != mak, "chinese_max", 
#                                                      ifelse(maori == mak &  nzeuro == mak, "maori_euro_max", 
#                                                             ifelse(pacific == mak & nzeuro == mak, "pacific_euro_max",
#                                                                    ifelse(indian == mak & nzeuro == mak, "indian_euro_max", 
#                                                                           ifelse(chinese == mak & nzeuro == mak, "chinese_euro_max", "others"))))))))))
#                                                     

dtt<- dtt%>% 
  mutate(max_eth = ifelse(maori == mak & nzeuro != mak, "maori_max", 
                           ifelse(nzeuro == mak &  maori != mak, "nzeuro_max", 
                                  ifelse(indian == mak & nzeuro != mak, "indian_max", 
                                          ifelse(pacific == mak & nzeuro != mak, "pacific_max", 
                                                 ifelse (chinese == mak & nzeuro != mak, "chinese_max", 
                                                     ifelse(maori == mak &  nzeuro == mak, "maori_euro_max", 
                                                            ifelse(pacific == mak & nzeuro == mak, "pacific_euro_max",
                                                                   ifelse(indian == mak & nzeuro == mak, "indian_euro_max", 
                                                                          ifelse(chinese == mak & nzeuro == mak, "chinese_euro_max", "others"))))))))))
                                        
glimpse(dtt)
  



```

Total

```{r cache = FALSE, include = FALSE}
hist(dt_1$total, breaks=100)
```

Diversity

```{r cache = FALSE, include = FALSE}
hist(dt_1$diversity)
```


Instances of diversity scores (range 1 - 6)

```{r}
dt_1 %>%
  group_by(diversity) %>%
  count(counts = n_distinct()) %>%
  select(-counts)
```



Table of superidentified

```{r  cache = FALSE, include = FALSE}
table(dt_1$superidentified)
```

Table of unidentified

```{r}
table(dt_1$underidentified)
```


Graph of spread of proportions by ethnicity 

```{r  cache = FALSE, include = FALSE}

# NZ Euro identity
dt_nz <-dt_1%>%
filter(proportion_nzeuro > .01) 

nze<- qplot(dt_nz$proportion_nzeuro, geom = "histogram",bins =100)+ 
    ggtitle("Histogram of identity in sample\nwho identify as > 1% NZ European") + xlab("Distributions of NZ European proportions")

# Māori Identity

dt_maori <- dt_1 %>%
  filter(proportion_maori > .01)

nzm <- qplot(dt_maori$proportion_maori, geom = "histogram", bins = 100) +
  ggtitle("Histogram of identity in sample\nwho identify as > 1% Māori") + xlab("Distributions of Māori proportions")


# Pacific Identity

dt_pac <-dt_1%>%
filter(proportion_pacific > .01) 

nzp <- qplot(dt_pac$proportion_pacific, geom = "histogram",bins =100) + 
  ggtitle("Histogram of identity in sample\nwho identify as > 1% Pacific") + xlab("Distributions of Pacific idenity proportions")



# Indian identity
dt_indian <-dt_1%>%
filter(proportion_indian > .01) 

nzi <- qplot(dt_indian$proportion_indian, geom = "histogram",bins =100) + 
  ggtitle( "Histogram of identity in sample\nwho identify as > 1% Indian") + xlab("Distributions of Indian idenity proportions")


# Chinese identity

dt_chinese <-dt_1%>%
filter(proportion_chinese > .01) 

nzc<- qplot(dt_chinese$proportion_chinese, geom = "histogram",bins =100) + ggtitle("Histogram of identity in sample\nwho identify as > 1% Chinese") + xlab("Distributions of Chinese idenity proportions")



library(patchwork)

nze + nzm + nzp + nzi + nzc +  plot_annotation("Historgrams of sample Ethnic proportions",  subtitle = "Histograms review greater distribution of identities among Māori and Pacific ethnic identities", tag_levels = 'a')

```


Create longer data frame for models

```{r cache = FALSE, include = FALSE}

dt_2 <- dt_1 %>%
  pivot_longer(
    !c(
      id,
      age,
      edu,
      gender_id,
      max_ethnic,
      total,
      diversity,
      superidentified,
      underidentified,
      starts_with("proportion")
    ),
    names_to = "eth_id",
    values_to = "ethnicity_rating"
  ) %>%
  mutate(eth_id = factor(eth_id))
# 
# # not used
# dt_3<- dt_1%>%
#   pivot_longer(
#     !c(
#       id,
#       age,
#       edu,
#       gender_id,
#       max_ethnic,
#       total,
#       diversity,
#       superidentified,
#       underidentified,
#       nzeuro,
#       maori,
#       pacific,
#       chinese,
#       indian,
#       african,
#       missing,
#       euro,
#       ea,
#       sa08,
#       se12,
#       sea,
#       wa
#     ),
#     names_to = "prop_eth",
#     values_to = "eth_prop"
#   )

```


Table of unique identities

```{r cache = FALSE, include = FALSE}
dt_2%>%
  group_by(eth_id)%>%
  tally(ethnicity_rating !=0) %>%
  arrange(desc(n))
```


## Some simple analyses (TBC)

How many people are >= 50% european or nzeuro and at least one other ethnicity?

```{r}
dt_1 %>%
  tally((nzeuro >= 50  | euro >= 50) & c_across(nzeuro:ea)!=0)
```


How many people are part maori and part european? 

```{r}
dt_1 %>%
  tally((maori > 1  & nzeuro > 1) )
```


## Latent profile analysis 

Here we perform a latent profile analysis to extract ethnic identity types

```{r, cache = TRUE}
library(tidyLPA)

# LPA on proportional identity 

out <- dt_1 %>%
  dplyr::select(
    proportion_chinese,
    proportion_indian,
    proportion_nzeuro,
    proportion_maori,
    proportion_nzeuro,
    proportion_pacific
  )
#%>%
 # dplyr::mutate_all(., scale)

out%>%
  single_imputation() %>%
  tidyLPA::estimate_profiles(5) %>%
    plot_profiles(add_line = TRUE)
```

Arguably a better way to estimate profiles is to use the raw scores. This allows us to adjust for super-identifiers and under-identifiers.



```{r cache = TRUE}
## Try this with counts 
out2 <- dt_1 %>%
  dplyr::select(
    chinese,
    indian,
    nzeuro,
    maori,
    nzeuro,
    pacific
  )

out2%>%
  single_imputation() %>%
  tidyLPA::estimate_profiles(5) %>%
    plot_profiles(add_line = TRUE)

```


Here we find that those who are find that the Māori category appears to be superidentified as Maori and NZeuro wheree as the Pacific category appears to be superidentified as Pacific and NZeuro. 



##  Formal models

Next we attempt to formally model total identity and diversity 


## Predictors of total identity

```{r}
hist(dt_1$total, breaks = 100)
```


```{r}
#mix <- mixture(gaussian, gaussian, gaussian)

# #
# prior <- c(
#   prior(normal(0, 2), Intercept, dpar = mu1),
#   prior(normal(0, 2), Intercept, dpar = mu2),
#   prior(normal(0, 2), Intercept, dpar = mu3)
# )


# Filter dominent ids or model will not run
# dt_3 <- dt_2 %>%
#   group_by(id) %>%
#   filter(eth_id == "nzeuro" | eth_id == "maori" |  eth_id == "chinese" | 
#            eth_id == "indian" | eth_id == "pacific" ) %>% ungroup() %>% droplevels()

# # This captures 180 ids
# length(unique(dt_3$id))
# 
# glimpse(dt_3)



fit_t <- brm(bf(ethnicity_rating ~ eth_id - 1  + (1|id)) , # random intercept for ids
            data = dt_2,
          # family = mix, # mixture takes *way* too long
           file = here::here("models", "hedwig-total"))
summary(fit_t)


```

This just tells us that the expect response for nzeuro is higher.


Lets focus on the predictors of superidentification


```{r}


fit_t2 <-
  brm(bf(superidentified ~ max_eth-1),
    data = dtt,
    family =  "bernoulli",
    file = here::here("models", "hedwig-total_2")
  )
par_m2 <- parameters::model_parameters(fit_t2)
par_m2
plot(par_m2)
```


We can graph the predicted probabilities for classification as superidentified on the probability scale, and we see it is the Maori / NZeuropean joint identifiers that are maximally identified. 


```{r}
plot(
  conditional_effects(
    fit_t2,
    categorical = FALSE,
    prob = 0.89,
    re_formula = NA,
  ),   # WE cannot graph points when the points arg = TRUE
  points = TRUE,
  point_args = list(
    alpha = 1,
    width = .1,
    size = .2
  )
) 

```



This result suggests that those who rate themselves as equally maximally european and maori are more likely to be superidentified.



Next lets focus on under identification. Because there are no instances of maximally maori_europeans who were underidentified we remove this group from the model to avoid complete separation. 


```{r}
dtt_removed <- dtt %>%
  filter(max_eth!= "maori_euro_max")

table(dtt$max_eth)
# 173 cases
#nrow(dtt_removed)

fit_t3 <-
  brm(bf(underidentified ~ max_eth-1),
    data = dtt_removed,
    family =  "bernoulli",
    file = here::here("models", "hedwig-total_3")
  )

summary(fit_t3)
par_m3 <- parameters::model_parameters(fit_t3)
par_m3
plot(par_m3)
```


Again we plot our results, and find that the expected classification for all groups as underidentified is low, with maori_max the lowest overall in underidentification (although with broad uncertainty). 

```{r}
plot(
  conditional_effects(
    fit_t3,
    categorical = FALSE,
    prob = 0.89,
    re_formula = NA,
  ),   # WE cannot graph points when the points arg = TRUE
  points = TRUE,
  point_args = list(
    alpha = 0.1,
    width = .1,
    size = .2
  )
) 

```



Finally we estimate diversity using an ordinal model


```{r}
fit_4 <- brm(bf(diversity ~ max_eth),  # random intercept for repeated measures
            data = dtt,
           family = cumulative(link = "logit"), 
           file = here::here("models", "hedwig-diversity"))

par_m4 <- parameters::model_parameters(fit_4)
par_m4
plot(par_m4)
```


We can plot the conditional expectations. Here we find that those who are maximally indian and maximally european reveal separation in the expected probabilities for one or at most two identities. 

In all other groups however, we substantial overlap with three or more expected numbers of identities.  

```{r}
plot(
  conditional_effects(
    fit_4,
    categorical = TRUE,
    prob = 0.89,
    re_formula = NA,
  ),   # WE cannot graph points when the points arg = TRUE
  points = TRUE,
  point_args = list(
    alpha = 0.1,
    width = .1,
    size = .2
  )
) 

```


We caution that the sample used here is not representative of the New Zealand population.  We do no extrapolate to features of this society. 

However, these results are nevertheless important because as a proof of concept that within people may exhibit multiple ethnic identities. 

Moreover, we find that people with join Maori and NZ european identities are abundant, and that among this group there is a greater tendency to super-identification. 

Finally those who are maximally Maori are in absolute terms the least likely group to present under-identification, wherease those who identify as maximally indian and those who idnetify as maximally chinese have a greater probability of expressing underidentification. NZ europeans sit somwehere between maori and indians/chinese population from which our sample is drawn. There is two much varaibility in the Pacific response to estimate a reliable difference. 





## Appendix: estimating causal effects.


```{r cache = FALSE}
###   Causal graph. What might affect identifcation? 
```{r}
library(ggdag)
dg <- dagify(
  total ~ age + norm + gender + diversity + edu,
  diversity ~ age + gender + edu,
 # latent = "U",
  exposure =  "norm",
  outcome =   "diversity" #,
  # labels = c(
  #   "dom" = "dominance",
  #   "pitch" = "pitch",
  #   "age" = "age",
  #   "male" = "male",
  #   "biology" = "biological endowment",
  #   "hs" = "hostile sexism",
  #   "bs" = "benevolent sexism",
  #   "sdo" = "Soc Dom Orientation",
  #   "U" = "Nastiness"
  # )
) %>%
  tidy_dagitty() 

dg %>%
  ggdag(#use_labels = "label", 
        text = TRUE) + theme_dag_blank()
```


Note that on this DAG, there are many potential collider confounds

```{r}
ggdag::ggdag_collider(dg, 
                    #  use_labels = "label", 
                      text = TRUE) + theme_dag_blank() +
 labs(title = "Colliders")
```



```{r}
ggdag::ggdag_adjustment_set(dg, 
                            #use_labels = "label", t
                            text = TRUE) + theme_dag_blank() +
  labs(title = "")
```

On the assumptions of this DAG, you would be correct to condition on age, benevolent sexism, hostile sexism, male gender and social dominance orientation. 


## Partial correlations 

```{r}
dt %>%
  correlation(partial = TRUE,
              multilevel = FALSE) %>%
  summary()
```

## Notes



For more information about the NZAVS see [here](https://www.psych.auckland.ac.nz/en/about/new-zealand-attitudes-and-values-study.html) and [here](https://go-bayes.github.io/reports/posts/nzavs/)

