---
title: "Measuring the intensity and diversity of ethnic identity reveals weakness in standard categorical measurements "
description: "Intial notes"
author:
  - name: Hedwig Eisenbarth
    url: --here--
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: -- here--
  - name: Joseph Bulbulia
    url: https://josephbulbulia.netlify.app
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: 0000-0002-5861-2056
date: 2021-JUN-21
output:
  distill::distill_article:
    self_contained: true
    toc: true
    code_folding: true
---

```{r setup, include=FALSE}
# setup
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  layout = "l-body-outset",
  fig.width = 12,
  fig.height = 15,
  collapse = TRUE,
  R.options = list(width = 60
  )
)
```

```{r libs, include=FALSE}
library("tidyverse")
library("here")
library("lubridate")
library("ggplot2")
library("ggthemes") #themes
library("ggpubr")
library("viridis")
library("patchwork")
library("ggforce")
library("kableExtra")
library("lme4")
library("ggplot2")
library("ggeffects")
library("sjPlot")
library("kableExtra")
library("easystats")
library("brms")
library("rstan")
library("rstanarm")
library("bayesplot")
library("easystats")
library("kableExtra")
library("broom")
library("tidybayes")
library("tidyLPA")
library("table1")
# rstan options
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores ())
theme_set(theme_classic())
```

## Introduction

The New Zealand national census asks people to respond to the following question:

> Which ethnic group(s) do you belong to?

A tick box with the following options appears:

-   New Zealand European
-   Māori
-   Samoan
-   Cook Island Māori
-   Tongan
-   Niuean
-   Chinese
-   Indian
-   Other such as DUTCH, JAPANESE, TOKELAUAN. Please state: [OPEN BOX]

The rate of multiple group identification among those who tick Maori is 45% [source](https://www.stats.govt.nz/tools/2018-census-ethnic-group-summaries/m%C4%81ori)

The rate of multiple group identification among those who tick European is 84.1% [source](https://www.stats.govt.nz/tools/2018-census-ethnic-group-summaries/european)

A clear limitation of this approach is we cannot determine the intensity of these ethnicity ratings.

That is, despite the evidence for multiple ethnic identifications among the majority of New Zealander, commonplace methods for measuring ethnicity do not clarify levels of individual ethnic commitments.

Here, we develop a novel measurement instrument and employ this instrument in a sub-sample of the New Zealand population. Although the sample is not reflective of the general New Zealand population, our task here is to clarify that the intensity of commitment enables estimation of fundamental dimensions of ethnic identification that elude commonplace measures of ethnicity, such as those found in national censuses.

Note: possible further readings;:

[here](https://www.stats.govt.nz/consultations/ethnicity-standard-classification-findings-from-public-consultation-november-2019) [here](https://www.otago.ac.nz/wellington/otago600094.pdf)

## Descriptive Analysis

### Import data

```{r}
#import data
df<-read.csv(here::here("data_raw","data_emapaccept_210614.csv"))

# check format
#str(df)
```

### Data wrangling

```{r}
# select variables
library(tidyverse)

dat <- df %>%
  select(
    CASE,
    ET06_01_NZEuropean,
    ET06_02_Maori,
    ET06_03_Pasifica,
    ET06_04_Chinese,
    ET06_05_Indian,
    ET06_06_African,
    ET06_07_NA,
    ET06_08_SA,
    ET06_09_European,
    ET06_11_EA,
    ET06_12_SA,
    ET06_13_SeA,
    ET06_14_WA,
    DE02_Gender_Identify_Most,
    Age,
    DE04_Highest_Ed
  ) %>%
  mutate(
    id = as.factor(CASE),
    nzeuro = as.integer(ET06_01_NZEuropean - 1),
    maori = as.integer(ET06_02_Maori - 1),
    pacific = as.integer(ET06_03_Pasifica - 1),
    chinese  = as.integer(ET06_04_Chinese - 1) ,
    indian  = as.integer(ET06_05_Indian - 1),
    african = as.integer(ET06_06_African - 1),
    missing = as.integer(ET06_07_NA - 1),
    euro = as.integer(ET06_09_European - 1),
    ea =  as.integer(ET06_11_EA - 1) ,
    # check with Hedwig what these mean
    sa08 = as.integer(ET06_08_SA - 1),
    # check with Hedwig what these mean
    se12 = as.integer(ET06_12_SA - 1),
    # check with Hedwig what these mean
    sea = as.integer(ET06_13_SeA - 1),
    # check with Hedwig what these mean
    wa = as.integer(ET06_14_WA - 1),
    # check with Hedwig what these mean
    gender_id = as.factor(DE02_Gender_Identify_Most),
    # male or female?
    age = as.numeric(Age),
    edu = DE04_Highest_Ed
  ) %>%
  na_if(-9) %>%  # from Hedwig's notes
  select(
    id,
    gender_id,
    age,
    edu,
    nzeuro,
    maori,
    pacific,
    chinese,
    indian,
    african,
    missing,
    euro,
    ea,
    sa08,
    se12,
    sea,
    wa
  ) 
glimpse(dat)
dt <- dat %>% rowwise(id)
glimpse(dt)

# create total response and diversity variables 
dt_1 <- dt %>%
  mutate(total = sum(
    c(nzeuro,
      maori,
      pacific,
      chinese,
      indian,
      african,
      missing,
      euro,
      ea,
      sa08,
      se12,
      sea,
      wa
    )
  ),
  diversity = 
  sum(
    c(nzeuro,
      maori,
      pacific,
      chinese,
      indian,
      african,
      missing,
      euro,
      ea,
      sa08,
      se12,
      sea,
      wa
    ) != 0
  )) %>%
  group_by(id) %>%
  mutate(max_ethnic = max(
    c(
      nzeuro,
      maori,
      pacific,
      chinese,
      indian,
      african,
      missing,
      euro,
      ea,
      sa08,
      se12,
      sea,
      wa
    )
  )) %>%
  mutate(
    proportion_maori = as.numeric(maori / total),
    proportion_nzeuro = as.numeric(nzeuro / total),
    proportion_pacific = as.numeric(pacific / total),
    proportion_indian = as.numeric(indian / total),
    proportion_chinese = as.numeric(chinese / total)
  ) %>%
  mutate(superidentified = as.integer(ifelse(total >= 120, 1, 0))) %>% # this is arbitrary
  mutate(underidentified = as.integer(ifelse(total <=80, 1, 0))) %>% # this is arbitrary
  ungroup()

nrow(dt_1)



# dtt<- dtt%>% 
#   mutate(max_eth = ifelse(maori == mak & across(nzeuro:wa) != mak, "maori_max", 
#                            ifelse(nzeuro == mak &  across(nzeuro:wa) != mak, "nzeuro_max", 
#                                   ifelse(indian == mak & across(nzeuro:wa) != mak, "indian_max", 
#                                           ifelse(pacific == mak & across(nzeuro:wa) != mak, "pacific_max", 
#                                                  ifelse (chinese == mak & across(nzeuro:wa) != mak, "chinese_max", 
#                                                      ifelse(maori == mak &  nzeuro == mak, "maori_euro_max", 
#                                                             ifelse(pacific == mak & nzeuro == mak, "pacific_euro_max",
#                                                                    ifelse(indian == mak & nzeuro == mak, "indian_euro_max", 
#                                                                           ifelse(chinese == mak & nzeuro == mak, "chinese_euro_max", "others"))))))))))
#                                                     


# looking for maximum identity
```

Below we calculate maximum-ethnic identity groups for each participant: 

```{r}
nm1 <- c(
  "nzeuro",
  "maori",
  "pacific",
  "chinese",
  "indian",
  "african",
  "missing",
  "euro",
  "ea",
  "sa08",
  "se12",
  "sea",
  "wa"
)



dtt <- dt_1 %>%
  mutate(mak = pmax(!!!rlang::syms(nm1)))

#nrow(dtt)


dtt <- dtt %>%
  mutate(max_eth = ifelse(
    maori == mak & nzeuro != mak,
    "maori_max",
    ifelse(
      nzeuro == mak &  maori != mak,
      "nzeuro_max",
      ifelse(
        indian == mak & nzeuro != mak,
        "indian_max",
        ifelse(
          pacific == mak & nzeuro != mak,
          "pacific_max",
          ifelse (
            chinese == mak & nzeuro != mak,
            "chinese_max",
            ifelse(
              maori == mak &  nzeuro == mak,
              "maori_euro_max",
              ifelse(
                pacific == mak & nzeuro == mak,
                "pacific_euro_max",
                ifelse(
                  indian == mak & nzeuro == mak,
                  "indian_euro_max",
                  ifelse(chinese == mak &
                           nzeuro == mak, "chinese_euro_max", "others")
                )
              )
            )
          )
        )
      )
    )
  ))

```

### Intensity in categorical identification

The average total responses by maximal identity groups are as follows

```{r}
library(kableExtra)
dtt %>%
  group_by(max_eth) %>%
  summarise(n = n(),
            average_total_all_response = mean(total),
            sd_total = sd(total)) %>%
  arrange(desc(n)) %>%
  kbl(digits  = 2, caption = "Totals") %>%
  kable_classic_2(c("striped", "hover"), full_width = TRUE) %>%
  collapse_rows()
```

Here we find substantial evidence both for multi-group membership and for intensity levels that exceed 100.

The range of responses are as follows:

```{r}
hist(dt_1$total, breaks=100)
```

### Diversity (or spread) of sample ethnic identifications

Instances of diversity scores (range 1 - 6)

```{r}
dt_1 %>%
  select(diversity, id) %>%
  group_by(diversity) %>%
  summarise(counts = n(),
            frequency = counts / nrow(dt_1)) %>%
  select(-counts) %>%
  kbl(caption = "Multiple ethnic ratings evident in over 60% of the sample", digits = 2) %>%
  kable_classic_2(c("striped", "hover"), full_width = F) %>%
  collapse_rows()
  
```

Average diversity by groups reveals substantial overlapping identities.

```{r}
library(kableExtra)
dtt %>%
  group_by(max_eth) %>%
  summarise(mean_diversity = mean(diversity),
            sd_diversity = sd(diversity)) %>%
  arrange(desc(mean_diversity)) %>%
  kbl(digits = 2, caption = "Average diversity score by max ethnicty group") %>%
  kable_classic_2(c("striped", "hover"), full_width = TRUE) %>%
  collapse_rows()
```

### Super-identification

Table of super-identified participants reveals 68.5% of the sample are super-identified.

```{r  cache = FALSE, include = TRUE}
dtt$Superidentified <- factor(dtt$superidentified )
table1::table1(~ (Superidentified)|max_eth, data = dtt)
```

Super-identified by group

```{r}
dtt %>%
  select(max_eth, superidentified) %>%
  group_by(max_eth) %>%
  summarise(
    n = n(),
    n_super = sum(superidentified == 1),
    prop_super = n_super / n
  ) %>%
  kbl(digits = 2, caption = "Proprotion of superidentified by max ethnic group") %>%
  kable_classic_2(c("striped", "hover"), full_width = TRUE) %>%
  collapse_rows()
```

### Under-identification

Under-identified by group. Note that noe of the maori-euro co-equal max participants are under-identified in this sample. We will need to exclude this group from the analysis of predictors of under-identification because the models would be -- so to speak -- under-identified.

<!-- ```{r}  commenting out to keep the format the same -->

<!-- dtt %>% -->

<!--   select(max_eth, underidentified) %>% -->

<!--   group_by(max_eth) %>% -->

<!--   summarise( -->

<!--     n = n(), -->

<!--     n_under = sum(underidentified == 1), -->

<!--     prop_under = n_under / n -->

<!--   ) %>% -->

<!--   kbl(digits = 2,caption = "Proportion of unidentified by max ethnic group") %>% -->

<!--   kable_classic_2(c("striped", "hover"), full_width = TRUE) %>% -->

<!--   collapse_rows() -->

<!-- ``` -->

```{r}
dtt$Underidentified <- factor(dtt$underidentified )
table1::table1(~ (Underidentified)|max_eth, data = dtt)

```

### Proportional diversity

Graph of spread of proportions by ethnicity

```{r}
# NZ Euro identity
dt_nz <- dt_1 %>%
  filter(proportion_nzeuro > .01)

nze <- qplot(dt_nz$proportion_nzeuro, geom = "histogram", bins = 100) +
  ggtitle("Histogram of identity in sample\nwho identify as > 1% NZ European") + xlab("Distributions of NZ European proportions")

# Māori Identity

dt_maori <- dt_1 %>%
  filter(proportion_maori > .01)

nzm <-
  qplot(dt_maori$proportion_maori, geom = "histogram", bins = 100) +
  ggtitle("Histogram of identity in sample\nwho identify as > 1% Māori") + xlab("Distributions of Māori proportions")


# Pacific Identity


dt_pac <- dt_1 %>%
  filter(proportion_pacific > .01)

nzp <-
  qplot(dt_pac$proportion_pacific, geom = "histogram", bins = 100) +
  ggtitle("Histogram of identity in sample\nwho identify as > 1% Pacific") + xlab("Distributions of Pacific idenity proportions")



# Indian identity
dt_indian <- dt_1 %>%
  filter(proportion_indian > .01)

nzi <-
  qplot(dt_indian$proportion_indian,
        geom = "histogram",
        bins = 100) +
  ggtitle("Histogram of identity in sample\nwho identify as > 1% Indian") + xlab("Distributions of Indian idenity proportions")


# Chinese identity
dt_chinese <- dt_1 %>%
  filter(proportion_chinese > .01)

nzc <-
  qplot(dt_chinese$proportion_chinese,
        geom = "histogram",
        bins = 100) + ggtitle("Histogram of identity in sample\nwho identify as > 1% Chinese") + xlab("Distributions of Chinese idenity proportions")

library(patchwork)
# graph 
graph <- nze + nzm + nzp + nzi + nzc +  plot_annotation(
  "Historgrams of sample Ethnic proportions",
  subtitle = "Histograms review greater distribution of identities among Māori and Pacific ethnic identities",
  tag_levels = 'a'
)
graph
```

### Multiple group identification characteristics

Next we create longer data frame to describe identities in multiple groups.

```{r cache = FALSE, include = TRUE}

dt_2 <- dt_1 %>%
  pivot_longer(
    !c(
      id,
      age,
      edu,
      gender_id,
      max_ethnic,
      total,
      diversity,
      superidentified,
      underidentified,
      starts_with("proportion")
    ),
    names_to = "eth_id",
    values_to = "ethnicity_rating"
  ) %>%
  mutate(eth_id = factor(eth_id))

```

Counts of ethnic identities

```{r cache = FALSE, include = TRUE}
dt_2%>%
  group_by(eth_id)%>%
  tally(ethnicity_rating !=0) %>%
  arrange(desc(n))  %>%
  kbl(digits = 2,caption = "Counts of ethnic identifications") %>%
  kable_classic_2(c("striped", "hover"), full_width = TRUE) %>%
  collapse_rows()
```

Sample average number of chosen identitis is 2.21.

```{r}
library(kableExtra)
dt_2 %>%
  select(id, ethnicity_rating) %>%
  summarise(
    counts_ethnicity_ratings = sum(ethnicity_rating != 0),
    n_sample = length(unique(id)),
    average_ids = counts_ethnicity_ratings / n_sample
  ) %>%
  kbl(digits = 2, caption = "Average counts of ethnic identifications") %>%
  kable_classic_2(c("striped", "hover"), full_width = F) %>%
  collapse_rows()
```

### A few observations about multiple-membership

How many people are \>= 50% NZ or other european and at least one other ethnicity?

```{r}
dt_1 %>%
  tally((nzeuro >= 50  | euro >= 50) & c_across(nzeuro:ea) != 0)
```

How many people are part maori and part european?

```{r}
dt_1 %>%
  tally((maori > 1  & nzeuro > 1))
```

## Statistical models

### Latent profile analysis of ethnic identifications

Here we perform a latent profile analysis to extract ethnic identity types:

```{r, cache = TRUE}
## Try this with counts 
outt <- dt_1 %>%
  dplyr::select(chinese,
                indian,
                nzeuro,
                maori,
                nzeuro,
                pacific)

p_outt <- outt %>%
  single_imputation() %>%
  tidyLPA::estimate_profiles(7)
p_outt %>%
  plot_profiles(add_line = TRUE)

```

We find that those who are high in Māori identification are also high in NZeuro identification. We also recover a group of middle-level Maori identifiers who are middle identified in NZeuro ethnicity. The highly identified Pacific group is expected to express some NZeuro identification.

The following is a table for the proportion of the sample that fits with these profiles.

```{r}
d_out <- tidyLPA::get_data(p_outt) ## 

d_out %>%
  dplyr::select(Class) %>%
  dplyr::mutate(class = as.factor(Class)) %>%
  dplyr::group_by(class) %>%
  dplyr::summarise(n = n()) %>%
  dplyr::mutate(freq = n / sum(n)) %>%
  dplyr::arrange(desc(n)) %>%
  kbl(digits = 2,caption = "proportion of sample in LPA lasses") %>%
  kable_classic_2(c("striped", "hover"), full_width = F) %>%
  collapse_rows()
```

The third class (green/ NZ euros) and the yellow class (not fitting into any of these categories) are the proportionally largest classes with about 50% of the sample fitting into one of these two categories (25% each). The other classifications describe about 10% of the sample each, with the exception of the 5th classification, which tracks the pacific identifiers at just under 5%.

Again, because of the specific sampling approach in this study, we cannot generalise from this sample to features of the general New Zealand population, but only genearlise to features of the population from which this sample was drawn.

See Appendix 2 for fit criteria in LPA model selection

### Bayesian model for intensity in categorical identification 

#### Expected probability for intensity in categorical identification ignoring maximum ethnic identification

Let's try a Zero 1 inflated probability model as described by Matti Vuorre [here](https://mvuorre.github.io/posts/2019-02-18-analyze-analog-scale-ratings-with-zero-one-inflated-beta-models/)

See Appendix 4 for the rational for using this model

#### Further data wrangling

```{r}
# rescale date to 0-1
dt_2z <- dt_2 %>%
  mutate(ethnicity_rating100 = (ethnicity_rating / 100))

```

Model:

```{r}
zoib_model <- bf(ethnicity_rating100 ~ eth_id  + (1 | id),
                 phi ~ eth_id,
                 zoi ~ eth_id,
                 coi ~ eth_id,
                 family = zero_one_inflated_beta())

# fit
fit_zoib  <- brm(
  formula = zoib_model,
  data = dt_2z,
  file = here::here("models", "hedwig-brm-zoib")
)
#prior_summary(fit_zoib)
par_z<- parameters::model_parameters(fit_zoib)
par_z
```

The effective samples are low, and we can see low variaion close at zero in rare ethnic groups, which might be causing problems. ale.

To understand the expected outcomes we transform the estimates to the probability scale

```{r}
library(kableExtra)

head(posterior_samples(fit_zoib, pars = "b_")[,1:4] )%>% 
  mutate_at(c("b_phi_Intercept"), exp) %>% 
  mutate_at(vars(-"b_phi_Intercept"), plogis) %>% 
  posterior_summary() %>% 
  as.data.frame() %>% 
  rownames_to_column("Parameter") %>% 
   kbl(caption = "", digits = 2) %>%
  kable_classic_2(c("striped", "hover"), full_width = TRUE) %>%
  collapse_rows()

```

The interpretation is as follows:

-   `b_Intercept` is estimate of the average response fitted to Africa (the lowest level factor)
-   `b_phi_Intercept` is the precision of the beta distribution.
-   `b_zoi_Intercept` is the zero-one inflation estimate.
-   `b_coi_Intercept` is the conditional one inflation estimate.

Note that although the mean sample ethnicity rating of African is .03, the estimated intercept is close to .5.

```{r}
library(tidyverse)
dt_2z%>%group_by(eth_id)%>%
  summarise(
    mean_rating = mean(ethnicity_rating100)) %>%
  kbl(caption = "Average sample response per category, N = 181", digits = 2) %>%
  kable_classic_2(c("striped", "hover"), full_width = TRUE) %>%
  collapse_rows()
```

Here, the expected response has been shrunk towards the population mean because we have employed a multi-level model. As an aside, this result illustrates an important benefit of multi-level models -- they are skeptical of the data (and so reduce tendencies for overfitting. )

The graph hints at potential problems, low N in the ethnic identification cells.

```{r}
plot(
  conditional_effects(fit_zoib, dpar = "mu"),
  points = TRUE,
  point_args = list(alpha = .2,
    width = .1,
    size = 3)
)
```

Although the model has trouble sampling, it produces a much closer fit with the data as evident in the posterior predictive checks:

```{r}
pp_check(fit_zoib) + scale_x_continuous(limits = c(0, 1)) + ggtitle("Posterior predictive check of Poisson model for ethicity rating")
```

We compare this fit with the different distrubtional assumptions in Appendix 4, where we see much poorer performance. However, to obtain a reliable posterior, however, this model should be run for longer, or we should use stronger priors.

<!-- Let's simply the model by merging very low n categories  -->

<!-- ```{r} -->

<!-- # recode -->

<!-- dt_2zz <- dt_2z %>% -->

<!--  mutate(eth_id = as.character(eth_id)) %>%  -->

<!--   mutate(eth_idM = -->

<!--   ifelse( -->

<!--     eth_id == "african" | -->

<!--       eth_id == "ea" | -->

<!--       eth_id == "sea" | -->

<!--       eth_id == "wa" | -->

<!--       eth_id == "missing" | -->

<!--       eth_id == "sa08" | -->

<!--       eth_id == "se12"| -->

<!--       eth_id == "euro", -->

<!--     "others", -->

<!--      eth_id)) %>% -->

<!--   mutate(eth_idM = factor(eth_idM)) %>% -->

<!--   mutate(eth_idM = forcats::fct_relevel(eth_idM, -->

<!--      c( "others","nzeuro","maori","pacific","indian","chinese"))) -->

<!-- ``` -->

<!-- I'm not sure this is a sensible model because we obtain lots of counts for "others", however because this category isn't going to be the focus of our inference perhaps we can set this complication to the side, for now: -->

<!-- ```{r} -->

<!-- table(dt_2zz$eth_idM) -->

<!-- ``` -->

<!-- We press on with the model, and remove the random effect (having found that the model with the random effect doesn't perform any better.) -->

<!-- ```{r} -->

<!-- zoib_model2 <- bf(ethnicity_rating100 ~ eth_idM + (1|id), -->

<!--                  phi ~ eth_id, -->

<!--                  zoi ~ eth_id, -->

<!--                  coi ~ eth_id, -->

<!--                  family = zero_one_inflated_beta()) -->

<!-- fit_zoib2  <- brm( -->

<!--   formula = zoib_model2, -->

<!--   data = dt_2zz, -->

<!--   file = here::here("models", "hedwig-brm-zoib2") -->

<!-- ) -->

<!-- #summary(fit_zoib2) -->

<!-- #prior_summary(fit_zoib2b) -->

<!-- par_z2<- parameters::model_parameters(fit_zoib2) -->

<!-- par_z2 -->

<!-- ``` -->

<!-- Again we find very low mixing. The model would need to be run for much longer to obtain a reliable posterior, however we again find a bitter model fit than in the other attempts (Appendix 4). -->

<!-- ```{r} -->

<!-- plot(par_z2) -->

<!-- ``` -->

<!-- Here are the expected responses -->

<!-- ```{r} -->

<!-- dev.off() -->

<!-- plot( -->

<!--   conditional_effects(fit_zoib2, dpar = "mu"), -->

<!--   points = TRUE, -->

<!--   point_args = list(alpha = .2, -->

<!--     width = .1, -->

<!--     size = 3)) -->

<!-- # plot( -->

<!-- #   conditional_effects(fit_zoib2, dpar = "mu"), -->

<!-- #   points = TRUE, -->

<!-- #   point_args = list(alpha = .2, -->

<!-- #     width = .1, -->

<!-- #     size = 3), -->

<!-- #   ask = FALSE -->

<!-- # )[[2]] -->

<!-- ``` -->

<!-- The predictive checks again look good. -->

<!-- ```{r} -->

<!-- pp_check(fit_zoib) + scale_x_continuous(limits = c(0, 1)) + ggtitle("Posterior predictive check of Poisson model for ethicity rating") -->

<!-- ``` -->

### Bayesian model for super-identification

#### Expected probability superidentification ignoring ethnic identification

Model and results

```{r}
fit_t2_i <-
  brm(
    bf(superidentified ~ 1),
    data = dtt,
    family =  "bernoulli",
    file = here::here("models", "hedwig-total_2-intercept")
  )
par_m2i <- parameters::model_parameters(fit_t2_i)
par_m2i
```

The expected probability of super-identifcition across the sample population is `r plogis((par_m2i$Median))`,[`r plogis((par_m2i$CI_low))`,`r plogis((par_m2i$CI_high))`]

##### Super-identification predicted by

```{r}
fit_t2 <-
  brm(
    bf(superidentified ~ max_eth + (1|id)),
    data = dtt,
    family =  "bernoulli",
    file = here::here("models", "hedwig-total_2")
  )
par_m2 <- parameters::model_parameters(fit_t2)
par_m2
plot(par_m2)
```

The expected probabilities for super-identification on ethnic identificationis:

```{r}
ggeffects::ggpredict(fit_t2)[1]
```

We can graph the predicted probabilities for classification as super-identified on the probability scale, and we see it is the Maori / NZeuropean joint identifiers that are maximally identified.

```{r}
plot(
  conditional_effects(
    fit_t2,
    categorical = FALSE,
    prob = 0.89,
    re_formula = NA,
  ),
  # WE cannot graph points when the points arg = TRUE
  points = TRUE,
  point_args = list(
    alpha = 1,
    width = .1,
    size = .2
  )
)

```

This result suggests that those who rate themselves as equally maximally european and maori are more likely to be superidentified.

#### Bayesian model for under-identification

Next lets focus on under-identification. Because there are no instances of maximally maori_europeans who were under-identified we remove this group from the model to avoid complete separation.

```{r}
dtt_removed <- dtt %>%
  filter(max_eth != "maori_euro_max")

table(dtt$max_eth)
# 173 cases
#nrow(dtt_removed)
```

#### Expected probability for under-identification ignoring maximum ethnic identification

Model

```{r}
fit_t3i <-
  brm(
    bf(underidentified ~ 1),
    data = dtt_removed,
    family =  "bernoulli",
    file = here::here("models", "hedwig-total_3i")
  )

#summary(fit_t3i)
par_m3i <- parameters::model_parameters(fit_t3i)
par_m3i
#plot(par_m3i)
```

The expected probability for under-identification in the sample population is `r plogis(par_m3i$Median)`,[ `r(plogis(par_m3i$CI_low)`,`r(plogis(par_m3i$CI_high)`].

#### Max ethnic identification as a predictor of under-identification

Model

```{r}
fit_t3 <-
  brms::brm(
    bf(underidentified ~ max_eth + (1|id)),
    data = dtt_removed,
    family =  "bernoulli",
    file = here::here("models", "hedwig-total_3")
  )
par_m3 <- parameters::model_parameters(fit_t3)
par_m3
plot(par_m3)
```

The expected probabilities for super-identification among the max identification groups is:

```{r}
ggeffects::ggpredict(fit_t3)[1]
```

Again, we plot our results:

```{r}
plot(
  conditional_effects(
    fit_t3,
    categorical = FALSE,
    prob = 0.89,
    re_formula = NA,
  ),
  # WE cannot graph points when the points arg = TRUE
  points = TRUE,
  point_args = list(
    alpha = 0.1,
    width = .1,
    size = .2
  )
) 

```

### Bayesian model for diversity

Next, we estimate diversity using an ordinal regression model for diversity.

#### Expected probability for diversity ignoring maximum ethnic identification

```{r}
fit_4i <-
  brm(
    bf(diversity ~ 1),
    data = dtt,
    family = cumulative(link = "logit"),
    file = here::here("models", "hedwig-diversityi")
  )

par_m4i <- parameters::model_parameters(fit_4i)
par_m4i
```

The expected probability for diversity in the sample population is `r plogis(par_m4i$Median)`,[ `r(plogis(par_m4i$CI_low)`,`r(plogis(par_m4i$CI_high)`].

#### Expected probability for diversity predicted by maximum ethnic identification

Model

```{r}
fit_4 <-
  brm(
    bf(diversity ~ max_eth + (1|id)),
    data = dtt,
    family = cumulative(link = "logit"),
    file = here::here("models", "hedwig-diversity")
  )

par_m4 <- parameters::model_parameters(fit_4)
par_m4
```

The expected probabilities for diversity on ethnic identification is:

```{r}
ggeffects::ggpredict(fit_4)[1]
```

We can plot the conditional expectations. Here we find that those who are maximally indian and maximally european exhibit separation in the expected probabilities for one or at most two identities. The effective sample sizes here look better.

In all other groups however, we find substantial overlap, and three or more expected numbers of identities.

```{r}
plot(
  conditional_effects(
    fit_4,
    categorical = TRUE,
    prob = 0.89,
    re_formula = NA,
  ),
  points = TRUE,
  point_args = list(
    alpha = 0.1,
    width = .1,
    size = .2
  )
) 

```

### Bayesian model for intensity in total identification

Finally, we estimate intensity of total ethnic identification (summed scores)

#### Expected probability for intensity in total identification ignoring maximum ethnic identification

```{r}
fit_5i <-
  brm(
    bf(total ~ 1),
    data = dtt,
    family ="negbinomial",
    file = here::here("models", "hedwig-intensityi")
  )

par_m5i <- parameters::model_parameters(fit_5i)
par_m5i
```

The expected probability for diversity in the sample population is `r exp(par_m5i$Median)`,[ `r(exp(par_m5i$CI_low)`,`r(exp(par_m5i$CI_high)`].

Posterior predictive checks: it would appear as if the model smooths scores at 100.

```{r}
pp_check(fit_5i)
```

\*We might investigate a mixture model.\*

#### Expected probability for intensity in total identification by maximum ethnic identification

Model

```{r}
fit_5 <-
  brm(
    bf(total ~ max_eth + (1|id)),
    data = dtt,
    family ="negbinomial",
    file = here::here("models", "hedwig-intensity")
  )

par_m5 <- parameters::model_parameters(fit_5)
par_m5
```

The expected probabilities for intensity on ethnic identification is:

```{r}
ggeffects::ggpredict(fit_5)[1]

```

We can plot the conditional expectations.

```{r}
plot(
  conditional_effects(
    fit_5,
    prob = 0.89,
    re_formula = NA,
  ),
  points = TRUE,
  point_args = list(
    alpha = 0.1,
    width = .1,
    size = .2
  )
) 

```

Posterior predictive checks

```{r}
pp_check(fit_5)
```

Max Maori_Europeans are expect to have the highest intensity scores.

## Conclusions

### Findings

The NZ Census reveals that people in NZ exhibit multiple ethnic identities. However, the intensity of ethnic commitments remains unclear.

Here, using a continuous scale, we obtain ratings of ethnic identification and use these rating to investigate the intensity and distribution (diversity) of ethnical identities in a sample of 181 study that required ethnic identity ratings. We observe:

-   the expected maximum ethnic identification in the population from which our sample is drawn is:$\dots$

-   the expected total identification summing across the sample ethnic identification is:$\dots$

-   the expected probability of super-identification (\> 120% identified) for the sample population is:$\dots$

-   the expected probability of under-identification (\< 80% identified) for the sample population is:$\dots$

Focusing on ethnic groups, where an ethnic group is defined as the group for which one has maximum ethnic identification we find:$\dots$

-   the expected maximum ethnic identification per group is:$\dots$

-   the expected total ethnic identification per group is:$\dots$

-   the expected probability of super-identification (\> 120% identified) per group is:$\dots$

-   the expected probability of under-identification (\< 80% identified) per group is$\dots$

-   the expected probability of diversity of identification (total counts of ethnic categories) is:

### Limitations

-   We caution that the sample used here is not representative of the New Zealand population. We do no extrapolate to features of this society. This sample is not a representative cross section of the New Zealand population. We cannot infer about the prevelance and diversity of ethnic identifications among New Zealanders.

-   Both cross-cutural variation and longitudinal trends remain unclear. Whether the features we have describe here generalise to other cultures, or whether these features are changing in New Zealand remains unclear.

-   Before speculating about the the importance of our results, the behavioral implications of high, low, and multiple ethnic identifications remains uncertain. Similarly, whether people are perceived differently because they have strong or weak, homogenous or diverse ethnic identifications remains to be unclear. Future research should investigate the practical implications of the categories our measures have identified.

### Importance

We wish to highlight the following key points:

-   The NZ Zealand Census, and other national censuses use tick boxes and open ended responses to measure ethnic identification. Although this allows for an estimation of the diversity of ethnic identifications, how much people are identified with the ethnic groups to which they identify remains unclear. For example, in New Zealand, although 85% of those who tick "NZ European" also tick another ethnic category, it is unclear how much people in this group maximally identify as NZ European, and how many strongly identify with other groups as well. Our novel method for measuring ethnic identification allows us to estimate these qualities.

-   In doing so, we identify new sub-populations of jointly highly identified Maori and NZ European identified New Zealanders. This observation challenges simplistic conceptions of bi-culturalism as a phenomenon of difference.

-   We also track groups of people for whom the sum of ethnicity scores is less than 100. Those who are maximally Māori are, in absolute terms, the least likely group to present under-identification. Those who identify as maximally Indian and those who identify as maximally Chinese tend to have greater probability of expressing under-identification. NZ Europeans sit somwehere in-between.

## Appendix 1: estimating causal effects.

Which variables do we need to include as co-variates to estimate causal effects? That depends on our theory of the causal underpinnings of maximum-group identification on total identification, and dispersion counts.

We can explore different theories using Directed Acyclical Graphs.

Here is one possible model. We assume unmeasured effects on the causes of maximum ethnic identification ("U"):

```{r cache = FALSE}
###   Causal graph. What might affect identifcation? 

library(ggdag)
dg <- dagify(
  total ~ age + max_eth + gender + diversity + edu,
  diversity ~ age + max_eth + gender + diversity + edu,
  max_eth ~ U,
  latent = "U",
  exposure =  "max_eth",
  outcome =   "diversity" ,
  labels = c(
    "total" = "total",
    "age" = "age",
    "max_eth" = "max ethnic\ncategory",
    "gender" = "gender",
    "diversity" = "diversity",
    "edu" = "education",
    "U" = "Unmeasured"
  )
) %>%
  tidy_dagitty() 

dg %>%
  ggdag(use_labels = "label",
        text = FALSE) + theme_dag_blank()
```

Note that on this DAG, `diversity` and `total` are potential collider-confounds:

```{r}
ggdag::ggdag_collider(dg,
                      use_labels = "label",
                      text = FALSE) + theme_dag_blank() +
  labs(title = "Colliders")
```

What is our adjustment set?

```{r}
ggdag::ggdag_adjustment_set(
  dg,
  exposure  = "max_eth",
  outcome  = "diversity",
  use_labels = "label",
  text = F
) + theme_dag_blank() +
  labs(title = "Diversity adjustment set")
```

Also the assumptions of this DAG, we can estimate the effect of max_ethnic identity on Totals

```{r}
ggdag::ggdag_adjustment_set(
  dg,
  exposure  = "max_eth",
  outcome  = "total",
  use_labels = "label",
  text = F
) + theme_dag_blank() +
  labs(title = "Diversity adjustment set")
```

## Appendix 2. LPA model evaluation

Code here for evaluating an LPA model

```{r  cache = TRUE, code_folding = TRUE}
library("tidyLPA")
p <- 8 # max number of classes

outt <- dt_1 %>%
  dplyr::select(chinese,
                indian,
                nzeuro,
                maori,
                nzeuro,
                pacific)

# Plot classes
p_outt_8 <- outt %>%
  single_imputation() %>%
  tidyLPA::estimate_profiles(5:p)
p_outt_8 %>%
  plot_profiles(add_line = TRUE)
```

### Results

A 7-class solution maximises entropy, and the solution is interpretable.

```{r  cache = TRUE}
tidyLPA::get_fit( p_outt_8 )
```

### Fit with 7 classes

```{r cache = TRUE, layout="l-body-outset",  fig.height=8, fig.width=12}
tidyLPA::plot_profiles( p_outt_8 [[3]] , add_line = TRUE) ## note we are counting up from 5, hence `[[3]]`
```

We can obtain proportions of the sample that fit into the 7 classes:

```{r}
lpa_d <- tidyLPA::get_data(p_outt_8[[3]]) ## note we are counting up from three, hence `[[2]]`
```

```{r}
lpa_d %>%
  dplyr::select(Class) %>%
  dplyr::mutate(class = as.factor(Class)) %>%
  dplyr::group_by(class) %>%
  dplyr::summarise(n = n()) %>%
  dplyr::mutate(freq = n / sum(n)) %>%
  dplyr::arrange(desc(n)) %>%
  kbl(caption = "Proportion of sample in LPA lasses") %>%
  kable_classic_2() %>% # differret styling 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% # different sytle
  collapse_rows()

```

## Appendix 3. Partial correlations (for no good reason)

```{r}
dt %>%
  correlation(partial = TRUE,
              multilevel = FALSE) %>%
  summary()
```

## Appendix 4. Bayesian model of categorical intensity identification under different assumptions

#### Gaussian model

First we try a gaussian model

```{r}
fit_t <- brm(bf(ethnicity_rating ~ eth_id  + (1|id)) , # random intercept for ids
            data = dt_2,
           file = here::here("models", "hedwig-total"))
par_m1 <- parameters::model_parameters(fit_t)
par_m1
plot(par_m1)
```

Graphing the expected outcomes for ethnicity selection we find that expected identification as NZeuro is highest in the population from which the sample is drawn.

(Note to Hedig, we'll need to get meaninful labels for "sa08", "se12" , "wa"$\dots$)

```{r}
plot(
  conditional_effects(
    fit_t,
    categorical = FALSE,
    prob = 0.89,
    re_formula = NA,
  ),
  # WE cannot graph points when the points arg = TRUE
  points = TRUE,
  point_args = list(
    alpha = .3,
    width = .1,
    size = .2
  )
) 
```

However we can see the the posterior predictive fit is not very good:

```{r}
pp_check(fit_t) + scale_x_continuous(limits = c(0, 200)) + ggtitle("Posterior predictive check of gaussain model for ethnicity ratings")
```

#### Poisson model

We might be better off with a poisson model:

```{r}
fit_tp <-
  brm(
    bf(ethnicity_rating ~ eth_id  + (1 | id)) ,
    # random intercept for ids
    data = dt_2,
    family = "poisson",
    # mixture takes *way* too long
    file = here::here("models", "hedwig-total-p")
  )
par_m_p <- parameters::model_parameters(fit_tp)
par_m_p
plot(par_m_p)
```

Here are the expectation graphs, the model is more reasonabl but ignores the bump at 100

```{r}
plot(
  conditional_effects(
    fit_tp,
    categorical = FALSE,
    prob = 0.89,
    re_formula = NA,
  ),
  # WE cannot graph points when the points arg = TRUE
  points = TRUE,
  point_args = list(
    alpha = .3,
    width = .1,
    size = .2
  )
) 
```

Posterior checks look better, however we, again we miss the bump at 100.

```{r}
pp_check(fit_tp) + scale_x_continuous(limits = c(0, 100)) + ggtitle("Posterior predictive check of Poisson model for ethicity rating")
```

#### Negative binomial model

We might be better off still with a negative binomial model

```{r}
fit_tnb <-
  brm(
    bf(ethnicity_rating ~ eth_id  + (1 | id)) ,
    # random intercept for ids
    data = dt_2,
    family = "negbinomial",
    # mixture takes *way* too long
    file = here::here("models", "hedwig-total-nb")
  )
par_m_nb <- parameters::model_parameters(fit_tnb)
par_m_nb
plot(par_m_nb)
```

Posterior checks look a little better

```{r}
pp_check(fit_tnb) + scale_x_continuous(limits = c(0, 100)) + ggtitle("Posterior predictive check of negative binomial model for ethicity rating")
```

#### Negative binomial with a stronger prior

However we need a stronger prior. Uncertainty in the NZeuro rating takes us out of the range of possiblity, with 100 being a maximum response value for each ethnicity.

```{r}
plot(
  conditional_effects(
    fit_tnb,
    categorical = FALSE,
    prob = 0.89,
    re_formula = NA,
  ),
  # WE cannot graph points when the points arg = TRUE
  points = TRUE,
  point_args = list(
    alpha = .3,
    width = .1,
    size = .2
  )
) 
```

Finally lets constrain our negative binomial model

First, how to consider the shape parameter for the overdispersion?

This is the default BRMS prior that we used above ([see Kurz book](https://bookdown.org/ajkurz/Statistical_Rethinking_recoded/monsters-and-mixtures.html#over-dispersed-outcomes) )

```{r}
library(ggthemes)
library(tidyverse)
ggplot(data = tibble(x = seq(from = 0, to = 60, by = .1)),
       aes(x = x)) +
  geom_ribbon(aes(ymin = 0, 
                  ymax = dgamma(x, 0.01, 0.01)),
              color = "transparent", 
              fill = canva_pal("Green fields")(4)[2])+
  scale_x_continuous(NULL) +
  scale_y_continuous(NULL, breaks = NULL) +
  ggtitle(expression(paste("Our brms default ", gamma, "(0.01, 0.01) prior"))) +
  theme_hc() +
  theme(plot.background = element_rect(fill = "grey92"))
```

How would it look if we changed it? We allow less disbursion with `dgamma(x, 0.2, 0.02)`

```{r}
library(ggthemes)
library(tidyverse)
ggplot(data = tibble(x = seq(from = 0, to = 500, by = .1)),
       aes(x = x)) +
  geom_ribbon(aes(ymin = 0, 
                  ymax = dgamma(x, 0.2, 0.02)),
              color = "transparent", 
              fill = canva_pal("Green fields")(4)[2])+
  scale_x_continuous(NULL) +
  scale_y_continuous(NULL, breaks = NULL) +
  ggtitle(expression(paste("Our brms default ", gamma, "(0.01, 0.01) prior"))) +
  theme_hc() +
  theme(plot.background = element_rect(fill = "grey92"))
```

Lets refit, and also keep the intercept

```{r}
fit_tnb2 <-
  brm(
    bf(ethnicity_rating ~ eth_id  + (1 | id)) ,
    # random intercept for ids
    data = dt_2,
    prior = c( prior(gamma(0.2, 0.02), class = shape)),
    family = "negbinomial",
    file = here::here("models", "hedwig-total-nb-b")
  )

#prior_summary(fit_tnb2)
par_m_nb2 <- parameters::model_parameters(fit_tnb2)
par_m_nb2
plot(par_m_nb)

```

Graph the posterior predictive checks

```{r}
pp_check(fit_tnb2) + 
  scale_x_continuous(limits = c(0,100)) + 
  ggtitle("Posterior predictive checks for model with stronger priors on the gamma")
```

Plot results

```{r}
plot(
  conditional_effects(fit_tnb2, dpar = "mu"),
  points = TRUE,
  point_args = list(width = .05, shape = 1)
)
```
