---
title: "How did New Zealand's first Covid lockdown affect Trust in Science (and for how long)?"
description: |
author:
  - name: Joseph Bulbulia
    url: https://josephbulbulia.netlify.app
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: 0000-0002-5861-2056
date: 2021-MAR-12
output:
  distill::distill_article:
    self_contained: false
    toc: true
    code_folding: true
bibliography: bibliography.bib
---


```{r load_libraries, include=FALSE}
# setup
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  layout = "l-body-outset",
  fig.width = 16,
  fig.height = 9,
  collapse = TRUE,
  R.options = list(width = 60
)
  )


library("tidyverse")
library("easystats")
library("patchwork")
library("kableExtra")
library("ggpubr")
library("here")
library("lubridate")
library("ggdag")
library("viridisLite")
library("geepack")
library("cobalt") # check balence
library("WeightIt")
library("ggeffects")
theme_set(theme_classic())
```


Here we estimate the effects of the COVID-19 pandemic on Trust in Science at various stages of the pandemic in New Zealand.  


```{r cache=TRUE, echo = FALSE}
# import data
df <- readRDS(here::here("data", "df"))

# prepare graph
ord_dates_class <- c(
  "Baseline", 
  "JanFeb", 
  "EarlyMarch", 
  "Lockdown",
  "PostLockdown")

# 3665 days after 30 June 2009 Saturday 13 July 2019
# 3842 days after 30 June 2009 Monday 6 January 2020
# 3895 days after 30 June 2009 Friday 28 February 2020
# 3921 days after 30 June 2009 WED MAR 25th
# 3954 days after 30 June 2009 Monday 27 April 2020
# 3672 days after June 30 2009 Saturday 20 July 2019

# prepare data
cv <- df %>%
  dplyr::filter(YearMeasured == 1) %>%
  droplevels() %>%
  dplyr::filter(Wave == 2019) %>%
  dplyr::mutate(Covid_Timeline =
                    as.factor(ifelse(
                      TSCORE %in% 3896:3921, # feb 29 - march 25th
                      "EarlyMarch",
                      ifelse(
                        TSCORE %in% 3922:3954,
                        "Lockdown", #march 26- Mon 27 April 2020
                        ifelse(
                          TSCORE > 3954, # after april 27th 20202
                          "PostLockdown",
                          ifelse(
                            TSCORE %in% 3842:3895, # jan 6 to feb 28
                            "JanFeb",
                            "Baseline"  # 3672 TSCORE or  20 July 2019
                          )
                        )
                      )
                    ) ))%>%
  dplyr::select(
    Wave,
    TSCORE,
    SCIENCE.TRUST,
    Partner,
    Employed,
    Sat.Government,
    NZ.Business.Conditions,
    NZ.Economic.Situation,
    Rel.Conflict,
    Rel.Satisfaction,
    Hours.SocialMedia,
    Hours.Exercise,
    HoursCharity,
    Hours.Internet,
    Hours.News,
    Hours.Family,
    Hours.Friends,
    Hours.Housework,
    Hours.Children,
    Hours.Religious,
    Hours.Work,
    Hours.Commute,
    Hours.TV,
    Hours.CompGames,
    Hours.Community,
    Family.Time,
    Community.Time,
    Friends.Time,
    Family.Money,
    Friends.Money,
    Community.Money,
    Id,
    Parent,
    SWB.SatPWI02, # your health
    Hours.Work,
    Hours.Exercise,
    LIFEMEANING,
    KESSLER6,
    KESSLER6sum,
    Age,
    Male,
    Relid,
    Pol.Orient,
    Urban,
    GenCohort,
    Edu,
    YearMeasured,
    Covid_Timeline,
    HLTH.SleepHours,
    HLTH.Fatigue,
    LIFESAT,
    PWI,
    EthnicCats,
    NZdep,
    Partner,
    Pol.Orient,
    Urban,
    Euro,
    Religious,
    NZdep,
    WSCORE,
    Religion.Church,
    Emp.JobSecure,
    Emp.JobSat,
    Emp.JobValued,
    Alcohol.Intensity,
    Alcohol.Frequency,
    Your.Future.Security
  ) %>%
  dplyr::mutate(
    Urban = (Urban),
    Euro = (Euro),
    Religious = as.factor(Religious),
    Your_Health = (SWB.SatPWI02),
    Your_Future_Security = Your.Future.Security,
    Covid_Timeline = as.factor(Covid_Timeline)
  ) %>%
  dplyr::mutate(
    WSCORE = as.factor(WSCORE),
    #EduC = scale(as.numeric(Edu), scale = F, center = TRUE),
    Sat.Government = scale(Sat.Government),
   # AgeDecadeC = scale(Age, scale = F, center = T) / 10,
    Hours.Work10 = as.integer(Hours.Work) / 10,
    Hours.Sleep = as.integer(HLTH.SleepHours),
    Hours.Exercise = as.integer(Hours.Exercise),
    Fatigue = as.integer(HLTH.Fatigue),
    K6sum = as.integer(KESSLER6 * 6),
    LIFEMEANING_S = scale(LIFEMEANING),
    NZdepS = scale(NZdep),
    PolOrientS = scale(Pol.Orient, scale = T, center = T),
    Conservative = Pol.Orient,
    logSM = log(Hours.SocialMedia + 1),
    logINT = log(Hours.Internet + 1),
    logEX = log(Hours.Exercise + 1),
    logWK= log(Hours.Work + 1),
    logCT = log(Hours.Commute + 1),
    KESSLER6sum = as.integer(KESSLER6sum),
    Alcohol.Intensity_S = scale(Alcohol.Intensity),
    Alcohol.Frequency_S = scale(Alcohol.Frequency),
    Hours.Work = as.integer(Hours.Work),
    Hours.Exercise = as.integer(Hours.Exercise)  )%>%
  dplyr::mutate(Covid_Timeline = forcats::fct_relevel(Covid_Timeline, ord_dates_class))
```


```{r cache = TRUE}
# covid timeline
# 3665 days after 30 June 2009 Saturday 13 July 2019
# 3842 days after 30 June 2009 Monday 6 January 2020
# 3895 days after 30 June 2009 Friday 28 February 2020
# 3921 days after 30 June 2009 WED MAR 25th
library(lubridate)
library(tidyverse)


carep <- cv %>%
  dplyr::mutate(timeline = make_date(year = 2009, month = 6, day = 30) + TSCORE) %>%
  count(day = floor_date(timeline, "day")) %>%
dplyr::mutate(condition = ifelse(
      day >= "2019-06-20" &
        day < "2020-01-06",
      "Baseline",
      ifelse(
        day >= "2020-01-06" & day < "2020-02-29",
        "JanFeb",
        ifelse(
          day >= "2020-02-29" & day < "2020-03-25",
          "EarlyMarch",
          ifelse(
            day >= "2020-03-25" &
              day < "2020-04-28",
            "Lockdown",
            "PostLockdown"
            ))))) %>%
  dplyr::mutate(condition = forcats::fct_relevel(condition, ord_dates_class)) %>%
  arrange(day)

# get COVID date
dates_vline1<- as.Date("2019-06-20")
dates_vline2<- as.Date("2020-01-06")
dates_vline3<- as.Date("2020-02-28")
# get data of change of baseline
dates_vline4<- as.Date("2020-03-25")
dates_vline5 <- as.Date("2020-04-27")
dates_vline6 <- as.Date("2020-10-15")
# for line in a graph

# for line in a graph
#
dates_vline1b <- which(carep$day %in% dates_vline1)
dates_vline2b <- which(carep$day %in% dates_vline2)
dates_vline3b <- which(carep$day %in% dates_vline3)
dates_vline4b <- which(carep$day %in% dates_vline4)
dates_vline5b <- which(carep$day %in% dates_vline5)
dates_vline6b <- which(carep$day %in% dates_vline6)


tline <- ggplot(carep, aes(day, n)) +
  geom_col(aes(fill = condition)) + scale_x_date(date_labels = "%b/%Y", limits = c(as.Date("2019-06-20"), as.Date("2020-10-15")))  + 
  scale_y_continuous(limits = c(0, 1000))  +
  geom_vline(xintercept = as.numeric(carep$day[dates_vline1b]),
             col = "red",
             linetype = "dashed") +
  geom_vline(xintercept = as.numeric(carep$day[dates_vline2b]),
             col = "red") +
  geom_vline(xintercept = as.numeric(carep$day[dates_vline3b]),
             col = "red",
             linetype = "dashed") +
  geom_vline(xintercept = as.numeric(carep$day[dates_vline4b]),
             col = "red",
             linetype = "dashed") +
  geom_vline(xintercept = as.numeric(carep$day[dates_vline5b]),
             col = "red",
             linetype = "dashed") + 
  xlab("NZAVS Waves 10 and 11 daily counts: repeated measures") + ylab("Count of Responses")  + theme_classic() +   scale_fill_viridis_d() + theme(
    legend.position = "top",
    legend.text = element_text(size = 6),
    legend.title = element_text(color = "Black", size = 8)
  ) +
  # annotate(
  #   "rect",
  #   xmin = as.Date("2019-06-20"),
  #   xmax = dates_vline1,
  #   ymin = 0,
  #   ymax = 1000,
  #   alpha = .1,
  #   fill = "darkblue"
  # )  +
  # annotate(
  #   "rect",
  #   xmin = dates_vline1,
  #   xmax = dates_vline6,
  #   ymin = 0,
  #   ymax = 1000,
  #   alpha = .001
  # ) +
  # annotate(
  #   geom = "curve",
  #   x = as.Date("2019-06-20"),
  #   y = 750,
  #   xend = as.Date("2019-10-15"),
  #   yend = 800,
  #   curvature = -.2,
  #   arrow = arrow(length = unit(2, "mm"))
  # ) +
  # annotate(
  #   geom = "curve",
  #   x = as.Date("2019-06-20"),
  #   y = 750,
  #   xend = as.Date("2020-01-30"),
  #   yend = 850,
  #   curvature = -.2,
  #   arrow = arrow(length = unit(2, "mm"))
  # ) +
  # annotate(
  #   geom = "curve",
  #   x = as.Date("2019-06-20"),
  #   y = 750,
  #   xend = as.Date("2020-03-10"),
  #   yend = 875,
  #   curvature = -.2,
  #   arrow = arrow(length = unit(2, "mm"))
  # ) +
  # annotate(
  #   geom = "curve",
  #   x = as.Date("2019-06-20"),
  #   y = 750,
  #   xend = as.Date("2020-04-10"),
  #   yend = 900,
  #   curvature = -.2,
  #   arrow = arrow(length = unit(2, "mm"))
  # ) +
  # annotate(
  #   geom = "curve",
  #   x = as.Date("2019-06-20"),
  #   y = 750,
  #   xend = as.Date("2020-06-10"),
  #   yend = 925,
  #   curvature = -.2,
  #   arrow = arrow(length = unit(2, "mm"))
  # ) +
  annotate("text",
           x = as.Date("2019-06-20"),
           y = 755,
           label = "0") +
  annotate("text",
           x = as.Date("2019-10-25"),
           y = 800,
           label = "1") + 
   annotate("text",
           x = as.Date("2020-02-10"),
           y = 850,
           label = "2") + 
  annotate("text",
           x = as.Date("2020-03-15"),
           y = 875,
           label = "3") +
  annotate("text",
           x = as.Date("2020-04-20"),
           y = 900,
           label = "4") +
  annotate("text",
           x = as.Date("2020-06-10"),
           y = 925,
           label = "5")
```






## The New Zealand Attitudes and Values Study

-   Planned 20-year longitudinal study, currently in its 12$^{th}$ year.
-   Sample frame drawn randomly from NZ Electoral Roll.
-   Postal questionnaire (coverage; retention \~ 80%)
-   Focus on personality, social attitudes, values, religion,
    meaning-making, perfectionism, virtues, habits, employment,
    experiences of discrimination, physical and psychological health,
    and environmental attitudes ...
-   Current sample contains `36524` unique people, which is $>$ 1% of
    the NZ adult population.
-   Here, *N* = `r  length(unique(cv$Id))` longitudinal participants who responded
    to **both** 2019/20 NZAVS waves.

## 

```{r eval=FALSE}
# GRAPH
tline + plot_annotation(title = "NZAVS COVID timeline", 
subtitle = "")
```





## First we check for balance and generate IPW for the conditions

There is some unbalence with respect to key indicators


Weight data and check weights
```{r}
cobalt::bal.tab(Covid_Timeline ~ Partner + Age + Male + Relid + Urban + EthnicCats + Edu,
        data = cv, estimand = "ATE", m.threshold = .05)


w_out <- WeightIt::weightit(Covid_Timeline ~ Partner  + Age + Male + Relid  + Urban + Edu  + EthnicCats,
        data = cv, estimand = "ATE", method = "ebal", stabilize = TRUE)

summary(w_out)
```

Inspect weights:

```{r}
cobalt::bal.tab(w_out, m.threshold = .05, disp.v.ratio = TRUE)

#sum(w_out$ipw.weights >= 10)

# create data frame
cv19w <- cv %>% 
  mutate(ipw = w_out$weights)
```


## Estimate model

Model 

```{r}
SCIENCE.TRUST  <- glm(
  SCIENCE.TRUST ~ Covid_Timeline,
  data = cv19w,
  weights = ipw
)
```



```{r, eval=TRUE}
# estimated marginal means
means <-  estimate_means(SCIENCE.TRUST, at = "Covid_Timeline") 

# print
means%>%
  print_html()
```


```{r, evalue = FALSE}
#
contrasts <-  estimate_contrasts(SCIENCE.TRUST, contrast = "Covid_Timeline", adjust = "bonferroni") 
contrasts%>%
  print_html()
```



Graph of the expected (marginal) means:


```{r}
#plot(means, alpha =.005) 
ggplot(cv19w, aes(x = Covid_Timeline, y = SCIENCE.TRUST)) +
  # Add base data
  geom_violin(aes(fill = Covid_Timeline), color = "white") +
  geom_jitter2(width = 0.05, alpha = 0.005) +
  # Add pointrange and line from means 
  geom_line(data = means, aes(y = Mean, group = 1), size = .3) +
  geom_pointrange(
    data = means,
    aes(y = Mean, ymin = CI_low, ymax = CI_high),
    size = .3,
    color = "white"
  ) +
  # Improve colors
  scale_fill_material() +
  theme_modern()
```

```{r, eval = FALSE}
# Hard to read
plot(ggeffects::ggemmeans(SCIENCE.TRUST, terms = "Covid_Timeline"),add.data=TRUE, dot.alpha =.005)
```



Trust in science increased, and then dropped. The key question, will it trust revert to baseline (or worse)?  


Below another graph of the same result.


```{r}
plot(ggeffects::ggemmeans(SCIENCE.TRUST, terms = "Covid_Timeline"))
```