---
title: "How did New Zealand's first Covid lockdown affect Trust in Science (and for how long)?"
description: |
author:
  - name: Joseph Bulbulia
    url: https://josephbulbulia.netlify.app
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: 0000-0002-5861-2056
date: 2022-FEB-09
output:
  distill::distill_article:
    self_contained: false
    toc: true
    code_folding: true
bibliography: bibliography.bib
editor_options: 
  chunk_output_type: console
---


```{r load_libraries, include=FALSE}
# setup
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  layout = "l-body-outset",
  fig.width = 16,
  fig.height = 9,
  collapse = TRUE,
  R.options = list(width = 60
)
  )


library("tidyverse")
library("dplyr")
library("tidyr")
library("easystats")
library("patchwork")
library("kableExtra")
library("ggpubr")
library("here")
library("lubridate")
library("ggdag")
library("viridisLite")
library("geepack")
library("cobalt") # check balence
library("WeightIt")
library("ggeffects")
library("CMAverse")
theme_set(theme_classic())
```



## Regression discontinuity 



Here we estimate the effects of the COVID-19 pandemic on Trust in Science at various stages of the pandemic in New Zealand.  


```{r cache=TRUE, echo = FALSE}
# import data
df <- readRDS(here::here("data", "df"))

# prepare graph
ord_dates_class <- c(
  "Baseline", 
  "JanFeb", 
  "EarlyMarch", 
  "Lockdown",
  "PostLockdown")

ord_prepost_class <- c(
  "pre", 
  "post")



# 3665 days after 30 June 2009 Saturday 13 July 2019
# 3842 days after 30 June 2009 Monday 6 January 2020
# 3895 days after 30 June 2009 Friday 28 February 2020
# 3921 days after 30 June 2009 WED MAR 25th
# 3954 days after 30 June 2009 Monday 27 April 2020
# 3672 days after June 30 2009 Saturday 20 July 2019


# prepare data
cv <- df %>%
  dplyr::filter(Wave == 2018 |
                  Wave == 2019 |
                  Wave == 2020) %>%  # first analysis just used 2019,
  droplevels() %>%
  droplevels() %>%
  dplyr::mutate(org2019 =  ifelse(Wave == 2019 &
                                    YearMeasured == 1, 1, 0)) %>%
  group_by(Id) %>%
  dplyr::mutate(hold = mean(org2019, na.rm = TRUE)) %>%  # Hack
  filter(hold > 0) %>% # hack!
  ungroup() %>%
  dplyr::mutate(org2018 =  ifelse(Wave == 2018 &
                                    YearMeasured == 1, 1, 0)) %>%
  group_by(Id) %>%
  dplyr::mutate(hold = mean(org2018, na.rm = TRUE)) %>%  # Hack
  filter(hold > 0) %>% # hack!
  ungroup(Id) %>%
  dplyr::mutate(
    Covid_Timeline =
      as.factor(
        ifelse(
          TSCORE %in% 3896:3921,
          # feb 29 - march 25th
          "EarlyMarch",
          ifelse(
            TSCORE %in% 3922:3954,
            "Lockdown",
            #march 26- Mon 27 April 2020
            ifelse(TSCORE > 3954,
                   # after april 27th 20202
                   "PostLockdown",
                   ifelse(TSCORE %in% 3842:3895, # jan 6 to feb 28
                          "JanFeb",
                          "Baseline"))))))  %>%
  dplyr::mutate(pre_post = as.factor(ifelse(TSCORE < 3896,  "pre", "post")) )%>%
  dplyr::select(
    Wave,
    TSCORE,
    SCIENCE.TRUST,
    Partner,
    Employed,
    Sat.Government,
    Id,
    Age,
    Male,
    Euro,
    Urban,
    Edu,
    Covid_Timeline,
    pre_post,
    Euro,
    Your.Personal.Relationships,
    Urban,
   # GenCohort,
    SUPPORT,
    BELONG,
    OPENNESS,
    NEUROTICISM,
    AGREEABLENESS,
    EXTRAVERSION,
    CONSCIENTIOUSNESS,
    Hours.Work,
    LIFEMEANING,
    HLTH.SleepHours,
    HLTH.Fatigue,
    Household.INC,
    NZ.Economic.Situation,
    KESSLER6sum,
    Urban,
    Religion.Church,
    HomeOwner,
    Parent,
    POLICE.TRUST,
    Covid_Timeline,
    Pol.PoliticianTrust,
    Your.Future.Security,
    Rel.Conflict,
    Hours.Exercise
  ) %>%
  dplyr::mutate() %>%
  dplyr::mutate(Covid_Timeline = forcats::fct_relevel(Covid_Timeline, ord_dates_class)) %>%
  dplyr::mutate(pre_post = forcats::fct_relevel(pre_post, ord_prepost_class)) %>%
  droplevels() %>%
  dplyr::mutate_at(c('Euro', 'Urban', "Parent", "Partner","Employed", "Male", "HomeOwner", "Edu"), as.numeric)%>%
  dplyr::arrange(Id, Wave)
    
head(cv)
Covid_Timeline_2019
table1::table1( ~ pre_post |Wave, data = cv)

table1::table1( ~ pre_post |Wave, data = cv)
table1::table1( ~ POLICE.TRUST |Wave, data = cv)

str(cv)
cv <- as.data.frame(cv)

# baseline covariates
values <-   c(
    "SCIENCE.TRUST",
    "Partner",
    "Employed",
    "Parent",
    "Sat.Government",
    "Age",
    "Male",
    "Urban",
    "Edu",
    "Covid_Timeline",
    "pre_post",
    "Euro",
    "Your.Personal.Relationships",
    "Urban",
    #"GenCohort",
    "SUPPORT",
    "BELONG", 
    "OPENNESS",
    "NEUROTICISM",
    "AGREEABLENESS",
    "EXTRAVERSION",
    "CONSCIENTIOUSNESS",
    "Hours.Work",
    "LIFEMEANING",
    "HLTH.SleepHours",
    "HLTH.Fatigue",
    "Household.INC",
    "NZ.Economic.Situation",
    "KESSLER6sum",
    "Urban",
    "SUPPORT",
    "BELONG",
    "Religion.Church",
    "HomeOwner",
    "POLICE.TRUST",
    "Covid_Timeline",
    "pre_post",
    "Pol.PoliticianTrust",
    "Your.Future.Security",
    "Rel.Conflict",
    "Hours.Exercise") 

dat <- cv %>%
  pivot_wider(id_cols = c("Id"), 
              names_from = Wave, values_from = values, names_vary = "slowest")%>%
  dplyr::select(-c("SCIENCE.TRUST_2018","Covid_Timeline_2020", "Covid_Timeline_2018","pre_post_2018", "pre_post_2020", "HomeOwner_2019", "HomeOwner_2020") ) %>% 
   dplyr::rename(pre_post = pre_post_2019) %>%
  dplyr::rename(Covid_Timeline = Covid_Timeline_2019) %>%
  dplyr::select(c(matches("_2018"),  "SCIENCE.TRUST_2019", "SCIENCE.TRUST_2020", "Pol.PoliticianTrust_2020", "Sat.Government_2020", "Covid_Timeline", "pre_post", "Id"))
 # dplyr::mutate_if(is.numeric, scale) #%>%
 # mutate(across(everything(), as.vector))


dat <- as.data.frame(dat)

head(dat)
table(dat$Covid_Timeline)

summary(dat)
summary(dat)
#datm <- as.matrix(dat)
# impute missing values 
library(mice)
cov_med_out<- mice::mice( datm, m = 10, seed = 0)


## ANother approach 
cv <- df %>%
  dplyr::filter(Wave == 2018 |
                  Wave == 2019 )%>%  # first analysis just used 2019,
  droplevels() %>%
  dplyr::mutate(org2019 =  ifelse(Wave == 2019 &
                                    YearMeasured == 1, 1, 0)) %>%
  group_by(Id) %>%
  dplyr::mutate(hold = mean(org2019, na.rm = TRUE)) %>%  # Hack
  filter(hold > 0) %>% # hack!
  ungroup() %>%
  dplyr::mutate(org2018 =  ifelse(Wave == 2018 &
                                    YearMeasured == 1, 1, 0)) %>%
  group_by(Id) %>%
  dplyr::mutate(hold = mean(org2018, na.rm = TRUE)) %>%  # Hack
  filter(hold > 0) %>% # hack!
  ungroup(Id) %>%
  dplyr::mutate(
    Covid_Timeline =
      as.factor(
        ifelse(
          TSCORE %in% 3896:3921,
          # feb 29 - march 25th
          "EarlyMarch",
          ifelse(
            TSCORE %in% 3922:3954,
            "Lockdown",
            #march 26- Mon 27 April 2020
            ifelse(TSCORE > 3954,
                   # after april 27th 20202
                   "PostLockdown",
                   ifelse(TSCORE %in% 3842:3895, # jan 6 to feb 28
                          "JanFeb",
                          "Baseline"))))))  %>%
  dplyr::mutate(pre_post = as.factor(ifelse(TSCORE < 3896,  "pre", "post"))) %>%
  dplyr::select(
    Wave,
    TSCORE,
    SCIENCE.TRUST,
    Partner,
    Employed,
    Sat.Government,
    Id,
    Age,
    Male,
    Euro,
    Urban,
    Edu,
    Covid_Timeline,
    pre_post,
    Euro,
    Your.Personal.Relationships,
    Urban,
    # GenCohort,
    SUPPORT,
    BELONG,
    OPENNESS,
    NEUROTICISM,
    AGREEABLENESS,
    EXTRAVERSION,
    CONSCIENTIOUSNESS,
    HONESTY_HUMILITY,
    Hours.Work,
    LIFEMEANING,
    HLTH.SleepHours,
    HLTH.Fatigue,
    Household.INC,
    NZ.Economic.Situation,
    KESSLER6sum,
    Urban,
    Religion.Church,
    HomeOwner,
    Parent,
    POLICE.TRUST,
    Covid_Timeline,
    Pol.PoliticianTrust,
    Your.Future.Security,
    Rel.Conflict,
    Hours.Exercise,
    Id,
    Wave,
    KESSLER6sum,
    LIFEMEANING,
    LIFESAT,
    SELF.ESTEEM,
    Respect.Self,
    ChildrenNum,
    PWI,
    NWI,
    SFHEALTH,
    SELF.CONTROL,
    Religion.Church,
    Household.INC,
    Id,
    YearMeasured,
    Wave,
    Pol.Orient,
    NZdep,
    Male,
    Employed,
    Urban,
    EthnicCats,
    SFHEALTH,
    NWI,
    Partner,
    lost_job,
    began_relationship,
    Hours.Work,
    # Believe.Spirit,
    #  Believe.God,
    HomeOwner,
    Religious,
    Rumination,
    Wave
  ) %>% 
  dplyr::mutate(Edu = as.numeric(Edu)) %>%
  dplyr::mutate(Covid_Timeline = forcats::fct_relevel(Covid_Timeline, ord_dates_class)) %>%
  dplyr::mutate(pre_post = forcats::fct_relevel(pre_post, ord_prepost_class)) %>%
  droplevels() %>%
  group_by(Id) %>%
  dplyr::mutate(SFHEALTH_bz = if_else(Wave == "2018", as.numeric(scale(SFHEALTH, scale = FALSE)), NA_real_)) %>%
  fill(SFHEALTH_bz) %>%
   dplyr::mutate(SUPPORT_bz = if_else(Wave == "2018", as.numeric(scale(SUPPORT, scale = FALSE)), NA_real_)) %>%
  fill(SUPPORT_bz) %>%
  dplyr::mutate(BELONG_bz = if_else(Wave == "2018", as.numeric(scale(BELONG, scale = FALSE)), NA_real_)) %>%
  fill(BELONG_bz) %>%
  dplyr::mutate(LIFESAT_bz = if_else(Wave == "2018", as.numeric(scale(LIFESAT, scale = FALSE)), NA_real_)) %>%
  fill(LIFESAT_bz) %>%
  dplyr::mutate(PWI_bz = if_else(Wave == "2018", as.numeric(scale(PWI, scale = FALSE)), NA_real_)) %>%
  fill(PWI_bz) %>%
  dplyr::mutate(SELF.ESTEEM_bz = if_else(Wave == "2018", as.numeric(scale(SELF.ESTEEM, scale = FALSE)), NA_real_)) %>%
  fill(SELF.ESTEEM_bz) %>%
  dplyr::mutate(Respect.Self_bz = if_else(Wave == "2018", as.numeric(scale(
    Respect.Self, scale = FALSE)), NA_real_)) %>%
  fill(Respect.Self_bz) %>%
  dplyr::mutate(Rumination_bz = if_else(Wave == "2018", as.numeric(scale(Rumination, scale = FALSE)), NA_real_)) %>%
  fill(Rumination_bz) %>%
  dplyr::mutate(ChildrenNum_bz = if_else(Wave == "2018", as.numeric(ChildrenNum), NA_real_)) %>%
  fill(ChildrenNum_bz) %>%
  dplyr::mutate(SELF.CONTROL_bz = if_else(Wave == "2018", as.numeric(scale(
    SELF.CONTROL, scale = FALSE
  )), NA_real_)) %>%
  fill(SELF.CONTROL_bz) %>%
  dplyr::mutate(k6_bz = if_else(Wave == "2018", as.numeric(KESSLER6sum), NA_real_)) %>%
  fill(k6_bz) %>%
  dplyr::mutate(HomeOwner_bz = if_else(Wave == "2018", as.numeric(HomeOwner), NA_real_)) %>%
  fill(HomeOwner_bz) %>%
  dplyr::mutate(LIFEMEANING_bz = if_else(Wave == "2018", as.numeric(scale(LIFEMEANING, scale = FALSE)), NA_real_)) %>%
  fill(LIFEMEANING_bz) %>%
  dplyr::mutate(Household.INC_bz = if_else(Wave == "2018", as.numeric(Household.INC), NA_real_)) %>%
  fill(Household.INC_bz) %>%
  dplyr::mutate(income19_bz = if_else(Wave == "2018", as.numeric(lead(Household.INC, n =
                                                                        1)), NA_real_)) %>%
  fill(income19_bz) %>%
  dplyr::mutate(agr_bz = if_else(Wave == "2018", as.numeric(scale(
    AGREEABLENESS, scale = FALSE
  )), NA_real_)) %>%
  fill(agr_bz) %>%
  dplyr::mutate(cs_bz = if_else(Wave == "2018", as.numeric(scale(
    CONSCIENTIOUSNESS, scale = FALSE
  )), NA_real_)) %>%
  fill(cs_bz) %>%
  dplyr::mutate(op_bz = if_else(Wave == "2018", as.numeric(scale(OPENNESS, scale = FALSE)), NA_real_)) %>%
  fill(op_bz) %>%
  dplyr::mutate(h_bz = if_else(Wave == "2018", as.numeric(scale(
    HONESTY_HUMILITY, scale = FALSE
  )), NA_real_)) %>%
  fill(h_bz) %>%
  dplyr::mutate(ex_bz = if_else(Wave == "2018", as.numeric(scale(
    EXTRAVERSION, scale = FALSE
  )), NA_real_)) %>%
  fill(ex_bz) %>%
  dplyr::mutate(nr_bz = if_else(Wave == "2018", as.numeric(scale(NEUROTICISM, scale = FALSE)), NA_real_)) %>%
  fill(nr_bz) %>%
  dplyr::mutate(Religion.Church_bz = if_else(Wave == "2018", as.numeric(Religion.Church), NA_real_)) %>%
  fill(Religion.Church_bz) %>%
  dplyr::mutate(pol_bz = if_else(Wave == "2018", as.numeric(scale(Pol.Orient, scale = FALSE)), NA_real_)) %>%
  fill(pol_bz) %>%
  dplyr::mutate(partner18_bz = if_else(Wave == "2018", as.numeric(Partner, scale = FALSE), NA_real_)) %>%
  fill(partner18_bz) %>%
  dplyr::mutate(parent_bz = if_else(Wave == "2018", as.numeric(Parent), NA_real_)) %>%
  fill(parent_bz) %>%
  dplyr::mutate(nzdep_bz = if_else(Wave == "2018", as.numeric(scale(NZdep, scale = FALSE)), NA_real_)) %>%
  fill(nzdep_bz) %>%
  dplyr::mutate(male_2z = if_else(Wave == "2018", as.numeric(Male), NA_real_)) %>%
  fill(male_2z)  %>%
  dplyr::mutate(employed_bz = if_else(Wave == "2018", as.numeric(Employed), NA_real_)) %>%
  fill(employed_bz) %>%
  dplyr::mutate(age_bz = if_else(Wave == "2018", as.numeric(scale(Age, scale = FALSE)), NA_real_)) %>%
  fill(age_bz) %>%
  dplyr::mutate(edu_bz = if_else(Wave == "2018", as.numeric(scale(Edu, scale = FALSE)), NA_real_)) %>%
  fill(edu_bz) %>%
  dplyr::mutate(ubran_bz = if_else(Wave == "2018", as.numeric(Urban), NA_real_)) %>%
  fill(ubran_bz) %>%
  dplyr::mutate(Euro = if_else(Wave == "2018", as.numeric(Euro), NA_real_)) %>%
  fill(Euro) %>%
  dplyr::mutate(SFHEALTH_bz = if_else(Wave == "2018", as.numeric(scale(SFHEALTH, scale = FALSE)), NA_real_)) %>%
  fill(SFHEALTH_bz) %>%
  dplyr::mutate(NWI_bz = if_else(Wave == "2018", as.numeric(scale(NWI, scale = FALSE)), NA_real_)) %>%
  fill(NWI_bz) %>%
  dplyr::mutate(partner19_bz = if_else(Wave == "2019", as.numeric(Partner), NA_real_)) %>%
  fill(partner19_bz) %>%
  # dplyr::mutate(partnerlost_job_bz = if_else(Wave == "2018", as.numeric(partnerlost_job), NA_real_)) %>%
  # fill(partnerlost_job_bz) %>%
  # dplyr::mutate(lost_job_bz = if_else(Wave == "2018", as.numeric(lost_job), NA_real_)) %>%
  # fill(lost_job_bz) %>%
  # dplyr::mutate(began_relationship_bz = if_else(Wave == "2018", as.numeric(began_relationship), NA_real_)) %>%
  # fill(began_relationship_bz) %>%
  dplyr::mutate(Hours.Work_bz = if_else(Wave == "2018", as.numeric(Hours.Work), NA_real_)) %>%
  dplyr::mutate(POLICE.TRUST_bz = if_else(Wave == "2018", as.numeric( POLICE.TRUST), NA_real_)) %>%
  fill(POLICE.TRUST_bz) %>%
  dplyr::mutate(Pol.PoliticianTrust_bz = if_else(Wave == "2018", as.numeric(Pol.PoliticianTrust), NA_real_)) %>%
  fill(Pol.PoliticianTrust_bz) %>%
  dplyr::mutate(Your.Future.Security_bz = if_else(Wave == "2018", as.numeric(Your.Future.Security), NA_real_)) %>%
  fill(Your.Future.Security_bz) %>%
  dplyr::mutate(Rel.Conflict_bz = if_else(Wave == "2018", as.numeric(Rel.Conflict), NA_real_)) %>%
  fill(Rel.Conflict_bz) %>%
  dplyr::mutate(HLTH.SleepHours_bz = if_else(Wave == "2018", as.numeric(HLTH.SleepHours), NA_real_)) %>%
  fill(HLTH.SleepHours_bz) %>%
  dplyr::mutate(HLTH.Fatigue_bz = if_else(Wave == "2018", as.numeric( HLTH.Fatigue), NA_real_)) %>%
  fill( HLTH.Fatigue_bz) %>%
  dplyr::mutate(NZ.Economic.Situation_bz= if_else(Wave == "2018", as.numeric(NZ.Economic.Situation), NA_real_)) %>%
  fill(NZ.Economic.Situation_bz) %>%
  dplyr::mutate(Sat.Government_bz= if_else(Wave == "2018", as.numeric(Sat.Government), NA_real_)) %>%
  fill(Sat.Government_bz) %>%
  dplyr::mutate(Your.Personal.Relationships_bz = if_else(Wave == "2018", as.numeric(Your.Personal.Relationships), NA_real_)) %>%
  fill(Your.Personal.Relationships_bz) %>%
  ungroup() %>%
  dplyr::mutate(yearW = as.numeric(Wave) - 1) %>%
  arrange(Id, yearW)

str(cv1$male_2z)

table1::table1(~ ubran_bz  , data = cv)

saveRDS(cv, here::here("_posts", "covscience", "mods", "cv.rds"))
cv$Euro
cv1 <- cv %>%
  dplyr::arrange(Id, Wave) %>%
  dplyr::mutate(pre_post = as.numeric(pre_post)-1) %>%
  dplyr::mutate(covid_timeline_lead1 = lead(Covid_Timeline, n = 1))%>%
  dplyr::mutate(pre_post_lead1 = lead(pre_post, n = 1))%>%
  dplyr::mutate(SCIENCE.TRUST_lead1  = as.numeric(lead(SCIENCE.TRUST, n = 1) ))%>%
  dplyr::mutate(SCIENCE.TRUST_lead2  = as.numeric(lead(SCIENCE.TRUST, n = 2 )))%>%
  dplyr::mutate(Pol.PoliticianTrust_lead1 =  as.numeric(lead(Pol.PoliticianTrust, n = 1) ))%>%
  dplyr::mutate(Pol.PoliticianTrust_lead2  =  as.numeric(lead(Pol.PoliticianTrust, n = 2) ))%>%
 dplyr::mutate(Sat.Government_lead1  = as.numeric(lead(Sat.Government, n = 1) ))%>%
#  dplyr::mutate(Sat.Government_lead2  = as.numeric(lead(Sat.Government, n = 2 )))%>%
  dplyr::mutate(income_base_log = as.numeric(log(Household.INC+1) ))%>%
 # dplyr::mutate(income_log_lead1 = as.numeric(log(lead(Household.INC, n = 1)+1) ))%>%
 # dplyr::mutate(income_log_lead2 = as.numeric(log(lead(Household.INC, n = 2)+1))) %>%  # delete to avoid leverage of extreme outliers
  dplyr::mutate(income_log_bz = as.numeric(scale(income_base_log, scale = FALSE))) %>%  # delete to avoid leverage of extreme outliers
# dplyr::mutate(income_logc_lead1 = as.numeric(scale(income_log_lead1, scale = FALSE))) %>%  # delete to avoid leverage of extreme outliers
#  dplyr::mutate(BELONG_lead2 = lead(BELONG, n = 2)) %>%
#  dplyr::mutate(SUPPORT_lead2 = lead(SUPPORT, n = 2)) %>%
 dplyr::mutate(k6_lead1 = as.integer(lead(KESSLER6sum, n = 1))) %>%
#  dplyr::mutate(LIFEMEANING_lead2 = as.numeric((lead(LIFEMEANING, n = 2)))) %>%
#  dplyr::mutate(LIFESAT_lead2 = as.numeric((lead(LIFESAT, n = 2)))) %>%
 # dplyr::mutate(SELF.ESTEEM_lead2 = as.numeric(lead(SELF.ESTEEM, n = 2))) %>%
 # dplyr::mutate(Respect.Self_lead2 = as.numeric((lead(Respect.Self, n = 2)))) %>%
#  dplyr::mutate(Rumination_lead2 = as.numeric(lead(Rumination, n = 2))) %>%
#  dplyr::mutate(ChildrenNum_lead2 = as.integer(lead(ChildrenNum, n = 2))) %>%
#  dplyr::mutate(PWI_lead2 = as.numeric((lead(PWI, n = 2)))) %>%
#  dplyr::mutate(NWI_lead2 = as.numeric((lead(NWI, n = 2)))) %>%
#  dplyr::mutate(SFHEALTH_lead2 = as.numeric((lead(SFHEALTH, n = 2)))) %>%
#  dplyr::mutate(SELF.CONTROL_lead2 = as.numeric((lead(SELF.CONTROL, n = 2)))) %>%
#  dplyr::mutate(Religion.Church_lead1 = as.numeric(lead(Religion.Church, n = 1))) %>%
#  dplyr::mutate(POLICE.TRUST_lead2 = as.numeric((lead(POLICE.TRUST, n = 2)))) %>%
#  dplyr::mutate(Pol.PoliticianTrust_lead2 = as.numeric((lead(Pol.PoliticianTrust_bz, n = 2))))%>%
#  dplyr::mutate(Your.Future.Security_lead2 = as.numeric((lead(Your.Future.Security_bz, n = 2)))) %>%
  filter(Wave == 2018) %>% 
#  dplyr::mutate(Rel.Conflict_lead2 = as.numeric((lead(Rel.Conflict_bz, n = 2))))%>%
#  dplyr::mutate(NZ.Economic.Situation_lead2 = as.numeric((lead(NZ.Economic.Situation_bz, n = 2)))) %>%
 # dplyr::mutate(Your.Personal.Relationships_lead1 = as.numeric(lead(Your.Personal.Relationships_bz, n = 1)))%>%
  droplevels() %>% # delete to avoid leverage of extreme outliers
  dplyr::mutate(Religion.Church_bz = as.numeric(ifelse(Religion.Church_bz > 5, 5, Religion.Church_bz)))%>%
  dplyr::mutate(Religion.Church_bz = as.numeric(scale( Religion.Church_bz)),
    # LIFEMEANING_lead2z = as.numeric(scale(LIFEMEANING_lead2)),
    # LIFESAT_lead2z = as.numeric(scale(LIFESAT_lead2)),
    # SELF.ESTEEM_lead2z = as.numeric(scale(SELF.ESTEEM_lead2)),
    # Respect.Self_lead2z = as.numeric(scale(Respect.Self_lead2)),
    # Rumination_lead2z = as.numeric(scale(Rumination_lead2)),
    # ChildrenNum_lead2z = as.numeric(scale(ChildrenNum_lead2)),
    # PWI_lead2z = as.numeric(scale(PWI_lead2)),
    # NWI_lead2z = as.numeric(scale(NWI_lead2)),
    # SFHEALTH_lead2z = as.numeric(scale(SFHEALTH_lead2)),
    # SELF.CONTROL_lead2z = as.numeric(scale(SELF.CONTROL_lead2)),
    # Rumination_lead2z = as.numeric(scale(Rumination_lead2)),
    h_bc = as.numeric(scale(h_bz, scale = FALSE)),
    op_bc = as.numeric(scale(op_bz, scale = FALSE)), 
    age_bz = as.numeric(scale(age_bz, scale = FALSE)),
    cs_bc = as.numeric(scale(cs_bz, scale = FALSE)),
    male_bz = as.numeric(scale(male_2z) / 2),
    partner18_bz = as.numeric(scale(as.numeric(partner18_bz))),
    partner19_bz = as.numeric(scale(as.numeric(partner19_bz))),
    Hours.Work_log_bz = as.numeric(scale(log(Hours.Work_bz + 1))),
    # began_relationship_bz = as.numeric(scale(began_relationship_bz)),
    # lost_job_bz = as.numeric(scale(lost_job_bz)),
    # partnerlost_job_bz = as.numeric(scale(partnerlost_job_bz)),
    k6_c_lead1 = as.numeric(scale(k6_lead1, scale = T)),
    # bg1_z = as.numeric(scale(bg1)),
    # bs1_z = as.numeric(scale(bs1)),
    Euro_bz = as.numeric(scale(Euro)),
    urban_bz = as.numeric(scale(ubran_bz)),
    nzdep_bz  = as.numeric(scale(nzdep_bz)),
    parent_bz  = as.numeric(scale(parent_bz)),
    pol_bz  = as.numeric(scale(pol_bz)),
    nr_bz = as.numeric(scale(nr_bz)),
    ex_bz = as.numeric(scale(ex_bz)),
    h_bz = as.numeric(scale(h_bz)),
    op_bz = as.numeric(scale(op_bz)),
    cs_bz = as.numeric(scale(cs_bz)),
    agr_bz = as.numeric(scale(agr_bz)),
    Sat.Government_bz = as.numeric(scale(Sat.Government)),
    SELF.CONTROL_bz = as.numeric(scale(SELF.CONTROL_bz)),
    LIFEMEANING_bz = as.numeric(scale(LIFEMEANING_bz)),
    k6_bz = as.numeric(scale(log(k6_bz + 1))),
    LIFESAT_bz = as.numeric(scale(LIFESAT_bz)),
    SELF.ESTEEM_bz = as.numeric(scale(SELF.ESTEEM_bz)),
    Respect.Self_bz = as.numeric(scale(Respect.Self_bz)),
    Rumination_bz = as.numeric(scale(Rumination_bz)),
    ChildrenNum_bz = as.numeric(scale(ChildrenNum_bz)),
    PWI_bz = as.numeric(scale(PWI_bz)),
    NWI_bz = as.numeric(scale(NWI_bz)),
    SFHEALTH_bz = as.numeric(scale(SFHEALTH_bz)),
   # lost_job_bz = as.numeric(scale(lost_job_bz)),
    HomeOwner_bz = as.numeric(scale(HomeOwner_bz)),
    POLICE.TRUST_bz = as.numeric(scale(POLICE.TRUST_bz)),
    Pol.PoliticianTrust_bz = as.numeric(scale(Pol.PoliticianTrust_bz)),
    Rel.Conflict_bz = as.numeric(scale( Rel.Conflict_bz)),
    NZ.Economic.Situation_bz = as.numeric(scale(NZ.Economic.Situation_bz)),
    HLTH.SleepHours_bz = as.numeric(scale( HLTH.SleepHours_bz)),
    HLTH.Fatigue_bz = as.numeric(scale(HLTH.Fatigue_bz)),
   Your.Personal.Relationships_bz = as.numeric(scale(Your.Personal.Relationships_bz)),
   Sat.Government_bz = as.numeric(scale(Sat.Government_bz))) %>%
  dplyr::select(-ubran_bz) %>% 
  dplyr::select(c(matches("_bz"), matches("_lead1"), "Id")) %>%
  as.data.frame()

str(cv1$pre_post_lead1)
dim(cv1) # too many 
table(cv$Wave)
table(cv1$Euro_bz)

cv2 <-cv1 %>%
  dplyr::select(
    c(
     # Id,
      pre_post_lead1,
      covid_timeline_lead1,
      nzdep_bz,
      urban_bz,
      male_bz,
      k6_bz,
      Religion.Church_bz,
      age_bz,
      income_log_bz,
      Euro_bz,
      nzdep_bz,
      parent_bz,
      partner18_bz,
      pol_bz,
      Sat.Government_bz,
      Your.Personal.Relationships_bz,
      Rel.Conflict_bz,
      Religion.Church_bz,
      HomeOwner_bz,
      SFHEALTH_bz,
      NWI_bz,
      PWI_bz,
      ChildrenNum_bz,
      Rumination_bz,
      LIFESAT_bz,
      LIFEMEANING_bz,
      nr_bz,
      ex_bz,
      h_bz,
      op_bz,
      cs_bz,
      agr_bz,
      NZ.Economic.Situation_bz,
      POLICE.TRUST_bz,
      Pol.PoliticianTrust_bz,
      k6_bz,
      k6_lead1,
      Sat.Government_lead1,
      Pol.PoliticianTrust_lead1,
      SCIENCE.TRUST_lead1  ))


# Impute missing values and save 
mice_cov <- mice::mice(cv2, seed = 0 )
saveRDS(mice_cov, here::here("_posts", "covscience", "mods", "mice_cov.rds"))

dfc <- mice::complete(mice_cov)

dfc$pre_post_lead1

#long <- mice::complete(mice_cov, "long", inc = TRUE)
dfc$SCIENCE.TRUST_lead1z<-  scale(dfc$SCIENCE.TRUST_lead1, scale = TRUE)
dfc$Pol.PoliticianTrust_lead1z <-scale(dfc$Pol.PoliticianTrust_lead1, scale = TRUE)
dfc$Sat.Government_lead1z <- scale(dfc$Sat.Government_lead1, scale = TRUE)
dfc$k6_lead1z <- scale(dfc$k6_lead1, scale = TRUE)


# # long$Rumination_lead2ord <- with(long, Rumination_lead2ord + 1)
# # long$SUPPORT_lead2ord <- with(long, round(SUPPORT_lead2, digits = 0))
# # long$LIFEMEANING_lead2ord <- with(long, round(LIFEMEANING_lead2, digits = 0))
# 
# long2<- long %>% mutate_if(is.matrix,as.vector)
# long3 <- mice::as.mids(long2)

cvar <-
 c("nzdep_bz",
    "urban_bz",
    "Religion.Church_bz",
    "age_bz",
    "income_log_bz",
    "Euro_bz",
    "urban_bz",
    "nzdep_bz",
     "male_bz",
     "k6_bz",
    "parent_bz",
    "partner18_bz",
    "pol_bz",
    "Sat.Government_bz",
    "Your.Personal.Relationships_bz",
    "Rel.Conflict_bz",
    "Religion.Church_bz",
    "HomeOwner_bz",
    "SFHEALTH_bz",
    "NWI_bz",
    "PWI_bz",
    "ChildrenNum_bz",
    "Rumination_bz",
    "LIFESAT_bz",
    "LIFEMEANING_bz",
    "nr_bz",
    "ex_bz",
    "h_bz",
    "op_bz",
    "cs_bz",
    "agr_bz",
    "NZ.Economic.Situation_bz",
    "POLICE.TRUST_bz",
    "Pol.PoliticianTrust_bz",
    "k6_bz"
  )

c_means <- colMeans(dfc[cvar])
c_means


# vars
# Sat.Government_lead1,
# Pol.PoliticianTrust_lead1,
# SCIENCE.TRUST_lead1,
# Sat.Government_lead2,
# Pol.PoliticianTrust_lead2,
# SCIENCE.TRUST_lead2,

dfc <- dfc %>%
  mutate_if(is.matrix,as.vector)


m1 <- cmest(data = dfc,
            model = "ne",
            outcome = "SCIENCE.TRUST_lead1z",
            exposure = "pre_post_lead1",
            mediator = "Sat.Government_lead1z",
            basec = cvar,
            EMint = TRUE,
            mreg = list("linear"),
            yreg = "linear",
            astar = 0,
            mval = list(c(-2, 2)),
            basecval = NULL,
            a = 1,
            estimation = "imputation",
            inference = "boot",
            multimp = TRUE,
            nboot = 10)
warnings()

library(ggplot2)
summary(m1, exponentiate = F)
cmsens(object = m1, sens = "uc")
gh <- ggcmest(m1) 
str(gh)
gh$layers
  theme_few() + coord_flip(xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") + 
  theme(axis.text.x = element_text(angle = 45)) + labs(title = "Causal mediation for the natural direct effect\nof Covid on Trust in Science", subtitle = "method = natural effect model, pre/post Covid: 2019-2020, New Zeland (NZAVS), N = 34,783")


m2 <- cmest(data = dfc,
            model = "ne",
            outcome = "Sat.Government_lead1z",
            exposure = "pre_post_lead1",
            mediator = "SCIENCE.TRUST_lead1z",
            basec =  cvar,
            EMint = TRUE,
            mreg = list("linear"),
            yreg = "linear",
            astar = 0,
            basecval = NULL,
            a = 1,
            mval = list(c(-2, 2)),
            estimation = "imputation",
            inference = "boot",
            multimp = TRUE,
            nboot = 10)
warnings()

library(ggplot2)
summary(m2, exponentiate = TRUE)
cmsens(object = m2, sens = "uc")
ggcmest(m2) +theme_few() + coord_flip(xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") + 
  theme(axis.text.x = element_text(angle = 45)) + 
  labs(title = "Causal mediation for the natural direct effect\nof Covid on Satisfaction with Government", subtitle = "method = natural effect model, pre/post Covid: 2019-2020, New Zeland (NZAVS), N = 34,783")


m1a <- cmest(data = dfc,
            model = "gformula",
            outcome = "SCIENCE.TRUST_lead1z",
            exposure = "pre_post_lead1",
            mediator = "Sat.Government_lead1z",
            basec = cvar,
            EMint = TRUE,
            mreg = list("linear"),
            yreg = "linear",
            postc = "Pol.PoliticianTrust_lead1z",
            astar = 0,
            mval = list(c(0, 1)),
            postcreg = list("linear"),
            ereg = "linear",
            basecval = NULL,
            a = 1,
            estimation = "imputation",
            inference = "boot",
            multimp = TRUE,
            nboot = 10)
warnings()

library(ggplot2)
summary(m1a, exponentiate = F)
cmsens(object = m1a, sens = "uc")
dev.off()

ggcmest(m1a) +theme_few() + coord_flip(xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") + 
  theme(axis.text.x = element_text(angle = 45)) +  labs(title = "Causal mediation for the controlled direct effect\nof COVID19 on Government Satisfaction: ", subtitle = "method = Gformula, pre/post Covid: 2019-2020, New Zeland (NZAVS), N = 34,783")


m2a <- cmest(data = dfc,
            model = "gformula",
            outcome = "Sat.Government_lead1z",
            exposure = "pre_post_lead1",
            mediator = "SCIENCE.TRUST_lead1z",
            basec = cvar,
            EMint = TRUE,
            mreg = list("linear"),
            yreg = "linear",
            postc = "Pol.PoliticianTrust_lead1z",
            astar = 0,
            mval = list(c(0, 1)),
            postcreg = list("linear"),
            ereg = "linear",
            basecval = NULL,
            a = 1,
            estimation = "imputation",
            inference = "boot",
            multimp = TRUE,
            nboot = 10)
warnings()

library(ggplot2)
summary(m2a)
cmsens(object = m2a, sens = "uc")
ggcmest(m2a) +theme_few() + theme(axis.text.x = element_text(angle = 45)) + labs(title = "Causal mediation for the controlled direct effect\nof Covid on Satisfaction with Government", subtitle = "method = Gformula,New Zeland (NZAVS), N = 34,783")




ggcmest(m1a) +theme_few() + coord_flip(xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") + 
  theme(axis.text.x = element_text(angle = 45)) +  labs(title = "Causal mediation for the controlled direct effect\nof COVID19 on Government Satisfaction: ", subtitle = "method = Gformula, pre/post Covid: 2019-2020, New Zeland (NZAVS), N = 34,783")


## Nar=te eeffect 
m3a <- cmest(data = dfc,
            model = "gformula",
            outcome = "Pol.PoliticianTrust_lead1z",
            exposure = "pre_post_lead1",
            mediator = "SCIENCE.TRUST_lead1z",
            basec = cvar,
            EMint = TRUE,
            mreg = list("linear"),
            yreg = "linear",
            postc = "Sat.Government_lead1z",
            astar = 0,
            mval = list(c(0, 1)),
            postcreg = list("linear"),
            ereg = "linear",
            basecval = NULL,
            a = 1,
            estimation = "imputation",
            inference = "boot",
            multimp = TRUE,
            nboot = 10)
warnings()

ggcmest(m1a) +theme_few() + coord_flip(xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") + 
  theme(axis.text.x = element_text(angle = 45)) +  labs(title = "Causal mediation for the controlled direct effect\nof COVID19 on Government Satisfaction: ", subtitle = "method = Gformula, pre/post Covid: 2019-2020, New Zeland (NZAVS), N = 34,783")


summary(m3a)
cmsens(object = m3a, sens = "uc")
ggcmest(m3a) +theme_few() + theme(axis.text.x = element_text(angle = 45)) + labs(title = "Causal mediation for the controlled direct effect\nof Covid on Trust in Politicians", subtitle = "method = Gformula,New Zeland (NZAVS), N = 34,783")





## Nar=te eeffect 
m4a <- cmest(data = dfc,
            model = "gformula",
            outcome = "SCIENCE.TRUST_lead1z",
            exposure = "pre_post_lead1",
            mediator = "Pol.PoliticianTrust_lead1z",
            basec = cvar,
            EMint = TRUE,
            mreg = list("linear"),
            yreg = "linear",
            postc = "Sat.Government_lead1z",
            astar = 0,
            mval = list(c(0, 1)),
            postcreg = list("linear"),
            ereg = "linear",
            basecval = NULL,
            a = 1,
            estimation = "imputation",
            inference = "boot",
            multimp = TRUE,
            nboot = 10)
warnings()

ggcmest(m4a) +theme_few() + coord_flip(xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") + 
  theme(axis.text.x = element_text(angle = 45)) +  labs(title = "Causal mediation for the controlled direct effect of COVID19 on\nTrust in Science (mediator Trust Politicians/L= Sat Gov.) ", subtitle = "method = Gformula, pre/post Covid: 2019-2020, New Zeland (NZAVS), N = 34,783")


summary(m3a)
cmsens(object = m3a, sens = "uc")
ggcmest(m3a) +theme_few() + theme(axis.text.x = element_text(angle = 45)) + labs(title = "Causal mediation for the controlled direct effect\nof Covid on Trust in Politicians", subtitle = "method = Gformula,New Zeland (NZAVS), N = 34,783")




# method by entropy balancing "which guarantees perfect balance on specified moments of the covariates while minimizing the entropy (a measure of dispersion) of the weights."
w_out <- WeightIt::weightit(pre_post_lead1    ~ urban_bz + age_bz+  male_bz + 
    Euro_bz+
    urban_bz+
    nzdep_bz+
    parent_bz+
    partner18_bz+
    pol_bz+
    Sat.Government_bz,
        data = dfc, estimand = "ATE", method = "ebal")

summary(w_out)


cobalt::bal.tab(w_out, m.threshold = .05, disp.v.ratio = TRUE)

#sum(w_out$ipw.weights >= 10)

# create data frame
cv19w <- cv %>% 
  mutate(ipw = w_out$weights)
```


### Estimate model

Model 

```{r}
SCIENCE.TRUST  <- glm(
  SCIENCE.TRUST ~ Covid_Timeline,
  data = cv19w,
  weights = ipw
)



```



```

# Causal Mediation 






## The New Zealand Attitudes and Values Study

-   Planned 20-year longitudinal study, currently in its 12$^{th}$ year.
-   Sample frame drawn randomly from NZ Electoral Roll.
-   Postal questionnaire (coverage; retention \~ 80%)
-   Focus on personality, social attitudes, values, religion,
    meaning-making, perfectionism, virtues, habits, employment,
    experiences of discrimination, physical and psychological health,
    and environmental attitudes ...
-   Current sample contains `36524` unique people, which is $>$ 1% of
    the NZ adult population.
-   Here, *N* = `r  length(unique(cv$Id))` longitudinal participants who responded
    to **both** 2019/20 NZAVS waves.



# Table of participants per condition

```{r}
cv%>%
  group_by(Covid_Timeline) %>%
  count() %>%
 kbl(caption = "NZAVS Respondents to Wave 11 of the NZAVS 2019-2020") %>%
  kable_material(c("hover"))
```



## Method

### Inverse Probability Weighting

To ensure balance across the condition in baseline covariates we use Inverse Probability Weighting. 

```{r}

#IPW data and check weights

cobalt::bal.tab(Covid_Timeline ~  GenCohort + Edu + EthnicCats + Male  + Urban,
        data = cv, estimand = "ATE", m.threshold = .05)


# method by entropy balancing "which guarantees perfect balance on specified moments of the covariates while minimizing the entropy (a measure of dispersion) of the weights."
w_out <- WeightIt::weightit(Covid_Timeline ~ Age + Edu + EthnicCats + Male + Urban,
        data = cv, estimand = "ATE", method = "ebal")

summary(w_out)



```

Inspect weights:

```{r}
cobalt::bal.tab(w_out, m.threshold = .05, disp.v.ratio = TRUE)

#sum(w_out$ipw.weights >= 10)

# create data frame
cv19w <- cv %>% 
  mutate(ipw = w_out$weights)
```


### Estimate model

Model 

```{r}
SCIENCE.TRUST  <- glm(
  SCIENCE.TRUST ~ Covid_Timeline,
  data = cv19w,
  weights = ipw
)



```


### Marginal means

```{r, eval=TRUE}
# estimated marginal means
means <-  estimate_means(SCIENCE.TRUST, at = "Covid_Timeline") 

# print
means%>%
  print_md()
```


```{r, evalue = FALSE}
#
contrasts <-  estimate_contrasts(SCIENCE.TRUST, contrast = "Covid_Timeline", adjust = "bonferroni") 
contrasts%>%
  print_md()
```



Graph of the expected (marginal) means:


```{r}
#plot(means, alpha =.005) 
ggplot(cv19w, aes(x = Covid_Timeline, y = SCIENCE.TRUST)) +
  # Add base data
  geom_violin(aes(fill = Covid_Timeline), color = "white") +
  geom_jitter2(width = 0.05, alpha = 0.005) +
  # Add pointrange and line from means 
  geom_line(data = means, aes(y = Mean, group = 1), size = .3) +
  geom_pointrange(
    data = means,
    aes(y = Mean, ymin = CI_low, ymax = CI_high),
    size = .3,
    color = "white"
  ) +
  # Improve colors
  scale_fill_material() +
  theme_modern() + 
  scale_color_discrete()

```

```{r, eval = FALSE}
# Hard to read
plot(ggeffects::ggemmeans(SCIENCE.TRUST, terms = "Covid_Timeline"),add.data=TRUE, dot.alpha =.005)
```



Trust in science increased, and then dropped. The key question, will it trust revert to baseline (or worse)?  


Below another graph of the same result.


```{r}
plot(ggeffects::ggemmeans(SCIENCE.TRUST, terms = "Covid_Timeline"))
```

## Causal mediation model


```{r}
library(mediation)
#length(unique(cv19n$Id))

# + Age + Edu + EthnicCats + Male + Relid + Partner + Urban

med.fit <- lm( Sat.Government_S  ~ Covid_Timeline + Age + Edu + EthnicCats + Male  + Urban,  data = cv19w)
out.fit <- lm( SCIENCE.TRUST_S   ~ Sat.Government_S  + Covid_Timeline +  Age + Edu + EthnicCats + Male + Urban, 
               data = cv19w)
med.out <- mediate(med.fit, out.fit, treat = "Covid_Timeline", mediator = "Sat.Government_S",
                   robustSE = TRUE, sims = 1000, control.value = "Baseline", treat.value = "Lockdown")

# save model
saveRDS(med.out, here::here("_posts", "covscience","mods", "med.out.rds"))

```

We observe that government satisfaction strongly mediates the effect of Lockdown on trust in science. 

```{r eval=TRUE}
med.out <- readRDS(here::here("_posts", "covscience","mods", "med.out.rds"))
summary(med.out)
```


```{r eval=TRUE}
plot(med.out,  
     effect.type = c("indirect", "direct", "total"), 
     xlim = c(0,.4))
```


 We next contrast the Locdown with the period following lockdown in which there was declining trust in science. 


### Sensitivity Analysis


```{r eval=FALSE}
sens.out <- medsens(med.out, rho.by = 0.2,  effect.type = "indirect", sims = 100)
# save sensitivity analysis
saveRDS(sens.out, here::here("_posts", "covscience","mods", "sens.out.rds"))
```

Sensitivity plot reveals that for sequential ignorability to be violated, the correlation between the the error terms of the mediator and outcome (rho) would need to be .25. We infer that the findings are reasonably robust in respect of unmeasured mediator outcome confounding. 

```{r eval=FALSE}
sens.out <- readRDS(sens.out, here::here("_posts", "covscience","mods", "sens.out.rds"))

#summary(sens.out)
plot(sens.out)
#plot(sens.out, sens.par = "R2", r.type = "total", sign.prod = "positive")
# This is the workhorse function for sensitivity analyses for average causal mediation effects. The sensitivity analysis can be used to assess the robustness of the findings from mediate to the violation of sequential ignorability, the crucial identification assumption necessary for the estimates to be valid. The analysis proceeds by quantifying the degree of sequential ignorability violation as the correlation between the error terms of the mediator and outcome models, and then calculating the true values of the average causal mediation effect for given values of this sensitivity parameter, rho. The original findings are deemed sensitive if the true effects are found to vary widely as function of rho.

#The resulting "rho" figures plot the estimated true values of ACME (or ADE, proportion mediated) against rho, along with the confidence intervals. When rho is zero, sequantial ignorability holds, so the estimated value at that point will be equal to the estimate returned by the mediate. The confidence level is determined by the 'conf.level' value of the original mediate object
```


### Negative Controls

```{r, eval=F}

med.fitR <- lm( Your.Personal.Relationships_S  ~ Covid_Timeline + Age + Edu + EthnicCats + Male  + Urban,  data = cv19w)
out.fitR <- lm( SCIENCE.TRUST_S   ~ Your.Personal.Relationships_S  + Covid_Timeline +  Age + Edu + EthnicCats + Male + Urban,
               data = cv19w)
med.outR <- mediate(med.fitR, out.fitR, treat = "Covid_Timeline", mediator = "Your.Personal.Relationships_S",
                   robustSE = TRUE, sims = 1000, control.value = "Baseline", treat.value = "Lockdown")

# save model
saveRDS(med.outR, here::here("_posts", "covscience","mods", "med.outR.rds"))
```

We do **not** find an effect for satisfaction with relationships

```{r eval=TRUE}
med.outR <- readRDS(here::here("_posts", "covscience","mods", "med.outR.rds"))
summary(med.outR)
plot(med.outR)
```



#### Reverse causation 

We next investigate whether declining satisfaction with government caused a drop in trust in science (reverse causal model)

```{r eval=F}
library(mediation)
med.out2 <- mediate(med.fit, out.fit, treat = "Covid_Timeline", mediator = "Sat.Government_S",
                   robustSE = TRUE, sims = 1000, control.value = "Lockdown", treat.value = "PostLockdown")
saveRDS(med.out2, here::here("_posts", "covscience","mods", "med.out2.rds"))

```


We find evidence for only a weak mediation effect 


```{r}
med.out2 <- readRDS( here::here("_posts", "covscience","mods", "med.out2.rds"))
summary(med.out2)
plot(med.out2)
```


```{r eval=FALSE}
sens.out2 <- medsens(med.out2, rho.by = 0.25,  effect.type = "indirect", sims = 100)
# save sensitivity analysis
saveRDS(sens.out2, here::here("_posts", "covscience","mods", "sens.out2.rds"))
```


As expected this small effect is robust to unmeasured confounding.

```{r eval=FALSE}
sens.out2 <- readRDS( here::here("_posts", "covscience","mods", "sens.out2.rds"))
summary(sens.out2)
plot(sens.out2)
```



## Does trust in science mediate the effect of government satisfaction? 


```{r eval=F}
med.fitb <- lm( SCIENCE.TRUST_S  ~ Covid_Timeline + Age + Edu + EthnicCats + Male  + Urban,  data = cv19w)
out.fitb <- lm( Sat.Government_S   ~ SCIENCE.TRUST_S  + Covid_Timeline +  Age + Edu + EthnicCats + Male + Urban, 
               data = cv19w)
med.outb <- mediate(med.fitb, out.fitb, treat = "Covid_Timeline", mediator = "SCIENCE.TRUST_S",
                   robustSE = TRUE, sims = 1000, control.value = "Baseline", treat.value = "Lockdown")

saveRDS(med.outb, here::here("_posts", "covscience","mods", "med.outb.rds"))
```


We find a very strong effect of lockdown on satisfaction with government, but we do not find any evidence for a substantial effect of mediation through trust in science. 

```{r eval=TRUE}
med.outb <- readRDS(here::here("_posts", "covscience","mods", "med.outb.rds"))

summary(med.outb)

plot(med.outb,  
     effect.type = c("indirect", "direct", "total"), 
     xlim = c(0,1))
```


### Sensitivity analysis

```{r eval=FALSE}
sens.outb2 <- medsens(med.outb2, rho.by = 0.25,  effect.type = "indirect", sims = 100)
# save sensitivity analysis
saveRDS(sens.outb2, here::here("_posts", "covscience","mods", "sens.outb2.rds"))
sens.outb2 <- readRDS(here::here("_posts", "covscience","mods", "sens.outb2.rds"))
plot(sens.outb2)
summary(sens.outb2)
```


###  Loss of gov't satisfaction does not mediate loss of trust in science. 

We can ask whether the fall in government satisfaction was mediated by a loss of confidence in science. 

```{r, eval= FALSE}
med.outb2 <- mediate(med.fitb, out.fitb, treat = "Covid_Timeline", mediator = "SCIENCE.TRUST_S",
                   robustSE = TRUE, sims = 1000, control.value = "Lockdown", treat.value = "PostLockdown")


saveRDS(med.outb2, here::here("_posts", "covscience","mods", "med.outb2.rds"))
```

We do not find strong evidence for a causal effect of loss of trust in science on satisfaction with the government.   

```{r}
med.outb2 <- readRDS(here::here("_posts", "covscience","mods", "med.outb2.rds"))
summary(med.outb2)
```


<!-- Sensitivity analysis  -->

<!-- ```{r eval=F} -->
<!-- sens.outb <- medsens(med.outb, rho.by = 0.25,  effect.type = "indirect", sims = 100) -->
<!-- sens.outb2 <- medsens(med.outb2, rho.by = 0.25,  effect.type = "indirect", sims = 100) -->

<!-- # save sensitivity analysis -->

<!-- saveRDS(sens.outb, here::here("_posts", "covscience","mods", "sens.outb.rds")) -->
<!-- saveRDS(sens.outb2, here::here("_posts", "covscience","mods", "sens.outb2.rds")) -->
<!-- ``` -->




<!-- ```{r eval=FALSE} -->
<!-- sens.outb <- readRDS(here::here("_posts", "covscience","mods", "sens.outb")) -->
<!-- sens.outb2 <- readRDS(here::here("_posts", "covscience","mods", "sens.outb2")) -->

<!-- summary(sens.outb) -->
<!-- plot(sens.outb) -->
<!-- plot(sens.outb2) -->
<!-- ``` -->



```{r cache = TRUE}
# covid timeline
# 3665 days after 30 June 2009 Saturday 13 July 2019
# 3842 days after 30 June 2009 Monday 6 January 2020
# 3895 days after 30 June 2009 Friday 28 February 2020
# 3921 days after 30 June 2009 WED MAR 25th
library(lubridate)
library(tidyverse)

carep <- cv %>%
  dplyr::mutate(timeline = make_date(year = 2009, month = 6, day = 30) + TSCORE) %>%
  count(day = floor_date(timeline, "day")) %>%
dplyr::mutate(condition = ifelse(
  #    day >= "2019-06-20" &
        day < "2020-01-06",
      "Baseline",
      ifelse(
        day >= "2020-01-06" & day < "2020-02-29",
        "JanFeb",
        ifelse(
          day >= "2020-02-29" & day < "2020-03-25",
          "EarlyMarch",
          ifelse(
            day >= "2020-03-25" &
              day < "2020-04-28",
            "Lockdown",
            "PostLockdown"
            ))))) %>%
  dplyr::mutate(condition = forcats::fct_relevel(condition, ord_dates_class)) %>%
  arrange(day)


# get COVID date
minday <- min(carep$day) # min day
dates_vline1<- as.Date(minday) # min day
dates_vline2<- as.Date("2020-01-06")
dates_vline3<- as.Date("2020-02-28")
# get data of change of baseline
dates_vline4<- as.Date("2020-03-25")
dates_vline5 <- as.Date("2020-04-27")
dates_vline6 <- as.Date("2020-10-15") # end day
# for line in a graph

# for line in a graph
#
dates_vline1b <- which(carep$day %in% dates_vline1)
dates_vline2b <- which(carep$day %in% dates_vline2)
dates_vline3b <- which(carep$day %in% dates_vline3)
dates_vline4b <- which(carep$day %in% dates_vline4)
dates_vline5b <- which(carep$day %in% dates_vline5)
dates_vline6b <- which(carep$day %in% dates_vline6)


tline <- ggplot(carep, aes(day, n)) +
  geom_col(aes(fill = condition)) + scale_x_date(date_labels = "%b/%Y", limits = c(as.Date(minday), 
                                                                                   as.Date("2020-10-15")))  + 
  scale_y_continuous(limits = c(0, 1000))  +
  geom_vline(xintercept = as.numeric(carep$day[dates_vline1b]),
             col = "red",
             linetype = "dashed") +
  geom_vline(xintercept = as.numeric(carep$day[dates_vline2b]),
             col = "red") +
  geom_vline(xintercept = as.numeric(carep$day[dates_vline3b]),
             col = "red",
             linetype = "dashed") +
  geom_vline(xintercept = as.numeric(carep$day[dates_vline4b]),
             col = "red",
             linetype = "dashed") +
  geom_vline(xintercept = as.numeric(carep$day[dates_vline5b]),
             col = "red",
             linetype = "dashed") + 
  xlab("NZAVS Waves 10 and 11 daily counts: repeated measures") + ylab("Count of Responses")  + theme_classic() +   scale_fill_viridis_d() + theme(
    legend.position = "top",
    legend.text = element_text(size = 6),
    legend.title = element_text(color = "Black", size = 8)) +
  # annotate(
  #   "rect",
  #   xmin = as.Date("2019-06-20"),
  #   xmax = dates_vline1,
  #   ymin = 0,
  #   ymax = 1000,
  #   alpha = .1,
  #   fill = "darkblue"
  # )  +
  # annotate(
  #   "rect",
  #   xmin = dates_vline1,
  #   xmax = dates_vline6,
  #   ymin = 0,
  #   ymax = 1000,
  #   alpha = .001
  # ) +
  # annotate(
  #   geom = "curve",
  #   x = as.Date("2019-06-20"),
  #   y = 750,
  #   xend = as.Date("2019-10-15"),
  #   yend = 800,
  #   curvature = -.2,
  #   arrow = arrow(length = unit(2, "mm"))
  # ) +
  # annotate(
  #   geom = "curve",
  #   x = as.Date("2019-06-20"),
  #   y = 750,
  #   xend = as.Date("2020-01-30"),
  #   yend = 850,
  #   curvature = -.2,
  #   arrow = arrow(length = unit(2, "mm"))
  # ) +
  # annotate(
  #   geom = "curve",
  #   x = as.Date("2019-06-20"),
  #   y = 750,
  #   xend = as.Date("2020-03-10"),
  #   yend = 875,
  #   curvature = -.2,
  #   arrow = arrow(length = unit(2, "mm"))
  # ) +
  # annotate(
  #   geom = "curve",
  #   x = as.Date("2019-06-20"),
  #   y = 750,
  #   xend = as.Date("2020-04-10"),
  #   yend = 900,
  #   curvature = -.2,
  #   arrow = arrow(length = unit(2, "mm"))
  # ) +
  # annotate(
  #   geom = "curve",
  #   x = as.Date("2019-06-20"),
  #   y = 750,
  #   xend = as.Date("2020-06-10"),
  #   yend = 925,
  #   curvature = -.2,
  #   arrow = arrow(length = unit(2, "mm"))
  # ) +
  annotate("text",
           x = as.Date("2019-06-20"),
           y = 755,
           label = "0") +
  annotate("text",
           x = as.Date("2019-10-25"),
           y = 800,
           label = "1") + 
   annotate("text",
           x = as.Date("2020-02-10"),
           y = 850,
           label = "2") + 
  annotate("text",
           x = as.Date("2020-03-15"),
           y = 875,
           label = "3") +
  annotate("text",
           x = as.Date("2020-04-20"),
           y = 900,
           label = "4") +
  annotate("text",
           x = as.Date("2020-06-10"),
           y = 925,
           label = "5")
```



## Appendix

Graph of timeline



```{r eval=T}
# GRAPH
tline + plot_annotation(title = "Histogram of Responses During COVID timeline:2019-2020", 
subtitle = "Focal contrast is pre-pandemic baseline (n= 22093) and stringent lockdown (n = 3189")
```


###  CMAverse approach







