---
title: "COVID-19 Lockdown"
description: |
author:
  - name: Joseph Bulbulia
    url: https://josephbulbulia.netlify.app
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: 0000-0002-5861-2056
date: 2021-FEB-28
output:
  distill::distill_article:
    self_contained: false
    toc: true
bibliography: bib.bib
editor_options: 
  chunk_output_type: console
---


```{r global_options, include = FALSE}
knitr::opts_chunk$set(
  fig.path = "figs/",
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  echo = FALSE,
  fig.width = 10,
  fig.height = 8
)
#results="hide",
#fig.width= 8,
#fig.height=,
#fig.fullwidth = TRUE)
```


```{r load_libraries, include=FALSE}
library("tidyverse")
library("easystats")
library("patchwork")
library("kableExtra")
library("ggpubr")
#library("viridis")
#library("wesanderson")
# library("papaja")
library("here")
library("citr")
library("here")
library("brms")
library("rstan")
library("rstanarm")
# library("tidybayes")
library("lubridate")
library("ggdag")
library("viridisLite")
library("bmlm")
library("bayesplot")
library("broom")
library("purrr")
#library("cmdstanr")  #multithreading bayesian models
# rstan options
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_classic())
```


```{r setup, include=FALSE}
# setup
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  layout = "l-body-outset",
  fig.width= 12,
  fig.height= 10,
  collapse =TRUE,
  R.options = list(width = 60)
)

# import data
df <- readRDS(here::here("data", "df"))
```

```{r cache = TRUE, echo = FALSE}
ord_dates_class <- c(
  "Baseline", 
  "PreCOVID", 
  "JanFeb", 
  "EarlyMarch", 
  "Lockdown",
  "PostLockdown")

# 3665 days after 30 June 2009 Saturday 13 July 2019
# 3842 days after 30 June 2009 Monday 6 January 2020
# 3895 days after 30 June 2009 Friday 28 February 2020
# 3921 days after 30 June 2009 WED MAR 25th
# 3954 days after 30 June 2009 Monday 27 April 2020
# 3672 days after June 30 2009 Saturday 20 July 2019

cv%>%
  dplyr::filter(Wave ==2019)%>%
  dplyr::select(Wave,TSCORE) %>%
  summarise (min(TSCORE))

cv <- df %>%
  dplyr::filter(YearMeasured == 1) %>%
  dplyr::filter(Wave == 2018 | Wave == 2019) %>%
  dplyr::group_by(Id) %>% 
  filter(n() > 1) %>%
  dplyr::filter(n() != 0) %>%
  dplyr::ungroup(Id) %>%
  dplyr::mutate(Covid_Timeline =
                 # ifelse(
                 # TSCORE %in% 3837:3894,
                 # "Baseling",
                    as.factor(ifelse(
                      TSCORE %in% 3896:3921, # feb 29 - march 25th
                      "EarlyMarch",
                      ifelse(
                        TSCORE %in% 3922:3954,
                        "Lockdown", #march 26- Mon 27 April 2020
                        ifelse(
                          TSCORE > 3954, # after april 27th 20202
                          "PostLockdown",
                          ifelse(
                            TSCORE %in% 3842:3895, # jan 6 to feb 28
                            "JanFeb",
                          ifelse(
                            TSCORE %in% 3665:3841 &
                              Wave == 2019,
                            "PreCOVID",
                            "Baseline"  # 3672 TSCORE or  20 July 2019
                          )
                        )
                      )
                    ) 
                 ) ))%>%
  dplyr::mutate(PrePostCovid =
                  ifelse(
                    TSCORE > 3895, "PostLockdown",
                    ifelse(
                      TSCORE < 3895 &
                        Wave == 2019,
                      "PreCOVID",
                      "Baseline"
                    )
                  ))%>% 
  dplyr::group_by(PrePostCovid) %>% 
  filter(n() > 1) %>%
  ungroup() %>% # There is overlap between waves, we only want repeated measures 
  dplyr::select(
    TSCORE,
    WSCORE,
    Wave,
    Partner,
    Employed,
    Sat.Government,
    NZ.Business.Conditions,
    NZ.Economic.Situation,
    PrePostCovid,
    Rel.Conflict,
    Rel.Satisfaction,
    Hours.SocialMedia,
    Hours.Exercise,
    Hours.Internet,
    Hours.News,
    Hours.Family,
    Hours.Friends,
    Hours.Housework,
    Hours.Children,
    Hours.Religious,
    Hours.Work,
    Hours.Community,
    Family.Time,
    Community.Time,
    Friends.Time,
    Family.Money,
    Friends.Money,
    Community.Money,
    years,
    Id,
    Parent,
    SWB.SatPWI02, # your health
    Hours.Work,
    Hours.Exercise,
    LIFEMEANING,
    KESSLER6,
    SWB.SatPWI03, # your future security
    #  K6sum,
    KESSLER6sum,
    Age,
    Male,
    Relid,
    Pol.Orient,
    Urban,
    GenCohort,
    Edu,
    YearMeasured,
    Covid_Timeline,
    HLTH.SleepHours,
    HLTH.Fatigue,
    LIFESAT,
    PWI,
    EthnicCats,
    NZdep,
    Partner,
    Pol.Orient,
    Urban,
    Euro,
    Religious,
    NZdep,
    WSCORE,
    Religion.Church,
    Emp.JobSecure,
    Emp.JobSat,
    Emp.JobValued,
    Alcohol.Intensity,
    Alcohol.Frequency
  ) %>%
  dplyr::group_by(Id) %>% filter(n() > 1) %>%
  dplyr::filter(n() != 0) %>%
  dplyr::ungroup(Id) %>%
  dplyr::mutate(
    Urban = (Urban),
    Euro = (Euro),
    Religious = as.factor(Religious),
    Your_Health = (SWB.SatPWI02),
    Your_Future_Security = SWB.SatPWI03,
    Covid_Timeline = as.factor(Covid_Timeline)
  ) %>%
  dplyr::mutate(
    WSCORE = as.factor(WSCORE),
    EduC = scale(as.numeric(Edu), scale = F, center = TRUE),
    Sat.Government = scale(Sat.Government),
    AgeDecadeC = scale(Age, scale = F, center = T) / 10,
    Hours.Work10 = as.integer(Hours.Work) / 10,
    Hours.Sleep = as.integer(HLTH.SleepHours),
    Hours.Exercise = as.integer(Hours.Exercise),
    Fatigue = as.integer(HLTH.Fatigue),
    f_s = scale(Fatigue),
    K6sum = as.integer(KESSLER6 * 6),
    LIFEMEANING_S = scale(LIFEMEANING),
    NZdepS = scale(NZdep),
    PolOrientS = scale(Pol.Orient, scale = T, center = T),
    Relid_S = scale(Relid, scale = T, center = T),
    Conservative = Pol.Orient,
    logSM = log(Hours.SocialMedia + 1),
    logINT = log(Hours.Internet + 1),
    logEX = log(Hours.Exercise + 1),
    logWK= log(Hours.Work + 1),
    k6_s = scale(KESSLER6sum),
    Conservative_S = PolOrientS,
    Religion_Church_S = scale(Religion.Church),
    Emp.JobSecure_S = scale(Emp.JobSecure),
    KESSLER6sum = as.integer(KESSLER6sum),
    Alcohol.Intensity_S = scale(Alcohol.Intensity),
    Alcohol.Frequency_S = scale(Alcohol.Frequency),
    Hours.Work = as.integer(Hours.Work),
    Hours.Exercise = as.integer(Hours.Exercise),
    yearS = years - min(years)
  ) %>%
  dplyr::mutate(Covid_Timeline = forcats::fct_relevel(Covid_Timeline, ord_dates_class))

cv <- cbind(cv,
            demean(
              cv,
              select = c(
                "KESSLER6sum",
                "k6_s",
                "logEX",
                "logSM",
                "logINT",
                "logWK",
                "Hours.Sleep",
                "Hours.Work10",
                "Hours.Exercise",
                "Sat.Government",
                "Hours.Children",
                "Hours.Internet",
                "Hours.Friends",
                "Hours.Family",
                "Hours.Religious",
                "Hours.Community",
                "Rel.Satisfaction",
                "Rel.Conflict",
                "Family.Time",
                "Family.Money",
                "Friends.Time",
                "Friends.Money",
                "Community.Time",
                "Community.Money",
                "Fatigue",
                "Alcohol.Intensity",
                "Alcohol.Frequency",
                "NZ.Economic.Situation",
                "Emp.JobSecure",
                "Friends.Time",
                "Family.Time",
                "Community.Time",
                "Hours.SocialMedia",
                "Hours.Internet",
                "Your_Future_Security"
              ),
              group = "Id"
            )) %>%
    dplyr::mutate(condition = forcats::fct_relevel(condition, ord_dates_class))

# test that we only have repeated measures
test <-cv %>%
  group_by(Id)%>%
  count()%>%
  ungroup() 

table(cv$Covid_Timeline)
```

```{r}
# covid timeline
# 3665 days after 30 June 2009 Saturday 13 July 2019
# 3842 days after 30 June 2009 Monday 6 January 2020
# 3895 days after 30 June 2009 Friday 28 February 2020
# 3921 days after 30 June 2009 WED MAR 25th
library(lubridate)
library(tidyverse)

dplyr::mutate(condition = forcats::fct_relevel(condition, ord_dates_class))

carep <- cv %>%
  dplyr::mutate(timeline = make_date(year = 2009, month = 6, day = 30) + TSCORE) %>%
  count(day = floor_date(timeline, "day")) %>%
dplyr::mutate(condition = ifelse(
    day < "2019-06-20",
    "Baseline",
    ifelse(
      day >= "2019-06-20" &
        day < "2020-01-06",
      "PreCOVID",
      ifelse(
        day >= "2020-01-06" & day < "2020-02-29",
        "Jan_Feb",
        ifelse(
          day >= "2020-02-29" & day < "2020-03-25",
          "EarlyMarch",
          ifelse(
            day >= "2020-03-25" &
              day < "2020-04-28",
            "Lockdown",
            "Postlockdown"
            )))))) %>%
  arrange(day)

# get COVID date
dates_vline0<- as.Date("2018-06-03")
dates_vline1<- as.Date("2019-06-20")
dates_vline2<- as.Date("2020-01-06")
dates_vline3<- as.Date("2020-02-28")
# get data of change of baseline
dates_vline4<- as.Date("2020-03-25")
dates_vline5 <- as.Date("2020-04-27")
dates_vline6 <- as.Date("2020-10-15")
# for line in a graph

# for line in a graph
#
dates_vline10 <- which(carep$day %in% dates_vline0)
dates_vline1b <- which(carep$day %in% dates_vline1)
dates_vline2b <- which(carep$day %in% dates_vline2)
dates_vline3b <- which(carep$day %in% dates_vline3)
dates_vline4b <- which(carep$day %in% dates_vline4)
dates_vline5b <- which(carep$day %in% dates_vline5)
dates_vline6b <- which(carep$day %in% dates_vline6)


tline <- ggplot(carep, aes(day, n)) +
  geom_col(aes(fill = condition)) + scale_x_date(date_labels = "%b/%Y", limits = c(as.Date("2018-06-10"), as.Date("2020-10-15")))  + scale_y_continuous(limits = c(0, 1000))  +
 geom_vline(xintercept = as.numeric(carep$day[dates_vline10]),
             col = "black",
             linetype = "dashed") +
  geom_vline(xintercept = as.numeric(carep$day[dates_vline1b]),
             col = "red",
             linetype = "dashed") +
  geom_vline(xintercept = as.numeric(carep$day[dates_vline2b]),
             col = "red") +
  geom_vline(xintercept = as.numeric(carep$day[dates_vline3b]),
             col = "red",
             linetype = "dashed") +
  geom_vline(xintercept = as.numeric(carep$day[dates_vline4b]),
             col = "red",
             linetype = "dashed") +
    geom_vline(xintercept = as.numeric(carep$day[dates_vline5b]),
             col = "red",
             linetype = "dashed") + 
  xlab("NZAVS Waves 9 and 10 daily counts: repeated measures") + ylab("Count of Responses")  + theme_classic() +   scale_fill_viridis_d() + theme(
    legend.position = "top",
    legend.text = element_text(size = 6),
    legend.title = element_text(color = "Black", size = 8)
  ) +
  annotate(
    "rect",
    xmin = as.Date("2018-01-03"),
    xmax = dates_vline5,
    ymin = 0,
    ymax = 1000,
    alpha = .001
  )  +
  annotate(
    "rect",
    xmin = dates_vline1,
    xmax = dates_vline6,
    ymin = 0,
    ymax = 1000,
    alpha = .05,
    fill = "darkblue"
  ) +
  annotate(
    geom = "curve",
    x = as.Date("2018-07-10"),
    y = 750,
    xend = as.Date("2019-10-15"),
    yend = 800,
    curvature = -.2,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(
    geom = "curve",
    x = as.Date("2018-07-10"),
    y = 750,
    xend = as.Date("2020-01-30"),
    yend = 850,
    curvature = -.2,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(
    geom = "curve",
    x = as.Date("2018-07-10"),
    y = 750,
    xend = as.Date("2020-03-10"),
    yend = 875,
    curvature = -.2,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(
    geom = "curve",
    x = as.Date("2018-07-10"),
    y = 750,
    xend = as.Date("2020-04-10"),
    yend = 900,
    curvature = -.2,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(
    geom = "curve",
    x = as.Date("2018-07-10"),
    y = 750,
    xend = as.Date("2020-06-10"),
    yend = 925,
    curvature = -.2,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate("text",
           x = as.Date("2018-07-01"),
           y = 755,
           label = "0") +  annotate("text",
           x = as.Date("2019-10-25"),
           y = 800,
           label = "1") + 
   annotate("text",
           x = as.Date("2020-02-10"),
           y = 850,
           label = "2") + 
  annotate("text",
           x = as.Date("2020-03-15"),
           y = 875,
           label = "3") +
  annotate("text",
           x = as.Date("2020-04-20"),
           y = 900,
           label = "4") +
  annotate("text",
           x = as.Date("2020-06-10"),
           y = 925,
           label = "5")

# GRAPH
tline + plot_annotation(title = "NZAVS COVID timeline", 
subtitle = "0.Baseline(34778) 1.PreCovid(23460) 2.JanFeb(2678) 3.EarlyMarch(2537) 4.Lockdown(1647) 5.Postlockdown(4456)")
```




##  Sample 

```{r}
cv %>%
  dplyr::select(c(KESSLER6sum, Covid_Timeline)) %>%
  dplyr::group_by(Covid_Timeline) %>%
  report::report() %>%
  summary()
```


## Distress

```{r}
cv %>%
  dplyr::select(c(KESSLER6sum, Covid_Timeline)) %>%
  dplyr::group_by(Covid_Timeline) %>%
  report::report() %>%
  summary()
```



## Causal inference : exercise

```{r echo = FALSE}
library("ggdag")
dg <- dagify(
  k6  ~ covid + income + jobsecurity + age + fatigue + sleep + 
    childcare + partner + male + exercise + healthsecurity + Hours.SocialMedia + hourswork,
  income ~ hourswork  + edu + ethnicity + male + covid,
  Hours.SocialMedia ~ hourswork + covid + age,
  exercise ~ age + ethnicity + hourswork,
  hourswork ~ covid, 
  childcare ~ hourswork + male, 
  partner ~ jobsecurity + childcare + hourswork,
  fatigue ~  age + hourswork + sleep + exercise,
  sleep ~   age + hourswork + exercise + jobsecurity,
  jobsecurity ~ hourswork + buisnessconfidence + covid,
  healthsecurity ~ govconfidence + covid + edu + exercise + age,
  govconfidence ~ covid + pol.orient, 
  buisnessconfidence ~ govconfidence + covid,
  exposure =  "covid",
  outcome =   "k6",
  labels = c(k6 = "Kessler 6", 
             covid = "Covid Timeline", 
             fatigue = "fatigue",
             Hours.SocialMedia = "Hours \n Social Media",
             income = "income",
             age = "age",
             healthsecurity = "health security",
             govconfidence = "government confidence",
             exercise = "exercise",
             sleep = "sleep",
             buisnessconfidence = "buisness confidence",
             childcare = "childcare",
             partner = "partner \n dissatifaction",
             employed = "employed",
             jobsecurity = "job security",
             exercise = "exercise",
             pol.orient = "political orientation",
             edu = "education",
             ethnicity = "ethnicity",
             male = "male",
             hourswork = "hours work"
             )) %>%
  control_for(c("exercise"))

ggdag_adjust(dg, text = FALSE, use_labels = "label", collider_lines = TRUE)
```



## No adjustment set

```{r echo = FALSE}
ggdag::ggdag_adjustment_set(dg, node_size = 14) +
  theme(legend.position = "bottom") + theme_dag_blank()
#  control_for(c("govconfidence"))
#control_for(c("partner"))
#control_for(c("healthsecurity"))
#control_for(c("buisnessconfidence"))
# no to healthsecurity
# no to childcare
# no to partner 
# no to buisness confidence
# no to income
# big no to fatigue!
# big no no to sleep
# yes to exercise! 
```


##  The GGDAG package will find colliders

```{r }
#Colliders
ggdag::ggdag_collider(tidy_k6_dag3,
                      from = "covid",
                      to = "k6") +   theme_dag_blank()
```

## The adjustment set command tells you which variables to include condition 


```{r}
library("ggdag")
tidy_k6_dag2 <- dagify(
  k6  ~ covid + income + jobsecurity + age + fatigue +
    childcare + partner + male + exercise + healthsecurity + Hours.SocialMedia + hourswork + hoursfriends,
  income ~ hourswork  + edu + ethnicity + male,
  Hours.SocialMedia ~ hourswork + hoursfriends + age,
  exercise ~ age + ethnicity + hourswork,
  hourswork ~ covid, 
  childcare ~ hourswork + male, 
  partner ~ jobsecurity + childcare + hourswork,
  fatigue ~  age + hourswork + sleep + exercise,
  sleep ~   age + hourswork + exercise,
  jobsecurity ~  covid,
  healthsecurity ~ govconfidence + covid + edu + exercise + age,
  govconfidence ~ covid + pol.orient, 
  buisnessconfidence ~ govconfidence + covid,
  exposure =  "covid",
  outcome =   "k6",
  labels = c(k6 = "Kessler 6", 
             covid = "Covid Timeline", 
             fatigue = "fatigue",
             Hours.SocialMedia = "Hours \n Social Media",
             income = "income",
             age = "age",
             healthsecurity = "health security",
             govconfidence = "government confidence",
             exercise = "exercise",
             sleep = "sleep",
             buisnessconfidence = "buisness confidence",
             childcare = "childcare",
             partner = "partner \n dissatifaction",
             employed = "employed",
             jobsecurity = "job security",
             exercise = "exercise",
             pol.orient = "political orientation",
             edu = "education",
             ethnicity = "ethnicity",
             male = "male",
             hourswork = "hours work"
             )) %>%
  control_for(c("hourswork"))
  
ggdag::ggdag_collider(tidy_k6_dag2,
                      from = "covid",
                      to = "k6") +   theme_dag_blank()

# graph adjustment sets
ggdag::ggdag_adjustment_set(tidy_k6_dag2, node_size = 14) +
  theme(legend.position = "bottom") + theme_dag_blank()
# no   control_for(c("Hours.SocialMedia"))
 # no Hours Work! 
# no to Exercise! 


```{r}
# evaluate the gs --> e theory
library("ggdag")
dg <- dagify(
  e  ~ l + rel,
  e ~  gs,
  gs ~ rel + l,
  exposure =  "gs",
  outcome =   "e")

ggdag::ggdag_adjustment_set(dg, node_size = 14) +
  theme(legend.position = "bottom") + theme_dag_blank()
```


```{r}
# evaluate the e --> gs theory
library("ggdag")
dg <- dagify(
  e  ~ l + rel,
  gs ~  e,
  gs ~ rel + l,
  exposure =  "e",
  outcome =   "gs")%>%
  control_for(c("gs"))

ggdag::ggdag_adjustment_set(dg, node_size = 14) +
  theme(legend.position = "bottom") + theme_dag_blank()




dg <- dagify(e  ~ l +  rel,
             gs ~  l + rel,
             e ~ gs,
             exposure =  "gs",
             outcome =   "e")

ggdag_adjust(dg, text = TRUE, collider_lines = TRUE)

ggdag::ggdag_adjustment_set(dg, node_size = 14) +
  theme(legend.position = "bottom") + theme_dag_blank()
ggdag::ggdag_collider(dg) +   theme_dag_blank()

```




## What if you adopt a causal salad approach? 




```{r}
cv$Sat.Government
k6_cv <- brm(KESSLER6sum_within ~ Covid_Timeline + (1|Id), cv, file = here::here("models","k6_cv"))
summary(k6_cv)

k6 <- lmer(KESSLER6sum ~ Covid_Timeline + (1|Id), cv)
summary(k6)
plot(ggeffects::ggpredict(k6))


m_exercise <- glmer(Hours.Exercise ~ Covid_Timeline + (1|Id), cv, family = "poisson")
plot(ggeffects::ggpredict(m_exercise))

# 
Your_Future_Security <- lmer(Your_Future_Security ~ Covid_Timeline + (1|Id), cv)
plot(ggeffects::ggpredict(Your_Future_Security))

Sat.Government <- lmer(Sat.Government ~ Covid_Timeline + (1|Id), cv)
plot(ggeffects::ggpredict(Sat.Government))


K6Sat.Government <- lmer(KESSLER6sum ~ Sat.Government + (1|Id), cv)
plot(ggeffects::ggpredict(Sat.Government))


K6logEX<- lmer(KESSLER6sum ~ logEX_within + logEX_between + (1|Id), cv)
plot(ggeffects::ggpredict(K6logEX))



#  Hours.Sleep
                
Hours.Children <- glmer(Hours.Children ~ Covid_Timeline + (1|Id), family = "poisson", cv)
plot(ggeffects::ggpredict(Hours.Children))

Hours.Friends <- glmer(Hours.Friends ~ Covid_Timeline + (1|Id), family = "poisson", cv)
plot(ggeffects::ggpredict(Hours.Friends))

Hours.Family <- glmer(Hours.Family ~ Covid_Timeline + (1|Id), family = "poisson", cv)
plot(ggeffects::ggpredict(Hours.Family))

cvR <- dplyr::filter(cv, Relid !=0)
Hours.Religious <- glmer(Hours.Religious ~ Covid_Timeline + (1|Id), family = "poisson", cvR)
plot(ggeffects::ggpredict(Hours.Religious))

Hours.Community <- glmer(Hours.Community ~ Covid_Timeline + (1|Id), family = "poisson", cv)
plot(ggeffects::ggpredict(Hours.Community))

Hours.Community <- glmer(Hours.Community ~ Covid_Timeline + (1|Id), family = "poisson", cv)
plot(ggeffects::ggpredict(Hours.Community))

Hours.Internet <- glmer(Hours.Internet ~ Covid_Timeline + (1|Id), family = "poisson", cv)
plot(ggeffects::ggpredict(Hours.Internet))

                
Hours.SocialMedia <- glmer(Hours.SocialMedia ~ Covid_Timeline + (1|Id), family = "poisson", cv)
plot(ggeffects::ggpredict(Hours.SocialMedia))


Hours.Exercise <- glmer(Hours.Exercise ~ Covid_Timeline + (1|Id), family = "poisson", cv)
plot(ggeffects::ggpredict(Hours.Exercise))

cvna <- cv%>%
  filter(!is.na(Hours.Sleep))
Hours.Sleep <- lmer(Hours.Sleep ~ Covid_Timeline + (1|Id) + (1|Covid_Timeline), cv)
plot(ggeffects::ggpredict(Hours.Sleep))

cvE <- dplyr::filter(cv, Employed ==1)


Hours.Housework <- glmer(Hours.Housework ~ Covid_Timeline + (1|Id), family = "poisson", cv)
plot(ggeffects::ggpredict(Hours.Housework))


Hours.Work <- glmer(Hours.Work ~ Covid_Timeline + (1|Id), family = "poisson", cvE)
plot(ggeffects::ggpredict(Hours.Work))

Emp.JobSecure <- lmer(Emp.JobSecure ~ Covid_Timeline + (1|Id), cvE)
plot(ggeffects::ggpredict(Emp.JobSecure))


###
cvP <- dplyr::filter(cv, Partner ==1)

hist(cv$Rel.Conflict)
hist(cvP$Rel.Satisfaction)


### 
cv %>%
  group_by(Covid_Timeline) %>%
  filter(!is.na(Partner))%>%
  count(Partner, Covid_Timeline) %>%
   mutate(prop = prop.table(n))



Rel.Conflict <- lmer(Rel.Conflict ~ Covid_Timeline + (1|Id), cvP)
plot(ggeffects::ggpredict(Rel.Conflict))

#
Rel.Satisfaction <- lmer(Rel.Satisfaction ~ Covid_Timeline + (1|Id), cv)
plot(ggeffects::ggpredict(Rel.Satisfaction))



Rel.Satisfaction <- lmer(Rel.Satisfaction ~ Covid_Timeline + (1|Id), cv)
plot(ggeffects::ggpredict(Rel.Satisfaction))


NZ.Business.Conditions <- lmer(NZ.Business.Conditions ~ Covid_Timeline + (1|Id), cv)
plot(ggeffects::ggpredict(NZ.Business.Conditions))


NZ.Economic.Situation <- lmer(NZ.Economic.Situation ~ Covid_Timeline + (1|Id), cv)
plot(ggeffects::ggpredict(NZ.Economic.Situation))


Alcohol.Intensity <- lmer(Alcohol.Intensity ~ Covid_Timeline + (1|Id), cv)
plot(ggeffects::ggpredict(Alcohol.Intensity))

Alcohol.Frequency <- lmer(Alcohol.Frequency ~ Covid_Timeline + (1|Id), cv)
plot(ggeffects::ggpredict(Alcohol.Frequency))



Fatigue <- lmer(Fatigue ~  Covid_Timeline + (1|Id), data = cv)
plot(ggeffects::ggpredict(Fatigue))


k6 <- glmer(KESSLER6sum ~  Covid_Timeline + (1|Id), family = "poisson", data = cv)
plot(ggeffects::ggpredict(k6))


## Mecahnisms
Hours.Sleep_withinM <- lmer(KESSLER6sum ~  Hours.Sleep_within  +  (1|Covid_Timeline) + (1|Id),  data = cv)
plot(ggeffects::ggpredict(Hours.Sleep_withinM))

Fatigue_withinM <- lmer(KESSLER6sum ~  Fatigue_within  +  (1|Covid_Timeline) + (1|Id),  data = cv)
plot(ggeffects::ggpredict(Fatigue_withinM))

Hours.Work10_withinM <- lmer(KESSLER6sum ~  Hours.Work10_within  +  (1|Covid_Timeline) + (1|Id),  data = cv)
plot(ggeffects::ggpredict(Hours.Work10_withinM))


Hours.Work10_withinM <- lmer(KESSLER6sum ~  Hours.Work10_within  +  (1|Covid_Timeline) + (1|Id),  data = cv)
plot(ggeffects::ggpredict(Hours.Work10_withinM))

Hours.Friends_withinM <- lmer(KESSLER6sum ~  Hours.Friends_within  +  (1|Covid_Timeline) + (1|Id),  data = cv)
plot(ggeffects::ggpredict(Hours.Friends_withinM))


Hours.Community_withinM <- lmer(KESSLER6sum ~  Hours.Community_within  +  (1|Covid_Timeline) + (1|Id),  data = cv)
plot(ggeffects::ggpredict(Hours.Community_withinM))

Hours.Family_withinM <- lmer(KESSLER6sum ~  Hours.Family_within  +  (1|Covid_Timeline) + (1|Id),  data = cv)
plot(ggeffects::ggpredict(Hours.Family_withinM))


Hours.Exercise_withinM <- lmer(KESSLER6sum ~  Hours.Exercise_within  +  (1|Covid_Timeline) + (1|Id),  data = cv)
plot(ggeffects::ggpredict(Hours.Exercise_withinM))


Hours.Exercise_withinM <- lmer(KESSLER6sum ~  Hours.Exercise_within  +  (1|Covid_Timeline) + (1|Id),  data = cv)
plot(ggeffects::ggpredict(Hours.Exercise_withinM))


Rel.Conflict <- lmer(Rel.Conflict ~    Covid_Timeline + (1|Id),  data = cv)
plot(ggeffects::ggpredict(Rel.Conflict))

Rel.Conflict_withinM <- lmer(KESSLER6sum ~  Rel.Conflict_within  +  (1|Covid_Timeline) + (1|Id),  data = cv)
plot(ggeffects::ggpredict(Rel.Conflict_withinM))

Rel.Satisfaction_withinM <- lmer(KESSLER6sum ~  Rel.Satisfaction_within  +  (1|Covid_Timeline) + (1|Id),  data = cv)
plot(ggeffects::ggpredict(Rel.Satisfaction_withinM))

###
Emp.JobSecure_withinM <- lmer(KESSLER6sum ~  Emp.JobSecure_within  +  (1|Covid_Timeline) + (1|Id),  data = cvE)
plot(ggeffects::ggpredict(Emp.JobSecure_withinM))




# Internet increase stress
Hours.Internet_withinM <- lmer(KESSLER6sum ~  Hours.Internet_within  +  (1|Covid_Timeline) + (1|Id),  data = cv)
plot(ggeffects::ggpredict(Hours.Internet_withinM))

#
Hours.SocialMedia_withinM <- lmer(KESSLER6sum ~  logSM_within  +  (1|Covid_Timeline) + (1|Id),  data = cv)
plot(ggeffects::ggpredict(Hours.SocialMedia_withinM))


table(cv$Covid_Timeline)
# trey without Lockdown
cvSM <- dplyr::filter(cv, Covid_Timeline == "L4_Lockdown_2020")%>%
  droplevels()


Hours.SocialMedia_withinM2 <- lm(KESSLER6sum ~  logSM_within + logSM_between,  data = cvSM)
plot(ggeffects::ggpredict(Hours.SocialMedia_withinM2))



estimate_contrasts(k6)%>%
  slice(1:5)
estimate_means(k6)%>%
  slice(1:5)

estimate_contrasts(he2)%>%
  slice(1:5)
estimate_means(he2)%>%
  slice(1:5)

### 

estimate_contrasts(she)
estimate_means(she)

estimate_contrasts(he)%>%
  slice(1:5)
estimate_means(he)%>%
  slice(1:5)

```

<!-- ```{r} -->
<!-- means <- estimate_means(k6) -->
<!-- means -->
<!-- ggplot(cv, aes(x = Covid_Timeline, y = KESSLER6sum, fill = Covid_Timeline)) + -->
<!--   geom_violin() + -->
<!--   geom_jitter2(width = 0.05, alpha = 0.5) + -->
<!--   geom_line(data = means, aes(y = rate, group = 1), size = 1) + -->
<!--   geom_pointrange(data = means,  -->
<!--                   aes(y = rate, ymin = CI_low, ymax = CI_high), -->
<!--                   size = 1,  -->
<!--                   color = "white") + -->
<!--   theme_modern() -->






<!-- means <- estimate_means(m_fat) -->
<!-- ggplot(cv, aes(x = Covid_Timeline, y = Fatigue_within, fill = Covid_Timeline)) + -->
<!--   geom_violin() + -->
<!--   geom_jitter2(width = 0.05, alpha = 0.5) + -->
<!--   geom_line(data = means, aes(y = Mean, group = 1), size = 1) + -->
<!--   geom_pointrange(data = means,  -->
<!--                   aes(y = Mean, ymin = CI_low, ymax = CI_high), -->
<!--                   size = 1,  -->
<!--                   color = "white") + -->
<!--   theme_modern() -->


<!-- means <- estimate_means(m_relconflict) -->
<!-- ggplot(cvp, aes(x = Covid_Timeline, y = Rel.Conflict_within, fill = Covid_Timeline)) + -->
<!--   geom_violin() + -->
<!--   geom_jitter2(width = 0.05, alpha = 0.5) + -->
<!--   geom_line(data = means, aes(y = Mean, group = 1), size = 1) + -->
<!--   geom_pointrange(data = means,  -->
<!--                   aes(y = Mean, ymin = CI_low, ymax = CI_high), -->
<!--                   size = 1,  -->
<!--                   color = "white") + -->
<!--   theme_modern() -->

<!-- ``` -->


<!-- ```{r} -->
<!-- estimate_contrasts(m_fat)%>% -->
<!--   slice(1:6) -->
<!-- estimate_means(m_fat)%>% -->
<!--   slice(1:6) -->
<!-- ``` -->






<!-- ```{r cache = TRUE} -->
<!-- estimate_contrasts(m0) -->
<!-- library(see) -->
<!-- library(ggplot2) -->
<!-- plot(estimate_contrasts(k6_cv)%>% -->
<!--   slice(1:6), estimate_means(k6_cv)%>% -->
<!--   slice(1:6)) + -->
<!--   theme_modern() -->
<!-- ``` -->


```{r}
bmlm::mlm_path_plot(
  xlab = "Covid\nCondition", 
  ylab = "Kessler6\n Distress", 
  mlab = "Fatigue"
  )

bmlm::mlm_path_plot(
  xlab = "Lesion", 
  ylab = "God-Score", 
  mlab = "Empathy"
  )

```

```{r}
library(tidyverse)
library(patchwork)
p1 <- cv %>%
  ggplot(aes(Covid_Timeline, Fatigue)) +
  stat_summary(fun.data = mean_cl_boot, size = 1) +
  geom_point(position = position_jitter(.15, .1), shape = 1, alpha = .01)
p2 <- cv %>%
  ggplot(aes(Covid_Timeline, KESSLER6sum)) +
  stat_summary(fun.data = mean_cl_boot, size = 1) +
  geom_point(position = position_jitter(.15, .1), shape = 1, alpha = .01)
p3 <- cv %>%
  ggplot(aes(Fatigue, KESSLER6sum)) +
  geom_point(position = position_jitter(.15, .1), shape = 1, alpha = .01) +
  geom_smooth(method = 'loess')
p1 | p2 | p3
```








```{r}
library(tidyverse)
library(patchwork)
p1 <- cv %>%
  ggplot(aes(Covid_Timeline, log(Hours.Exercise+1))) +
  stat_summary(fun.data = mean_cl_boot, size = 1) +
  geom_point(position = position_jitter(.15, .1), shape = 1, alpha = .01)
p2 <- cv %>%
  ggplot(aes(Covid_Timeline, KESSLER6sum)) +
  stat_summary(fun.data = mean_cl_boot, size = 1) +
  geom_point(position = position_jitter(.15, .1), shape = 1, alpha = .01)
p3 <- cv %>%
  ggplot(aes(log(Hours.Exercise+1), KESSLER6sum)) +
  geom_point(position = position_jitter(.15, .1), shape = 1, alpha = .01) +
  geom_smooth(method = 'loess')
p1 | p2 | p3
```






```{r}
library(tidyverse)
library(patchwork)
p1 <- cv %>%
  ggplot(aes(Covid_Timeline, Hours.Work10)) +
  stat_summary(fun.data = mean_cl_boot, size = 1) +
  geom_point(position = position_jitter(.15, .1), shape = 1, alpha = .01)
p2 <- cv %>%
  ggplot(aes(Covid_Timeline, KESSLER6sum)) +
  stat_summary(fun.data = mean_cl_boot, size = 1) +
  geom_point(position = position_jitter(.15, .1), shape = 1, alpha = .01)
p3 <- cv %>%
  ggplot(aes(Hours.Work10, KESSLER6sum)) +
  geom_point(position = position_jitter(.15, .1), shape = 1, alpha = .01) +
  geom_smooth(method = 'loess')
p1 | p2 | p3
```






```{r}
library(tidyverse)
library(patchwork)
p1 <- cv %>%
  ggplot(aes(Covid_Timeline, Fatigue)) +
  stat_summary(fun.data = mean_cl_boot, size = 1) +
  geom_point(position = position_jitter(.15, .1), shape = 1, alpha = .01)
p2 <- cv %>%
  ggplot(aes(Covid_Timeline, KESSLER6sum)) +
  stat_summary(fun.data = mean_cl_boot, size = 1) +
  geom_point(position = position_jitter(.15, .1), shape = 1, alpha = .01)
p3 <- cv %>%
  ggplot(aes(Fatigue, KESSLER6sum)) +
  geom_point(position = position_jitter(.15, .1), shape = 1, alpha = .01) +
  geom_smooth(method = 'loess')
p1 | p2 | p3
```



```{r}
library(tidyverse)
library(patchwork)
p1 <- cv %>%
  ggplot(aes(Covid_Timeline, Your_Future_Security)) +
  stat_summary(fun.data = mean_cl_boot, size = 1) +
  geom_point(position = position_jitter(.15, .1), shape = 1, alpha = .01)
p2 <- cv %>%
  ggplot(aes(Covid_Timeline, KESSLER6sum)) +
  stat_summary(fun.data = mean_cl_boot, size = 1) +
  geom_point(position = position_jitter(.15, .1), shape = 1, alpha = .01)
p3 <- cv %>%
  ggplot(aes(Your_Future_Security, KESSLER6sum)) +
  geom_point(position = position_jitter(.15, .1), shape = 1, alpha = .01) +
  geom_smooth(method = 'loess')
p1 | p2 | p3
```







# suggests monotonic effects of Fatigue on distress

```{r}
library(splines)
st<-lme4::lmer(k6_s ~ bs(Fatigue) + (1|Id), data = cv)
plot(ggeffects::ggpredict(st, terms = "Fatigue"))
```

```{r}
x <-cv$Covid_Timeline
mF <-cv$Fatigue
y<- cv$KESSLER6sum
id <-cv$Id
mF_w <-as.integer(cv$Fatigue_within)
mF_b <-as.integer(cv$Fatigue_between)

datF <-data.frame(x,mF,mF_w,mF_b,y,id)
```


```{r echo = TRUE}
path_m <- bf(
  mF ~ x + 
    (1| id)
)
path_y <- bf(
  y ~ x + mF +
    ( 1  |  id)
)
f1 <- brm(
  path_m + path_y + set_rescor(FALSE),
  data = datF,
  file = here("models/mediation-k6-covid-fatigue")
)
summary(f1)

datF$mF_w
datF$mF_b
```



```{r echo = TRUE}
path_m <- bf(
  mF ~ x + 
    (1|  id)
)
path_y <- bf(
  y ~ x + mF_w + mF_b +
    ( 1  | id)
)
f1a <- brm(
  path_m + path_y + set_rescor(FALSE),
  data = datF,
  file = here("models/mediation-k6-covid-fatigueW")
)
summary(f1a)
```



<!-- ## model 2  Social media  -->

```{r}
x <-cv$Covid_Timeline
mSM <-cv$logSM
y<- cv$KESSLER6sum
id <-cv$Id
mSM_w <-as.integer(cv$logSM_within)
mSM_b <-as.integer(cv$logSM_between)

datSM <-data.frame(x,mSM,mSM_b,mSM_w,y,id)
```


```{r echo = TRUE}
path_m <- bf(
  mSM ~ x + 
    (1 | id)
)
path_y <- bf(
  y ~ x + mSM_w + mSM_b + 
    ( 1 | id)
)
f2 <- brm(
  path_m + path_y + set_rescor(FALSE),
  data = datSM,
  file = here("models/mediation-k6-covid-social-media")
)
```


# Excercise
```{r}
x <-cv$Covid_Timeline
mEX <-cv$logEX
y<- cv$KESSLER6sum
id <-cv$Id
mEX_w <-as.integer(cv$logEX_within)
mEX_b <-as.integer(cv$logEX_between)

datEX <-data.frame(x,mEX,mEX_w,mEX_b,y,id)
```


```{r echo = TRUE}
path_m <- bf(
  mEX ~ x + 
    (1| id)
)
path_y <- bf(
  y ~ x + mEX_w  + mEX_b + 
    ( 1  |  id)
)
f4 <- brm(
  path_m + path_y + set_rescor(FALSE),
  data = datEX,
  file = here("models/mediation-k6-covid-logEX")
)
summary(f4)
```




Relationships

Rel.Conflict

```{r}
x <-cv$Covid_Timeline
mR <-cv$Rel.Conflict
y<- cv$KESSLER6sum
id <-cv$Id
mR_w  <-as.integer(cv$Rel.Conflict_within)
mR_b <-as.integer(cv$Rel.Conflict_between)

datR <-data.frame(x,mR,mR_w,mR_b,y,id)
```



```{r echo = TRUE}
path_m <- bf(
  mR ~ x + 
    (1| id)
)
path_y <- bf(
  y ~ x + mR_w  + mR_b + 
    ( 1  |  id)
)
f5 <- brm(
  path_m + path_y + set_rescor(FALSE),
  data = datR,
  file = here("models/mediation-k6-covid-rel-conflict")
)
summary(f5)
```






```{r}

f20 <- lmer(logSM_within ~     Covid_Timeline + (1|Id), data = cv)
plot(ggeffects::ggpredict(f20, terms = c("Covid_Timeline")), grid = TRUE)
sjPlot::tab_model(f2)

cv$Your_Future_Security
f20 <- lmer(KESSLER6sum ~   Your_Future_Security * Covid_Timeline + (1|Id), data = cv)
plot(ggeffects::ggpredict(f20, terms = c("Your_Future_Security", "Covid_Timeline")), grid = TRUE)
sjPlot::tab_model(f2)
```


```{r}
cv$log
f2a <- lmer(KESSLER6sum ~ logINT_between * Covid_Timeline + logINT_within  * Covid_Timeline + (1|Id), data = cv)
plot(ggeffects::ggpredict(f2a, terms = c("logINT_within", "Covid_Timeline")), grid = TRUE)
sjPlot::tab_model(f2a)
```

```{r}
cv$log
f2b<- lmer(KESSLER6sum ~ logWK_between * Covid_Timeline + logWK_within  * Covid_Timeline + (1|Id), data = cvE)
plot(ggeffects::ggpredict(f2b, terms = c("logWK_within", "Covid_Timeline")), grid = TRUE)
sjPlot::tab_model(f2b)
```

```{r}
f2c <- lmer(KESSLER6sum ~ logINT_between * Covid_Timeline + logINT_within  * Covid_Timeline + (1|Id), data = cv)
plot(ggeffects::ggpredict(f2c, terms = c("logSM_between", "Covid_Timeline")), grid = TRUE)
sjPlot::tab_model(f2c)
```








## model 3  Your_Future_Security

```{r}
x <-cv$Covid_Timeline
mFS <-cv$Your_Future_Security
y<- cv$KESSLER6sum
id <-cv$Id
mFS_w <-as.integer(cv$Your_Future_Security_within)
mFS_b <-as.integer(cv$Your_Future_Security_between)
datFS <-data.frame(x,mFS,mFS_w,mFS_b,y,id)
str(datFS)
```


```{r echo = TRUE}
path_m <- bf(
  mFS ~ x + 
    (1 |  id)
)
path_y <- bf(
  y ~ x + mFS_w + mFS_b + 
    ( 1 | id)
)
f3 <- brm(
  path_m + path_y + set_rescor(FALSE),
  data = datFS,
  file = here("models/mediation-k6-covid-future-security")
)
```






```{r}
summary(f3)
s1<-bayestestR::mediation(f1) # nat, no  FAT 

# s1<- bayestestR::mediation(f1, centrality = "mean", ci = .95, 
#                            treatment = x, 
#                            mediator = m_w, 
#                            response = y)

sjPlot::plot_model(f1)
summary(f1)
summary(f3)
summary(f2)







d1<-bayestestR::describe_posterior(as.data.frame(f1),centrality = "mean", test="p_direction",ci=.95)
d1

  a = "TE_H241 = 0",
  b = "Mood_TE = 0",
  cp = "Mood_H241 = 0",
  me = "TE_H241 * Mood_TE = 0",
  c = "TE_H241 * Mood_TE + Mood_H241 = 0"

summary(f2)
summary(f1a)
summary(f3)
post1 <- posterior_samples(f1a)
post2 <- posterior_samples(f2)
post3 <- posterior_samples(f3)
post4 <- posterior_samples(f4)
post5 <- posterior_samples(f5)
# covab <- VarCorr(f1, summary = FALSE)$id$ cov %>%
#         .[,"m_Intercept","y_Intercept"]

post_marF <- post1%>% 
  transmute(
    a = b_mF_xEarly_March_2020,
    b = b_y_mF_w,
    cp = b_y_xEarly_March_2020,
    me = a * b,
    c = cp + me#,
   # pme = me / c
  )
mcmc_intervals(post_marF)

#covab <- VarCorr(f1, summary = FALSE)$id$ cov %>%
#        .[,"m_Intercept","y_Intercept"]


post_lF <- post1 %>% 
  transmute(
    a = b_mF_xL4_Lockdown_2020,
    b = b_y_mF_w,
    cp = b_y_xL4_Lockdown_2020,
    me = a * b,#+ covab,
    c = cp + me
  )

posterior_summary(post_lF
                  )
mcmc_intervals(post_lF)


posterior_summary(post_marF)
mcmc_intervals(post_marF)

### 2
post_marSM <- post2%>% 
  transmute(
    a = b_mSM_xEarly_March_2020,
    b = b_y_mSM_w,
    cp = b_y_xEarly_March_2020,
    me = a * b,
    c = cp + me,
    pme = me / c
  )
mcmc_intervals(post_marSM)

#covab <- VarCorr(f1, summary = FALSE)$id$ cov %>%
        .[,"m_Intercept","y_Intercept"]


post_lSM <- post2 %>% 
  transmute(
    a = b_mSM_xL4_Lockdown_2020,
    b = b_y_mSM_w,
    cp = b_y_xL4_Lockdown_2020,
    me = a * b,#+ covab,
    c = cp + me 
  )

posterior_summary(post_lSM )
mcmc_intervals(post_lSM)


posterior_summary(post_marF)
mcmc_intervals(post_marF)


### 3

post_marFS <- post3%>% 
  transmute(
    a = b_mFS_xEarly_March_2020,
    b = b_y_mFS_w,
    cp = b_y_xEarly_March_2020,
    me = a * b,
    c = cp + me,
    pme = me / c
  )
mcmc_intervals(post_marFS)

#covab <- VarCorr(f1, summary = FALSE)$id$ cov %>%
        .[,"m_Intercept","y_Intercept"]


post_lFS <- post3 %>% 
  transmute(
    a = b_mFS_xL4_Lockdown_2020,
    b = b_y_mFS_w,
    cp = b_y_xL4_Lockdown_2020,
    me = a * b,#+ covab,
    c = cp + me 
  )

posterior_summary(post_lFS
                  )
mcmc_intervals(post_lFS)


posterior_summary(post_marF)
mcmc_intervals(post_marF)



# Hours Excercise 

post_marFS <- post3%>% 
  transmute(
    a = b_mFS_xEarly_March_2020,
    b = b_y_mFS_w,
    cp = b_y_xEarly_March_2020,
    me = a * b,
    c = cp + me,
    pme = me / c
  )
mcmc_intervals(post_marFS)





post_marEX <- post4%>% 
  transmute(
    a = b_mEX_xEarly_March_2020,
    b = b_y_mEX_w,
    cp = b_y_xEarly_March_2020,
    me = a * b,
    c = cp + me#,
   # pme = me / c
  )
mcmc_intervals(post_marEX)

#covab <- VarCorr(f1, summary = FALSE)$id$ cov %>%
#        .[,"m_Intercept","y_Intercept"]


post_lF <- post4 %>% 
  transmute(
    a = b_mEX_xL4_Lockdown_2020,
    b = b_y_mEX_w,
    cp = b_y_xL4_Lockdown_2020,
    me = a * b,#+ covab,
    c = cp + me
  )

posterior_summary(post_lF
                  )
mcmc_intervals(post_lF)

summary(f4)




post_marEX <- post4%>% 
  transmute(
    a = b_mEX_xEarly_March_2020,
    b = b_y_mEX_w,
    cp = b_y_xEarly_March_2020,
    me = a * b,
    c = cp + me#,
   # pme = me / c
  )
mcmc_intervals(post_marEX)

#covab <- VarCorr(f1, summary = FALSE)$id$ cov %>%
#        .[,"m_Intercept","y_Intercept"]



summary(f5)
post_lR <- post5 %>% 
  transmute(
    a = b_mR_xL4_Lockdown_2020,
    b = b_y_mR_w,
    cp = b_y_xL4_Lockdown_2020,
    me = a * b,#+ covab,
    c = cp + me
  )

posterior_summary(post_lR)
mcmc_intervals(post_lR)


post_marR <- post5%>% 
  transmute(
    a = b_mR_xEarly_March_2020,
    b = b_y_mR_w,
    cp = b_y_xEarly_March_2020,
    me = a * b,
    c = cp + me#,
   # pme = me / c
  )
mcmc_intervals(post_marR)





h1 <- c(
  a = "mEX_xEarly_March_2020  = 0",
  b = "y_mEX_w = 0",
  cp = "y_xEarly_March_2020 = 0",
  me = "mEX_xL4_Lockdown_2020 * y_mEX_w = 0",
  c = "mEX_xEarly_March_2020 * y_mEX_w + y_xEarly_March_2020 = 0"
  )

h2 <- c(
  a = "mEX_xL4_Lockdown_2020  = 0",
  b = "y_mEX_w = 0",
  cp = "y_xL4_Lockdown_2020 = 0",
  me = "mEX_xL4_Lockdown_2020 * y_mEX_w = 0",
  c = "mEX_xL4_Lockdown_2020 * y_mEX_w + y_xL4_Lockdown_2020 = 0"
  )



h3 <- c(
  a = "mEX_xL4_Lockdown_2020  < mEX_xEarly_March_2020",
  b = "y_mEX_w = 0",
  cp = "y_xL4_Lockdown_2020 < y_xEarly_March_2020",
  me = "mEX_xL4_Lockdown_2020 * y_mEX_w < mEX_xEarly_March_2020 * y_mEX_w",
  c = "mEX_xL4_Lockdown_2020 * y_mEX_w + y_xL4_Lockdown_2020 < mEX_xEarly_March_2020 * y_mEX_w + y_xEarly_March_2020"
  )


plot(
  hypothesis(f4, h1)
)

plot(  
  hypothesis(f4, h2)
)
  
plot(
  hypothesis(f4, h3)
)

```


```{r echo = TRUE, eval = FALSE}
conditional_effects(f1)
```

```{r}
summary(f1)
x <- conditional_effects(f1, effects = "m_w")
p <- plot(x, points = TRUE,plot = FALSE)
p
x2 <- conditional_effects(f1, effects = "m_w", resp = "y",   spaghetti = TRUE, nsamples = 100) 
p2 <- plot(x2, plot = FALSE, points = TRUE)# +  scale_y_continuous(limits = c(0,10)) 
p2
p[[2]] | p[[1]] | p2




```{r, fig.height = 4, fig.width = 6}
mlm_path_plot(xlab = "Stimulus\n(X)",
              mlab = "Organism\n(M)",
              ylab = "Response\n(Y)")
```



```{r}
summary(f3)
s1<-bayestestR::mediation(f3) # nat, no  FAT 

# s1<- bayestestR::mediation(f1, centrality = "mean", ci = .95, 
#                            treatment = x, 
#                            mediator = m_w, 
#                            response = y)

sjPlot::plot_model(f3)
summary(f1)

d1<-bayestestR::describe_posterior(as.data.frame(f1),centrality = "mean", test="p_direction",ci=.95)
d1

  a = "TE_H241 = 0",
  b = "Mood_TE = 0",
  cp = "Mood_H241 = 0",
  me = "TE_H241 * Mood_TE = 0",
  c = "TE_H241 * Mood_TE + Mood_H241 = 0"

summary(f1)
post <- posterior_samples(f3)

post_mar <- post %>% 
  transmute(
    a = b_m_xEarly_March_2020,
    b = b_y_bsm_w3,
    cp = b_y_xPost_Lockdown_2020,
    me = a * b ,
    c = cp + me,
    pme = me / c
  )
mcmc_intervals(post_mar)

# covab <- VarCorr(f1, summary = FALSE)$id$ cov %>%
#        .[,"m_Intercept","y_Intercept"]


post_l <- post %>% 
  transmute(
    a = b_m_xL4_Lockdown_2020,
    b = b_y_bsm_w3,
    cp = b_y_xL4_Lockdown_2020,
    me = a * b  ,
    c = cp + me #,
   # pme = me / c
  )

posterior_summary(post_l)
mcmc_intervals(post_l)


posterior_summary(post_mar)
mcmc_intervals(post_mar)


```


###

pt1<-d1%>%
  tibble::as_tibble(include.rownames = FALSE)%>%
  dplyr::slice(n=1:10)%>%
  dplyr::select(-CI)%>%
  mutate_if(is.numeric, ~round(., 3))%>%
  ggpubr::ggtexttable(rows = NULL,
                      theme = ttheme("mRed"))

pt1
bbt18<-bayestestR::mediation(f1,centrality = "mean",ci=.95) # nat, no  FAT 


dm20<-as.data.frame(bbt20S)%>%
  dplyr::select(-proportion_mediated)%>%
  bayestestR::estimate_density()%>%
  plot(labels = FALSE)%>%
  ggpar(main = "")#+theme_solarized()
dm20



# BLM Approach
```{r}
cvf <- cv%>%
  dplyr::select(Covid_Timeline, Fatigue)%>%
  filter(Covid_Timeline == )
cv1<-dplyr::filter(cv, !is.na(Fatigue_within))
x <-cv1$Covid_Timeline
m <-cv1$Fatigue
y<- cv1$KESSLER6sum
id <-cv1$Id

m_w <-as.integer(cv1$Fatigue_within)

dat <-data.frame(x,m,m_w, y,id)
str(dat)
table(dat$m_w)
length(unique(dat$id))
```

``





# ```{r}
# ncv<-filter(cv, yearS > 1)
# 
# m2 <- lmer(KESSLER6sum_within ~ bs(yearS ) + (1|Id), ncv)
# summary(m2)
# plot(ggeffects::ggpredict(m2, terms = "yearS[all]" ))
# ```

