---
title: "COVID-19 Lockdown"
description: |
author:
  - name: Joseph Bulbulia
    url: https://josephbulbulia.netlify.app
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: 0000-0002-5861-2056
date: 2021-FEB-28
output:
  distill::distill_article:
    self_contained: false
    toc: true
bibliography: bib.bib
editor_options: 
  chunk_output_type: console
---


```{r global_options, include = FALSE}
knitr::opts_chunk$set(
  fig.path = "figs/",
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  echo = FALSE,
  fig.width = 10,
  fig.height = 8
)
#results="hide",
#fig.width= 8,
#fig.height=,
#fig.fullwidth = TRUE)
```


```{r load_libraries, include=FALSE}
library("tidyverse")
library("easystats")
library("patchwork")
library("kableExtra")
library("ggpubr")
#library("viridis")
#library("wesanderson")
# library("papaja")
library("here")
library("citr")
library("here")
library("brms")
library("rstan")
library("rstanarm")
# library("tidybayes")
library("lubridate")
library("ggdag")
library("viridisLite")
library("bmlm")
library("bayesplot")
library("broom")
library("purrr")
#library("cmdstanr")  #multithreading bayesian models
# rstan options
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_classic())
```


```{r setup, include=FALSE}
# setup
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  layout = "l-body-outset",
  fig.width= 12,
  fig.height= 10,
  collapse =TRUE,
  R.options = list(width = 60)
)

# import data
df <- readRDS(here::here("data", "df"))
```

```{r cache = TRUE, echo = FALSE}
ord_dates_class <- c(
  "Baseline", 
  "PreCOVID", 
  "JanFeb", 
  "EarlyMarch", 
  "Lockdown",
  "PostLockdown")

# 3665 days after 30 June 2009 Saturday 13 July 2019
# 3842 days after 30 June 2009 Monday 6 January 2020
# 3895 days after 30 June 2009 Friday 28 February 2020
# 3921 days after 30 June 2009 WED MAR 25th
# 3954 days after 30 June 2009 Monday 27 April 2020
# 3672 days after June 30 2009 Saturday 20 July 2019

# cv%>%
#   dplyr::filter(Wave ==2019)%>%
#   dplyr::select(Wave,TSCORE) %>%
#   summarise (min(TSCORE))

cv <- df %>%
  dplyr::filter(YearMeasured == 1) %>%
  dplyr::filter(Wave == 2018 | Wave == 2019) %>%
  dplyr::group_by(Id) %>% 
  filter(n() > 1) %>%
  dplyr::filter(n() != 0) %>%
  dplyr::ungroup(Id) %>%
  dplyr::mutate(Covid_Timeline =
                 # ifelse(
                 # TSCORE %in% 3837:3894,
                 # "Baseling",
                    as.factor(ifelse(
                      TSCORE %in% 3896:3921, # feb 29 - march 25th
                      "EarlyMarch",
                      ifelse(
                        TSCORE %in% 3922:3954,
                        "Lockdown", #march 26- Mon 27 April 2020
                        ifelse(
                          TSCORE > 3954, # after april 27th 20202
                          "PostLockdown",
                          ifelse(
                            TSCORE %in% 3842:3895, # jan 6 to feb 28
                            "JanFeb",
                          ifelse(
                            TSCORE %in% 3665:3841 &
                              Wave == 2019,
                            "PreCOVID",
                            "Baseline"  # 3672 TSCORE or  20 July 2019
                          )
                        )
                      )
                    ) 
                 ) ))%>%
  dplyr::mutate(PrePostCovid =
                  ifelse(
                    TSCORE > 3895, "PostLockdown",
                    ifelse(
                      TSCORE < 3895 &
                        Wave == 2019,
                      "PreCOVID",
                      "Baseline"
                    )
                  ))%>% 
  dplyr::group_by(PrePostCovid) %>% 
  filter(n() > 1) %>%
  ungroup() %>% # There is overlap between waves, we only want repeated measures 
  dplyr::select(
    TSCORE,
    WSCORE,
    Wave,
    Partner,
    Employed,
    Sat.Government,
    NZ.Business.Conditions,
    NZ.Economic.Situation,
    PrePostCovid,
    Rel.Conflict,
    Rel.Satisfaction,
    Hours.SocialMedia,
    Hours.Exercise,
    Hours.Internet,
    Hours.News,
    Hours.Family,
    Hours.Friends,
    Hours.Housework,
    Hours.Children,
    Hours.Religious,
    Hours.Work,
    Hours.Community,
    Family.Time,
    Community.Time,
    Friends.Time,
    Family.Money,
    Friends.Money,
    Community.Money,
    years,
    Id,
    Parent,
    SWB.SatPWI02, # your health
    Hours.Work,
    Hours.Exercise,
    LIFEMEANING,
    KESSLER6,
    SWB.SatPWI03, # your future security
    #  K6sum,
    KESSLER6sum,
    Age,
    Male,
    Relid,
    Pol.Orient,
    Urban,
    GenCohort,
    Edu,
    YearMeasured,
    Covid_Timeline,
    HLTH.SleepHours,
    HLTH.Fatigue,
    LIFESAT,
    PWI,
    EthnicCats,
    NZdep,
    Partner,
    Pol.Orient,
    Urban,
    Euro,
    Religious,
    NZdep,
    WSCORE,
    Religion.Church,
    Emp.JobSecure,
    Emp.JobSat,
    Emp.JobValued,
    Alcohol.Intensity,
    Alcohol.Frequency
  ) %>%
  dplyr::group_by(Id) %>% filter(n() > 1) %>%
  dplyr::filter(n() != 0) %>%
  dplyr::ungroup(Id) %>%
  dplyr::mutate(
    Urban = (Urban),
    Euro = (Euro),
    Religious = as.factor(Religious),
    Your_Health = (SWB.SatPWI02),
    Your_Future_Security = SWB.SatPWI03,
    Covid_Timeline = as.factor(Covid_Timeline)
  ) %>%
  dplyr::mutate(
    WSCORE = as.factor(WSCORE),
    EduC = scale(as.numeric(Edu), scale = F, center = TRUE),
    Sat.Government = scale(Sat.Government),
    AgeDecadeC = scale(Age, scale = F, center = T) / 10,
    Hours.Work10 = as.integer(Hours.Work) / 10,
    Hours.Sleep = as.integer(HLTH.SleepHours),
    Hours.Exercise = as.integer(Hours.Exercise),
    Fatigue = as.integer(HLTH.Fatigue),
    f_s = scale(Fatigue),
    K6sum = as.integer(KESSLER6 * 6),
    LIFEMEANING_S = scale(LIFEMEANING),
    NZdepS = scale(NZdep),
    PolOrientS = scale(Pol.Orient, scale = T, center = T),
    Relid_S = scale(Relid, scale = T, center = T),
    Conservative = Pol.Orient,
    logSM = log(Hours.SocialMedia + 1),
    logINT = log(Hours.Internet + 1),
    logEX = log(Hours.Exercise + 1),
    logWK= log(Hours.Work + 1),
    k6_s = scale(KESSLER6sum),
    Conservative_S = PolOrientS,
    Religion_Church_S = scale(Religion.Church),
    Emp.JobSecure_S = scale(Emp.JobSecure),
    KESSLER6sum = as.integer(KESSLER6sum),
    Alcohol.Intensity_S = scale(Alcohol.Intensity),
    Alcohol.Frequency_S = scale(Alcohol.Frequency),
    Hours.Work = as.integer(Hours.Work),
    Hours.Exercise = as.integer(Hours.Exercise),
    yearS = years - min(years)
  ) %>%
  dplyr::mutate(Covid_Timeline = forcats::fct_relevel(Covid_Timeline, ord_dates_class))

cv <- cbind(cv,
            demean(
              cv,
              select = c(
                "KESSLER6sum",
                "k6_s",
                "logEX",
                "logSM",
                "logINT",
                "logWK",
                "Hours.Sleep",
                "Hours.Work10",
                "Hours.Exercise",
                "Sat.Government",
                "Hours.Children",
                "Hours.Internet",
                "Hours.Friends",
                "Hours.Family",
                "Hours.Religious",
                "Hours.Community",
                "Rel.Satisfaction",
                "Rel.Conflict",
                "Family.Time",
                "Family.Money",
                "Friends.Time",
                "Friends.Money",
                "Community.Time",
                "Community.Money",
                "Fatigue",
                "Alcohol.Intensity",
                "Alcohol.Frequency",
                "NZ.Economic.Situation",
                "Emp.JobSecure",
                "Friends.Time",
                "Family.Time",
                "Community.Time",
                "Hours.SocialMedia",
                "Hours.Internet",
                "Your_Future_Security"
              ),
              group = "Id"
            )) %>%
    dplyr::mutate(condition = forcats::fct_relevel(condition, ord_dates_class))

# test that we only have repeated measures
test <-cv %>%
  group_by(Id)%>%
  count()%>%
  ungroup() 

table(cv$Covid_Timeline)
```

```{r}
# covid timeline
# 3665 days after 30 June 2009 Saturday 13 July 2019
# 3842 days after 30 June 2009 Monday 6 January 2020
# 3895 days after 30 June 2009 Friday 28 February 2020
# 3921 days after 30 June 2009 WED MAR 25th
library(lubridate)
library(tidyverse)

dplyr::mutate(condition = forcats::fct_relevel(condition, ord_dates_class))

carep <- cv %>%
  dplyr::mutate(timeline = make_date(year = 2009, month = 6, day = 30) + TSCORE) %>%
  count(day = floor_date(timeline, "day")) %>%
dplyr::mutate(condition = ifelse(
    day < "2019-06-20",
    "Baseline",
    ifelse(
      day >= "2019-06-20" &
        day < "2020-01-06",
      "PreCOVID",
      ifelse(
        day >= "2020-01-06" & day < "2020-02-29",
        "Jan_Feb",
        ifelse(
          day >= "2020-02-29" & day < "2020-03-25",
          "EarlyMarch",
          ifelse(
            day >= "2020-03-25" &
              day < "2020-04-28",
            "Lockdown",
            "Postlockdown"
            )))))) %>%
  arrange(day)

# get COVID date
dates_vline0<- as.Date("2018-06-03")
dates_vline1<- as.Date("2019-06-20")
dates_vline2<- as.Date("2020-01-06")
dates_vline3<- as.Date("2020-02-28")
# get data of change of baseline
dates_vline4<- as.Date("2020-03-25")
dates_vline5 <- as.Date("2020-04-27")
dates_vline6 <- as.Date("2020-10-15")
# for line in a graph

# for line in a graph
#
dates_vline10 <- which(carep$day %in% dates_vline0)
dates_vline1b <- which(carep$day %in% dates_vline1)
dates_vline2b <- which(carep$day %in% dates_vline2)
dates_vline3b <- which(carep$day %in% dates_vline3)
dates_vline4b <- which(carep$day %in% dates_vline4)
dates_vline5b <- which(carep$day %in% dates_vline5)
dates_vline6b <- which(carep$day %in% dates_vline6)


tline <- ggplot(carep, aes(day, n)) +
  geom_col(aes(fill = condition)) + scale_x_date(date_labels = "%b/%Y", limits = c(as.Date("2018-06-10"), as.Date("2020-10-15")))  + scale_y_continuous(limits = c(0, 1000))  +
 geom_vline(xintercept = as.numeric(carep$day[dates_vline10]),
             col = "black",
             linetype = "dashed") +
  geom_vline(xintercept = as.numeric(carep$day[dates_vline1b]),
             col = "red",
             linetype = "dashed") +
  geom_vline(xintercept = as.numeric(carep$day[dates_vline2b]),
             col = "red") +
  geom_vline(xintercept = as.numeric(carep$day[dates_vline3b]),
             col = "red",
             linetype = "dashed") +
  geom_vline(xintercept = as.numeric(carep$day[dates_vline4b]),
             col = "red",
             linetype = "dashed") +
    geom_vline(xintercept = as.numeric(carep$day[dates_vline5b]),
             col = "red",
             linetype = "dashed") + 
  xlab("NZAVS Waves 9 and 10 daily counts: repeated measures") + ylab("Count of Responses")  + theme_classic() +   scale_fill_viridis_d() + theme(
    legend.position = "top",
    legend.text = element_text(size = 6),
    legend.title = element_text(color = "Black", size = 8)
  ) +
  annotate(
    "rect",
    xmin = as.Date("2018-01-03"),
    xmax = dates_vline5,
    ymin = 0,
    ymax = 1000,
    alpha = .001
  )  +
  annotate(
    "rect",
    xmin = dates_vline1,
    xmax = dates_vline6,
    ymin = 0,
    ymax = 1000,
    alpha = .05,
    fill = "darkblue"
  ) +
  annotate(
    geom = "curve",
    x = as.Date("2018-07-10"),
    y = 750,
    xend = as.Date("2019-10-15"),
    yend = 800,
    curvature = -.2,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(
    geom = "curve",
    x = as.Date("2018-07-10"),
    y = 750,
    xend = as.Date("2020-01-30"),
    yend = 850,
    curvature = -.2,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(
    geom = "curve",
    x = as.Date("2018-07-10"),
    y = 750,
    xend = as.Date("2020-03-10"),
    yend = 875,
    curvature = -.2,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(
    geom = "curve",
    x = as.Date("2018-07-10"),
    y = 750,
    xend = as.Date("2020-04-10"),
    yend = 900,
    curvature = -.2,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(
    geom = "curve",
    x = as.Date("2018-07-10"),
    y = 750,
    xend = as.Date("2020-06-10"),
    yend = 925,
    curvature = -.2,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate("text",
           x = as.Date("2018-07-01"),
           y = 755,
           label = "0") +  annotate("text",
           x = as.Date("2019-10-25"),
           y = 800,
           label = "1") + 
   annotate("text",
           x = as.Date("2020-02-10"),
           y = 850,
           label = "2") + 
  annotate("text",
           x = as.Date("2020-03-15"),
           y = 875,
           label = "3") +
  annotate("text",
           x = as.Date("2020-04-20"),
           y = 900,
           label = "4") +
  annotate("text",
           x = as.Date("2020-06-10"),
           y = 925,
           label = "5")

# GRAPH
tline + plot_annotation(title = "NZAVS COVID timeline", 
subtitle = "0.Baseline(34778) 1.PreCovid(23460) 2.JanFeb(2678) 3.EarlyMarch(2537) 4.Lockdown(1647) 5.Postlockdown(4456)")
```




##  Sample 

```{r}
cv %>%
  dplyr::select(c(KESSLER6sum, Covid_Timeline)) %>%
  dplyr::group_by(Covid_Timeline) %>%
  report::report() %>%
  summary()
```


## Distress

```{r}
cv %>%
  dplyr::select(c(KESSLER6sum, Covid_Timeline)) %>%
  dplyr::group_by(Covid_Timeline) %>%
  report::report() %>%
  summary()
```



## Causal inference : exercise

```{r echo = FALSE}
library("ggdag")
dg <- dagify(
  k6  ~ covid + income + jobsecurity + age + fatigue + sleep + 
    childcare + partner + male + exercise + healthsecurity + Hours.SocialMedia + hourswork,
  income ~ hourswork  + edu + ethnicity + male + covid,
  Hours.SocialMedia ~ hourswork + covid + age,
  exercise ~ age + ethnicity + hourswork,
  hourswork ~ covid, 
  childcare ~ hourswork + male, 
  partner ~ jobsecurity + childcare + hourswork,
  fatigue ~  age + hourswork + sleep + exercise,
  sleep ~   age + hourswork + exercise + jobsecurity,
  jobsecurity ~ hourswork + buisnessconfidence + covid,
  healthsecurity ~ govconfidence + covid + edu + exercise + age,
  govconfidence ~ covid + pol.orient, 
  buisnessconfidence ~ govconfidence + covid,
  exposure =  "covid",
  outcome =   "k6",
  labels = c(k6 = "Kessler 6", 
             covid = "Covid Timeline", 
             fatigue = "fatigue",
             Hours.SocialMedia = "Hours \n Social Media",
             income = "income",
             age = "age",
             healthsecurity = "health security",
             govconfidence = "government confidence",
             exercise = "exercise",
             sleep = "sleep",
             buisnessconfidence = "buisness confidence",
             childcare = "childcare",
             partner = "partner \n dissatifaction",
             employed = "employed",
             jobsecurity = "job security",
             exercise = "exercise",
             pol.orient = "political orientation",
             edu = "education",
             ethnicity = "ethnicity",
             male = "male",
             hourswork = "hours work"
             )) %>%
  control_for(c("exercise"))

ggdag_adjust(dg, text = FALSE, use_labels = "label", collider_lines = TRUE)
```



## No adjustment set

```{r echo = FALSE}
ggdag::ggdag_adjustment_set(dg, node_size = 14) +
  theme(legend.position = "bottom") + theme_dag_blank()
#  control_for(c("govconfidence"))
#control_for(c("partner"))
#control_for(c("healthsecurity"))
#control_for(c("buisnessconfidence"))
# no to healthsecurity
# no to childcare
# no to partner 
# no to buisness confidence
# no to income
# big no to fatigue!
# big no no to sleep
# yes to exercise! 
```


##  The GGDAG package will find colliders

```{r }
#Colliders
ggdag::ggdag_collider(tidy_k6_dag3,
                      from = "covid",
                      to = "k6") +   theme_dag_blank()
```

## The adjustment set command tells you which variables to include condition 


```{r}
library("ggdag")
d1<-dagify(
  k6  ~ covid + commute + work,
  commute ~ work + covid,
  work ~ covid,
  exposure =  "commute",
  outcome =   "k6",
  labels = c(k6 = "Kessler 6", 
             covid = "Covid Timeline", 
             work = "hours work",
             commute = "hours commute"
             ))

%>%
  control_for(c("covid"))
  
ggdag::ggdag_collider(d1) +   theme_dag_blank()

ggdag::ggdag_adjustment_set(d1, node_size = 14) +
  theme(legend.position = "bottom") + theme_dag_blank()



d2<-dagify(
  k6  ~ covid + commute + work,
  commute ~ work + covid,
  work ~ covid,
  exposure =  "covid",
  outcome =   "k6",
  labels = c(k6 = "Kessler 6", 
             covid = "Covid Timeline", 
             work = "hours work",
             commute = "hours commute"
             ))
ggdag::ggdag_adjustment_set(d2, node_size = 14) +
  theme(legend.position = "bottom") + theme_dag_blank()


####


tidy_k6_dag2 <- dagify(
  k6  ~ covid + income + jobsecurity + age + fatigue +
    childcare + partner + male + exercise + healthsecurity + Hours.SocialMedia + hourswork + hoursfriends,
  income ~ hourswork  + edu + ethnicity + male + hourscommute,
  Hours.SocialMedia ~ hourswork + hoursfriends + age,
  exercise ~ age + ethnicity + hourswork,
  hourscommute ~ covid,
  hourswork ~ covid, 
  childcare ~ hourswork + male, 
  partner ~ jobsecurity + childcare + hourswork,
  fatigue ~  age + hourswork + sleep + exercise,
  sleep ~   age + hourswork + exercise,
  jobsecurity ~  govconfidence,
  healthsecurity ~ govconfidence + edu + exercise + age,
  govconfidence ~  pol.orient, 
  buisnessconfidence ~ govconfidence,
  exposure =  "covid",
  outcome =   "k6",
  labels = c(k6 = "Kessler 6", 
             covid = "Covid Timeline", 
             hourscommute = "hourscommute",
             fatigue = "fatigue",
             Hours.SocialMedia = "Hours \n Social Media",
             income = "income",
             age = "age",
             healthsecurity = "health security",
             govconfidence = "government confidence",
             exercise = "exercise",
             sleep = "sleep",
             buisnessconfidence = "buisness confidence",
             childcare = "childcare",
             partner = "partner \n dissatifaction",
             employed = "employed",
             jobsecurity = "job security",
             exercise = "exercise",
             pol.orient = "political orientation",
             edu = "education",
             ethnicity = "ethnicity",
             male = "male",
             hourswork = "hours work"
             ))%>%
  control_for(c("covid"))
  
ggdag::ggdag_collider(tidy_k6_dag2,
                      from = "hourswork",
                      to = "k6") +   theme_dag_blank()

# graph adjustment sets
ggdag::ggdag_adjustment_set(tidy_k6_dag2, node_size = 14) +
  theme(legend.position = "bottom") + theme_dag_blank()

ggdag_adjust(tidy_k6_dag2, text = TRUE, collider_lines = TRUE)

# no Hours Work! 
# no to Exercise! 


```{r}
# evaluate the gs --> e theory
library("ggdag")
dg <- dagify(
  e  ~ l + rel,
  e ~  gs,
  gs ~ rel + l,
  exposure =  "gs",
  outcome =   "e")

ggdag::ggdag_adjustment_set(dg, node_size = 14) +
  theme(legend.position = "bottom") + theme_dag_blank()
```


```{r}
# evaluate the e --> gs theory
library("ggdag")
dg <- dagify(
  e  ~ l + rel,
  gs ~  e,
  gs ~ rel + l,
  exposure =  "e",
  outcome =   "gs")%>%
  control_for(c("gs"))

ggdag::ggdag_adjustment_set(dg, node_size = 14) +
  theme(legend.position = "bottom") + theme_dag_blank()




dg <- dagify(e  ~ l +  rel,
             gs ~  l + rel,
             e ~ gs,
             exposure =  "gs",
             outcome =   "e")

ggdag_adjust(dg, text = TRUE, collider_lines = TRUE)

ggdag::ggdag_adjustment_set(dg, node_size = 14) +
  theme(legend.position = "bottom") + theme_dag_blank()
ggdag::ggdag_collider(dg) +   theme_dag_blank()

```



# 
# 
# # Internet increase stress
# Hours.Internet_withinM <- lmer(KESSLER6sum ~  Hours.Internet_within  +  (1|Covid_Timeline) + (1|Id),  data = cv)
# plot(ggeffects::ggpredict(Hours.Internet_withinM))
# 
# #
# Hours.SocialMedia_withinM <- lmer(KESSLER6sum ~  logSM_within  +  (1|Covid_Timeline) + (1|Id),  data = cv)
# plot(ggeffects::ggpredict(Hours.SocialMedia_withinM))
# 
# 
# table(cv$Covid_Timeline)
# # trey without Lockdown
# cvSM <- dplyr::filter(cv, Covid_Timeline == "L4_Lockdown_2020")%>%
#   droplevels()
# 
# 
# Hours.SocialMedia_withinM2 <- lm(KESSLER6sum ~  logSM_within + logSM_between,  data = cvSM)
# plot(ggeffects::ggpredict(Hours.SocialMedia_withinM2))
# 
# 
# 
# estimate_contrasts(k6)%>%
#   slice(1:5)
# estimate_means(k6)%>%
#   slice(1:5)
# 
# estimate_contrasts(he2)%>%
#   slice(1:5)
# estimate_means(he2)%>%
#   slice(1:5)
# 
# ### 
# 
# estimate_contrasts(she)
# estimate_means(she)
# 
# estimate_contrasts(he)%>%
#   slice(1:5)
# estimate_means(he)%>%
#   slice(1:5)
# 
# ```

<!-- ```{r} -->
<!-- means <- estimate_means(k6) -->
<!-- means -->
<!-- ggplot(cv, aes(x = Covid_Timeline, y = KESSLER6sum, fill = Covid_Timeline)) + -->
<!--   geom_violin() + -->
<!--   geom_jitter2(width = 0.05, alpha = 0.5) + -->
<!--   geom_line(data = means, aes(y = rate, group = 1), size = 1) + -->
<!--   geom_pointrange(data = means,  -->
<!--                   aes(y = rate, ymin = CI_low, ymax = CI_high), -->
<!--                   size = 1,  -->
<!--                   color = "white") + -->
<!--   theme_modern() -->
<!-- means <- estimate_means(m_fat) -->
<!-- ggplot(cv, aes(x = Covid_Timeline, y = Fatigue_within, fill = Covid_Timeline)) + -->
<!--   geom_violin() + -->
<!--   geom_jitter2(width = 0.05, alpha = 0.5) + -->
<!--   geom_line(data = means, aes(y = Mean, group = 1), size = 1) + -->
<!--   geom_pointrange(data = means,  -->
<!--                   aes(y = Mean, ymin = CI_low, ymax = CI_high), -->
<!--                   size = 1,  -->
<!--                   color = "white") + -->
<!--   theme_modern() -->
<!-- means <- estimate_means(m_relconflict) -->
<!-- ggplot(cvp, aes(x = Covid_Timeline, y = Rel.Conflict_within, fill = Covid_Timeline)) + -->
<!--   geom_violin() + -->
<!--   geom_jitter2(width = 0.05, alpha = 0.5) + -->
<!--   geom_line(data = means, aes(y = Mean, group = 1), size = 1) + -->
<!--   geom_pointrange(data = means,  -->
<!--                   aes(y = Mean, ymin = CI_low, ymax = CI_high), -->
<!--                   size = 1,  -->
<!--                   color = "white") + -->
<!--   theme_modern() -->
<!-- ``` -->
<!-- ```{r} -->
<!-- estimate_contrasts(m_fat)%>% -->
<!--   slice(1:6) -->
<!-- estimate_means(m_fat)%>% -->
<!--   slice(1:6) -->
<!-- ``` -->
<!-- ### -->
<!-- pt1<-d1%>% -->
<!--   tibble::as_tibble(include.rownames = FALSE)%>% -->
<!--   dplyr::slice(n=1:10)%>% -->
<!--   dplyr::select(-CI)%>% -->
<!--   mutate_if(is.numeric, ~round(., 3))%>% -->
<!--   ggpubr::ggtexttable(rows = NULL, -->
<!--                       theme = ttheme("mRed")) -->

<!-- pt1 -->
<!-- bbt18<-bayestestR::mediation(f1,centrality = "mean",ci=.95) # nat, no  FAT  -->


<!-- dm20<-as.data.frame(bbt20S)%>% -->
<!--   dplyr::select(-proportion_mediated)%>% -->
<!--   bayestestR::estimate_density()%>% -->
<!--   plot(labels = FALSE)%>% -->
<!--   ggpar(main = "")#+theme_solarized() -->
<!-- dm20 -->




