---
title: "Longitudinal Effects of Pandemic Distress in New Zealand"
subtitle: "February/March 2020"
author: "Joseph Bulbulia, Psychology, Victoria University"
date: 2020-APRIL-23
bibliography: bibliography.bib
output: 
  ioslides_presentation:
    mainfont: roboto
    incremental: true
    transition: 0
    smaller: true
    css: extra.css
editor_options: 
  markdown: 
    wrap: 72
---



```{r load_libraries, include=FALSE}
# see: https://github.com/rjknell/Ioslides_css
library("tidyverse")
library("easystats")
library("patchwork")
library("kableExtra")
library("ggpubr")
#library("viridis")
#library("wesanderson")
# library("papaja")
library("here")
library("citr")
library("here")
library("brms")
library("rstan")
library("rstanarm")
# library("tidybayes")
library("lubridate")
library("ggdag")
library("viridisLite")
library("bmlm")
library("bayesplot")
library("broom")
library("purrr")
#library("cmdstanr")  #multithreading bayesian models
# rstan options
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_classic())
```



```{r setup, include=FALSE}
# See: https://rstudio-pubs-static.s3.amazonaws.com/27777_55697c3a476640caa0ad2099fe914ae5.html#/
# setup
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE #,
#  layout = "l-body-outset" #,
 # fig.width= 12,
 # fig.height= 10,
#  collapse =TRUE,
#  R.options = list(width = 60)
)

```
```{r cache=TRUE}
# import data
df <- readRDS(here::here("data", "df"))
```

```{r cache = TRUE, include = FALSE}
ord_dates_class <- c(
  "BaseLine_2018_19_w10", 
  "Pre_COVID_2019_w11", 
  "Jan_Feb_2020", 
  "Early_March_2020", 
  "L4_Lockdown_2020",
  "Post_Lockdown_2020")
rm(cv)


cv <- df %>%
  dplyr::filter(YearMeasured == 1) %>%
  dplyr::filter(Wave == 2018 | Wave == 2019) %>%
  dplyr::group_by(Id) %>% filter(n() > 1) %>%
  dplyr::filter(n() != 0) %>%
  dplyr::ungroup(Id) %>%
  dplyr::mutate(Covid_Timeline =
                 # ifelse(
                 # TSCORE %in% 3837:3894,
                 # "Baseling",
                    as.factor(ifelse(
                      TSCORE %in% 3895:3921,
                      "Early_March_2020",
                      ifelse(
                        TSCORE %in% 3921:3954,
                        "L4_Lockdown_2020",
                        ifelse(
                          TSCORE > 3954,
                          "Post_Lockdown_2020",
                          ifelse(
                            TSCORE %in% 3842:3894,
                            "Jan_Feb_2020",
                          ifelse(
                            TSCORE %in% 3665:3842 &
                              Wave == 2019,
                            "Pre_COVID_2019_w11",
                            "BaseLine_2018_19_w10"
                          )
                        )
                      )
                    ) 
                 ) ))%>%
  dplyr::mutate(PrePostCovid =
                  ifelse(
                    TSCORE > 3895, "post_covid",
                    ifelse(
                      TSCORE < 3895 &
                        Wave == 2019,
                      "before_COVID_wave11",
                      "baseline_wave10"
                    )
                  ))%>% 
  dplyr::select(
    TSCORE,
    WSCORE,
    Wave,
    Partner,
    Employed,
    Sat.Government,
    NZ.Business.Conditions,
    NZ.Economic.Situation,
    PrePostCovid,
    Rel.Conflict,
    Rel.Satisfaction,
    Hours.SocialMedia,
    Hours.Exercise,
    Hours.Internet,
    Hours.News,
    Hours.Family,
    Hours.Friends,
    Hours.Housework,
    Hours.Children,
    Hours.Religious,
    Hours.Work,
    Hours.Community,
    Family.Time,
    Community.Time,
    Friends.Time,
    Family.Money,
    Friends.Money,
    Community.Money,
    years,
    Id,
    Parent,
    SWB.SatPWI02, # your health
    Hours.Work,
    Hours.Exercise,
    LIFEMEANING,
    KESSLER6,
    SWB.SatPWI03, # your future security
    #  K6sum,
    KESSLER6sum,
    Age,
    Male,
    Relid,
    Pol.Orient,
    Urban,
    GenCohort,
    Edu,
    YearMeasured,
    Covid_Timeline,
    HLTH.SleepHours,
    HLTH.Fatigue,
    LIFESAT,
    PWI,
    EthnicCats,
    NZdep,
    Partner,
    Pol.Orient,
    Urban,
    Euro,
    Religious,
    NZdep,
    WSCORE,
    Religion.Church,
    Emp.JobSecure,
    Emp.JobSat,
    Emp.JobValued,
    Alcohol.Intensity,
    Alcohol.Frequency
  ) %>%
  dplyr::group_by(Id) %>% filter(n() > 1) %>%
  dplyr::filter(n() != 0) %>%
  dplyr::ungroup(Id) %>%
  dplyr::filter(!is.na(KESSLER6sum),
                !is.na(LIFEMEANING)) %>%
  dplyr::mutate(
    Urban = (Urban),
    Euro = (Euro),
    Religious = as.factor(Religious),
    Your_Health = (SWB.SatPWI02),
    Your_Future_Security = SWB.SatPWI03,
    Covid_Timeline = as.factor(Covid_Timeline)
  ) %>%
  dplyr::mutate(
    WSCORE = as.factor(WSCORE),
    EduC = scale(as.numeric(Edu), scale = F, center = TRUE),
    Sat.Government = scale(Sat.Government),
    AgeDecadeC = scale(Age, scale = F, center = T) / 10,
    Hours.Work10 = as.integer(Hours.Work) / 10,
    Hours.Sleep = as.integer(HLTH.SleepHours),
    Hours.Exercise = as.integer(Hours.Exercise),
    Fatigue = as.integer(HLTH.Fatigue),
    f_s = scale(Fatigue),
    K6sum = as.integer(KESSLER6 * 6),
    LIFEMEANING_S = scale(LIFEMEANING),
    NZdepS = scale(NZdep),
    PolOrientS = scale(Pol.Orient, scale = T, center = T),
    Relid_S = scale(Relid, scale = T, center = T),
    Conservative = Pol.Orient,
    logSM = log(Hours.SocialMedia + 1),
    logINT = log(Hours.Internet + 1),
    logEX = log(Hours.Exercise + 1),
    logWK= log(Hours.Work + 1),
    k6_s = scale(KESSLER6sum),
    Conservative_S = PolOrientS,
    Religion_Church_S = scale(Religion.Church),
    Emp.JobSecure_S = scale(Emp.JobSecure),
    KESSLER6sum = as.integer(KESSLER6sum),
    Alcohol.Intensity_S = scale(Alcohol.Intensity),
    Alcohol.Frequency_S = scale(Alcohol.Frequency),
    Hours.Work = as.integer(Hours.Work),
    Hours.Exercise = as.integer(Hours.Exercise),
    yearS = years - min(years)
  ) %>%
  dplyr::mutate(Covid_Timeline = forcats::fct_relevel(Covid_Timeline, ord_dates_class))

cv <- cbind(cv,
            demean(
              cv,
              select = c(
                "KESSLER6sum",
                "k6_s",
                "logEX",
                "logSM",
                "logINT",
                "logWK",
                "Hours.Sleep",
                "Hours.Work10",
                "Hours.Exercise",
                "Sat.Government",
                "Hours.Children",
                "Hours.Internet",
                "Hours.Friends",
                "Hours.Family",
                "Hours.Religious",
                "Hours.Community",
                "Rel.Satisfaction",
                "Rel.Conflict",
                "Family.Time",
                "Family.Money",
                "Friends.Time",
                "Friends.Money",
                "Community.Time",
                "Community.Money",
                "Fatigue",
                "Alcohol.Intensity",
                "Alcohol.Frequency",
                "NZ.Economic.Situation",
                "Emp.JobSecure",
                "Friends.Time",
                "Family.Time",
                "Community.Time",
                "Hours.SocialMedia",
                "Hours.Internet",
                "Your_Future_Security"
              ),
              group = "Id"
            ))
```

# opening slide


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets


```{r, layout = "l-body-outset"}
mlm_path_plot(xlab = "Stimulus\n(X)",
              mlab = "Organism\n(M)",
              ylab = "Response\n(Y)")
```


## Graph

```{r}
library(tidyverse)
library(patchwork)
p1 <- cv %>%
  ggplot(aes(Covid_Timeline, Hours.Work10)) +
  stat_summary(fun.data = mean_cl_boot, size = 1) +
  geom_point(position = position_jitter(.15, .1), shape = 1, alpha = .01)
p2 <- cv %>%
  ggplot(aes(Covid_Timeline, KESSLER6sum)) +
  stat_summary(fun.data = mean_cl_boot, size = 1) +
  geom_point(position = position_jitter(.15, .1), shape = 1, alpha = .01)
p3 <- cv %>%
  ggplot(aes(Hours.Work10, KESSLER6sum)) +
  geom_point(position = position_jitter(.15, .1), shape = 1, alpha = .01) +
  geom_smooth(method = 'loess')
p1 | p2 | p3
```


## {.fullslide}

```{r pressure}
plot(pressure)
```


## next slide

```{r}
plot(pressure)
```


