---
title: "Longitudinal Anatomy of Covid-19 Distress: For High School Students"
author: "Joseph Bulbulia, Psychology, Victoria University"
date: "2020-APRIL-23"
output:
  ioslides_presentation:
    mainfont: roboto
    incremental: no
    transition: 0
    smaller: no
    widescreen: no
    selfcontained: yes
    css: extra.css
  beamer_presentation:
    incremental: yes
bibliography: bibliography.bib
editor_options:
  markdown:
    wrap: 72
---

```{r load_libraries, include=FALSE}
# see: https://github.com/rjknell/Ioslides_css
library("tidyverse")
library("easystats")
library("patchwork")
library("kableExtra")
library("ggpubr")
#library("viridis")
#library("wesanderson")
# library("papaja")
library("here")
library("citr")
library("here")
library("brms")
library("rstan")
library("rstanarm")
# library("tidybayes")
library("lubridate")
library("ggdag")
library("viridisLite")
library("bmlm")
library("bayesplot")
library("broom")
library("purrr")
library("lme4")
library("ggeffects")
library("tidybayes")
library("glmmTMB")
#library("cmdstanr")  #multithreading bayesian models
# rstan options
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_classic())
```

```{r setup, include=FALSE}
# See: https://rstudio-pubs-static.s3.amazonaws.com/27777_55697c3a476640caa0ad2099fe914ae5.html#/
# setup
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE #,
#  layout = "l-body-outset" #,
 # fig.width= 12,
 # fig.height= 10,
#  collapse =TRUE,
#  R.options = list(width = 60)
)

```

```{r cache=TRUE, echo = FALSE}
# import data
df <- readRDS(here::here("data", "df"))
```

```{r cache = TRUE, echo = FALSE}
ord_dates_class <- c(
  "Baseline", 
  "PreCOVID", 
  "JanFeb", 
  "EarlyMarch", 
  "Lockdown",
  "PostLockdown")

# 3665 days after 30 June 2009 Saturday 13 July 2019
# 3842 days after 30 June 2009 Monday 6 January 2020
# 3895 days after 30 June 2009 Friday 28 February 2020
# 3921 days after 30 June 2009 WED MAR 25th
# 3954 days after 30 June 2009 Monday 27 April 2020
# 3672 days after June 30 2009 Saturday 20 July 2019
```


```{r cache = TRUE, echo = FALSE}
cv <- df %>%
  dplyr::filter(YearMeasured == 1) %>%
  dplyr::filter(Wave == 2018 | Wave == 2019) %>%
  dplyr::group_by(Id) %>% 
  filter(n() > 1) %>%
  dplyr::filter(n() != 0) %>%
  dplyr::ungroup(Id) %>%
  dplyr::mutate(Covid_Timeline =
                    as.factor(ifelse(
                      TSCORE %in% 3896:3921, # feb 29 - march 25th
                      "EarlyMarch",
                      ifelse(
                        TSCORE %in% 3922:3954,
                        "Lockdown", #march 26- Mon 27 April 2020
                        ifelse(
                          TSCORE > 3954, # after april 27th 20202
                          "PostLockdown",
                          ifelse(
                            TSCORE %in% 3842:3895, # jan 6 to feb 28
                            "JanFeb",
                          ifelse(
                            TSCORE %in% 3665:3841 &
                              Wave == 2019,
                            "PreCOVID",
                            "Baseline"  # 3672 TSCORE or  20 July 2019
                          )
                        )
                      )
                    ) 
                 ) ))%>%
  dplyr::mutate(PrePostCovid =
                  ifelse(
                    TSCORE > 3895, "PostLockdown",
                    ifelse(
                      TSCORE < 3895 &
                        Wave == 2019,
                      "PreCOVID",
                      "Baseline"
                    )
                  ))%>% 
  dplyr::group_by(PrePostCovid) %>% 
  filter(n() > 1) %>%
  ungroup() %>% # There is overlap between waves, we only want repeated measures 
  dplyr::select(
    TSCORE,
    WSCORE,
    Wave,
    Partner,
    Employed,
    Sat.Government,
    NZ.Business.Conditions,
    NZ.Economic.Situation,
    PrePostCovid,
    Rel.Conflict,
    Rel.Satisfaction,
    Hours.SocialMedia,
    Hours.Exercise,
    HoursCharity,
    Hours.Internet,
    Hours.News,
    Hours.Family,
    Hours.Friends,
    Hours.Housework,
    Hours.Children,
    Hours.Religious,
    Hours.Work,
    Hours.Commute,
    Hours.TV,
    Hours.CompGames,
    Hours.Community,
    Family.Time,
    Community.Time,
    Friends.Time,
    Family.Money,
    Friends.Money,
    Community.Money,
    years,
    Id,
    Parent,
    SWB.SatPWI02, # your health
    Hours.Work,
    Hours.Exercise,
    LIFEMEANING,
    KESSLER6,
    KESSLER6sum,
    Age,
    Male,
    Relid,
    Pol.Orient,
    Urban,
    GenCohort,
    Edu,
    YearMeasured,
    Covid_Timeline,
    HLTH.SleepHours,
    HLTH.Fatigue,
    LIFESAT,
    PWI,
    EthnicCats,
    NZdep,
    Partner,
    Pol.Orient,
    Urban,
    Euro,
    Religious,
    NZdep,
    WSCORE,
    Religion.Church,
    Emp.JobSecure,
    Emp.JobSat,
    Emp.JobValued,
    Alcohol.Intensity,
    Alcohol.Frequency,
    Your.Future.Security
  ) %>%
  dplyr::group_by(Id) %>% filter(n() > 1) %>%
  dplyr::filter(n() != 0) %>%
  dplyr::ungroup(Id) %>%
  dplyr::mutate(
    Urban = (Urban),
    Euro = (Euro),
    Religious = as.factor(Religious),
    Your_Health = (SWB.SatPWI02),
    Your_Future_Security = Your.Future.Security,
    Covid_Timeline = as.factor(Covid_Timeline)
  ) %>%
  dplyr::mutate(
    WSCORE = as.factor(WSCORE),
    #EduC = scale(as.numeric(Edu), scale = F, center = TRUE),
    Sat.Government = scale(Sat.Government),
   # AgeDecadeC = scale(Age, scale = F, center = T) / 10,
    Hours.Work10 = as.integer(Hours.Work) / 10,
    Hours.Sleep = as.integer(HLTH.SleepHours),
    Hours.Exercise = as.integer(Hours.Exercise),
    Fatigue = as.integer(HLTH.Fatigue),
    K6sum = as.integer(KESSLER6 * 6),
    LIFEMEANING_S = scale(LIFEMEANING),
    NZdepS = scale(NZdep),
    PolOrientS = scale(Pol.Orient, scale = T, center = T),
    Conservative = Pol.Orient,
    logSM = log(Hours.SocialMedia + 1),
    logINT = log(Hours.Internet + 1),
    logEX = log(Hours.Exercise + 1),
    logWK= log(Hours.Work + 1),
    logCT = log(Hours.Commute + 1),
    KESSLER6sum = as.integer(KESSLER6sum),
    Alcohol.Intensity_S = scale(Alcohol.Intensity),
    Alcohol.Frequency_S = scale(Alcohol.Frequency),
    Hours.Work = as.integer(Hours.Work),
    Hours.Exercise = as.integer(Hours.Exercise),
    yearS = years - min(years)
  ) %>%
  dplyr::mutate(Covid_Timeline = forcats::fct_relevel(Covid_Timeline, ord_dates_class))
```

```{r cache = TRUE, echo = FALSE}
# Subset Employed
cvE <- cv%>%
  dplyr::filter(Employed == 1)

# Subset Partner
cvP <- cv%>%
  dplyr::filter(Partner == 1)

# Subset Religious
cvR <- cv%>%
  dplyr::filter(Relid != 0)
```

```{r cache = TRUE, echo = FALSE}
cv <- cbind(cv,
            demean(
              cv,
              select = c(
                "KESSLER6sum",
                "logEX",
                "logSM",
                "logINT",
                "logWK",
                "logCT",
                "Hours.Sleep",
                "Hours.Work10",
                "Hours.Exercise",
                "Sat.Government",
                "Hours.Children",
                "Hours.Internet",
                "Hours.Friends",
                "Hours.Family",
                "Hours.Religious",
                "Hours.Community",
                "Rel.Satisfaction",
                "Rel.Conflict",
                "Family.Time",
                "Family.Money",
                "Friends.Time",
                "Friends.Money",
                "Community.Time",
                "Community.Money",
                "Fatigue",
                "Alcohol.Intensity",
                "Alcohol.Frequency",
                "Emp.JobSecure",
                "Friends.Time",
                "Family.Time",
                "Community.Time",
                "Hours.SocialMedia",
                "Hours.Internet",
                "Your_Future_Security",
                "LIFEMEANING"
              ),
              group = "Id"
            )) 



# Demean employed
# cf <- dplyr::filter(df, Wave == 2019)%>% filter(YearMeasured ==1)
# length(unique(cf$Id))

# test that we only have repeated measures
# test <-cv %>%
#   group_by(Id)%>%
#   count()%>%
#   ungroup() 
```

```{r cache = TRUE}
# covid timeline
# 3665 days after 30 June 2009 Saturday 13 July 2019
# 3842 days after 30 June 2009 Monday 6 January 2020
# 3895 days after 30 June 2009 Friday 28 February 2020
# 3921 days after 30 June 2009 WED MAR 25th
library(lubridate)
library(tidyverse)


carep <- cv %>%
  dplyr::mutate(timeline = make_date(year = 2009, month = 6, day = 30) + TSCORE) %>%
  count(day = floor_date(timeline, "day")) %>%
dplyr::mutate(condition = ifelse(
    day < "2019-06-20",
    "Baseline",
    ifelse(
      day >= "2019-06-20" &
        day < "2020-01-06",
      "PreCOVID",
      ifelse(
        day >= "2020-01-06" & day < "2020-02-29",
        "Jan_Feb",
        ifelse(
          day >= "2020-02-29" & day < "2020-03-25",
          "EarlyMarch",
          ifelse(
            day >= "2020-03-25" &
              day < "2020-04-28",
            "Lockdown",
            "Postlockdown"
            )))))) %>%
  dplyr::mutate(condition = forcats::fct_relevel(condition, ord_dates_class)) %>%
  arrange(day)

# get COVID date
dates_vline0<- as.Date("2018-06-03")
dates_vline1<- as.Date("2019-06-20")
dates_vline2<- as.Date("2020-01-06")
dates_vline3<- as.Date("2020-02-28")
# get data of change of baseline
dates_vline4<- as.Date("2020-03-25")
dates_vline5 <- as.Date("2020-04-27")
dates_vline6 <- as.Date("2020-10-15")
# for line in a graph

# for line in a graph
#
dates_vline10 <- which(carep$day %in% dates_vline0)
dates_vline1b <- which(carep$day %in% dates_vline1)
dates_vline2b <- which(carep$day %in% dates_vline2)
dates_vline3b <- which(carep$day %in% dates_vline3)
dates_vline4b <- which(carep$day %in% dates_vline4)
dates_vline5b <- which(carep$day %in% dates_vline5)
dates_vline6b <- which(carep$day %in% dates_vline6)


tline <- ggplot(carep, aes(day, n)) +
  geom_col(aes(fill = condition)) + scale_x_date(date_labels = "%b/%Y", limits = c(as.Date("2018-06-10"), as.Date("2020-10-15")))  + scale_y_continuous(limits = c(0, 1000))  +
 geom_vline(xintercept = as.numeric(carep$day[dates_vline10]),
             col = "black",
             linetype = "dashed") +
  geom_vline(xintercept = as.numeric(carep$day[dates_vline1b]),
             col = "red",
             linetype = "dashed") +
  geom_vline(xintercept = as.numeric(carep$day[dates_vline2b]),
             col = "red") +
  geom_vline(xintercept = as.numeric(carep$day[dates_vline3b]),
             col = "red",
             linetype = "dashed") +
  geom_vline(xintercept = as.numeric(carep$day[dates_vline4b]),
             col = "red",
             linetype = "dashed") +
    geom_vline(xintercept = as.numeric(carep$day[dates_vline5b]),
             col = "red",
             linetype = "dashed") + 
  xlab("NZAVS Waves 10 and 11 daily counts: repeated measures") + ylab("Count of Responses")  + theme_classic() +   scale_fill_viridis_d() + theme(
    legend.position = "top",
    legend.text = element_text(size = 6),
    legend.title = element_text(color = "Black", size = 8)
  ) +
  annotate(
    "rect",
    xmin = as.Date("2018-01-03"),
    xmax = dates_vline1,
    ymin = 0,
    ymax = 1000,
    alpha = .1,
    fill = "darkblue"
  )  +
  annotate(
    "rect",
    xmin = dates_vline1,
    xmax = dates_vline6,
    ymin = 0,
    ymax = 1000,
    alpha = .001
  ) +
  annotate(
    geom = "curve",
    x = as.Date("2018-07-10"),
    y = 750,
    xend = as.Date("2019-10-15"),
    yend = 800,
    curvature = -.2,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(
    geom = "curve",
    x = as.Date("2018-07-10"),
    y = 750,
    xend = as.Date("2020-01-30"),
    yend = 850,
    curvature = -.2,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(
    geom = "curve",
    x = as.Date("2018-07-10"),
    y = 750,
    xend = as.Date("2020-03-10"),
    yend = 875,
    curvature = -.2,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(
    geom = "curve",
    x = as.Date("2018-07-10"),
    y = 750,
    xend = as.Date("2020-04-10"),
    yend = 900,
    curvature = -.2,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(
    geom = "curve",
    x = as.Date("2018-07-10"),
    y = 750,
    xend = as.Date("2020-06-10"),
    yend = 925,
    curvature = -.2,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate("text",
           x = as.Date("2018-07-01"),
           y = 755,
           label = "0") +  annotate("text",
           x = as.Date("2019-10-25"),
           y = 800,
           label = "1") + 
   annotate("text",
           x = as.Date("2020-02-10"),
           y = 850,
           label = "2") + 
  annotate("text",
           x = as.Date("2020-03-15"),
           y = 875,
           label = "3") +
  annotate("text",
           x = as.Date("2020-04-20"),
           y = 900,
           label = "4") +
  annotate("text",
           x = as.Date("2020-06-10"),
           y = 925,
           label = "5")
```

## Interest

-   How did Covid-19 affected people?
-   What do these effects tell us about human psychology?

## The New Zealand Attitudes and Values Study

-   Planned 20-year longitudinal study, currently in its 12$^{th}$ year.
-   Sample frame drawn randomly from NZ Electoral Roll.
-   Postal questionnaire (coverage; retention \~ 80%)
-   Focus on personality, social attitudes, values, religion,
    meaning-making, perfectionism, virtues, habits, employment,
    experiences of discrimination, physical and psychological health,
    and environmental attitudes ...
-   Current sample contains `36524` unique people, which is $>$ 1% of
    the NZ adult population.
-   Here, *N* = `r  length(unique(cv$Id))` longitudinal participants who responded
    to **both** the 2018/19 and 2019/20 NZAVS waves.

## 

```{r cache = TRUE}
# GRAPH
tline + plot_annotation(title = "NZAVS COVID timeline", 
subtitle = "0(34778) 1.PreCVD(23460) 2.JanFeb(2678) 3.March(2537) 4.LckDwn(1647) 5.PostLD(4456)")
```

# What we did with our time?

## Slept - more

```{r cache=TRUE}
Hours.Sleep <- lmer(Hours.Sleep ~ Covid_Timeline + (1|Id),  cv)
plot(ggeffects::ggpredict(Hours.Sleep, terms = "Covid_Timeline")) 
```

##  Exercised - more

```{r}
Hours.Exercise <- glmer(Hours.Exercise ~ Covid_Timeline + (1|Id), cv, family = "poisson")
plot(ggeffects::ggpredict(Hours.Exercise,  terms = "Covid_Timeline"))
```

## Hours with friends - loss

```{r cache=TRUE}
Hours.Friends <- lmer(Hours.Friends ~ Covid_Timeline + (1|Id),  cv)
plot(ggeffects::ggpredict(Hours.Friends, terms = "Covid_Timeline"))
# check_zeroinflation(Hours.Friends, tolerance = 0.05) ## NEEDS ZERO INFLATION
```

## Hours with family - more

```{r cache=TRUE}
Hours.Family <- lmer(Hours.Family ~ Covid_Timeline + (1|Id),  cv)
plot(ggeffects::ggpredict(Hours.Family, terms = "Covid_Timeline"))
#check_zeroinflation(Hours.Family, tolerance = 0.05)
```

## Hours with community - loss

```{r cache=TRUE}
Hours.Community <- lmer(Hours.Community ~ Covid_Timeline + (1|Id),  cv)
plot(ggeffects::ggpredict(Hours.Community,terms = "Covid_Timeline"), add.data=TRUE, dot.alpha =.05) +   
  scale_y_continuous(trans = 'log2') + labs(subtitle = "log2 y axis")
```

## Religious community - loss

```{r cache=TRUE}
Hours.Religious <- lmer(Hours.Religious ~ Covid_Timeline + (1|Id),  cvR)
plot(ggeffects::ggpredict(Hours.Religious,terms = "Covid_Timeline"))
#check_zeroinflation(Hours.Religious, tolerance = 0.05)
```

## Hours charity - loss

```{r cache=TRUE}
HoursCharity <- glmer(HoursCharity ~ Covid_Timeline + (1|Id), family = "poisson", cv)
plot(ggeffects::ggpredict(HoursCharity, terms = "Covid_Timeline")) 
```



## Hours news - big gain

```{r cache=TRUE}
Hours.News <- glmer(Hours.News ~ Covid_Timeline + (1 | Id),  cv)
plot(ggeffects::ggpredict(Hours.News, terms = "Covid_Timeline"))
```

## Hours TV - yes/Ozark?

```{r cache=TRUE}
Hours.TV <- glmer(Hours.TV ~ Covid_Timeline + (1|Id),  cv)
plot(ggeffects::ggpredict(Hours.TV , terms = "Covid_Timeline"))
```

## Computer games - yes

```{r cache=TRUE}
Hours.CompGames <- lmer(Hours.CompGames ~ Covid_Timeline + (1|Id), cv)
plot(ggeffects::ggpredict(Hours.CompGames , terms = "Covid_Timeline"))
```

## Hours internet - big gain

```{r cache=TRUE}
Hours.Internet <- glmer(Hours.Internet ~ Covid_Timeline + (1|Id),  cv)
plot(ggeffects::ggpredict(Hours.Internet , terms = "Covid_Timeline"))
```

## Hours social media - big gain

```{r cache=TRUE}
Hours.SocialMedia <- glmer(Hours.SocialMedia ~ Covid_Timeline + (1|Id), cv)
plot(ggeffects::ggpredict(Hours.SocialMedia , terms = "Covid_Timeline"))
```

## Hours work - fewer

```{r cache=TRUE}
Hours.Work <- lmer(Hours.Work ~ Covid_Timeline + (1|Id),  cv)
plot(ggeffects::ggpredict(Hours.Work, terms = "Covid_Timeline"))
```

## Hours housework - more

```{r cache=TRUE}
Hours.Housework <- lmer(Hours.Housework ~ Covid_Timeline + (1|Id), cv)
plot(ggeffects::ggpredict(Hours.Housework, terms = "Covid_Timeline"))
```

## Hours commuting - much less

```{r cache=TRUE}
Hours.Commute <- lmer(Hours.Commute ~ Covid_Timeline + (1|Id), cv)

plot(ggeffects::ggpredict(Hours.Commute, terms = "Covid_Timeline"))
```

# Core psycho-physical effects

## Fatigue - huge drop

```{r cache=TRUE}
## MENTAL HEALTH 
Fatigue <- lmer(Fatigue ~  Covid_Timeline + (1 | Id), data = cv)
plot(ggeffects::ggpredict(Fatigue,
                          terms =  "Covid_Timeline"))
```

## Meaning of life - unreliable

```{r cache=TRUE}
LIFEMEANING <- lmer(LIFEMEANING ~  Covid_Timeline + (1|Id), data = cv)
plot(ggeffects::ggpredict(LIFEMEANING,
                          terms =  "Covid_Timeline"))
```

## Sat with gov't - big gain

```{r cache=TRUE}
Sat.Government <- lmer(Sat.Government ~ Covid_Timeline + (1|Id), cv)
plot(ggeffects::ggpredict(Sat.Government,
                          terms =  "Covid_Timeline"))
```

## Future security -  gain > March

```{r cache=TRUE}
Your_Future_Security <- lmer(Your_Future_Security ~ Covid_Timeline + (1|Id), cv)
plot(ggeffects::ggpredict(Your_Future_Security,
                          terms =  "Covid_Timeline"))
```

## Job security - March slide

```{r cache=TRUE}
Emp.JobSecure <- lmer(Emp.JobSecure ~  Covid_Timeline + (1|Id),  data = cvE)
plot(ggeffects::ggpredict(Emp.JobSecure,
                          terms =  "Covid_Timeline"))
```

## Valued by employer - steady

```{r cache=TRUE}
Emp.JobValued <- lmer( Emp.JobValued ~ Covid_Timeline + (1|Id), cv)
plot(ggeffects::ggpredict(Emp.JobValued,
                          terms =  "Covid_Timeline"))
```

## Partner conflict - steady

```{r cache=TRUE}
Rel.Conflict <- lmer(Rel.Conflict ~ Covid_Timeline + (1|Id), cvP)
plot(ggeffects::ggpredict(Rel.Conflict,
                          terms =  "Covid_Timeline"))
```

## Partner satisfaction - steady-ish?

```{r cache=TRUE}
Rel.Satisfaction <- lmer(Rel.Satisfaction ~ Covid_Timeline + (1|Id), cv)
plot(ggeffects::ggpredict(Rel.Satisfaction, terms = "Covid_Timeline"),add.data=TRUE, dot.alpha =.05) 
```

## Business optimism - slide 

```{r cache=TRUE}
NZ.Business.Conditions <- lmer(NZ.Business.Conditions ~ Covid_Timeline + (1|Id), cv)
plot(ggeffects::ggpredict(NZ.Business.Conditions, terms = "Covid_Timeline"))
```

## Economic outlook - slide 

```{r cache=TRUE}
NZ.Economic.Situation <- lmer(NZ.Economic.Situation ~ Covid_Timeline + (1|Id), cv)
plot(ggeffects::ggpredict(NZ.Economic.Situation , terms = "Covid_Timeline"))
```

# Kessler-6 distress

## Kessler-items

during the past 30 days, how often did... 

(a). . . . you feel hopeless;
(b). . . . you feel so depressed that nothing could cheer you up; 
(c). . . . you feel restless or fidgety; 
(d). . . . you feel that everything
was an effort; 
(e). . . . you feel worthless; 
(f). . . you feel
nervous? 

Answers: None of the time; A little of the time; Some of the time;
Most of the time; All of the time."

## Pandemic distress

1.  Distress elevation from SARS-CoV-2 health risks
    [@Qiu2020-qa][@Twenge2020-xc]
2.  Distress elevation from economic downturn [@Twenge2020-xc];
3.  Distress elevation from social isolation [@Van_Bavel2020-po].
4.  Distress buffering from greater institutional trust [@Sibley2020-kp].
5.  Distress buffering from an elevated sense of civic community
    [@Sibley2020-kp].



## Distress by timeline

```{r cache=TRUE}
k6_cv <- glmer(KESSLER6sum ~ Covid_Timeline + (1|Id), cv, family = "poisson")
plot(ggeffects::ggpredict(k6_cv, terms = 
                            c("Covid_Timeline"))) + theme_classic()
```

<!-- ## Estimated means -->

<!-- ```{r cache=TRUE} -->
<!-- modelbased::estimate_means(k6_cv) -->
<!-- ``` -->

## Estimated Contrasts

```{r cache=TRUE}
modelbased::estimate_contrasts(k6_cv)%>%
  slice(1:5)
```


## Distress was all about March!

<!-- ```{r} -->
<!-- cv1 <- cv %>% -->
<!--   dplyr::filter(TSCORE> 3302) -->
<!-- p <- # Date is 15 July 2018 -->
<!--   ggplot(data = cv1, -->
<!--          aes( -->
<!--            x = yearS, -->
<!--            y = KESSLER6sum, -->
<!--            group = Covid_Timeline, -->
<!--            colour = Covid_Timeline -->
<!--          )) + -->
<!--   geom_point(alpha = .01) +  -->
<!--   #geom_line(alpha = .01) + -->
<!--   # stat_summary( -->
<!--   #   aes(group = 1), -->
<!--   #   geom = "point", -->
<!--   #   fun = mean, -->
<!--   #   size = 1, -->
<!--   #   alpha = .01 -->
<!--   # ) +  -->
<!--   scale_fill_viridis_c(option = "plasma") -->

<!-- k6_disc_smooth <- -->
<!--   p + geom_smooth( -->
<!--     aes(group = Covid_Timeline), -->
<!--     method = "lm", -->
<!--     formula = y ~ s(x),  #y ~ bs(x), -->
<!--     se = TRUE -->
<!--   ) + scale_color_viridis_d(option = "plasma")  + theme_classic() + labs("Regression discontinuity model of Wave 11 Covid Timeline")  +   theme( -->
<!--     legend.position = "right", -->
<!--     legend.text = element_text(size = 6), -->
<!--     legend.title = element_text(color = "Black", size = 8) -->
<!--   ) -->

<!-- k6_disc_smooth_points <- p + -->
<!--   geom_smooth() + -->
<!--   theme_classic() +  -->
<!--   scale_color_viridis_d(option = "plasma") +    labs(title = "Regression discontinuity covid timeline (gam smooth)")  +   theme( -->
<!--     legend.position = "right", -->
<!--     legend.text = element_text(size = 6), -->
<!--     legend.title = element_text(color = "Black", size = 8) -->
<!--   ) -->
<!-- k6_disc_smooth_points   -->
<!-- ``` -->

```{r cache=TRUE}
cv2 <- cv %>%
  dplyr::filter(TSCORE> 3842) # Jan62020
np <-
  ggplot(data = cv2,
         aes(
           x = years,
           y = KESSLER6sum,
           group = Covid_Timeline,
           colour = Covid_Timeline
         ))+ scale_fill_viridis_c(option = "plasma")
marlock <- np +
  geom_point(alpha = .03) +
  geom_smooth() +
  theme_classic() + 
  scale_color_viridis_d(option = "plasma") +  
  labs(title = "Regression discontinuity covid timeline reveals stress pulse was prior to lockdown")  +   theme(
    legend.position = "right",
    legend.text = element_text(size = 6),
    legend.title = element_text(color = "Black", size = 8))

marlock + ylab("NZAVS Years Data collection: Jan-6-2020 to Oct-15-2020")
```


# What **buffered** us from distress?

## Not gov't satisfaction

```{r cache = TRUE}
Sat.GovernmentK6 <- glmer(KESSLER6sum ~ Sat.Government_within + Sat.Government_between + (1|Id), cv, family = "poisson")
plot(ggeffects::ggpredict(Sat.GovernmentK6,
                          terms =  c("Sat.Government_within", "Sat.Government_between")), facet=TRUE)
```

## Loss of fatigue = buffer?

```{r cache = TRUE}
library(tidyverse)
library(patchwork)
p1 <- cv %>% 
  ggplot(aes(Covid_Timeline, Fatigue)) +
  stat_summary(fun.data = mean_cl_boot, size = 1) +
  geom_point(position = position_jitter(.15, .1), shape = .5, alpha = .01)+
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
p2 <- cv %>% 
  ggplot(aes(Covid_Timeline, KESSLER6sum)) +
  stat_summary(fun.data = mean_cl_boot, size = 1) +
  geom_point(position = position_jitter(.15, .1), shape = .5, alpha = .01)+
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
p3 <- cv %>% 
  ggplot(aes(Fatigue, KESSLER6sum)) +
  geom_point(position = position_jitter(.15, .1), shape = .5, alpha = .01) +
  stat_smooth(aes(Fatigue, KESSLER6sum), method = "gam")
p1 | p2 | p3
```

## Fatigue counterfactual

```{r cache = TRUE}
FatigueK6 <- glmer(KESSLER6sum ~ Fatigue_within + Fatigue_between + (1|Id), cv, family ="poisson")
plot(ggeffects::ggpredict(FatigueK6,
                          terms =  c("Fatigue_within", "Fatigue_between")))
```

## Existential insecurity?

```{r cache = TRUE}
p7 <- cv %>% 
  ggplot(aes(Covid_Timeline, Your_Future_Security)) +
  stat_summary(fun.data = mean_cl_boot, size = 1) +
  geom_point(position = position_jitter(.15, .1), shape = .5, alpha = .01) + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
p8 <- cv %>% 
  ggplot(aes(Covid_Timeline, KESSLER6sum)) +
  stat_summary(fun.data = mean_cl_boot, size = 1) +
  geom_point(position = position_jitter(.15, .1), shape = .5, alpha = .01) + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
p9 <- cv %>% 
  ggplot(aes(Your_Future_Security, KESSLER6sum)) +
  geom_point(position = position_jitter(.15, .1), shape = .5, alpha = .01) +
  geom_smooth(method = 'loess') 
p7 | p8 | p9
```

## Security counterfactual

```{r, cache = TRUE}
Your_Future_SecurityK6 <- glmer(KESSLER6sum ~ Your_Future_Security_within + Your_Future_Security_between + (1|Id),
                               family = "poisson", cv)
plot(ggeffects::ggpredict(Your_Future_SecurityK6,
                          terms =  c("Your_Future_Security_within", "Your_Future_Security_between")))
```

## Exercise increase?

```{r cache = TRUE}
library(patchwork)
p4 <- cv %>% 
  ggplot(aes(Covid_Timeline, log(Hours.Exercise+1))) +
  stat_summary(fun.data = mean_cl_boot, size = 1) +
  geom_point(position = position_jitter(.15, .1), shape = .5, alpha = .01) + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
p5 <- cv %>% 
  ggplot(aes(Covid_Timeline, KESSLER6sum)) +
  stat_summary(fun.data = mean_cl_boot, size = 1) +
  geom_point(position = position_jitter(.15, .1), shape = .5, alpha = .01) + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
p6 <- cv %>% 
  ggplot(aes(log(Hours.Exercise+1), KESSLER6sum)) +
  geom_point(position = position_jitter(.15, .1), shape = .5, alpha = .01) +
  geom_smooth(method = 'loess') 
p4 | p5 | p6
```

## Exercise counterfactual

```{r  cache = TRUE}
logEXK6 <- glmer(KESSLER6sum ~ logEX_within + logEX_between + (1|Id),
                               family = "poisson", cv)
plot(ggeffects::ggpredict(logEXK6,
                          terms =  c("logEX_within", "logEX_between")))
```

## Mediation Models

-   Manipulate X, measure M and Y
-   Regress M on X; Y on X and M

```{r, layout = "l-body-outset", cache =TRUE}
mlm_path_plot(xlab = "Condition\n(X)",
              mlab = "Mediator\n(M)",
              ylab = "Distress\n(Y)")
```

## Assumptions

-   Y does not affect M
-   No 3rd variable on M to Y relationship
-   M is measured without error
-   Y and M residuals are not correlated [@vuorre2020multilevel]


## Set up

```{r echo = TRUE, eval = FALSE}
path_m <- bf(
  mF ~ x + (1 | c | id)
  )
path_y <- bf(
  y ~ x + mF_w + mF_b +
               (1 | c | id)
  )
m1 <- brm(
  path_m + path_y + set_rescor(FALSE),
  data = datF,
  file = here("models/mediation-k6-covid-fatigue")
)
```


## Fatigue: DAG

```{r}
library(ggdag)
dg <- dagify(k6  ~ fatigue +  covid,
             fatigue ~  sleep + exercise + covid,
             sleep ~ covid,
             exercise ~ covid,
             exposure =  "fatigue",
             outcome =   "k6")
ggdag::ggdag_collider(dg) +   theme_dag_blank()
```

## Adjustment set: Fatigue

```{r}
ggdag::ggdag_adjustment_set(dg, node_size = 14) +
  theme(legend.position = "bottom") + theme_dag_blank()
```

# Mediation: Fatigue

## Model form 
```{r echo = FALSE}
x <-cv$Covid_Timeline
mF <-cv$Fatigue
y<- cv$KESSLER6sum
id <-cv$Id
mF_w <-as.integer(cv$Fatigue_within)
mF_b <-as.integer(cv$Fatigue_between)
datF <-data.frame(x,mF,mF_w,mF_b,y,id)
```

```{r echo = FALSE}
path_m <- bf(
  mF ~ x + (1 | id)
  )
path_y <- bf(
  y ~ x + mF_w + mF_b +
               (1 | id)
  )
f1a <- brm(
  path_m + path_y + set_rescor(FALSE),
  data = datF,
  file = here("models/mediation-k6-covid-fatigueW")
)
```

## Results: fatigue - March

```{r echo=FALSE, cache = FALSE}
post1F <- brms::posterior_samples(f1a)
post_marF <- post1F %>% 
  transmute(
    a = b_mF_xEarly_March_2020,
    b = b_y_mF_w,
    cp = b_y_xEarly_March_2020,
    me = a * b,
    c = cp + me#,
   # pme = me / c
  )
# posterior_summary(post_marF)
```
```{r}
mcmc_intervals(post_marF)
??mcmc_intervals
```

## Results: fatigue - L4

```{r echo=FALSE, cache = TRUE}
## Results: Fatigue Mediation in Lockodown
post_lF <- post1F %>% 
  transmute(
    a = b_mF_xL4_Lockdown_2020,
    b = b_y_mF_w,
    cp = b_y_xL4_Lockdown_2020,
    me = a * b,#+ covab,
    c = cp + me
  )

# posterior_summary(post_lF)
```

```{r echo=FALSE, cache = TRUE}
mcmc_intervals(post_lF)
```

# Mediation: Future Security

## Future Security: DAG

```{r}
library(ggdag)
dg2 <- dagify(k6  ~ FS +  covid,
             FS ~  health + income,
             health ~ covid,
             income ~ covid,
             FS ~ covid,
             exposure =  "FS",
             outcome =   "k6")
ggdag::ggdag_collider(dg2) +   theme_dag_blank()
```

## Adjustment set: Future Security

```{r}
ggdag::ggdag_adjustment_set(dg2, node_size = 14) +
  theme(legend.position = "bottom") + theme_dag_blank()
```

## F.Security - March

```{r}
x <-cv$Covid_Timeline
mFS <-cv$Your_Future_Security
y<- cv$KESSLER6sum
id <-cv$Id
mFS_w <-as.integer(cv$Your_Future_Security_within)
mFS_b <-as.integer(cv$Your_Future_Security_between)
datFS <-data.frame(x,mFS,mFS_w,mFS_b,y,id)
```

```{r echo = FALSE}
path_m <- bf(
  mFS ~ x + 
    (1 |  id)
)
path_y <- bf(
  y ~ x + mFS_w + mFS_b + 
    ( 1 | id)
)
f3 <- brm(
  path_m + path_y + set_rescor(FALSE),
  data = datFS,
  file = here("models/mediation-k6-covid-future-security")
)
post3 <- posterior_samples(f3)
```

```{r}
post_marFS <- post3%>% 
  transmute(
    a = b_mFS_xEarly_March_2020,
    b = b_y_mFS_w,
    cp = b_y_xEarly_March_2020,
    me = a * b,
    c = cp + me,
    pme = me / c
  )
# posterior_summary(post_marFS )
```
```{r}
mcmc_intervals(post_marFS)
```

## F.Security - L4

```{r}
post_lFS <- post3 %>% 
  transmute(
    a = b_mFS_xL4_Lockdown_2020,
    b = b_y_mFS_w,
    cp = b_y_xL4_Lockdown_2020,
    me = a * b,#+ covab,
    c = cp + me 
  )

#posterior_summary(post_lFS )
```
```{r}
mcmc_intervals(post_lFS)
```

#  Mediation:Exercise

## Exercise: DAG

```{r}
library(ggdag)
dg3 <- dagify(k6  ~ exercise +  covid,
             exercise ~  work + freetime + Latent,
             work ~ covid,
             freetime ~ covid,
             latent = "Latent",
             exposure =  "exercise",
             outcome =   "k6")
ggdag::ggdag_collider(dg3) +   theme_dag_blank()
```

## Adjustment set: Exercise

```{r}
ggdag::ggdag_adjustment_set(dg3, node_size = 14) +
  theme(legend.position = "bottom") + theme_dag_blank()
```

## Exercise - March

```{r}
x <-cv$Covid_Timeline
mEX <-cv$logEX
y<- cv$KESSLER6sum
id <-cv$Id
mEX_w <-as.integer(cv$logEX_within)
mEX_b <-as.integer(cv$logEX_between)
datEX <-data.frame(x,mEX,mEX_w,mEX_b,y,id)
```
```{r echo = FALSE}
path_m <- bf(
  mEX ~ x + 
    (1| id)
)
path_y <- bf(
  y ~ x + mEX_w  + mEX_b + 
    ( 1  |  id)
)
f4 <- brm(
  path_m + path_y + set_rescor(FALSE),
  data = datEX,
  file = here("models/mediation-k6-covid-logEX")
)
post4 <- posterior_samples(f4)
```
```{r}
post_marEX <- post4%>% 
  transmute(
    a = b_mEX_xEarly_March_2020,
    b = b_y_mEX_w,
    cp = b_y_xEarly_March_2020,
    me = a * b,
    c = cp + me#,
   # pme = me / c
  )
#posterior_summary(post_marEX)
```
```{r}
mcmc_intervals(post_marEX)
```

## Exercise: L4

```{r}
post_lEX <- post4 %>% 
  transmute(
    a = b_mEX_xL4_Lockdown_2020,
    b = b_y_mEX_w,
    cp = b_y_xL4_Lockdown_2020,
    me = a * b,#+ covab,
    c = cp + me
  )
# posterior_summary(post_lEX)
```
```{r}
mcmc_intervals(post_lEX)
```

## Excercise: March vs. L4

```{r}
h1 <- c(
  a = "mEX_xEarly_March_2020  = 0",
  b = "y_mEX_w = 0",
  cp = "y_xEarly_March_2020 = 0",
  me = "mEX_xL4_Lockdown_2020 * y_mEX_w = 0",
  c = "mEX_xEarly_March_2020 * y_mEX_w + y_xEarly_March_2020 = 0"
)

h2 <- c(
  a = "mEX_xL4_Lockdown_2020  = 0",
  b = "y_mEX_w = 0",
  cp = "y_xL4_Lockdown_2020 = 0",
  me = "mEX_xL4_Lockdown_2020 * y_mEX_w = 0",
  c = "mEX_xL4_Lockdown_2020 * y_mEX_w + y_xL4_Lockdown_2020 = 0"
)

h3 <- c(
  a = "mEX_xL4_Lockdown_2020  < mEX_xEarly_March_2020",
 # b = "y_mEX_w"
  cp = "y_xL4_Lockdown_2020 < y_xEarly_March_2020",
  me = "mEX_xL4_Lockdown_2020 * y_mEX_w < mEX_xEarly_March_2020 * y_mEX_w",
  c = "mEX_xL4_Lockdown_2020 * y_mEX_w + y_xL4_Lockdown_2020 < mEX_xEarly_March_2020 * y_mEX_w + y_xEarly_March_2020"
)
# plot(
#   hypothesis(f4, h1)
# )
# 
# plot(  
#   hypothesis(f4, h2)
# )
#   
plot(
  hypothesis(f4, h3)
)
```

## Future: employer gratitude?

```{r}
Valemployer <- glmer( KESSLER6sum ~ Emp.JobValued + (1|Id), cv, family = "poisson")
plot(ggeffects::ggpredict(Valemployer,
                          terms =  "Emp.JobValued"))
```

## Recap

-   L4-Lockdown eased distress
-   Rest, security, exercise were buffers
-   Relevant for future pandemic planning 
-   contact: joseph.bulbulia@vuw.ac.nz

## Thanks

-   Prof Chris G. Sibley & the NZAVS team
-   Dr.Matti Vuorre (former VUW graduate, now at Oxford) for his
    [workshop](https://mvuorre.github.io/brms-workshop/)
-   NZAVS participants


## Funders {.flexbox .vcenter}
 
Templeton Religion Trust Grant 0196


## Slides here

https://go-bayes.github.io/reports/posts/covid/


# EXTRA SLIDES

## Commute -> Distress: dag

```{r echo = TRUE}
library("ggdag")
d1<-dagify(
  k6  ~ covid + commute + work,
  commute ~ work + covid,
  work ~ covid,
  exposure =  "commute",
  outcome =   "k6",
  labels = c(k6 = "Kessler 6", 
             covid = "Covid Timeline", 
             work = "hours work",
             commute = "hours commute"
             ))
```

## Colliders

```{r}
ggdag::ggdag_collider(d1) +   theme_dag_blank()
```

## Commute -> Distress adjustment

```{r}
ggdag::ggdag_adjustment_set(d1, node_size = 14) +
  theme(legend.position = "bottom") + theme_dag_blank()
```

## Commute and distress

```{r cache=TRUE}
Hours.CommuteK6 <- lmer(KESSLER6sum ~ Covid_Timeline * (logCT_within + logCT_between + logWK_within + logWK_between) +  (1|Id), cv)
plot(ggeffects::ggpredict(Hours.CommuteK6, terms = 
                            c( "logCT_within", "Covid_Timeline")), facet = TRUE) + theme_classic()
```

<!-- ## Note: COVID->DISTRESS -->

<!-- ```{r} -->
<!-- d2 <- dagify( -->
<!--   k6  ~ covid + commute + work, -->
<!--   commute ~ work + covid, -->
<!--   work ~ covid, -->
<!--   exposure =  "covid", -->
<!--   outcome =   "k6", -->
<!--   labels = c( -->
<!--     k6 = "Kessler 6", -->
<!--     covid = "Covid Timeline", -->
<!--     work = "hours work", -->
<!--     commute = "hours commute" -->
<!--   ) -->
<!-- ) -->
<!-- ggdag::ggdag_adjustment_set(d2, node_size = 14) + -->
<!--   theme(legend.position = "bottom") + theme_dag_blank() -->
<!-- ``` -->

## Many causes = many colliders!

```{r}
d3 <- dagify(
  k6  ~ covid + income + jobsecurity + age + fatigue +
    childcare + partner + male + exercise + healthsecurity + Hours.SocialMedia + hourswork + hoursfriends,
  income ~ hourswork  + edu + ethnicity + male + hourscommute,
  Hours.SocialMedia ~ hourswork + hoursfriends + age,
  exercise ~ age + ethnicity + hourswork,
  hourscommute ~ covid,
  hourswork ~ covid, 
  childcare ~ hourswork + male, 
  partner ~ jobsecurity + childcare + hourswork,
  fatigue ~  age + hourswork + sleep + exercise,
  sleep ~   age + hourswork + exercise,
  jobsecurity ~  govconfidence,
  healthsecurity ~ govconfidence + edu + exercise + age,
  govconfidence ~  pol.orient, 
  buisnessconfidence ~ govconfidence,
  exposure =  "covid",
  outcome =   "k6",
  labels = c(k6 = "Kessler 6", 
             covid = "Covid Timeline", 
             hourscommute = "hourscommute",
             fatigue = "fatigue",
             Hours.SocialMedia = "Hours \n Social Media",
             income = "income",
             age = "age",
             healthsecurity = "health security",
             govconfidence = "government confidence",
             exercise = "exercise",
             sleep = "sleep",
             buisnessconfidence = "buisness confidence",
             childcare = "childcare",
             partner = "partner \n dissatifaction",
             employed = "employed",
             jobsecurity = "job security",
             exercise = "exercise",
             pol.orient = "political orientation",
             edu = "education",
             ethnicity = "ethnicity",
             male = "male",
             hourswork = "hours work"
             ))%>%
  control_for(c("covid"))
  
ggdag::ggdag_collider(d3) +   theme_dag_blank()
```

## Covid --> K6: keep it simple.

```{r}
# graph adjustment sets
ggdag::ggdag_adjustment_set(d3, node_size = 14) +
  theme(legend.position = "bottom") + theme_dag_blank()
```


<!-- ## Mediation model: meaning -->

<!-- ```{r echo=FALSE, cache = TRUE} -->

<!-- ## Meaning of life -->

<!-- x <-cv$Covid_Timeline -->

<!-- mLM <-cv$LIFEMEANING -->

<!-- y<- cv$KESSLER6sum -->

<!-- id <-cv$Id -->

<!-- mLM_w <-as.integer(cv$LIFEMEANING_within) -->

<!-- mLM_b <-as.integer(cv$LIFEMEANING_between) -->

<!-- datLM <-data.frame(x,mLM,mLM_w,mLM_b,y,id) -->

<!-- ``` -->

<!-- ```{r echo = FALSE, cache=FALSE} -->

<!-- path_m <- bf( -->

<!--   mLM ~ x +  -->

<!--     (1|  id) -->

<!-- ) -->

<!-- path_y <- bf( -->

<!--   y ~ x + mLM_w + mLM_b + -->

<!--     ( 1  | id) -->

<!-- ) -->

<!-- f7 <- brm( -->

<!--   path_m + path_y + set_rescor(FALSE), -->

<!--   data = datLM, -->

<!--   file = here("models/mediation-k6-covid-lifemeaning.rds") -->

<!-- ) -->

<!-- ``` -->

<!-- ## Results: meaning - early March -->

<!-- ```{r cache = FALSE, echo=FALSE} -->

<!-- library(bayesplot) -->

<!-- postLM <- posterior_samples(f7) -->

<!-- post_marLM <- postLM%>%  -->

<!--   transmute( -->

<!--     a = b_mLM_xEarlyMarch, -->

<!--     b = b_y_mLM_w, -->

<!--     cp = b_y_xEarlyMarch, -->

<!--     me = a * b, -->

<!--     c = cp + me -->

<!--   ) -->

<!-- # -->

<!-- ``` -->

<!-- ## Graph -->

<!-- ```{r cache = FALSE, echo=FALSE} -->

<!-- brms::posterior_summary(post_marLM) -->

<!-- mcmc_intervals(post_marLM) +   -->

<!--   labs( -->

<!--     title = "Meaning of Life mediated distress in March"#, -->

<!--   #  subtitle = "A wide, uncertain interval is spread thin when areas are equal" -->

<!--    ) + scale_x_discrete(limits = c(-1,1)) -->

<!-- ``` -->

<!-- ## Results: meaning - Lockdown -->

<!-- ```{r echo=FALSE, cache = FALSE} -->

<!-- ## Results: Fatigue Mediation in Lockdown -->

<!-- post_LLM <- postLM%>%  -->

<!--   transmute( -->

<!--     a = b_mLM_xLockdown, -->

<!--     b = b_y_mLM_w, -->

<!--     cp = b_y_xLockdown, -->

<!--     me = a * b, -->

<!--     c = cp + me -->

<!--   ) -->

<!-- posterior_summary(post_LLM) -->

<!-- ``` -->

<!-- ## Graph -->

<!-- ```{r echo=FALSE, cache = FALSE} -->

<!-- mcmc_intervals(post_LLM) +  -->

<!--   labs( -->

<!--     title = "Meaning of Life did not meadiate distress during lockdown"#, -->

<!--   #  subtitle = "A wide, uncertain interval is spread thin when areas are equal" -->

<!--    ) + scale_x_discrete(limits = c(-1,1)) -->

<!-- ``` -->

## Bibliography
