au---
title: "NZAVS Sankey Network for Retention "
description: ""
author:
  - name: Joseph Bulbulia
    url: https://josephbulbulia.netlify.app
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: 0000-0002-5861-2056
  - name          : Chris G. Sibley
    affiliation   : School of Psychology, University of Auckland
    orcid_id: 0000-0002-4064-8800
date: 2021-JUL-22
output:
  distill::distill_article:
    self_contained: true
    toc: true
    code_folding: true
---

```{r setup, include=FALSE}
# setup
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  layout = "l-body-outset",
  fig.width = 15,
  fig.height = 15,
  collapse = TRUE,
  R.options = list(width = 60
  )
)
```

```{r libs, include=TRUE}
# packages
library("tidyverse") # data wrangling 
library("here") # setting directories
library("ggplot2") # graph 
library("ggthemes") # themes
library("table1") # tables
library("ggalluvial") # alluvial graphs
```


```{r}
# read data. note that Wave 2011.5 = T035
# sdf <- readRDS(here::here("data", "sdf"))

# First we import the data, and create an indicator for measured/lost/withdrawn.

sampling_data <-
  haven::read_sav(here::here("data", "GraphData2.sav"))
# table(sampling_data$SampleOriginYear) check data

# remove SPSS labels
sampling_data <- haven::zap_formats(sampling_data)
sampling_data <- haven::zap_label(sampling_data)
sampling_data <- haven::zap_widths(sampling_data)
sampling_data <- haven::zap_labels(sampling_data)

# rename Id variable
sampling_data <- sampling_data %>%
  rename(Id = Questionnaire.Num)
str(sampling_data)


# checks
# str(sampling_data)
# table(sampling_data$SampleOriginYear)


## transform data into long form, required for ggalluvial, and rename the waves

inner_join(
  sampling_data  %>%
    dplyr::select(c(
      Id,
      c(
        'T01',
        "T02",
        'T03',
        "T035",
        "T04",
        'T05',
        "T06",
        'T07',
        "T08",
        "T09",
        "T10",
        "T11",
        "T12"
      )
    )) %>%      #~~~~ Left side = date component ~~~~~~~~
    gather(Wave, YearMeasured, -Id) %>%  #~ long form = 1 row per prod per seq   ~
    mutate(
      Wave = recode_factor(
        Wave,
        T01 = "2009",
        T02 = "2010",
        T03 = "2011",
        T035 = "2011.5",
        T04  = "2012",
        T05 = "2013",
        T06 = "2014",
        T07 = "2015",
        T08 = "2016",
        T09 = "2017",
        T10 = "2018",
        T11 = "2019",
        T12 = "2020"
      )
    ) %>%
    arrange(Id),
  sampling_data %>%
    dplyr::select(c(Id, starts_with('SampleOriginYear'))) %>%
    arrange(Id),
) -> sdf

# check data
# head(sdf)

# define sample origin year
sdf <- sdf %>%
  mutate(SampleOriginYear = SampleOriginYear + 2008)

#  Make sample frame into a factor
sdf$SampleOriginYear <- as.factor(sdf$SampleOriginYear)

# Check
# table(sdf$SampleOriginYear)

## Created levels for "missing", "not yet measured" and "deceased"
## then filter "not yet measured"

sdf.0 <- sdf %>%
  mutate(Wave = as.numeric(as.character(Wave))) %>%
  arrange(Wave, Id) %>%
  group_by(Id) %>%
  mutate(first = {
    YearMeasured == 1
  } %>% {
    . * !duplicated(.)
  }) %>%
  mutate(
    value_tmp = if_else(first == 1, Wave, NA_real_),
    firstwave  = mean(value_tmp, na.rm = TRUE) # this is a hack, but works
  ) %>%
  mutate(state  = ifelse(
    YearMeasured == -1,
    "deceased",
    ifelse(
      YearMeasured == 0 & Wave < firstwave,
      "notyetmeasured",
      ifelse(YearMeasured == 0 &
               Wave > firstwave, "missing",
             "measured")
    )
  )) %>%
  dplyr::mutate(Wave = as.factor(Wave)) %>% # return Wave to a factor
  dplyr::select(Wave, Id, state, YearMeasured, SampleOriginYear) %>%
  dplyr::filter(state != "notyetmeasured") %>%
  droplevels() %>%
  arrange(Id, Wave)

# Check
# table(sdf.0$SampleOriginYear)

# This is to create a "recovered" state. Not used but could be useful for modelling recovery:

sdf.01 <- sdf.0 %>%
  group_by(Id) %>%
  mutate(lag_state = dplyr::lag(state, n = 1, default = "init"))

sdf.1 <- sdf.01 %>%
  group_by(Id, Wave) %>%
  mutate(recovered = ifelse(lag_state == "missing" &
                              state == "measured", "recovered", state)) 


# We need to back fill the missing values for our alluvial graph.
# This is OK because a participants original sampling frame does not change. 

ssdf0 <-sdf.1%>%  # Fill missing values for Sample.Frame
  arrange(Id) %>%
  group_by(Id) %>%
  fill(SampleOriginYear)  %>%
  ungroup() 

# now we create the "state_frame" variable
tf <- ssdf0 %>%
  mutate(SampleOriginYear = as.character(SampleOriginYear))

ssdf <- tf %>%
   mutate(state_frame = ifelse(state == "missing", "missing",  
                               ifelse(state == "deceased", "deceased",
                                      SampleOriginYear)))
ssdf.0 <- ssdf %>%
    mutate(state_frame = factor(state_frame))

# check 
# levels(ssdf.0$state_frame)

# next we order the levels of the factor to create a pretty graph 
ssdf.01 <- ssdf.0 %>%
    mutate(state_frame = forcats::fct_relevel(state_frame,
                                              c("2009",
                                                "2010",
                                                "2011",
                                                "2011.5",
                                                "2012",
                                                "2013",
                                                "2014",
                                                "2015",
                                                "2016",
                                                "2017",
                                                "2018",
                                                "2019",
                                                "2020",
                                                "missing",
                                                "deceased" )))

# This is code for the tables: uncomment to run
ssdf.01 <- ssdf.01 %>%
  rename(Recovered = recovered)
# 
# table1::table1( ~ state_frame | Wave, data = ssdf.01, overall = FALSE)
# table1::table1( ~ Recovered | Wave, data = ssdf.01, overall = FALSE)
```



Next we create the alluvial graph for subject within wave x sample frame:


```{r ,fig.height = 20}
# prepare data
datsSF <- ssdf.01 %>%
  group_by(Wave, state_frame, Id) %>%
  summarise(n = n())

# check data
# datsSF

# Graph 

p <- ggplot(
  datsSF,
  aes(
    x = Wave,
    stratum = state_frame,
    alluvium = Id,
    y = n,
    fill = state_frame,
    label = state_frame
  )
) +
  geom_flow() +
  geom_stratum(alpha = .5) +
  geom_text(stat = "stratum", size = 2) +
  guides(color = guide_legend(override.aes = list(size = 20))) +
  scale_x_discrete(position = 'top', expand = c(0, 0)) +
  scale_y_reverse(
    expand = c(0.001, 0.001),
    minor_breaks = seq(0, 70000, by = 1000),
    breaks = seq(0, 70000, by = 5000)
  ) + 
  scale_fill_viridis_d(option = "turbo") +
  ggtitle("NZAVS alluvial retention graph: waves 2009-2020")  +
   theme_bw() +   # other themese below. 
  # theme_wsj() +
  # theme_radar() +
  # theme_solarized() +
  # theme_abyss() +
  # theme_economist() +
  # theme_economist_white() +
  # theme(axis.text = element_text(colour = "blue")) +
  theme(legend.justification = "top") +
  theme(legend.title = element_blank())  # remove legend title

# graph 
p 

# to save file in your directory at correct resolution, uncomment below 
# file <- here("figs", paste("alluvial_highres_turbo_BW", ".png", sep = ""))
# 
# ggsave(
#   file,
#   device = "png",
#   scale = 1,
#   width = 16,
#   height = 9,
#   units = "in",
#   dpi = 300,
#   limitsize = TRUE
# )
```


## Facet graph 


```{r ,fig.height = 20}
# prepare data
ssdf.01
datsSS <- ssdf.01 %>%
  group_by(Wave, state, SampleOriginYear,Id) %>%
  summarise(n = n())


# Graph
ggplot(datsSS,
       aes(
         x = Wave,
         stratum = state,
         alluvium = Id,
         y = n,
         fill = state,
         label = state
       )) +
  scale_x_discrete(expand = c(.1, .1)) +
  geom_flow() +
  geom_stratum(alpha = .5) +
  geom_text(stat = "stratum", size = 2) +
  theme(legend.position = "none") +
  scale_x_discrete(position = 'top') +
    scale_y_reverse(
    expand = c(0.001, 0.001),
    minor_breaks = seq(0, 70000, by = 1000),
    breaks = seq(0, 70000, by = 1000)) +
  facet_grid(SampleOriginYear ~ ., scales = "free", space = "free") +
  theme(strip.text.y = element_text(angle = 0))+
   scale_fill_viridis_d(option="viridis") +
 # scale_fill_viridis_d(option="turbo") + # another option 
  ggtitle("NZAVS alluvial retention graph: waves 2009-2020",
          subtitle  = "Facets are sample frames")  + theme_bw() + 
    theme(legend.title = element_blank())  # remove legend title


# # uncomment to save file 
# 
# file <- here("figs", paste("alluvial_facets_turbo_highres_VIRIDIS_3", ".png", sep = ""))
# 
# ggsave(
#   file,
#   device = "png",
# #  path = here::here("figs", paste("alluvial_highres", ".png", sep = "")),
#   scale = 1,
#   width = 16,
#   height = 9,
#   units = "in",
#   dpi = 300,
#   limitsize = TRUE
# )

# 
# 
# #aug_5_alluvial_missing_fixed_v1_SIMPLE_NO_SAMPLE_FRAMES
# ggplot(datsSS,
#        aes(
#          x = Wave,
#          stratum = state,
#          alluvium = Id,
#          y = n,
#          fill = state,
#          label = state
#        )) +
#   scale_x_discrete(expand = c(.1, .1)) +
#   geom_flow() +
#   geom_stratum(alpha = .5) +
#   geom_text(stat = "stratum", size = 3) +
#   theme(legend.position = "none") +
#   scale_x_discrete(position = 'top') +
#   scale_y_reverse()  + 
#   scale_fill_viridis_d() +
#   ggtitle("NZAVS alluvial retention graph: wave to wave")  + theme_bw()
```

```{r} 
wdatsSF
ggplot(data = wdatsSF,
       aes(x = Wave, 
           y = n, 
           alluvium = state_frame)) +
  geom_alluvium(aes(
    fill = state_frame, 
    colour = state_frame),
                alpha = .75,
                decreasing = F) +
  theme_bw() +
 scale_fill_viridis_d() +
  ggtitle("") + theme_classic()


```



Another method (not working)




```{r}

# https://www.titanwolf.org/Network/q/4343508a-5b1e-4da0-b6e4-0448995f4f91/y

dat <- data.frame(customer = c(rep(c(1, 2), each=3), 3, 3),
              holiday_loc = c("SA", "SA", "AB", "SA", "SA", "SA", "AB", "AB"),
              holiday_num = c(1, 2, 3, 1, 2, 3, 1, 2))
dat_wide <- dat %>%
        spread(key=holiday_num, value=holiday_loc)
dat_wide
# dat
# 
# dat_wide <- dat %>%
#         spread(key=holiday_num, value= "holiday_loc")
# 
# dat_wide

datsSF
dat

links <- 
  dat %>% 
  mutate("source" = paste(holiday_loc, holiday_num, sep = "_")) %>% 
  group_by(customer) %>% 
  arrange(holiday_num) %>% 
  mutate("target" =  lead(source)) %>% 
  ungroup() %>% 
  arrange(customer) %>% 
  filter(!is.na(target)) %>% 
  select(source, target)
links


library(visNetwork)
library(networkD3)

# example
URL <- paste0(
        "https://cdn.rawgit.com/christophergandrud/networkD3/",
        "master/JSONdata/energy.json")
Energy <- jsonlite::fromJSON(URL)

Energy
# Plot
sankeyNetwork(Links = Energy$links, Nodes = Energy$nodes, Source = "source",
             Target = "target", Value = "value", NodeID = "name",
             units = "TWh", fontSize = 12, nodeWidth = 30)


ssdf.01

dat <- data.frame(customer = c(rep(c(1, 2), each=3), 3, 3),
              holiday_loc = c("SA", "SA", "AB", "SA", "SA", "SA", "AB", "AB"),
              holiday_num = c(1, 2, 3, 1, 2, 3, 1, 2))

df <- ssdf.01 %>% 
  group_by(state_frame,SampleOriginYear, Wave) %>%
  summarise(n = n()) %>%
#%>%
#  mutate(freq = n / sum(n)) %>%
  ungroup() %>%
  arrange(SampleOriginYear) 
df

df2 <- ssdf.01 %>% 
  group_by(state_frame, Wave ,SampleOriginYear) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  arrange(SampleOriginYear, Wave, state_frame, n) 

df2
tail(df2)

 links <-df2 %>% 
  mutate("group" = paste(state_frame, Wave, sep = "_")) %>% 
  group_by(SampleOriginYear) %>% 
  arrange(Wave) %>% 
  mutate("target" = Wave) %>%
  mutate("source" =  SampleOriginYearve) %>% 
  ungroup() %>% 
  arrange(SampleOriginYear) %>% 
  filter(!is.na(target)) %>% 
  select(source, target,  n)
 links
# 
# links <- 
#   df2 %>% 
#   mutate("source" = state_frame) %>% 
#   group_by(SampleOriginYear) %>% 
#   arrange(SampleOriginYear) %>% 
#   mutate("target" =  Wave) %>% 
#   ungroup() %>% 
#   arrange(state_frame) %>% 
#   filter(!is.na(target)) %>% 
#   select(source, target, n)

links

# %>%
#   rename( source = state_frame,
#           target = Wave,
#           value = n) %>%
#   arrange(source,target)
# df

df
dat
df



# df <- ssdf %>%
#   group_by(Wave, state_frame) %>%
#   summarise(n = n()) %>%
#   arrange(state_frame,Wave)
# df

# 
# df <- ssdf %>%
#   group_by(state_frame, Wave) %>%
#   summarise(n = n()) %>%
#   arrange(state_frame,Wave)
# df

df

# 
# links <- 
#   df %>% 
#  # mutate("source" = paste(SampleOriginYear, Wave, sep = "_")) %>% 
#   mutate("source" = (SampleOriginYear)) %>% 
#   group_by(Wave) %>% 
#   arrange(state_frame) %>%
#  # mutate("target" =  lead(source)) %>% 
#   mutate("target" =  Wave) %>% 
#   ungroup() %>% 
#   arrange(state_frame) %>% 
#   filter(!is.na(target)) %>% 
#   mutate(value = n) %>%
#   select(source, target, value,Wave, state_frame)
# links
# 
# 
# 
# links <- data.frame(links)
# links

node_names <- factor(sort(unique(c(as.character(links$source)))))
node_names
                                   
nodes <- data.frame(name = node_names)

links <- data.frame(source = match(links$source, node_names) - 1,
                    target = match(links$target, node_names) - 1,
                    value = links$n)
links
nodes

colnames(nodes) <-"name"
nodes
#links
library(networkD3)

links <- links[links$source < links$target, ]

sankeyNetwork(Links = links, Nodes = nodes,
 Source = "source", Target = "target",
 Value = "value", NodeID = "name")
 
# remove cyclical links (source node is downstream from target node)
links <- links[links$source < links$target, ]

sankeyNetwork(Links = links, 
               Nodes = nodes, 
               Source = "source", 
               Target = "target", 
               LinkGroup = "Wave",
               NodeID = "name", 
               Value = "value", 
               fontSize = 25,
              nodeWidth = 10,
              # iterations = 100, 
               sinksRight = T)

 saveNetwork(op, file="nzavs_sankey.html", selfcontained = T)

# forceNetwork(
#   Links = links,
#   Nodes = nodes,
#   Source = "source",
#   Target = "target",
#   Group = "Wave",
#   NodeID = "name",
#   Value = "value",
#   opacity = .8,
#   fontSize = 16,
#   zoom = T
# )

print(df,n=20)


## TRY AGAIN
df
df  <-df %>%
  rename(value = n)

dat_wide <- df2 %>%
        spread(key=Wave, value=n)
dat_wide
print(dat_wide, n = 40)
print(df, n = 40)
df


```





















<!-- ## Appendix Old Analysis -->


<!-- ```{r} -->
<!-- # read data -->
<!-- df <- readRDS(here::here("data", "df")) -->
<!-- df$Relid -->
<!-- # df%>% -->
<!-- #   select(Id,YearMeasured,Sample.Frame,Wave,Religious,Male,Pol.Orient,Age) %>% -->
<!-- #   filter(Id == 11303) -->
<!-- #  -->
<!-- # df %>% -->
<!-- #   filter(Id == 11303) %>% -->
<!-- #   filter(!is.na(.)) -->



<!-- # make sample frame a factor -->
<!-- df$Sample.Frame <- as.factor(df$Sample.Frame) -->

<!-- # year measured codes, 1 = measured, 0 = not measured, -1 = withdrawn or died -->
<!-- dat <- df %>% -->
<!--   select(YearMeasured, Wave, Id, EthnicCats, GenCohort, Male, Sample.Frame) %>% -->
<!--   mutate(Wave = as.numeric(as.character(Wave))) %>% -->
<!--   group_by(Id) %>% -->
<!--   mutate(first = { -->
<!--     YearMeasured == 1 -->
<!--   } %>% { -->
<!--     . * !duplicated(.) -->
<!--   }) %>% -->
<!--   mutate( -->
<!--     value_tmp = if_else(first == 1, Wave, NA_real_), -->
<!--     firstwave  = mean(value_tmp, na.rm = TRUE) # this is a  hack (but works) -->
<!--   ) %>% -->
<!--   mutate(state  = ifelse( -->
<!--     YearMeasured == -1, -->
<!--     "withdrawn", -->
<!--     ifelse( -->
<!--       YearMeasured == 0 & Wave < firstwave, -->
<!--       "notyetmeasured", -->
<!--       ifelse(YearMeasured == 0 & -->
<!--                Wave > firstwave, "lost", -->
<!--              "measured") -->
<!--     ) -->
<!--   )) %>% -->
<!--   ungroup() %>% -->
<!--   dplyr::mutate(Wave = as.factor(Wave)) %>% # return Wave to a factor -->
<!--   dplyr::select(Wave, Id, state, GenCohort, Male, EthnicCats, Sample.Frame) %>% -->
<!--   dplyr::filter(state != "notyetmeasured") %>% -->
<!--   droplevels() -->

<!-- # fill missing values in dataset (when people are not measured all other indicators are "NA") -->

<!-- datt <- dat %>% -->
<!--   group_by(Id) %>% -->
<!--   fill(GenCohort, Male, EthnicCats, Sample.Frame) # fill is a useful function.  -->

<!-- str(datt$Sample.Frame) -->

<!-- datt%>% -->
<!--   select(Id,Sample.Frame) %>% -->
<!--   filter(is.na(Sample.Frame)) -->
<!-- ``` -->


<!-- Let's quickly inspect the data frame: -->

<!-- ```{r} -->
<!-- glimpse(datt) -->
<!-- # looks good -->
<!-- ``` -->

<!-- And let's make sure that we've ordered the id variables correctly for the repeated measures: -->


<!-- ```{r} -->
<!-- head(datt) -->
<!-- ``` -->

<!-- Next, we create a table to indicate the measurement states by waves. Note that the "Overall" column sums over measurements within subjects, not measured subjects.   -->

<!-- ```{r} -->
<!-- table1::table1(~ state + Male + EthnicCats + GenCohort|as.factor(Wave), data = datt) -->
<!-- ``` -->

<!-- How many participants were measured?  -->

<!-- ```{r} -->
<!-- length( unique( datt$Id ) ) -->
<!-- ``` -->




<!-- ## Alluvial Graphs -->

<!-- Next we get the data in to shape for our graphs.  -->


<!-- This is just some data wrangling  -->

<!-- ```{r} -->
<!-- # summarise measurement states by waves -->
<!-- dats <- datt %>% -->
<!--   group_by(Wave, state) %>% -->
<!--   summarise(n = n()) -->

<!-- # check if data is OK for ggalluvial -->
<!-- is_alluvia_form(as.data.frame(dats), axes = 1:2, silent = TRUE) -->
<!-- ``` -->


<!-- ### Overall graph of measured and retained -->



<!-- ### Graph of survival aggregated by waves -->

<!-- ```{r} -->
<!-- ggplot(as.data.frame(dats), -->
<!--        aes(y = n, axis1 = Wave, axis2 = state)) + -->
<!--   geom_alluvium(aes(fill = state), width = 1 / 12) + -->
<!--   geom_stratum(width = 1 / 12, -->
<!--                fill = "black", -->
<!--                color = "grey") + -->
<!--   geom_label(stat = "stratum", aes(label = after_stat(stratum))) + -->
<!--   scale_x_discrete(limits = c("Wave", "State"), -->
<!--                    expand = c(.05, .05)) + -->
<!--   theme( -->
<!--     axis.text.x = element_blank(), -->
<!--     axis.text.y = element_blank(), -->
<!--     axis.ticks = element_blank() -->
<!--   ) + -->
<!--   ylab("") + -->
<!--   scale_fill_brewer(type = "qual", palette = "Set1") + -->
<!--   ggtitle("NZAVS alluvial graph. wave-level: measured, lost, withdrawn") -->
<!-- ``` -->


<!-- ### Graph of survival aggregated by ethnicity and wave -->


<!-- I think we probably want to remove the "Wave" column. This seems cluttered -->

<!-- ```{r} -->

<!-- # prepare data -->
<!-- dats2 <- datt %>% -->
<!--   group_by(Wave) %>% -->
<!--   count(EthnicCats, state) -->

<!-- # graph -->
<!-- ggplot(as.data.frame(dats2), -->
<!--        aes( -->
<!--          y = n, -->
<!--          axis1 = Wave, -->
<!--          axis2 = EthnicCats, -->
<!--          axis3 = state -->
<!--        )) + -->
<!--   geom_alluvium(aes(fill = state)) + -->
<!--   geom_stratum() + -->
<!--   geom_text(stat = "stratum", aes(label = after_stat(stratum))) + -->
<!--   scale_x_discrete(limits = c("Wave", "EthnicCats", "State"), -->
<!--                    expand = c(.2, .05)) + -->
<!--   theme( -->
<!--     axis.text.x = element_blank(), -->
<!--     axis.text.y = element_blank(), -->
<!--     axis.ticks = element_blank() -->
<!--   ) + -->
<!--   ylab("") + -->
<!--   scale_fill_brewer(type = "qual", palette = "Set1") + -->
<!--   ggtitle("NZAVS alluvial graph: ethnicity") -->

<!-- ``` -->


<!-- ### Graph of survival aggregated by gender and ethnicity -->


<!-- Note that gender identification changes within some people (the code throws a warning) -->

<!-- ```{r} -->
<!-- # prepare data -->
<!-- dats3 <- datt %>% -->
<!--   group_by(Male) %>% -->
<!--   count(state, EthnicCats) -->

<!-- # is_alluvia_form(as.data.frame(dats3), axes = 1:2, silent = TRUE) -->
<!-- # dats3 -->

<!-- #graph -->
<!-- ggplot(as.data.frame(dats3), -->
<!--        aes( -->
<!--          y = n, -->
<!--          axis1 = Male, -->
<!--          axis2 = EthnicCats, -->
<!--          axis3 = state -->
<!--        )) + -->
<!--   geom_alluvium(aes(fill = state)) + -->
<!--   geom_stratum() + -->
<!--   geom_text(stat = "stratum", aes(label = after_stat(stratum))) + -->
<!--   scale_x_discrete(limits = c("Male", "EthnicCats", "state"), -->
<!--                    expand = c(.2, .05)) + -->
<!--   theme( -->
<!--     axis.text.x = element_blank(), -->
<!--     axis.text.y = element_blank(), -->
<!--     axis.ticks = element_blank() -->
<!--   ) + -->
<!--   ylab("") + -->
<!--   scale_fill_brewer(type = "qual", palette = "Set1") + -->
<!--   ggtitle("NZAVS alluvial graph: gender x ethnicity") -->

<!-- # warning indicateds category transition (some people changed gender I think??) -->
<!-- ``` -->

<!-- ### Graph of survival of gender (only) -->

<!-- ```{r} -->
<!-- # prepare data -->
<!-- dats4 <- datt %>% -->
<!--   group_by(Male) %>% -->
<!--   count(state) -->

<!-- # dats4 -->

<!-- #graph -->
<!-- ggplot(as.data.frame(dats4), -->
<!--        aes( -->
<!--          y = n, -->
<!--          axis1 = Male, -->
<!--          axis2 = state -->
<!--        )) + -->
<!--   geom_alluvium(aes(fill = state)) + -->
<!--   geom_stratum() + -->
<!--   geom_text(stat = "stratum", aes(label = after_stat(stratum))) + -->
<!--   scale_x_discrete(limits = c("Male","state"), -->
<!--                    expand = c(.2, .05)) + -->
<!--   theme( -->
<!--     axis.text.x = element_blank(), -->
<!--     axis.text.y = element_blank(), -->
<!--     axis.ticks = element_blank() -->
<!--   ) + -->
<!--   ylab("") + -->
<!--   scale_fill_brewer(type = "qual", palette = "Set1") + -->
<!--   ggtitle("NZAVS alluvial graph: gender") -->

<!-- ``` -->


<!-- ### Graph of survival of Cohort and Wave -->

<!-- The illustrates another approach, in which we colour code by the predictor not by the state. -->


<!-- ```{r} -->
<!-- # prepare data -->
<!-- dats5 <- datt %>% -->
<!--   group_by(Wave,GenCohort) %>% -->
<!--   count(state) -->

<!-- # dats4 -->

<!-- #graph -->
<!-- ggplot(as.data.frame(dats5), -->
<!--        aes( -->
<!--          y = n, -->
<!--          axis1 = Wave, -->
<!--          axis2 = GenCohort, -->
<!--          axis3 = state -->
<!--        )) + -->
<!--   geom_alluvium(aes(fill = GenCohort)) + -->
<!--   geom_stratum() + -->
<!--   geom_text(stat = "stratum", aes(label = after_stat(stratum))) + -->
<!--   scale_x_discrete(limits = c("Wave", "GenCohort","state"), -->
<!--                    expand = c(.2, .05)) + -->
<!--   theme( -->
<!--     axis.text.x = element_blank(), -->
<!--     axis.text.y = element_blank(), -->
<!--     axis.ticks = element_blank() -->
<!--   ) + -->
<!--   ylab("") + -->
<!--   scale_fill_brewer(type = "qual", palette = "Set1") + -->
<!--   ggtitle("NZAVS alluvial graph: Cohort x Wave") + theme_classic() -->

<!-- ``` -->


```{r}
yola
# prepare data
sdf.01
datsSS <- sdf.01 %>%
  group_by(Wave, state, SampleOriginYear,Id) %>%
  summarise(n = n())

ggplot(datsSS,
       aes(
         x = Wave,
         stratum = state,
         alluvium = Id,
         y = n,
         fill = state,
         label = state
       )) +
  scale_x_discrete(expand = c(.1, .1)) +
  geom_flow() +
  geom_stratum(alpha = .5) +
  geom_text(stat = "stratum", size = 3) +
  theme(legend.position = "none") +
  ggtitle("NZAVS alluvial graph: within-subject x wave") +
  theme_classic()


ggplot(datsSS,
       aes(
         x = Wave,
         stratum = state,
         alluvium = Id,
         y = n,
         fill = state,
         label = state
       )) +
  scale_x_discrete(expand = c(.1, .1)) +
  geom_flow() +
  geom_stratum(alpha = .5) +
 # geom_text(stat = "stratum", size = 3) +
  theme(legend.position = "none") +
  #   facet_wrap(~ Sample.Frame) +
  facet_grid(SampleOriginYear ~ ., scales = "free") +
    scale_fill_viridis_d() +
  ggtitle("NZAVS alluvial graph: facets are sample frames") +
  theme_classic()


ggplot(datsSS,
       aes(
         x = Wave,
         stratum = state,
         alluvium = Id,
         y = n,
         fill = state,
         label = state
       )) +
  scale_x_discrete(expand = c(.1, .1)) +
  geom_flow() +
  geom_stratum(alpha = .5) +
 # geom_text(stat = "stratum", size = 3) +
  theme(legend.position = "none") +
 # #   facet_wrap(~ Sample.Frame) +
  facet_grid(SampleOriginYear ~ ., scales = "free", space = "free") +
  theme(strip.text.y = element_text(angle = 0))+
    scale_fill_viridis_d() +
  ggtitle("NZAVS alluvial graph: facets: scales and space are free") +
  theme_classic()




ggplot(datsSS,
       aes(
         x = Wave,
         stratum = state,
         alluvium = Id,
         y = n,
         fill = state,
         label = state
       )) +
  scale_x_discrete(expand = c(.1, .1)) +
  geom_flow() +
  geom_stratum(alpha = .5) +
 # geom_text(stat = "stratum", size = 3) +
  theme(legend.position = "none") +
 # #   facet_wrap(~ Sample.Frame) +
  facet_grid(Wave ~ ., scales = "free", space = "free") +
  theme(strip.text.y = element_text(angle = 0))+
    scale_fill_viridis_d() +
  theme_classic()
```



<!-- ## Graph of survival by Sample Frame -->


```{r}
#graph
library(viridisLite)
sdf.01
dats2 <- sdf.01 %>%
  group_by(Wave,SampleOriginYear) %>%
  count(state)


ggplot(as.data.frame(dats2),
       aes(
         y = n,
         axis1 = SampleOriginYear,
         axis2 = Wave,
         axis3 = state
       )) +
  geom_alluvium(aes(fill = SampleOriginYear)) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("SampleOriginYear","Wave", "state"),
                   expand = c(.2, .05)) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  ) +
  ylab("") +
  scale_fill_viridis_d() +
  ggtitle("NZAVS alluvial graph:  Sample.Frame X Wave") + theme_classic()


```


Fill with state

```{r}
#graph
library(viridisLite)
dats2 <- datt %>%
  group_by(Wave,Sample.Frame) %>%
  count(state)


ggplot(as.data.frame(dats2),
       aes(
         y = n,
         axis1 = Sample.Frame,
         axis2 = Wave,
         axis3 = state
       )) +
  geom_alluvium(aes(fill = state)) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Sample.Frame","Wave", "state"),
                   expand = c(.2, .05)) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  ) +
  ylab("") +
  scale_fill_viridis_d() +
  ggtitle("NZAVS alluvial graph:  Sample.Frame X Wave") + theme_classic()

```





<!-- No Wave -->


<!-- ```{r} -->
<!-- #graph -->
<!-- library(viridisLite) -->
<!-- dats2s <- datt %>% -->
<!--   group_by(Sample.Frame) %>% -->
<!--   count(state) -->

<!-- dats2s -->
<!-- ggplot(as.data.frame(dats2s), -->
<!--        aes( -->
<!--          y = n, -->
<!--          axis1 = Sample.Frame, -->
<!--          axis2 = state -->
<!--        )) + -->
<!--   geom_alluvium(aes(fill = state)) + -->
<!--   geom_stratum() + -->
<!--   geom_text(stat = "stratum", aes(label = after_stat(stratum))) + -->
<!--   scale_x_discrete(limits = c("Sample.Frame", "state"), -->
<!--                    expand = c(.2, .05)) + -->
<!--   theme( -->
<!--     axis.text.x = element_blank(), -->
<!--     axis.text.y = element_blank(), -->
<!--     axis.ticks = element_blank() -->
<!--   ) + -->
<!--   ylab("") + -->
<!--   scale_fill_viridis_d() + -->
<!--   ggtitle("NZAVS alluvial graph:  Sample.Frame") + theme_classic() -->

<!-- ``` -->



<!-- Within subject facet by sample frame -->



<!-- ```{r} -->
<!-- # prepare data -->
<!-- datt %>% -->
<!--   group_by(Sample.Frame) %>% -->
<!--   tally() %>% -->
<!--   arrange(desc(n)) %>% -->
<!--   print(n=24) -->


<!-- datsSF <- datt %>% -->
<!--   group_by(Wave, state, Sample.Frame, Id) %>% -->
<!--   summarise(n = n())  -->





<!-- # find NA Sample.Frame -->

<!-- datsSF %>% -->
<!--   filter(is.na(Sample.Frame)) -->


<!-- ``` -->



g_6_alluvial_missing_fixed_v1_SPACE_FREE_FACET_LONG