---
title: "NZAVS Sankey Network for Retention "
description: ""
author:
  - name          : Chris G. Sibley
    affiliation   : School of Psychology, University of Auckland
    orcid_id: 0000-0002-4064-8800
  - name: Joseph Bulbulia
    url: https://josephbulbulia.netlify.app
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: 0000-0002-5861-2056
date: 2021-JUL-22
output:
  distill::distill_article:
    self_contained: true
    toc: true
    code_folding: true
---

```{r setup, include=FALSE}
# setup
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  layout = "l-body-outset",
  fig.width = 12,
  fig.height = 15,
  collapse = TRUE,
  R.options = list(width = 60
  )
)
```

```{r libs, include=FALSE}
#packages
library("tidyverse")
library("here")
library("ggalluvial")
library("ggplot2")
library("table1")
library("rstan")
library("broom")
library("tidybayes")
#library("networkD3")
#library("pmdplyr")
# rstan options
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores ())
```


First we import the data, and create an indicator for measured/lost/withdrawn. 



```{r}
# read data
df <- readRDS(here::here("data", "df"))

# year measured codes, 1 = measured, 0 = not measured, -1 = withdrawn or died
dat <- df %>%
  select(YearMeasured, Wave, Id, EthnicCats, GenCohort, Male) %>%
  mutate(Wave = as.numeric(as.character(Wave))) %>%
  group_by(Id) %>%
  mutate(first = {
    YearMeasured == 1
  } %>% {
    . * !duplicated(.)
  }) %>%
  mutate(
    value_tmp = if_else(first == 1, Wave, NA_real_),
    firstwave  = mean(value_tmp, na.rm = TRUE) # this is a  hack (but works)
  ) %>%
  mutate(state  = ifelse(
    YearMeasured == -1,
    "withdrawn",
    ifelse(
      YearMeasured == 0 & Wave < firstwave,
      "notyetmeasured",
      ifelse(YearMeasured == 0 &
               Wave > firstwave, "lost",
             "measured")
    )
  )) %>%
  ungroup() %>%
  dplyr::mutate(Wave = as.factor(Wave)) %>% # return Wave to a factor
  dplyr::select(Wave, Id, state, GenCohort, Male, EthnicCats) %>%
  dplyr::filter(state != "notyetmeasured") %>%
  droplevels()

# fill missing values in dataset

datt <- dat %>%
  group_by(Id) %>%
  fill(GenCohort, Male, EthnicCats)
```

Let's quickly inspect the data frame

```{r}
head(datt)
```


```{r}
glimpse(datt)
```


Next, we create a table to indicate the measurement states by waves. The "Overall" column sums over measurements within subjects, not measured subjects. 


```{r}
table1::table1(~ state + Male + EthnicCats + GenCohort|as.factor(Wave), data = datt)
```


## Alluvial Graphs

Next we get the data in to shape for our graphs. 



```{r}
# summarise measurement states by waves
dats <- datt %>%
  group_by(Wave, state) %>%
  summarise(n = n())

# check if data is OK for ggalluvial
is_alluvia_form(as.data.frame(dats), axes = 1:2, silent = TRUE)
```


### Overall graph of measured and retained

```{r}
ggplot(data = dats,
       aes(x = Wave, y = n, alluvium = state)) +
  geom_alluvium(aes(fill = state, colour = state),
                alpha = .75,
                decreasing = FALSE) +
  theme_bw() +
  scale_fill_brewer(type = "qual", palette = "Set3") +
  scale_color_brewer(type = "qual", palette = "Set3") +
  ggtitle("") + theme_classic()
```

### Graph of survival aggregated by waves

```{r}
ggplot(as.data.frame(dats),
       aes(y = n, axis1 = Wave, axis2 = state)) +
  geom_alluvium(aes(fill = state), width = 1 / 12) +
  geom_stratum(width = 1 / 12,
               fill = "black",
               color = "grey") +
  geom_label(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Wave", "State"),
                   expand = c(.05, .05)) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  ) +
  ylab("") +
  scale_fill_brewer(type = "qual", palette = "Set1") +
  ggtitle("NZAVS alluvial graph. wave-level: measured, lost, withdrawn")
```


### Graph of survival aggregated by ethnicity and wave


I think we probably want to remove the "Wave" column. This seems cluttered

```{r}

# prepare data
dats2 <- datt %>%
  group_by(Wave) %>%
  count(EthnicCats, state)

# graph
ggplot(as.data.frame(dats2),
       aes(
         y = n,
         axis1 = Wave,
         axis2 = EthnicCats,
         axis3 = state
       )) +
  geom_alluvium(aes(fill = state)) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Wave", "EthnicCats", "State"),
                   expand = c(.2, .05)) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  ) +
  ylab("") +
  scale_fill_brewer(type = "qual", palette = "Set1") +
  ggtitle("NZAVS alluvial graph: ethnicity")

```


### Graph of survival aggregated by gender and ethnicity


Note that gender identification changes within some people (the code throws a warning)

```{r}
# prepare data
dats3 <- datt %>%
  group_by(Male) %>%
  count(state, EthnicCats)

# is_alluvia_form(as.data.frame(dats3), axes = 1:2, silent = TRUE)
# dats3

#graph
ggplot(as.data.frame(dats3),
       aes(
         y = n,
         axis1 = Male,
         axis2 = EthnicCats,
         axis3 = state
       )) +
  geom_alluvium(aes(fill = state)) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Male", "EthnicCats", "state"),
                   expand = c(.2, .05)) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  ) +
  ylab("") +
  scale_fill_brewer(type = "qual", palette = "Set1") +
  ggtitle("NZAVS alluvial graph: male x ethnicity")

# warning indicateds category transition (some people changed gender I think??)
```

### Graph of survival of gender (only)

```{r}
# prepare data
dats4 <- datt %>%
  group_by(Male) %>%
  count(state)

# dats4

#graph
ggplot(as.data.frame(dats4),
       aes(
         y = n,
         axis1 = Male,
         axis2 = state
       )) +
  geom_alluvium(aes(fill = state)) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Male","state"),
                   expand = c(.2, .05)) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  ) +
  ylab("") +
  scale_fill_brewer(type = "qual", palette = "Set1") +
  ggtitle("NZAVS alluvial graph: male (only")

```

###  Subject-level graph by waves

This graphs take a long time to plot

```{r}
# graph takes time to plot
ggplot(dat,
       aes(
         x = Wave,
         stratum = state,
         alluvium = Id,
         fill = state,
         label = state
       )) +
  scale_fill_brewer(type = "qual", palette = "Set2") +
  geom_flow(stat = "alluvium",
            lode.guidance = "frontback",
            color = "darkgray") +
  geom_stratum() +
  theme(legend.position = "bottom") +
  ggtitle("NZAVS alluvial graph, subject-level: measured, lost, withdrawn")
```




