---
title: "NZAVS Sankey Network for Retention "
description: ""
author:
  - name          : Chris G. Sibley
    affiliation   : School of Psychology, University of Auckland
    orcid_id: 0000-0002-4064-8800
  - name: Joseph Bulbulia
    url: https://josephbulbulia.netlify.app
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: 0000-0002-5861-2056
date: 2021-JUL-22
output:
  distill::distill_article:
    self_contained: true
    toc: true
    code_folding: true
---

```{r setup, include=FALSE}
# setup
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  layout = "l-body-outset",
  fig.width = 15,
  fig.height = 15,
  collapse = TRUE,
  R.options = list(width = 60
  )
)
```

```{r libs, include=FALSE}
#packages
library("tidyverse")
library("here")
library("ggalluvial")
library("ggplot2")
library("table1")
```


First we import the data, and create an indicator for measured/lost/withdrawn. Below is some data wrangling.




```{r, eval=FALSE}
Labels:
 value                                        label
   1.1     T01 - Original Random Electoral (40,500)
   1.9                                 T01 - Opt-in
   2.9                                 T02 - Opt-in
   3.1 T03 - Booster Sample - SST Additions (3,208)
   3.2 T03.5 - Pacific Booster (Snowball N Unknown)
   3.8                               T03.5 - Opt-in
   3.9                                 T03 - Opt-in
   4.1   T04 - Weighted Deprivation Booster (9,000)
   4.2      T04 - Random Electoral Booster (20,000)
   4.3    T04 - Auckland Electoral Booster (10,000)
   4.4        T04 - Maori Electoral Booster (9,000)
   4.5 T04 - Christchurch Electoral Booster (2,500)
   4.9                                 T04 - Opt-in
   5.1      T05 - Random Electoral Booster (70,000)
   5.2        T05 - Maori Electoral Booster (1,400)
   5.9                                 T05 - Opt-in
   6.9                                 T06 - Opt-in
   7.9                                 T07 - Opt-in
   8.1      T08 - Random Electoral Booster (80,000)
   8.9                           T08 - Opt-in (T08)
   9.9                                 T09 - Opt-in
  10.1     T10 - Random Electoral Booster (325,000)
  10.9                                 T10 - Opt-in
  11.8      T11 - Opt-in via Facebook Advertisement
  11.9                                 T11 - Opt-in
```


```{r}
# read data
df <- readRDS(here::here("data", "df"))
df$Relid
df%>%
  select(Id,YearMeasured,Sample.Frame,Wave,Religious,Male,Pol.Orient,Age) %>%
  filter(Id == 11303)

df %>%
  filter(Id == 11303) %>%
  filter(!is.na(.))



# make sample frame a factor
df$Sample.Frame <- as.factor(df$Sample.Frame)

# year measured codes, 1 = measured, 0 = not measured, -1 = withdrawn or died
dat <- df %>%
  select(YearMeasured, Wave, Id, EthnicCats, GenCohort, Male, Sample.Frame) %>%
  mutate(Wave = as.numeric(as.character(Wave))) %>%
  group_by(Id) %>%
  mutate(first = {
    YearMeasured == 1
  } %>% {
    . * !duplicated(.)
  }) %>%
  mutate(
    value_tmp = if_else(first == 1, Wave, NA_real_),
    firstwave  = mean(value_tmp, na.rm = TRUE) # this is a  hack (but works)
  ) %>%
  mutate(state  = ifelse(
    YearMeasured == -1,
    "withdrawn",
    ifelse(
      YearMeasured == 0 & Wave < firstwave,
      "notyetmeasured",
      ifelse(YearMeasured == 0 &
               Wave > firstwave, "lost",
             "measured")
    )
  )) %>%
  ungroup() %>%
  dplyr::mutate(Wave = as.factor(Wave)) %>% # return Wave to a factor
  dplyr::select(Wave, Id, state, GenCohort, Male, EthnicCats, Sample.Frame) %>%
  dplyr::filter(state != "notyetmeasured") %>%
  droplevels()

# fill missing values in dataset (when people are not measured all other indicators are "NA")

datt <- dat %>%
  group_by(Id) %>%
  fill(GenCohort, Male, EthnicCats, Sample.Frame) # fill is a useful function. 

str(datt$Sample.Frame)

datt%>%
  select(Id,Sample.Frame) %>%
  filter(is.na(Sample.Frame))


Let's quickly inspect the data frame:

```{r}
glimpse(datt)
# looks good
```

And let's make sure that we've ordered the id variables correctly for the repeated measures:


```{r}
head(datt)
```

Next, we create a table to indicate the measurement states by waves. Note that the "Overall" column sums over measurements within subjects, not measured subjects.  

```{r}
table1::table1(~ state + Male + EthnicCats + GenCohort|as.factor(Wave), data = datt)
```

How many participants were measured? 

```{r}
length( unique( datt$Id ) )
```




## Alluvial Graphs

Next we get the data in to shape for our graphs. 


This is just some data wrangling 

```{r}
# summarise measurement states by waves
dats <- datt %>%
  group_by(Wave, state) %>%
  summarise(n = n())

# check if data is OK for ggalluvial
is_alluvia_form(as.data.frame(dats), axes = 1:2, silent = TRUE)
```


### Overall graph of measured and retained

```{r}
ggplot(data = dats,
       aes(x = Wave, y = n, alluvium = state)) +
  geom_alluvium(aes(fill = state, colour = state),
                alpha = .75,
                decreasing = FALSE) +
  theme_bw() +
  scale_fill_brewer(type = "qual", palette = "Set3") +
  scale_color_brewer(type = "qual", palette = "Set3") +
  ggtitle("") + theme_classic()
```

### Graph of survival aggregated by waves

```{r}
ggplot(as.data.frame(dats),
       aes(y = n, axis1 = Wave, axis2 = state)) +
  geom_alluvium(aes(fill = state), width = 1 / 12) +
  geom_stratum(width = 1 / 12,
               fill = "black",
               color = "grey") +
  geom_label(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Wave", "State"),
                   expand = c(.05, .05)) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  ) +
  ylab("") +
  scale_fill_brewer(type = "qual", palette = "Set1") +
  ggtitle("NZAVS alluvial graph. wave-level: measured, lost, withdrawn")
```


### Graph of survival aggregated by ethnicity and wave


I think we probably want to remove the "Wave" column. This seems cluttered

```{r}

# prepare data
dats2 <- datt %>%
  group_by(Wave) %>%
  count(EthnicCats, state)

# graph
ggplot(as.data.frame(dats2),
       aes(
         y = n,
         axis1 = Wave,
         axis2 = EthnicCats,
         axis3 = state
       )) +
  geom_alluvium(aes(fill = state)) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Wave", "EthnicCats", "State"),
                   expand = c(.2, .05)) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  ) +
  ylab("") +
  scale_fill_brewer(type = "qual", palette = "Set1") +
  ggtitle("NZAVS alluvial graph: ethnicity")

```


### Graph of survival aggregated by gender and ethnicity


Note that gender identification changes within some people (the code throws a warning)

```{r}
# prepare data
dats3 <- datt %>%
  group_by(Male) %>%
  count(state, EthnicCats)

# is_alluvia_form(as.data.frame(dats3), axes = 1:2, silent = TRUE)
# dats3

#graph
ggplot(as.data.frame(dats3),
       aes(
         y = n,
         axis1 = Male,
         axis2 = EthnicCats,
         axis3 = state
       )) +
  geom_alluvium(aes(fill = state)) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Male", "EthnicCats", "state"),
                   expand = c(.2, .05)) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  ) +
  ylab("") +
  scale_fill_brewer(type = "qual", palette = "Set1") +
  ggtitle("NZAVS alluvial graph: gender x ethnicity")

# warning indicateds category transition (some people changed gender I think??)
```

### Graph of survival of gender (only)

```{r}
# prepare data
dats4 <- datt %>%
  group_by(Male) %>%
  count(state)

# dats4

#graph
ggplot(as.data.frame(dats4),
       aes(
         y = n,
         axis1 = Male,
         axis2 = state
       )) +
  geom_alluvium(aes(fill = state)) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Male","state"),
                   expand = c(.2, .05)) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  ) +
  ylab("") +
  scale_fill_brewer(type = "qual", palette = "Set1") +
  ggtitle("NZAVS alluvial graph: gender")

```


### Graph of survival of Cohort and Wave

The illustrates another approach, in which we colour code by the predictor not by the state.


```{r}
# prepare data
dats5 <- datt %>%
  group_by(Wave,GenCohort) %>%
  count(state)

# dats4

#graph
ggplot(as.data.frame(dats5),
       aes(
         y = n,
         axis1 = Wave,
         axis2 = GenCohort,
         axis3 = state
       )) +
  geom_alluvium(aes(fill = GenCohort)) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Wave", "GenCohort","state"),
                   expand = c(.2, .05)) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  ) +
  ylab("") +
  scale_fill_brewer(type = "qual", palette = "Set1") +
  ggtitle("NZAVS alluvial graph: Cohort x Wave") + theme_classic()

```


Here we can focus on ethnicity by wave


```{r}
#graph
dats2 <- datt %>%
  group_by(Wave,EthnicCats) %>%
  count(state)


ggplot(as.data.frame(dats2),
       aes(
         y = n,
         axis1 = Wave,
         axis2 = EthnicCats,
         axis3 = state
       )) +
  geom_alluvium(aes(fill = EthnicCats)) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Wave", "EthnicCats","state"),
                   expand = c(.2, .05)) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  ) +
  ylab("") +
  scale_fill_brewer(type = "qual", palette = "Set1") +
  ggtitle("NZAVS alluvial graph: Ethnic Categories X Wave") + theme_classic()

```



Because the ethnic proportions do not change much by time, we can simplify the graph

```{r}
dats2s <- datt %>%
  group_by(EthnicCats) %>%
  count(state)


ggplot(as.data.frame(dats2s),
       aes(
         y = n,
         axis1 = EthnicCats,
         axis2 = state
       )) +
  geom_alluvium(aes(fill = EthnicCats)) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("EthnicCats","state"),
                   expand = c(.2, .05)) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  ) +
  ylab("") +
  scale_fill_brewer(type = "qual", palette = "Set1") +
  ggtitle("NZAVS alluvial graph: Ethnic Categories") + theme_classic()

```





###  Graph of survival: subject-level by waves

With an individual level graph, I don't think we have have more another variable (aside from wave).

```{r}
# prepare data
datsSS <- dat %>%
  group_by(Wave, state, Id) %>%
  summarise(n = n())

ggplot(datsSS,
       aes(
         x = Wave,
         stratum = state,
         alluvium = Id,
         y = n,
         fill = state,
         label = state
       )) +
  scale_x_discrete(expand = c(.1, .1)) +
  geom_flow() +
  geom_stratum(alpha = .5) +
  geom_text(stat = "stratum", size = 3) +
  theme(legend.position = "none") +
  ggtitle("NZAVS alluvial graph: within-subject x wave") +
  theme_classic()

```



## Graph of survival by Sample Frame


```{r}
#graph
library(viridisLite)
dats2 <- datt %>%
  group_by(Wave,Sample.Frame) %>%
  count(state)


ggplot(as.data.frame(dats2),
       aes(
         y = n,
         axis1 = Sample.Frame,
         axis2 = Wave,
         axis3 = state
       )) +
  geom_alluvium(aes(fill = Sample.Frame)) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Sample.Frame","Wave", "state"),
                   expand = c(.2, .05)) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  ) +
  ylab("") +
  scale_fill_viridis_d() +
  ggtitle("NZAVS alluvial graph:  Sample.Frame X Wave") + theme_classic()

```


Fill with state

```{r}
#graph
library(viridisLite)
dats2 <- datt %>%
  group_by(Wave,Sample.Frame) %>%
  count(state)


ggplot(as.data.frame(dats2),
       aes(
         y = n,
         axis1 = Sample.Frame,
         axis2 = Wave,
         axis3 = state
       )) +
  geom_alluvium(aes(fill = state)) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Sample.Frame","Wave", "state"),
                   expand = c(.2, .05)) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  ) +
  ylab("") +
  scale_fill_viridis_d() +
  ggtitle("NZAVS alluvial graph:  Sample.Frame X Wave") + theme_classic()

```





No Wave


```{r}
#graph
library(viridisLite)
dats2s <- datt %>%
  group_by(Sample.Frame) %>%
  count(state)

dats2s
ggplot(as.data.frame(dats2s),
       aes(
         y = n,
         axis1 = Sample.Frame,
         axis2 = state
       )) +
  geom_alluvium(aes(fill = state)) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Sample.Frame", "state"),
                   expand = c(.2, .05)) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  ) +
  ylab("") +
  scale_fill_viridis_d() +
  ggtitle("NZAVS alluvial graph:  Sample.Frame") + theme_classic()

```



Within subject facet by sample frame



```{r}
# prepare data
datt %>%
  group_by(Sample.Frame) %>%
  tally() %>%
  arrange(desc(n)) %>%
  print(n=24)


datsSF <- datt %>%
  group_by(Wave, state, Sample.Frame, Id) %>%
  summarise(n = n()) 



ggplot(datsSF,
       aes(
         x = Wave,
         stratum = state,
         alluvium = Id,
         y = n,
         fill = state,
         label = state
       )) +
  scale_x_discrete(expand = c(.1, .1)) +
  geom_flow() +
  geom_stratum(alpha = .5) +
 # geom_text(stat = "stratum", size = 3) +
  theme(legend.position = "none") +
  #   facet_wrap(~ Sample.Frame) +
  facet_wrap(~ Sample.Frame, scales = "free") +
    scale_fill_viridis_d() +
  ggtitle("NZAVS alluvial graph: within-subject x wave and sample frame") +
  theme_classic()


# find NA Sample.Frame

datsSF %>%
  filter(is.na(Sample.Frame))


```



