---
title: "NZAVS Sankey Network for Retention "
description: ""
author:
  - name: Joseph Bulbulia
    url: https://josephbulbulia.netlify.app
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: 0000-0002-5861-2056
date: 2021-JUL-22
output:
  distill::distill_article:
    self_contained: true
    toc: true
    code_folding: true
---

```{r setup, include=FALSE}
# setup
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  layout = "l-body-outset",
  fig.width = 12,
  fig.height = 15,
  collapse = TRUE,
  R.options = list(width = 60
  )
)
```

```{r libs, include=FALSE}
library("tidyverse")
library("here")
library("lubridate")
library("ggthemes") #themes
library("ggpubr")
library("viridis")
library("patchwork")
library("ggforce")
library("lme4")
library("ggeffects")
library("sjPlot")
library("kableExtra")
library("brms")
library("rstan")
library("rstanarm")
library("bayesplot")
library("broom")
library("tidybayes")
library("networkD3")
library("pmdplyr")
# rstan options
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores ())
theme_set(theme_classic())
```


First we importa the data, and create a "first_measured" and a "retained" indicator. The years indicator is constructed from the TSCORE variable, which measures when a participant responded. 

We're not using the "sampling frame" variable because there are 17 of these. 

```{r}
df<-readRDS(here::here("data","df"))


# yearmeasured codes, 1 = measured, 0 = not measured, -1 = withdrawn or desceased
dat <- df %>%
  select(YearMeasured, Wave, Id) %>%
  mutate(Wave = as.numeric(as.character(Wave))) %>%
  group_by(Id) %>%
  mutate(first = {
    YearMeasured == 1
  } %>% {
    . * !duplicated(.)
  }) %>%
  mutate(
    value_tmp = if_else(first == 1, Wave, NA_real_),
    firstwave  = mean(value_tmp, na.rm = TRUE)
  ) %>%
  mutate(state  = ifelse(
    YearMeasured == -1,
    "withdrawn",
    ifelse(
      YearMeasured == 0 & Wave < firstwave,
      "notyetmeasured",
      ifelse(YearMeasured == 0 &
               Wave > firstwave, "lost",
             "measured")
    )
  )) %>%
  dplyr::mutate(Wave = as.factor(Wave)) %>% # return Wave to a factor
  dplyr::filter(state != "notyetmeasured") %>%
  droplevels() %>%
  ungroup() %>%
  dplyr::select(Wave,Id,state) 



table1::table1(~ state|as.factor(Wave), data = dat)

head(dat)
```

Get data into shape for sankey


```{r}
dats <- dat %>%
  group_by(Wave, state) %>%
  summarise(n =n())
dats
#nodes <-sjlabelled::get_labels(dats$Wave)

library("ggalluvial")
is_alluvia_form(as.data.frame(dats), axes = 1:2, silent = TRUE)

ggplot(as.data.frame(dats),
       aes(y = n, axis1 = Wave, axis2 = state)) +
  geom_alluvium(aes(fill = state), width = 1/12) +
  geom_stratum(width = 1/12, fill = "black", color = "grey") +
  geom_label(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Wave", "State"), expand = c(.05, .05)) +
  theme(
  axis.text.x = element_blank(),
  axis.text.y = element_blank(),
  axis.ticks = element_blank()) +
  ylab("") +
  scale_fill_brewer(type = "qual", palette = "Set1") +
  ggtitle("NZAVS alluvial graph: measured, lost, withdrawn")
```



Simple plot

```{r}
ggplot(data = dats,
       aes(x = Wave, y = n, alluvium = state)) +
  geom_alluvium(aes(fill = state, colour = state),
                alpha = .75, decreasing = FALSE) +
  theme_bw() +
  scale_fill_brewer(type = "qual", palette = "Set3") +
  scale_color_brewer(type = "qual", palette = "Set3") +
  ggtitle("") + theme_classic()
```


States

```{r}
head(dat)
ggplot(dat,
       aes(x = Wave, stratum = state, alluvium = Id,
           fill = state, label = state)) +
  scale_fill_brewer(type = "qual", palette = "Set2") +
  geom_flow(stat = "alluvium", lode.guidance = "frontback",
            color = "darkgray") +
  geom_stratum() +
  theme(legend.position = "bottom") +
  ggtitle("")
```




```{r}
dats2 <- dat %>%
  group_by(Wave, state, Id) %>%
  summarise(n =n())
dats2


ggplot(dats2,
       aes(x = Wave, stratum = state, alluvium = Id,
           y = n,
           fill = state, label = state)) +
  scale_x_discrete(expand = c(.1, .1)) +
  geom_flow() +
  geom_stratum(alpha = .5) +
  geom_text(stat = "stratum", size = 3) +
  theme(legend.position = "none") +
  ggtitle("")

```


What we want next is to show a sk

## network graph ####
tib1<-bbt1S%>%
  as_tibble()%>%
  mutate(Indirect = rep("SatisfiedBuisness",n()))%>%
  dplyr::select("Indirect","Effect","Estimate")%>%
  slice(1:4)
tib1
str(tib1S)
tib2<-bbt2S%>%
  as_tibble()%>%
  mutate(Indirect = rep("SatisfiedRelationships",n()))%>%
  dplyr::select("Indirect","Effect","Estimate")%>%
  slice(1:4)
tib2
bbt3
tib3<-bbt3S%>%
  as_tibble()%>%
  mutate(Indirect = rep("SatisfiedHealth",n()))%>%
  dplyr::select("Indirect","Effect","Estimate")%>%
  slice(1:4)
tib3
bbt4
tib4<-bbt4S%>%
  as_tibble()%>%
  mutate(Indirect = rep("SatisfiedGovernment",n()))%>%
  dplyr::select("Indirect","Effect","Estimate")%>%
  slice(1:4)
bbt5
tib5<-bbt5S%>%
  as_tibble()%>%
  mutate(Indirect = rep("Sense of Community",n()))%>%
  dplyr::select("Indirect","Effect","Estimate")%>%
  slice(1:4)
bbt6
tib6<-bbt6S%>%
  as_tibble()%>%
  mutate(Indirect = rep("SatisfiedStandardOfLiving",n()))%>%
  dplyr::select("Indirect","Effect","Estimate")%>%
  slice(1:4)
bbt7
tib7<-bbt7S%>%
  as_tibble()%>%
  mutate(Indirect = rep("SocialSupport",n()))%>%
  dplyr::select("Indirect","Effect","Estimate")%>%
  slice(1:4)
bbt8
tib8<-bbt8S%>%
  as_tibble()%>%
  mutate(Indirect = rep("ShortHealth",n()))%>%
  dplyr::select("Indirect","Effect","Estimate")%>%
  slice(1:4)
bbt9
tib9<-bbt9S%>%
  as_tibble()%>%
  mutate(Indirect = rep("SatisfiedFutureSecurity",n()))%>%
  dplyr::select("Indirect","Effect","Estimate")%>%
  slice(1:4)
bbt10
tib10<-bbt10S%>%
  as_tibble()%>%
  mutate(Indirect = rep("SocialBelonging",n()))%>%
  dplyr::select("Indirect","Effect","Estimate")%>%
  slice(1:4)
# 11 na

bbt12
tib12<-bbt12S%>%
  as_tibble()%>%
  mutate(Indirect = rep("SatisfiedEconomy",n()))%>%
  dplyr::select("Indirect","Effect","Estimate")%>%
  slice(1:4)
tib12
bbt13
tib13<-bbt13S%>%
  as_tibble()%>%
  mutate(Indirect = rep("Rumination",n()))%>%
  dplyr::select("Indirect","Effect","Estimate")%>%
  slice(1:4)
tib13
bbt14
tib14<-bbt14S%>%
  as_tibble()%>%
  mutate(Indirect = rep("Fatigue",n()))%>%
  dplyr::select("Indirect","Effect","Estimate")%>%
  slice(1:4)
tib14
bbt15
tib15<-bbt15S%>%
  as_tibble()%>%
  mutate(Indirect = rep("SatisfiedSocialConditions",n()))%>%
  dplyr::select("Indirect","Effect","Estimate")%>%
  slice(1:4)
bbt16
tib16<-bbt16S%>%
  as_tibble()%>%
  mutate(Indirect = rep("Patriotism",n()))%>%
  dplyr::select("Indirect","Effect","Estimate")%>%
  slice(1:4)
bbt17
tib17<-bbt17S%>%
  as_tibble()%>%
  mutate(Indirect = rep("NationalIdentity",n()))%>%
  dplyr::select("Indirect","Effect","Estimate")%>%
  slice(1:4)
bbt18
tib18<-bbt18S%>%
  as_tibble()%>%
  mutate(Indirect = rep("PoliceEngage",n()))%>%
  dplyr::select("Indirect","Effect","Estimate")%>%
  slice(1:4)
bbt19
tib19<-bbt19S%>%
  as_tibble()%>%
  mutate(Indirect = rep("PoliceTrust",n()))%>%
  dplyr::select("Indirect","Effect","Estimate")%>%
  slice(1:4)
bbt20
tib20<-bbt20S%>%
  as_tibble()%>%
  mutate(Indirect = rep("PoliticianTrust",n()))%>%
  dplyr::select("Indirect","Effect","Estimate")%>%
  slice(1:4)





# Only reliable indirect effects
fj<-full_join(tib1,tib2, by = c("Indirect", "Effect", "Estimate"))%>%
  full_join(tib5, by = c("Indirect", "Effect", "Estimate"))%>%
  full_join(tib14, by = c("Indirect", "Effect", "Estimate"))%>%
  full_join(tib15, by = c("Indirect", "Effect", "Estimate"))%>%
  full_join(tib16, by = c("Indirect", "Effect", "Estimate"))%>%
  full_join(tib17, by = c("Indirect", "Effect", "Estimate"))%>%
  full_join(tib18, by = c("Indirect", "Effect", "Estimate"))%>%
  full_join(tib19, by = c("Indirect", "Effect", "Estimate"))%>%
  full_join(tib20, by = c("Indirect", "Effect", "Estimate"))


fj1<-fj%>%
  filter(Effect!="Mediator Effect")
fj1

fj1<-fj1%>% # 
  mutate(Start =  factor(ifelse(Effect == "Direct Effect (ADE)"|Effect == "Total Effect", "LOCKDOWN", Indirect)))%>%
  mutate(End =  factor(ifelse(Effect == "Indirect Effect (ACME)"|Effect == "Total Effect" ,"KESSLER-6 DISTRESS",Indirect)))


fj1
# create source list
sources <- fj1 %>%
  distinct(Start) %>%
  rename(label = Start)
sources

destinations <- fj1 %>%
  distinct(End) %>%
  rename(label = End)
destinations

nodes<-full_join(sources, destinations,by="label")
nodes
nodes <- nodes %>% rowid_to_column("id")
nodes


# edgelist
per_route <- dplyr::select(fj1, Start, End, Estimate,Indirect,Effect)
per_route
edges <- per_route %>% 
  left_join(nodes, by = c("Start" = "label")) %>% 
  rename(from = id)%>%
  rename(weight = Estimate)

edges
edges <- edges %>%
  left_join(nodes, by = c("End" = "label")) %>%
  rename(to = id)
edges
edges <-dplyr::select(edges, from, to, weight,Indirect,Effect,End)

edges
edgesS<-edges%>%
  filter(Effect !="Total Effect")%>%
  mutate(label= round(weight,3),
         arrows = "End")
nodes
nodesS<-nodes%>%
  mutate(group = factor(ifelse(label !="WaveL4"|label !="K6", "mediator","node")))


library(igraph)
routes_igraph <- graph_from_data_frame(d = edgesS, vertices = nodesS, directed = TRUE)
routes_igraph2 <- graph_from_data_frame(d = edges, vertices = nodes, directed = TRUE)
routes_igraph

library(ggraph)
library(tidygraph)
library(seriation)
routes_igraph_tidy <- as_tbl_graph(routes_igraph)
routes_tidy <- tbl_graph(nodes = nodesS, edges = edgesS, directed = TRUE)
routes_tidy
routes_tidy %>% 
  activate(edges) %>% 
  arrange(desc(weight))
#ggraph(routes_tidy) + geom_edge_link() + geom_node_point() + theme_graph()
routes_tidy <- tbl_graph(nodes = nodes, edges = edges, directed = TRUE)
routes_igraph_tidy <- as_tbl_graph(routes_igraph)

routes_tidy %>%
  activate(edgesS) %>%
  arrange(desc(weight))
#ggraph(routes_tidy) + geom_edge_link() + geom_node_point() + theme_graph()

# routes_tidy
# ggraph(routes_tidy, layout = "graphopt") + 
#   geom_node_point() +
#   geom_edge_link(aes(width = weight), alpha = 0.5) + 
#   scale_edge_width(range = c(0.2, 4)) +
#   geom_node_text(aes(label = label), repel = TRUE) +
#   labs(edge_width = "Coefficients") +
#   theme_graph()


## USE THIS 12x 18000
ggraph(routes_igraph2, layout = "fr") + 
  geom_edge_arc2(aes(width = weight,colour = Effect), alpha = .7)+ 
  scale_edge_alpha('Magnitude', guide = 'edge_direction') + 
  scale_edge_size('weight') + 
  scale_edge_width(range = c(0.2, 4)) +
  geom_edge_link(alpha = 1) +geom_node_text(aes(label = label), repel = T) +labs(edge_width = "Coefficients") +
  theme_graph()
newtworkuse#12X800
scaleNetworkgraph0 ## 1000 x 1000
dev.off()
ggraph(routes_igraph2, layout = 'fr') + 
  geom_edge_arc(aes(colour = Effect,alpha = stat(index))) + 
  scale_edge_alpha('Magnitude', guide = 'edge_direction') + 
  scale_edge_size('weight') + 
  scale_edge_width(range = c(0.2, 4)) +
  geom_node_text(aes(label = label), repel = TRUE) +
  geom_edge_link(alpha = 1)+
  theme_graph()
scaleNetworkgraph # 1 x 1
scaleNetworkgraph2

# ggraph(routes_igraph2, layout = 'linear') + 
#   geom_edge_arc2(aes(colour = Effect,alpha = stat(index))) + 
#   scale_edge_alpha('Magnitude', guide = 'edge_direction') + 
#   scale_edge_size('weight') + 
#   scale_edge_width(range = c(0.2, 4)) +
#   geom_node_text(aes(label = label), repel = TRUE) +
#   geom_edge_link(alpha = 0.5)
# scaleNetworkgraph # 1 x 1
# scaleNetworkgraph2


library(visNetwork)
library(networkD3)

visNetwork(nodes, edges)

visNetwork(nodes, edges) %>% 
  visIgraphLayout(layout = "layout_with_fr") %>% 
  visEdges(arrows = "middle")%>%
  visEdges(arrows ="to")%>%
  visOptions(selectedBy = "Indirect")



visNetwork(nodesS, edgesS) %>% 
  visIgraphLayout(layout = "layout_with_fr") %>% 
  visEdges(arrows = "middle")%>%
  visLegend(useGroups = T, addNodes = data.frame(label = "Nodes", shape = "circle"))  


visNetwork(nodes, edges, width = "100%") %>% 
  visEdges(arrows = 'from')


m2
nodes_d3 <- mutate(nodesS, id = id - 1)
edges_d3 <- mutate(edgesS, from = from - 1, to = to - 1)
edges_d3

visNetwork(nodesS, edgesS, width = "100%") %>% 
visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)

visNetwork(nodeS, edgeS, width = "100%") %>% 
visOptions(selectedBy = "group")

visNetwork(nodesS, edgesS, width = "100%") %>% 
  visIgraphLayout(layout = "layout_with_fr") %>% 
  visEdges(arrows = "to") %>% 
   visHierarchicalLayout() 
%>%
  visOptions(highlightNearest = F, nodesIdSelection = R)
%>%
  visSave(file = "network.html")


edges_d3
nodes_d3

forceNetwork(Links = edges_d3, Nodes = nodes_d3, Source = "from", Target = "to", 
             NodeID = "label", 
             Group = "label", 
             Value = "weight", 
             opacity = .8, 
             fontSize = 16, zoom = T)
edgesS
op<-sankeyNetwork(Links = edges_d3, 
              Nodes = nodes_d3, 
              Source = "from", 
              Target = "to", 
              LinkGroup = "Effect",
              NodeID = "label", 
              Value = "weight", 
              fontSize = 16,
             # iterations = 100, 
              sinksRight = T)
op

saveNetwork(op, file="sankey.html", selfcontained = T)
nodes_d3
op<-sankeyNetwork(Links = edges_d3, 
              Nodes = nodes_d3, 
              Source = "from", 
              Target = "to", 
              NodeID = "label",
              Value = "weight",
              units='weight',
              NodeGroup = "group",
              LinkGroup = "Effect",
             # nodePadding = 10, 
              iterations = 1000, 
              sinksRight = T)
op 
sankeyNetworkOutput(op, op,width = "100%", height = "500px")
bbt1$CI_high

### MEDIATOR GRAPH ####
tib1m<-bbt1S%>%
  as_tibble()%>%
  mutate(Indirect = rep("SatisfiedBuisness",n()))%>%
  dplyr::select("Indirect","Effect","Estimate","CI_low","CI_high")%>%
  slice(3)
tib1m

tib2m<-bbt2S%>%
  as_tibble()%>%
  mutate(Indirect = rep("SatisfiedRelationships",n()))%>%
  dplyr::select("Indirect","Effect","Estimate","CI_low","CI_high")%>%
  slice(3)

tib3m<-bbt3S%>%
  as_tibble()%>%
  mutate(Indirect = rep("SatisfiedHealth",n()))%>%
  dplyr::select("Indirect","Effect","Estimate","CI_low","CI_high")%>%
  slice(3)

tib4m<-bbt4S%>%
  as_tibble()%>%
  mutate(Indirect = rep("SatisfiedGovernment",n()))%>%
  dplyr::select("Indirect","Effect","Estimate","CI_low","CI_high")%>%
  slice(3)

tib5m<-bbt5S%>%
  as_tibble()%>%
  mutate(Indirect = rep("Sense of Community",n()))%>%
  dplyr::select("Indirect","Effect","Estimate","CI_low","CI_high")%>%
  slice(3)

tib6m<-bbt6S%>%
  as_tibble()%>%
  mutate(Indirect = rep("SatisfiedStandardOfLiving",n()))%>%
  dplyr::select("Indirect","Effect","Estimate","CI_low","CI_high")%>%
  slice(3)

tib7m<-bbt7S%>%
  as_tibble()%>%
  mutate(Indirect = rep("SocialSupport",n()))%>%
  dplyr::select("Indirect","Effect","Estimate","CI_low","CI_high")%>%
  slice(3)
tib8m<-bbt8S%>%
  as_tibble()%>%
  mutate(Indirect = rep("ShortHealth",n()))%>%
  dplyr::select("Indirect","Effect","Estimate","CI_low","CI_high")%>%
  slice(3)

tib9m<-bbt9S%>%
  as_tibble()%>%
  mutate(Indirect = rep("SatisfiedFutureSecurity",n()))%>%
  dplyr::select("Indirect","Effect","Estimate","CI_low","CI_high")%>%
  slice(3)

tib10m<-bbt10S%>%
  as_tibble()%>%
  mutate(Indirect = rep("SocialBelonging",n()))%>%
  dplyr::select("Indirect","Effect","Estimate","CI_low","CI_high")%>%
  slice(3)
# 11 na

tib12m<-bbt12S%>%
  as_tibble()%>%
  mutate(Indirect = rep("SatisfiedEconomy",n()))%>%
  dplyr::select("Indirect","Effect","Estimate","CI_low","CI_high")%>%
  slice(3)
tib13m<-bbt13S%>%
  as_tibble()%>%
  mutate(Indirect = rep("Rumination",n()))%>%
  dplyr::select("Indirect","Effect","Estimate","CI_low","CI_high")%>%
  slice(3)

tib14m<-bbt14S%>%
  as_tibble()%>%
  mutate(Indirect = rep("Fatigue",n()))%>%
  dplyr::select("Indirect","Effect","Estimate","CI_low","CI_high")%>%
  slice(3)

tib15m<-bbt15S%>%
  as_tibble()%>%
  mutate(Indirect = rep("SatisfiedSocialConditions",n()))%>%
  dplyr::select("Indirect","Effect","Estimate","CI_low","CI_high")%>%
  slice(3)

tib16m<-bbt16S%>%
  as_tibble()%>%
  mutate(Indirect = rep("Patriotism",n()))%>%
  dplyr::select("Indirect","Effect","Estimate","CI_low","CI_high")%>%
  slice(3)

tib17m<-bbt17S%>%
  as_tibble()%>%
  mutate(Indirect = rep("NationalIdentity",n()))%>%
  dplyr::select("Indirect","Effect","Estimate","CI_low","CI_high")%>%
  slice(3)

tib18m<-bbt18S%>%
  as_tibble()%>%
  mutate(Indirect = rep("PoliceEngage",n()))%>%
  dplyr::select("Indirect","Effect","Estimate","CI_low","CI_high")%>%
  slice(3)

tib19m<-bbt19S%>%
  as_tibble()%>%
  mutate(Indirect = rep("PoliceTrust",n()))%>%
  dplyr::select("Indirect","Effect","Estimate","CI_low","CI_high")%>%
  slice(3)

tib20m<-bbt20S%>%
  as_tibble()%>%
  mutate(Indirect = rep("PoliticianTrust",n()))%>%
  dplyr::select("Indirect","Effect","Estimate","CI_low","CI_high")%>%
  slice(3)
tib20m

mj
## Mediator 
mj<-full_join(tib1m,tib2m, by = c("Indirect","Effect","Estimate","CI_low","CI_high"))%>%
  full_join(tib3m,by = c("Indirect","Effect","Estimate","CI_low","CI_high"))%>%
  full_join(tib4m,by = c("Indirect","Effect","Estimate","CI_low","CI_high"))%>%
  full_join(tib5m, by = c("Indirect", "Effect", "Estimate","CI_low","CI_high"))%>%
  full_join(tib6m, by = c("Indirect", "Effect", "Estimate","CI_low","CI_high"))%>%
  full_join(tib7m, by = c("Indirect", "Effect", "Estimate","CI_low","CI_high"))%>%
  full_join(tib8m, by = c("Indirect", "Effect", "Estimate","CI_low","CI_high"))%>%
  full_join(tib9m, by = c("Indirect", "Effect", "Estimate","CI_low","CI_high"))%>%
  full_join(tib10m, by = c("Indirect", "Effect", "Estimate","CI_low","CI_high"))%>%
  full_join(tib12m, by = c("Indirect", "Effect", "Estimate","CI_low","CI_high"))%>%
  full_join(tib13m, by = c("Indirect", "Effect", "Estimate","CI_low","CI_high"))%>%
  full_join(tib14m, by = c("Indirect", "Effect", "Estimate","CI_low","CI_high"))%>%
  full_join(tib15m, by = c("Indirect", "Effect", "Estimate","CI_low","CI_high"))%>%
  full_join(tib16m, by = c("Indirect", "Effect", "Estimate","CI_low","CI_high"))%>%
  full_join(tib17m, by = c("Indirect", "Effect", "Estimate","CI_low","CI_high"))%>%
  full_join(tib18m, by = c("Indirect", "Effect", "Estimate","CI_low","CI_high"))%>%
  full_join(tib19m, by = c("Indirect", "Effect", "Estimate","CI_low","CI_high"))%>%
  full_join(tib20m, by = c("Indirect", "Effect", "Estimate","CI_low","CI_high"))%>%
  dplyr::mutate(Dimension = factor(ifelse(Indirect =="Fatigue"|Indirect =="Rumination"|Indirect =="ShortHealth"|Indirect =="SatisfiedHealth", "Health", ifelse(Indirect =="SatisfiedEconomy"|Indirect =="SatisfiedBuisness"|Indirect =="SatisfiedStandardOfLiving"|Indirect =="SatisfiedFutureSecurity", "Economy",ifelse(Indirect =="SatisfiedGovernment"|Indirect =="PoliceEngage"|Indirect =="PoliceTrust"|Indirect =="PoliticianTrust", "Institutional Trust",ifelse(Indirect =="Sense of Community"|Indirect =="SatisfiedSocialConditions"|Indirect =="Patriotism"|Indirect =="NationalIdentity", "Civic Community",ifelse(Indirect =="SocialSupport"|Indirect =="SatisfiedRelationships"|Indirect =="SocialBelonging", "Relationships","Other")))))))%>%
  dplyr::mutate(AffectedDistress = factor(ifelse(Indirect =="Fatigue"|Indirect =="SatisfiedBuisness"|Indirect =="SatisfiedRelationships"|Indirect =="PoliceEngage"|Indirect =="PoliticianTrust"|Indirect =="PoliceTrust"|Indirect =="Sense of Community"|Indirect =="SatisfiedSocialConditions"|Indirect =="Patriotism"|Indirect =="NationalIdentity", "Affected Distress","Not Affected Distress")))



mj$Dimensions=  factor(mj$Dimension, levels=c('Health',"Economy","Relationships","Institutional Trust",'Civic Community',"Other"))

library(gghighlight)
medplot<-ggplot(aes(x=Indirect, y=Estimate, ymin=CI_low, ymax=CI_high), data=mj, group=Changed)+
  geom_point(alpha=1, aes(colour=AffectedDistress)) +   geom_linerange(alpha=1, aes(colour=AffectedDistress)) + facet_wrap(~Dimensions,scales="free_x") +labs(x="", y="Effects on Distress of 1 SD increase") + theme_bw()  + theme(axis.text.x = element_text(angle = 45,hjust=1)) + ggtitle("Estimated Effects of +1 Standard Devition Increase in Mediators on (log) Kessler-6 Psychological Distress")  

medplot


# medplot<-ggplot(aes(x=Indirect, y=Estimate, ymin=CI_low, ymax=CI_high), data=mj)+
#   geom_point(alpha=1, aes(colour=Dimensions)) +   geom_linerange(alpha=1, aes(colour=Dimensions)) + facet_wrap(~Dimension_f,scales="free_x") +labs(x="", y="Mediation Effects on Distress for 1 SD increase") + theme_bw()  + theme(axis.text.x = element_text(angle = 45,hjust=1)) + ggtitle("Estimated Effects of +1 Standard Devition Increase in Mediators on (log) Kessler-6 Psychological Distress")
# medplot
# 
