---
title: "Attitudes to Muslims in New Zealand"
description: |
author:
  - name: Joseph Bulbulia
    url: https://josephbulbulia.netlify.app
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: 0000-0002-5861-2056
date: 2021-FEB-28
output:
  distill::distill_article:
    self_contained: false
    toc: true
bibliography: bib.bib
---

<!-- --- -->
<!-- title: "Time and Age Confounding in Panel Studies" -->
<!-- author: "Joseph Bulbulia" -->
<!-- date: "`r Sys.Date()`" -->
<!-- output: -->
<!--   tufte::tufte_html: -->
<!--     tufte_variant: "envisioned" -->
<!--     citation_package: natbib -->
<!-- bibliography: bib.bib -->
<!-- link-citations: yes -->
<!-- --- -->


```{r setup, include=FALSE}
## TUFTE WEBSITE: http://motioninsocial.com/tufte/
# invalidate cache when the tufte version changes
# knitr::opts_chunk$set(cache.extra = packageVersion('tufte'),
#                       message=FALSE, 
#                       warning=FALSE,
#                       collapse =TRUE,
#                       echo=FALSE)
# options(htmltools.dir.version = FALSE)
# 
knitr::opts_chunk$set(message=FALSE,
                      warning=FALSE,
                      collapse =TRUE,
                      echo=FALSE)
```
```{r, include=FALSE}
library("tidyverse")
library("here")
library("equatiomatic")
library("lubridate")
library("ggplot2")
library("ggthemes") #themes
library("ggpubr")
library("viridis")
library("patchwork")
library("ggforce")
```


```{r, cache = TRUE}
#import data
df<-readRDS(here::here("data","df"))
```


## The New Zealand Attitudes and Values Study


New Zealand ranks among the world’s most tolerant societies [@Oecd2011-qv].

<aside>
The NZAVS measures tolerance using validated "affective thermometers."
</aside>

However, Muslims are New Zealand's least accepted minority group [@Shaver2016-fs] [@shaver2017news; @hawi2019terrorism; @yogeeswaran2019exploring;  [@greaves2020comparative; @sibley2020prejudice; @highland2019attitudes;@hawi2019terrorism]. 

The tragic 2019 Christchurch mosque attacks raised awareness of Muslim adversity, and were followed by gains in Muslim acceptance . This gave Muslims hope. Yet acceptance changed at different rates within New Zealanders, and among a sizeable minority, prejudice remained entrenched. The New Zealand Attitudes and Values Study (NZAVS) is a pioneering nationally representative panel study started in 2009 [@nzavs2021]. 


```{r timeline, fig.width=12, fig.height=8, fig.fullwidth = TRUE, fig.cap="Sampling from the electoral role,  combines with repeated measures within the same people across New Zealand's social diversity to affer confidence.", cache = TRUE}
datrep <- df %>%
  dplyr::mutate(timeline = make_date(year = 2009, month = 6, day = 30) + TSCORE) %>%
  count(day = floor_date(timeline, "day")) %>%
  dplyr::mutate(Year = factor(ifelse(
    day < "2010-01-01",
    2009,
    ifelse(
      day < "2011-01-01",
      2010,
      ifelse(
        day < "2012-01-01",
        2011,
        ifelse(
          day < "2013-01-01",
          2012,
          ifelse(
            day < "2014-01-01",
            2013,
            ifelse(
              day < "2015-01-01",
              2014,
              ifelse(
                day < "2016-01-01",
                2015,
                ifelse(
                  day < "2017-01-01",
                  2016,
                  ifelse(
                    day < "2018-01-01",
                    2017,
                    ifelse(day < "2019-01-01", 2018,
                           ifelse(day < "2020-01-01", 2019, 2020))
                  )
                )
              )
            )
          )
        )
      )
    )
  ))) %>%
  arrange(day)

# create date lines
ceq <- as.Date("2011-02-22")
keq <- as.Date("2016-11-14")
ter <- as.Date("2019-03-15")
cov <- as.Date("2020-03-24")

# get number for dates
ceqD <- which(datrep$day %in% ceq)
keqD <- which(datrep$day %in% keq)
terD <- which(datrep$day %in% ter)
covD <- which(datrep$day %in% cov)


# create dates

d1 <- as.numeric(datrep$day[ceqD])
d2 <- as.numeric(datrep$day[keqD])
d3 <- as.numeric(datrep$day[terD])
d4 <- as.numeric(datrep$day[covD])

# create break points
cuts <-
  data.frame(
    Big_Events = c(
      "Christchurch Earthquake",
      "Kaikoura Earthquake",
      "Mosque Attacks",
      "Stringent COVID-19 LockDown"
    ),
    vals = c(d1, d2, d3, d4),
    stringsAsFactors = FALSE
  )


ggplot2::ggplot(datrep, aes(day, n)) +
  geom_col(aes(fill = Year)) + scale_x_date(date_labels = "%b/%Y")  +
  geom_vline(
    mapping = aes(xintercept = vals,
                  colour = Big_Events),
    data = cuts,
    linetype = "dashed",
    show.legend = TRUE
  )  +
  xlab("NZAVS daily counts") + ylab("Count of Responses") + ggtitle("New Zealand Attitudes and Values Study Daily Response Counts\n Years 2009-2020; N = 61,535")  + theme_classic()  +  scale_fill_viridis_d() + theme(legend.position = "top")

# another approach
# ggplot(datrep, aes(day, n)) +
#  # geom_col(aes(fill = Year)) + scale_x_date(date_labels = "%b/%Y")  +
#   geom_vline(
#     xintercept = as.numeric(datrep$day[ceqD]),
#     col = "red",
#     linetype = "dashed"
#   ) +
#   geom_vline(
#     xintercept = as.numeric(datrep$day[keqD]),
#     col = "red",
#     linetype = "dashed"
#   ) +
#   geom_vline(
#     xintercept = as.numeric(datrep$day[terD]),
#     col = "red",
#     linetype = "dashed"
#   ) +
#   geom_vline(
#     xintercept = as.numeric(datrep$day[covD]),
#     col = "red",
#     linetype = "dashed"
#   ) +
#   xlab("NZAVS daily counts") + ylab("Count of Responses") + ggtitle("NZAVS Daily Counts")  + theme_blank()  +  scale_fill_viridis_d()
```


## Trends in acceptance of Muslims 2012-2020 


```{r dataprep, cache=TRUE}
#data preparation for graphs -- filtering out key warmth indicators
dat<-df
dt <- dat %>%
  dplyr::filter(YearMeasured == 1)  %>%
  dplyr::filter(Wave == 2019 |
                  Wave == 2018 |
                  Wave == 2017 |
                  Wave == 2016 |
                  Wave == 2015|
                  Wave == 2014|
                  Wave == 2013|
                  Wave == 2012) %>%
  dplyr::group_by(Id) %>% filter(n() > 2) %>%
  dplyr::ungroup(Id)  %>%
  dplyr::select(Id, TSCORE, Warm.Muslims)%>%
  dplyr::filter(!is.na(Warm.Muslims)) %>%
  dplyr::mutate(
    wm_s = scale(Warm.Muslims),
    days = as.integer(TSCORE),
    yr_0 = ((days - min(days)) / 365),
    yrs = (days / 365),
    yr_a = 3545/365,
  ) %>%
  dplyr::mutate(Pre_PostATTACK = factor(ifelse(
    TSCORE >= 3545, "post_attack",
    "pre_attack"
  )))%>%
  dplyr::mutate(Pre_PostATTACK = forcats::fct_relevel(Pre_PostATTACK, c("pre_attack","post_attack")))

dm <- dat %>%
  dplyr::filter(YearMeasured == 1)  %>%
  dplyr::filter(Wave == 2019 |
                  Wave == 2018 |
                  Wave == 2017 |
                  Wave == 2016 |
                  Wave == 2015|
                  Wave == 2014|
                  Wave == 2013|
                  Wave == 2012) %>%
  dplyr::group_by(Id) %>% filter(n() > 2) %>%
  dplyr::ungroup(Id)  %>%
  dplyr::select(Id, TSCORE, Warm.Maori)%>%
  dplyr::filter(!is.na(Warm.Maori)) %>%
  dplyr::mutate(
    wm_s = scale(Warm.Maori),
    days = as.integer(TSCORE),
    yr_0 = ((days - min(days)) / 365),
    yrs = (days / 365),
    yr_a = 3545/365,
  ) %>%
  dplyr::mutate(Pre_PostATTACK = factor(ifelse(
    TSCORE >= 3545, "post_attack",
    "pre_attack"
  )))%>%
  dplyr::mutate(Pre_PostATTACK = forcats::fct_relevel(Pre_PostATTACK, c("pre_attack","post_attack")))


di <- dat %>%
  dplyr::filter(YearMeasured == 1)  %>%
  dplyr::filter(Wave == 2019 |
                  Wave == 2018 |
                  Wave == 2017 |
                  Wave == 2016 |
                  Wave == 2015|
                  Wave == 2014|
                  Wave == 2013|
                  Wave == 2012) %>%
  dplyr::group_by(Id) %>% filter(n() > 2) %>%
  dplyr::ungroup(Id)  %>%
  dplyr::select(Id, TSCORE, Warm.Immigrants)%>%
  dplyr::filter(!is.na(Warm.Immigrants)) %>%
  dplyr::mutate(
    wm_s = scale(Warm.Immigrants),
    days = as.integer(TSCORE),
    yr_0 = ((days - min(days)) / 365),
    yrs = (days / 365),
    yr_a = 3545/365,
  ) %>%
  dplyr::mutate(Pre_PostATTACK = factor(ifelse(
    TSCORE >= 3545, "post_attack",
    "pre_attack"
  )))%>%
  dplyr::mutate(Pre_PostATTACK = forcats::fct_relevel(Pre_PostATTACK, c("pre_attack","post_attack")))

dnz <- dat %>%
  dplyr::filter(YearMeasured == 1)  %>%
  dplyr::filter(Wave == 2019 |
                  Wave == 2018 |
                  Wave == 2017 |
                  Wave == 2016 |
                  Wave == 2015|
                  Wave == 2014|
                  Wave == 2013|
                  Wave == 2012) %>%
  dplyr::group_by(Id) %>% filter(n() > 2) %>%
  dplyr::ungroup(Id)  %>%
  dplyr::select(Id, TSCORE, Warm.NZEuro)%>%
  dplyr::filter(!is.na(Warm.NZEuro)) %>%
  dplyr::mutate(
    wm_s = scale(Warm.NZEuro),
    days = as.integer(TSCORE),
    yr_0 = ((days - min(days)) / 365),
    yrs = (days / 365),
    yr_a = 3545/365,
  ) %>%
  dplyr::mutate(Pre_PostATTACK = factor(ifelse(
    TSCORE >= 3545, "post_attack",
    "pre_attack"
  )))%>%
  dplyr::mutate(Pre_PostATTACK = forcats::fct_relevel(Pre_PostATTACK, c("pre_attack","post_attack")))
```

```{r warmthtime, fig.width=12, fig.height=6, fig.cap="\\label{fig:warmthtime}Within-person prejudice change pre/post attacks towards (a) Muslims, (b) #Immigrants, (c) Māori, (d) NZ Europeans. Redline indicates mosque attacks. Greenline indicates maximum warmth to Muslims, which was strongly boosted post-attacks, yet lags behind other groups", cache = TRUE, fig.fullwidth = TRUE}
ld <- ggplot(data = dt,
             aes(x = yrs,
                 y = Warm.Muslims))

lds_0 <-ld + geom_line(alpha = .005) +
  stat_summary(
    geom = "point",
    fun = mean,
    size = .1,
    alpha = .2
  ) +
  geom_smooth() + 
  theme_minimal() + labs("")   + theme(
    legend.position = "right",
    legend.text = element_text(size = 6),
    legend.title = element_text(color = "Black", size = 8)
  ) + scale_colour_viridis_d(option = "plasma") +   geom_vline(xintercept= 9.71, linetype="dashed", color = "red") +
   geom_hline(yintercept= 4.4, color = "green") +
  ylab("Warmth (1-7)") +
  labs(title="Warmth to Muslims") + 
   xlab("Years 2011-2020, N = 22,254") 
# + 
#    theme(plot.title = element_text(color="black", size=20,face="bold"),
# axis.title.x = element_text(color="black", size=20,face="bold"),
# axis.title.y = element_text(color="black", size=20,face="bold"))

#  labs(title = "NZAVS longitudinal evidence for accellerated acceptance of 
# Muslims following 15 March 2019 Attacks (red line); N = 22,254, years 2010-2020)")

li <- ggplot(data = di,
             aes(x = yrs,
                 y = Warm.Immigrants))


li_0 <-li + geom_line(alpha = .005) +
  stat_summary(
    geom = "point",
    fun = mean,
    size = .1,
    alpha = .2
  ) +
  geom_smooth() + 
  theme_minimal() + labs("")   + theme(
    legend.position = "right",
    legend.text = element_text(size = 6),
    legend.title = element_text(color = "Black", size = 8)
  ) + scale_colour_viridis_d(option = "plasma") +   
  geom_vline(xintercept= 9.71, linetype="dashed", color = "red") +
   geom_hline(yintercept= 4.4, color = "green") +
  ylab("Warmth (1-7)") +
  labs(title="Warmth to Immigrants") + 
    xlab("Years 2011-2020, N = 22,254") 
# + 
#    theme(plot.title = element_text(color="black", size=20,face="bold"),
# axis.title.x = element_text(color="black", size=20,face="bold"),
# axis.title.y = element_text(color="black", size=20,face="bold"))

## maori
lm <- ggplot(data = dm,
             aes(x = yrs,
                 y = Warm.Maori))

lm_m <-lm + geom_line(alpha = .005) +
  stat_summary(
    geom = "point",
    fun = mean,
    size = .1,
    alpha = .2
  ) +
  geom_smooth() + 
  theme_minimal() + labs("")   + theme(
    legend.position = "right",
    legend.text = element_text(size = 6),
    legend.title = element_text(color = "Black", size = 8)
  ) + scale_colour_viridis_d(option = "plasma") +   
  geom_vline(xintercept= 9.71, linetype="dashed", color = "red") +
   geom_hline(yintercept= 4.4, color = "green") +
  ylab("Warmth (1-7)") +
  labs(title="Warmth to Māori")+
    xlab("Years 2011-2020, N = 22,254") 
# + 
#    theme(plot.title = element_text(color="black", size=20,face="bold"),
# axis.title.x = element_text(color="black", size=20,face="bold"),
# axis.title.y = element_text(color="black", size=20,face="bold"))



# Europeans
lnz <- ggplot(data = dnz,
             aes(x = yrs,
                 y = Warm.NZEuro))

lnz_0 <-lnz + geom_line(alpha = .005) +
    stat_summary(
    geom = "point",
    fun = mean,
    size = .1,
    alpha = .2
  ) +
  geom_smooth() + 
  theme_classic() + labs("")   + theme(
    legend.position = "right",
    legend.text = element_text(size = 6),
    legend.title = element_text(color = "Black", size = 8)
  ) + scale_colour_viridis_d(option = "plasma") +   
  geom_vline(xintercept= 9.71, linetype="dashed", color = "red") +
   geom_hline(yintercept= 4.4, color = "green") +
  ylab("Warmth (1-7)") + 
  labs(title="Warmth to NZ Europeans") +
  xlab("Years 2011-2020, N = 22,254") 
#    theme(plot.title = element_text(color="black", size=20,face="bold"),
# axis.title.x = element_text(color="black", size=20,face="bold"),
# axis.title.y = element_text(color="black", size=20,face="bold"))

timeline<-lds_0 + li_0 + lm_m + lnz_0 +  plot_layout(guides = 'collect') + plot_layout(nrow = 1, byrow = FALSE)
##  plot_annotation(title = "Timeline of attitudes to different groups in New Zealand years 2011-2020: Source: NZAVS, N = 22,254", subtitle = "Alpha for points on graph were set to .02 to avoid overplotting.", tag_levels = 'a') + 

# Graph 
timeline

# subtitle = "Within-person prejudice change pre/post attacks towards (a) Muslims, (b) #Immigrants, (c) Māori, (d) NZ Europeans. 
#Redline indicates mosque attacks. Greenline indicates maximum warmth to Muslims, which was strongly boosted post-attacks, yet lags behind other groups.
#This project will assess whether Muslim warmth continues to climb, stabalises, or regresses to the pre-attack trend. It will also enable independent monitoring of government policy effectiveness for intereventions.
```


## Natural Experiment




```{r pptimeline, cache=TRUE, fig.fullwidth = TRUE, fig.width=12, fig.height=8}
## timeline
rarep<-df%>%
  dplyr::filter(YearMeasured == 1) %>%
  dplyr::filter(Wave == 2017 | Wave == 2018 | Wave == 2019) %>%
  dplyr::group_by(Id) %>% filter(n() == 3) %>%
  dplyr::filter(Wave == 2017 | Wave == 2018 | Wave == 2019) %>%
  droplevels() %>%
  dplyr::ungroup(Id) %>%
  dplyr::mutate(timeline = make_date(year = 2009, month = 6, day = 30)+ TSCORE)%>%
  dplyr:::count(day = floor_date(timeline, "day"))%>%
  dplyr::mutate(Condition = factor(ifelse(day < "2018-06-18", -1, 
                                          ifelse(day >="2018-06-18" & day < "2019-03-15", 0,
                                                 ifelse( day >="2019-03-15" & day < "2019-06-18",1 , 
                                                         2))),
                                                 labels= c("PRE-ATTACK Baseline wv9 N = 11,455","PRE-ATTACK CONTROL rep measure wv10: n = 8111","IMMEDIATE POST-ATTACK rep measure wv10: PostAttack n = 3355", "DELAY POST-ATTACK Repeated measure post attack 2019: N= 11,287")))%>%
  arrange(day)
#table(rarep$Condition)
# get data of change of baseline
dates_vline1<- as.Date("2018-06-18")

# get attack date
dates_vline2<- as.Date("2019-03-15")
dates_vline3<- as.Date("2019-06-18")

# for line in a graph
dates_vline2b<-which(rarep$day %in% dates_vline2)
dates_vline1b<-which(rarep$day %in% dates_vline1)
dates_vline3b<-which(rarep$day %in% dates_vline3)

lds2 <- ggplot(rarep, aes(day, n)) +
  geom_col(aes(fill = Condition)) + scale_x_date(date_labels = "%b/%Y",
                                                 limits = c(as.Date("2017-08-25"), as.Date("2020-10-15")))  +
   scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) + 
  geom_vline(xintercept = as.numeric(rarep$day[dates_vline2b]),
             col = "red",
             linetype = "dashed") +
  # geom_vline(xintercept = as.numeric(rarep$day[dates_vline1b]), col ="black",linetype="dashed") +
  # geom_vline(xintercept = as.numeric(rarep$day[dates_vline3b]), col ="black",linetype="dashed") +
  xlab("NZAVS Waves years 2017 - 2020 daily counts") + ylab("Count of Responses") + 
  #ggtitle("Mosque attacks on NZAVS timeline (N = 11,330 repeatedly sampled in NZAVS Waves 9,10,11)") # + 
  theme_classic() +
  annotate(
    "rect",
    xmin = as.Date("2017-08-25"),
    xmax = dates_vline1,
    ymin = 0,
    ymax = 900,
    alpha = 0
  ) +
  annotate(
    "rect",
    xmin = dates_vline2,
    xmax = dates_vline3,
    ymin = 0,
    ymax = 900,
    alpha = .3,
    fill = "darkred"
  ) +
  annotate(
    "rect",
    xmin = dates_vline1,
    xmax = dates_vline2,
    ymin = 0,
    ymax = 900,
    alpha = .3
  ) +
  annotate(
    "rect",
    xmin = dates_vline3,
    xmax = as.Date("2020-10-15"),
    ymin = 0,
    ymax = 900,
    alpha = .05,
    fill = "red"
  ) +
  annotate(
    "text",
    x = as.Date("2018-10-15"),
    y = 980,
    label = "Wave 10
           repeated pre-attacks"
  ) +
  annotate(
    "text",
    x = as.Date("2018-01-15"),
    y = 980,
    label = "Wave 9
           baseline (control)"
  ) +
  annotate(
    "text",
    x = as.Date("2019-04-30"),
    y = 980,
    label = "Wave 10
           repeated post attacks"
  ) +
  annotate(
    "text",
    x = as.Date("2020-02-15"),
    y = 980,
    label = "Wave 11
           repeated during the year following attacks"
  ) +
  annotate(
    geom = "curve",
    x = as.Date("2018-02-15"),
    y = 750,
    xend = as.Date("2018-10-15"),
    yend = 750,
    curvature = -.3,
    arrow = arrow(length = unit(2, "mm"))
  ) + 
  annotate(
    geom = "curve",
    x = as.Date("2018-02-15"),
    y = 750,
    xend = as.Date("2019-05-15"),
    yend = 750,
    curvature = -.3,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate("text",
           x = as.Date("2018-02-01"),
           y = 750,
           label = "0") +
  annotate("text",
           x = as.Date("2018-11-05"),
           y = 750,
           label = "+1") +
  annotate(
    geom = "curve",
    x = as.Date("2019-05-15"),
    y = 800,
    xend = as.Date("2020-05-15"),
    yend = 750,
    curvature = -.3,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate("text",
           x = as.Date("2019-06-05"),
           y = 750,
           label = "+1") +
  annotate("text",
           x = as.Date("2020-05-30"),
           y = 750,
           label = "+2") +
  annotate(
    geom = "curve",
    x = as.Date("2018-11-15"),
    y = 800,
    xend = as.Date("2020-05-15"),
    yend = 750,
    curvature = -.3,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  theme(
    legend.position = "top",
    legend.text = element_text(size = 6),
    legend.title = element_text(color = "Black", size = 8)
  ) +
  scale_fill_viridis_d(option = "plasma")

### USE GRAPH OF TIMELINE
lds2
```


```{r danalysisdata, cach=TRUE}
km2 <- df %>%
  dplyr::filter(YearMeasured == 1) %>%
  dplyr::filter(Wave == 2017 | Wave == 2018 | Wave == 2019) %>%
  dplyr::group_by(Id) %>% filter(n() == 3) %>%
  dplyr::filter(Wave == 2017 | Wave == 2018 | Wave == 2019) %>%
  droplevels() %>%
  dplyr::ungroup(Id) %>%
  dplyr::select(
    Id,
    Age,
    TSCORE,
    EthnicCats,
    Warm.Muslims,
    Warm.Immigrants,
    Warm.Asians,
    Wave,
    Warm.Maori,
    Warm.NZEuro,
    Muslim,
    Euro,
    Relid,
    Religious,
    Pol.Orient,
    TSCORE,
    WSCORE
  ) %>%
  # dplyr::filter(!is.na(Warm.Muslims)) %>%
  dplyr::mutate(Pre_PostATTACK = as.factor(ifelse(
    TSCORE >= 3545 & Wave == 2018,
    "pst_wv10",
    ifelse(
      TSCORE >= 3545 & Wave == 2019,
      "pst_wv11",
      ifelse(TSCORE < 3545 & Wave == 2018, "pr_wv10",
             "baseline_wv10")
    )
  ))) %>%
  dplyr::mutate(Atack = ifelse(TSCORE >= 3545, "Post_Attack", "Pre_Attack"))%>%
  dplyr::mutate(days = as.integer(TSCORE),
                years = days / 365) %>%
  dplyr::filter(Muslim == 0) %>%
  dplyr::mutate(
    cons_s = scale(Pol.Orient),
    r_s = scale(Relid),
    a_s = scale(Age) ) # We are merely including these vars for "controls" -- they only policitical consrv will be of interest

#length(unique((km2$Id)))# 11470

#library(table1)  # make pretty tables quickly
#table1::table1(~Muslim|Wave, data = km, overall=F)# there are 31 muslims in 2017
```

```{r natexperiment, fig.fullwidth = TRUE, fig.width=12, fig.height=6, cache=TRUE}
## timeline
rarep<-df%>%
  dplyr::filter(YearMeasured == 1) %>%
  dplyr::filter(Wave == 2017 | Wave == 2018 | Wave == 2019) %>%
  dplyr::group_by(Id) %>% filter(n() == 3) %>%
  dplyr::filter(Wave == 2017 | Wave == 2018 | Wave == 2019) %>%
  droplevels() %>%
  dplyr::ungroup(Id) %>%
  dplyr::mutate(timeline = make_date(year = 2009, month = 6, day = 30)+ TSCORE)%>%
  count(day = floor_date(timeline, "day"))%>%
  dplyr::mutate(Condition = factor(ifelse(day < "2018-06-18", -1, 
                                          ifelse(day >="2018-06-18" & day < "2019-03-15", 0,
                                                 ifelse( day >="2019-03-15" & day < "2019-06-18",1 , 
                                                         2))),
                                                 labels= c("PRE-ATTACK Baseline wv9 N = 11,455","PRE-ATTACK CONTROL rep measure wv10: n = 8111","IMMEDIATE POST-ATTACK rep measure wv10: PostAttack n = 3355", "DELAY POST-ATTACK Repeated measure post attack 2019: N= 11287 ")))%>%
  arrange(day)

# get data of change of baseline
dates_vline1<- as.Date("2018-06-18")

# get attack date
dates_vline2<- as.Date("2019-03-15")
dates_vline3<- as.Date("2019-06-18")

# for line in a graph
dates_vline2b<-which(rarep$day %in% dates_vline2)
dates_vline1b<-which(rarep$day %in% dates_vline1)
dates_vline3b<-which(rarep$day %in% dates_vline3)

lds2 <- ggplot(rarep, aes(day, n)) +
  geom_col(aes(fill = Condition)) + scale_x_date(date_labels = "%b/%Y",
                                                 limits = c(as.Date("2017-08-25"), as.Date("2020-10-15")))  +
  scale_y_continuous(limits = c(0, 1000))  +
  geom_vline(xintercept = as.numeric(rarep$day[dates_vline2b]),
             col = "red",
             linetype = "dashed") +
  # geom_vline(xintercept = as.numeric(rarep$day[dates_vline1b]), col ="black",linetype="dashed") +
  # geom_vline(xintercept = as.numeric(rarep$day[dates_vline3b]), col ="black",linetype="dashed") +
  xlab("NZAVS Waves years 2017 - 2020 daily counts") + ylab("Count of Responses") + 
  #ggtitle("Mosque attacks on NZAVS timeline (N = 11,330 repeatedly sampled in NZAVS Waves 9,10,11)") # + 
  theme_classic() +
  annotate(
    "rect",
    xmin = as.Date("2017-08-25"),
    xmax = dates_vline1,
    ymin = 0,
    ymax = 900,
    alpha = 0
  ) +
  annotate(
    "rect",
    xmin = dates_vline2,
    xmax = dates_vline3,
    ymin = 0,
    ymax = 900,
    alpha = .3,
    fill = "darkred"
  ) +
  annotate(
    "rect",
    xmin = dates_vline1,
    xmax = dates_vline2,
    ymin = 0,
    ymax = 900,
    alpha = .3
  ) +
  annotate(
    "rect",
    xmin = dates_vline3,
    xmax = as.Date("2020-10-15"),
    ymin = 0,
    ymax = 900,
    alpha = .05,
    fill = "red"
  ) +
  annotate(
    "text",
    x = as.Date("2018-10-15"),
    y = 980,
    label = "Wave 10
           repeated pre-attacks"
  ) +
  annotate(
    "text",
    x = as.Date("2018-01-15"),
    y = 980,
    label = "Wave 9
           baseline (control)"
  ) +
  annotate(
    "text",
    x = as.Date("2019-04-30"),
    y = 980,
    label = "Wave 10
           repeated post attacks"
  ) +
  annotate(
    "text",
    x = as.Date("2020-02-15"),
    y = 980,
    label = "Wave 11
           repeated during the year following attacks"
  ) +
  annotate(
    geom = "curve",
    x = as.Date("2018-02-15"),
    y = 750,
    xend = as.Date("2018-10-15"),
    yend = 750,
    curvature = -.3,
    arrow = arrow(length = unit(2, "mm"))
  ) + 
  annotate(
    geom = "curve",
    x = as.Date("2018-02-15"),
    y = 750,
    xend = as.Date("2019-05-15"),
    yend = 750,
    curvature = -.3,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate("text",
           x = as.Date("2018-02-01"),
           y = 750,
           label = "0") +
  annotate("text",
           x = as.Date("2018-11-05"),
           y = 750,
           label = "+1") +
  annotate(
    geom = "curve",
    x = as.Date("2019-05-15"),
    y = 800,
    xend = as.Date("2020-05-15"),
    yend = 750,
    curvature = -.3,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate("text",
           x = as.Date("2019-06-05"),
           y = 750,
           label = "+1") +
  annotate("text",
           x = as.Date("2020-05-30"),
           y = 750,
           label = "+2") +
  annotate(
    geom = "curve",
    x = as.Date("2018-11-15"),
    y = 800,
    xend = as.Date("2020-05-15"),
    yend = 750,
    curvature = -.3,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  theme(
    legend.position = "top",
    legend.text = element_text(size = 6),
    legend.title = element_text(color = "Black", size = 8)
  ) +
  scale_fill_viridis_d(option = "plasma")
dev.off()
### USE GRAPH OF TIMELINE
lds2
```


## Model

```{r models, cache=TRUE}
library(lme4)
library(ggeffects)
m1 <- lmer(Warm.Muslims ~   Pre_PostATTACK +
             EthnicCats +
             a_s +
             r_s +
             cons_s +
             (1 |
                Id) ,
           data = km2)

# Check model
# parameters::model_parameters(m1) %>%

p1 <-plot(ggeffects::ggpredict(m1, terms = "Pre_PostATTACK", ci = .89)) + xlab("pre-attack") + ylab("Warmth to Muslims (1-7)") + labs(title = "Warm Muslims") +
  scale_y_continuous(limits = c(4, 6)) + scale_colour_viridis_d() + xlab("Attack Timeline")



m2 <- lmer(Warm.NZEuro ~    Pre_PostATTACK +
             EthnicCats +
             a_s +
             r_s +
             cons_s +   (1 | Id) ,
           data = km2)
p2 <- plot(ggeffects::ggpredict(m2, terms = "Pre_PostATTACK", ci = .89)) +
       # add.data = TRUE,
       # dot.alpha = 0.03,
       # jitter = .1) + 
       xlab("Attack Timeline") + ylab("Warmth to NZ Europeans (1-7)") + labs(title = "Warm NZ Euros") +
       scale_y_continuous(limits = c(4, 6)) + scale_colour_viridis_d()


m3 <- lmer(Warm.Maori ~    Pre_PostATTACK +
             EthnicCats +
             a_s +
             r_s +
             cons_s +   (1 | Id) ,
           # dependence owing to the week of response
           data = km2)
p3 <-
  plot(ggeffects::ggpredict(m3, terms = "Pre_PostATTACK", ci = .89)) + xlab("pre-attack") + ylab("Warmth to Māori (1-7)") + labs(title = "Warm Māori") +
  scale_y_continuous(limits = c(4, 6)) + scale_colour_viridis_d() + xlab("Attack Timeline")


m4 <- lmer(Warm.Immigrants ~   Pre_PostATTACK +
             EthnicCats +
             a_s +
             r_s +
             cons_s +   (1 | Id),
           data = km2)


p4 <- plot(ggeffects::ggpredict(m4, terms = "Pre_PostATTACK", ci = .89)) + xlab("pre-attack") + ylab("Warmth to Immigrants (1-7)") + labs(title = "Warm Immigrants") +
  scale_y_continuous(limits = c(4, 6)) + scale_colour_viridis_d() + xlab("Attack Timeline")

m5 <- lmer(Warm.Asians ~    Pre_PostATTACK + 
             EthnicCats + 
             a_s +
             r_s +
             cons_s +  (1 | Id) ,
           # dependence owing to the week of response
           data = km2)



p5 <-
  plot(ggeffects::ggpredict(m5, terms = "Pre_PostATTACK", ci = .89)) + xlab("pre-attack") + ylab("Warmth to Asians (1-7)") + labs(title = "Warm Asians") +
  scale_y_continuous(limits = c(4, 6)) + scale_colour_viridis_d() + xlab("Attack Timeline")

p5b <-
  plot(ggeffects::ggpredict(m5, terms = c("cons_s[all]","Pre_PostATTACK [all]"), ci = .89), add.data = TRUE, dot.alpha = 0.02, jitter = .2 ) +
    scale_y_continuous(limits = c(1, 7)) + 
 xlab("Political Conservativism (Standard Deviation Units") + 
  ylab("Warmth to Asians (1-7)") + labs(title = "Warm Asians")  + scale_colour_viridis_d() + xlab("Attack Timeline") 


# 
# lds3 <-
#   (p1 +  p4 + p3 + p2) + plot_annotation(title = "Increase in Warmth to Muslims After Shootings",
#                                          subtitle = "However, Muslim acceptance lags behind other minority groups",
#                                          tag_levels = 'a') +   plot_layout(guides = 'collect') + plot_layout(nrow = 1, byrow = FALSE)
# 
# lds3a <-
#   (p1 +  p4 + p3 + p2) + plot_annotation(tag_levels = 'a') +   plot_layout(guides = 'collect') + plot_layout(nrow = 1, byrow = FALSE)
```


```{r  graphsmodels, fig.fullwidth = TRUE, fig.width=12, fig.height=6, cache=TRUE}
desc <- 'Large boost in Muslim acceptance following shootings; However Muslim acceptance still lags behind.'
p1a<- p1 +   ggforce::geom_mark_ellipse(aes( label = 'Pre/Post Attack', description = desc), colour = "red") 
p2a<- p2 +   ggforce::geom_mark_ellipse(aes( label = 'Pre/Post Attack'))
p3a<- p3 +   ggforce::geom_mark_ellipse(aes( label = 'Pre/Post Attack'))
p4a<- p4 +   ggforce::geom_mark_ellipse(aes( label = 'Pre/Post Attack'))


lds3<-(p1a +  p4a + p3a + p2a) + plot_annotation(title = "Increase in Warmth to Muslims After Shootings",
                                 subtitle = "However, Muslim acceptance lags behind other minority groups", tag_levels = 'a') +   plot_layout(guides = 'collect') + plot_layout(nrow = 1, byrow = FALSE)

lds3
```



```{r  models_politics, cache = TRUE}
m6 <- lmer(Warm.Muslims ~  cons_s * Pre_PostATTACK +  EthnicCats + 
             a_s +
             r_s + (1|Id) , # dependence owing to the week of response
           data=km2)

p6 <- plot(ggeffects::ggpredict(m6, terms = c("Pre_PostATTACK [all]", "cons_s[all]"), ci = .89)) + xlab("Conservativism") + ylab("Warmth Muslims") + labs(title = "Warmth to Muslims Increased the most among political conservatives:
however, only to the midrange of the warmth scale: there's lots of headroom") + scale_colour_viridis_d()

####### 
p7 <- plot(ggeffects::ggpredict(m6, terms = c("cons_s[all]","Pre_PostATTACK [all]"), ci = .89), add.data = TRUE, dot.alpha = 0.02, jitter = .2 ) + scale_y_continuous(limits = c(.5,7.5)) +
  xlab("Political Conservativism (SD)") + ylab("Warmth Muslims (1-7") + 
  labs(title = "Warmth to Muslims") + scale_colour_viridis_d() 

#p7 +  ggforce::geom_mark_ellipse(aes(fill = "Pre_PostATTACK", label = "Pre_PostATTACK")) 
#p7 +   ggforce::facet_zoom(xlim = c(0, .2), ylim = c(4, 4.5), horizontal = FALSE)
desc <- "Post Shooting Difference"

p71<-p7 + annotate("rect", 
              xmin = 2., 
              xmax = 2.5, 
              ymin = 3.5, 
              ymax = 4.1,
              alpha = .2, 
              colour = "red") + 
  annotate(
    "rect",
    xmin = -2.,
    xmax = -1.5,
    ymin = 4.4,
    ymax = 4.8,
    alpha = .2,
    colour = "red"
  ) + 
  annotate(
    "text",
    x = 0,
    y = 7.2,
    label = " Greater relative growth in 
    acceptance among conservatives",
    colour = "brown3"
  ) + 
  annotate(
    geom = "curve",
    x = -1,
    y = 6.7,
    xend = -1.75,
    yend = 4.9,
    curvature = 0,
    arrow = arrow(length = unit(2, "mm")),
    colour = "red"
  ) +
   annotate(
    geom = "curve",
    x = 1,
    y = 6.7,
    xend = 2.25,
    yend = 4.2,
    curvature = 0,
    arrow = arrow(length = unit(2, "mm")),
    colour = "red"
  )

## Compare this to warmth to maori

m8 <- lmer(Warm.Maori ~  cons_s * Pre_PostATTACK +  EthnicCats + 
             a_s +
             r_s +(1|Id) , # dependence owing to the week of response
           data=km2)

p8 <- plot(ggeffects::ggpredict(m8, terms = c("cons_s[all]","Pre_PostATTACK [all]"), ci = .89), 
          add.data = TRUE, dot.alpha = 0.02, jitter = .2 ) + scale_y_continuous(limits = c(.5,7.5)) +
  xlab("Political Conservativism (SD)") + ylab("Warmth Māori (1-7") + 
  labs(title = "Warmth to Māori") + scale_colour_viridis_d()


## Warmth to NZEuRO
m9 <- lmer(Warm.NZEuro ~  cons_s * Pre_PostATTACK +  EthnicCats + 
             a_s +
             r_s +(1|Id) , # dependence owing to the week of response
           data=km2)

p9 <- plot(ggeffects::ggpredict(m9, terms = c("cons_s[all]","Pre_PostATTACK [all]"), ci = .89), 
          add.data = TRUE, dot.alpha = 0.02, jitter = .2 ) + scale_y_continuous(limits = c(.5,7.5)) +
  xlab("Political Conservativism (SD)") + ylab("Warmth NZ Europeans (1-7") + 
  labs(title = "Warmth to NZ Europeans") + scale_colour_viridis_d()


m10 <- lmer(Warm.Immigrants ~  cons_s * Pre_PostATTACK +  EthnicCats + 
             a_s +
             r_s +(1|Id) , # dependence owing to the week of response
           data=km2)

p10 <- plot(ggeffects::ggpredict(m10, terms = c("cons_s[all]","Pre_PostATTACK [all]"), ci = .89), 
          add.data = TRUE, dot.alpha = 0.02, jitter = .2 ) + scale_y_continuous(limits = c(.5,7.5)) +
  xlab("Political Conservativism (SD)") + ylab("Warmth Immigrants (1-7") + 
  labs(title = "Warmth to Immigrants") + scale_colour_viridis_d()


# Graph
# p71 + p10 + p8 + p9 +  plot_layout(nrow = 1, byrow = FALSE) + plot_annotation(title = "Warmth to Muslims and other groups by political conservatvisms pre/post shootings
# (N = 11330, repeated measures 2018-2020)", subtitle = "Muslim acceptance lags behind other minority groups (graph shows all predicted responses)", tag_levels = 'a') +   plot_layout(guides = 'collect')  
#   
# p71 <-p71 + theme(legend.position = "top")
# 
# p10 <-p10 + theme(legend.position = "top")
# p8 <-p8 + theme(legend.position = "top")
# p9 <-p9 + theme(legend.position = "top")
#
```


```{r  graphsmodelsPol, fig.fullwidth = TRUE, fig.width=12, fig.height=6, cache = TRUE}

lds4 <-p71 + p10 + p8 + p9 +  plot_layout(nrow = 1, byrow = FALSE) + plot_annotation(title = "Warmth to Muslims and other groups by political conservatvisms pre/post shootings
(N = 11330, repeated measures 2018-2020)", subtitle = "Muslim acceptance lags behind other minority groups (graph shows all predicted responses)", tag_levels = 'a') +   plot_layout(guides = 'collect')  
lds4
```


```{r  dagpol, include = FALSE, eval = FALSE}
## ADD FIG
## 
dg2 <- dagify(
  wm ~ pp+  cs + ml + news + U + yr + rel + edu + a + eth + ur,
  cs ~ ml + rel + a,
  rel ~ ml + rel + a + eth,
  pp ~ yr,
  a ~ yr,
  ur ~ eth + a + edu + time,
  rel ~ yr + ur,
  edu ~ ml + eth + ur,
  news ~ pp + yr,
  U ~ pp + cs + ml + news + yr  + rel + edu + a + ur,
  exposure =  "yr",
  outcome =   "wm",
  labels = c("wm" = "Warmth Muslims",
             "a" = "age",
             "eth" = "ethnicity",
             "pp" = "pre/postattacks",
             "cs" = "political conservativism",
             "edu" = "education",
             "ur" = "urban",
             "yr" = "time",
             "rel" = "religion",
             "news" = "media",
             "ml" = "male",
            "U" = "Soc Networks")
) %>%
  tidy_dagitty()

dplot1 <-ggdag::ggdag_collider(dg2, use_labels = "label", text = FALSE) + theme_dag_blank() +
  labs(title = "Causal analysis of Muslim Acceptance requires care to avoid confounding")
dplot1

f5 <-ggdag::ggdag_collider(dg2, use_labels = "label", text = FALSE) + theme_dag_blank() +
  labs(title = "")
f5

## BETTER
(lds_0 + dplot1)/ lds2 /  lds3 / lds4  + plot_annotation(tag_levels = 'a')

marsden_fig1v2 # 1750 x 2000

```







