---
title: "NZAVS Vaccination Attitudes"
description: ""
author:
  - name: Joseph Bulbulia
    url: https://josephbulbulia.netlify.app
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: 0000-0002-5861-2056
  - name          : Chris G. Sibley
    affiliation   : School of Psychology, University of Auckland
    orcid_id: 0000-0002-4064-8800
date: 2021-AUG-10
output:
  distill::distill_article:
    self_contained: true
    toc: true
    code_folding: true
---

Here we investigate attitudes to vaccinating children in New Zealand. 
<!-- Figure \@ref(fig:) presents results.   -->


```{r setup, code_folding = FALSE, include=FALSE}
# setup
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  layout = "l-body-outset",
  fig.width = 16,                            
  fig.height = 9,
  collapse = TRUE,
  R.options = list(width = 60
  )
)
# packages
library("tidyverse") # data wrangling 
library("haven")
library("here") # setting directories
library("ggplot2") # graph 
library("ggthemes") # themes
library("table1") # tables
library("lme4")

library("ggdag")
library("brms")
library("rstan")
library("rstanarm")
library("bayesplot")
library("easystats")
library("kableExtra")
library("broom")
library("tidybayes")
library("bmlm")
# rstan options
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores ())
theme_set(theme_classic())
```

## Did the Covid Pandemic affect attitudes to Vaccination? 

Here we investigate whether, and how, the Covid pandemic in New Zealand affected attitudes to the safety of vaccination in New Zealand. 

This question is theoretically interesting. The covid-19 pandemic was accompagnied by misinformation and conspiracy theories about the saftey of vaccines, which may have reduced confidence in vaccine safety. 

However, in New Zealand, the government adopted a pro-science attitude to science, which may have increased confidence in vaccine saftety.

The New Zealand Attitudes and Values Study (NZAVS) is a national panel study launched in 2009 that investigating stability and change in attitudes and values among New Zealanders over time. In both the year previous to the pandemic (2018/19) and the year of the pandemic (2019/20) study contained the question 

> "It is safe to vaccinate children following the standard NZ immunization schedule." 

Here, using responses within the same individuals, we investigate whether, and how, attitudes to the vaccination of children changed after 29 February 2020 when New Zealand experienced its first case of community Covid transmission.   


## Matts paper

```{r dagg}
# urban? 
library(ggdag)
dg <- dagify(
   vax ~ age + male + eth + nzdep + edu + parent + partner + rel + hoursint + hoursoc + hlthac +  gphas + gpres + gpsat + sfhealth + sensecommunity + belonging + satgov + poltrust + policetrust + 
    meaning + lifesat + polidentity + poleff + polorient + sciencetrust + personality +
    CovLab + CovTrust + disgust + healthcontrol + conspiracy,
  parent ~ age + partner,
  edu ~ nzdep + U,
  rel  ~ age + eth  + male, 
  hoursint ~ age + age + nzdep + male + U,
  hoursoc ~ hoursint + age + nzdep + male + U, 
  hlthac ~ eth + nzdep + U,
  gphas ~ age + eth + edu + nzdep + U, 
  gpres ~ gphas + eth + edu + nzdep + personality, 
  gpsat ~ age + eth + personality, 
  sfhealth ~ gphas + age + eth + edu + male + personality + U,
  lifesat ~ sfhealth + meaning + rel + eth + age + male + partner, 
  parent  ~ partner + age + eth,
  sensecommunity ~ rel + belonging + polorient + nzdep + eth + male + age + personality + U,
  belonging ~ age + eth + edu + male + personality + U, 
  satgov ~ polidentity + poleff + polorient,
  poltrust ~ age + male + eth + nzdep + polorient +  edu + personality + U,
  policetrust ~ age +  male + nzdep + eth +  edu + personality + U + U2,
  poleff ~ polorient + age + male + personality + edu + U + U2,
  polorient ~ age + male + personality + edu + U + U2,
  sciencetrust ~ U2,
  CovLab ~ U2 + edu, 
  CovTrust ~ male + U2 + edu, 
  healthcontrol ~ age + eth + nzdep + male +    personality, 
  conspiracy ~ U2,
  exposure =  "poltrust",
  outcome =   "vax",
  latent = c("U","U2"),
  labels = c(
    "vax" = "vaccination",
    "eth" = "ethnicity",
    "age" = "age",
    "male" = "male",
    "nzdep" = "nz dep",
    "edu" = "education",
    "parent" = "parent",
    "partner" = "partner",
    "rel" = "religious",
    "hoursint" = "hours internet",
    "hoursoc" = "hours social media",
    "hlthac" = "healthcare access",
    "gphas" = "has GP",
    "gpres" = "respects gp",
    "gpsat" = "gp satisfaction",
    "sfhealth" = "subjective health",
    "sensecommunity" = "sense community",
    "belonging" = "soc belonging",
    "meaning" = "life meaning",
    "lifesat" = "life satisfaction",
    "polidentity" = "political identity",
    "poleff" = "political efficacy",
    "polorient" = "political orientation",
    "satgov" = "satisfied with government",
    "poltrust" = "trust in politicians",
    "policetrust" = "trust in police",
    "sciencetrust" = "trust in science",
    "personality" = "personality",
    "CovLab" = "Covid made in a lab",
    "CovTrust" = "trust gov covid",
    "disgust" = "disgust sensitivity",
    "healthcontrol" = "health locus control",
    "conspiracy" = "conspiracy beliefs",
    "U" = "Unmeasured Priviledge",
    "U2" = "Unmeasured Conspiratorial Personality"
  )
) %>%
  # control_for(c( "hoursint",
  #   "hoursoc",
  #   "hlthac",
  #   "gphas",
  #   "gpres",
  #   "gpsat",
  #   "sfhealth",
  #   "sensecommunity",
  #   "belonging",
  #   "meaning",
  #   "lifesat",
  #   "polidentity",
  #   "poleff",
  #   "polorient",
  #   "satgov",
  #   "policetrust",
  #   "sciencetrust",
  #   "personality",
  #   "CovLab",
  #   "CovTrust",
  #   "healthcontrol",
  #   "conspiracy") )%>%
  tidy_dagitty() 

dplot1 <-
  ggdag::ggdag_collider(dg, use_labels = "label", text = FALSE) + theme_dag_blank() +
  labs(title = "An abundance of collider confounders reveals risks of an overparameterised model")
dplot1


ggdag::ggdag_adjustment_set(dg, use_labels = "label", text = FALSE) + theme_dag_blank() +
  labs(title = "Adjustment set for variables needed to obtain an unbaiased causal estimate of trust in government on vacciation status")


# Diff exposure
dg1 <- dagify(
   vax ~ age + male + eth + nzdep + edu + parent + partner + rel + hoursint + hoursoc + hlthac +  gphas + gpres + gpsat + sfhealth + sensecommunity + belonging + satgov + poltrust + policetrust + 
    meaning + lifesat + polidentity + poleff + polorient + sciencetrust + personality +
    CovLab + CovTrust + disgust + healthcontrol + conspiracy + urban,
  parent ~ age + partner,
  edu ~ nzdep + U,
  rel  ~ age + eth  + male, 
  hoursint ~ age + age + nzdep + male + U,
  hoursoc ~ hoursint + age + nzdep + male + U, 
  hlthac ~ eth + nzdep + U,
  gphas ~ age + eth + edu + nzdep + U, 
  gpres ~ gphas + eth + edu + nzdep + personality, 
  gpsat ~ age + eth + personality, 
  sfhealth ~ gphas + age + eth + edu + male + personality,
  lifesat ~ sfhealth + meaning + rel + eth + age + male + partner, 
  parent  ~ partner + age + eth,
  sensecommunity ~ rel + belonging + polorient + nzdep + eth + male + age + personality + U,
  belonging ~ age + eth + edu + male + personality + U, 
  satgov ~ polidentity + poleff + polorient,
  poltrust ~ age + male + eth + nzdep + polorient +  edu + personality + U,
  policetrust ~ age +  male + nzdep + eth +  edu + personality + U + U2,
  poleff ~ polorient + age + male + personality + edu + U + U2,
  polorient ~ age + male + personality + edu + U + U2,
  sciencetrust ~ U2,
  CovLab ~ U2 + edu, 
  CovTrust ~ male + U2 + edu, 
  healthcontrol ~ age + eth + nzdep + male +    personality, 
  conspiracy ~ U2,
  exposure =  "age",
  outcome =   "vax",
  latent = c("U","U2"),
  labels = c(
    "vax" = "vaccination",
    "eth" = "ethnicity",
    "age" = "age",
    "male" = "male",
    "nzdep" = "nz dep",
    "edu" = "education",
    "parent" = "parent",
    "partner" = "partner",
    "rel" = "religious",
    "hoursint" = "hours internet",
    "hoursoc" = "hours social media",
    "hlthac" = "healthcare access",
    "gphas" = "has GP",
    "gpres" = "respects gp",
    "gpsat" = "gp satisfaction",
    "sfhealth" = "subjective health",
    "sensecommunity" = "sense community",
    "belonging" = "soc belonging",
    "meaning" = "life meaning",
    "lifesat" = "life satisfaction",
    "polidentity" = "political identity",
    "poleff" = "political efficacy",
    "polorient" = "political orientation",
    "satgov" = "satisfied with government",
    "poltrust" = "trust in politicians",
    "policetrust" = "trust in police",
    "sciencetrust" = "trust in science",
    "personality" = "personality",
    "CovLab" = "Covid made in a lab",
    "CovTrust" = "trust gov covid",
    "disgust" = "disgust sensitivity",
    "healthcontrol" = "health locus control",
    "conspiracy" = "conspiracy beliefs",
    "U" = "Unmeasured Priviledge",
    "U2" = "Unmeasured Conspiratorial Personality"
  )
) %>%
  # control_for(c( "hoursint",
  #   "hoursoc",
  #   "hlthac",
  #   "gphas",
  #   "gpres",
  #   "gpsat",
  #   "sfhealth",
  #   "sensecommunity",
  #   "belonging",
  #   "meaning",
  #   "lifesat",
  #   "polidentity",
  #   "poleff",
  #   "polorient",
  #   "satgov",
  #   "policetrust",
  #   "sciencetrust",
  #   "personality",
  #   "CovLab",
  #   "CovTrust",
  #   "healthcontrol",
  #   "conspiracy") )%>%
  tidy_dagitty() 


ggdag::ggdag_adjustment_set(dg1, use_labels = "label", text = FALSE) + theme_dag_blank() +
  labs(title = "Adjustment set for variables needed to obtain an unbaiased causal estimate of social media use vacciation status")

```




## Method


```{r cache=TRUE, echo = FALSE,code_folding = FALSE}
# import data
df <- readRDS(here::here("data", "df"))

# df%>%
#   group_by(Wave) %>%
#   summarise(mean = mean(HLTH.ChildVaccination, na.rm=TRUE))

# df$Child.VaccinationActual # If you have children under 18, are their vaccinations up-to-date, as per the recommendations of your doctor/GP?
# df$HLTH.ChildVaccination  # It is safe to vaccinate children following the standard NZ immunization schedule.
```

```{r cache = TRUE, echo = FALSE}
ord_dates_class <- c(
  "Baseline", 
  "PreCOVID", 
  "JanFeb", 
  "EarlyMarch", 
  "Lockdown",
  "PostLockdown")


ord_cov <- c(
  "PreCovid", 
  "PostCovid")


# 3665 days after 30 June 2009 Saturday 13 July 2019
# 3842 days after 30 June 2009 Monday 6 January 2020
# 3895 days after 30 June 2009 Friday 28 February 2020
# 3921 days after 30 June 2009 WED MAR 25th
# 3954 days after 30 June 2009 Monday 27 April 2020
# 3672 days after June 30 2009 Saturday 20 July 2019
```


```{r cache = TRUE, echo = FALSE}
cv <- df %>%
  dplyr::filter(YearMeasured == 1) %>%
  dplyr::filter(Wave == 2018 |  Wave == 2019) %>%
  droplevels() %>%
  dplyr::group_by(Id) %>% 
  dplyr::filter(n() == 2) %>%
  dplyr::ungroup(Id) %>%
  dplyr::filter(Parent == 1) %>%
  droplevels() %>%
  dplyr::mutate(Covid_Timeline =
                    as.factor(ifelse(
                      TSCORE %in% 3896:3921, # feb 29 - march 25th
                      "EarlyMarch",
                      ifelse(
                        TSCORE %in% 3922:3954,
                        "Lockdown", #march 26- Mon 27 April 2020
                        ifelse(
                          TSCORE > 3954, # after april 27th 20202
                          "PostLockdown",
                          ifelse(
                            TSCORE %in% 3842:3895, # jan 6 to feb 28
                            "JanFeb",
                          ifelse(
                            TSCORE %in% 3665:3841 &
                              Wave == 2019,
                            "PreCOVID",
                            "Baseline"  # 3672 TSCORE or  20 July 2019
                          )
                        )
                      )
                    ) 
                 ) ))%>%
  dplyr::mutate(PrePostCovid0 =
                  ifelse(
                    TSCORE > 3895, "PostLockdown",
                    ifelse(
                      TSCORE < 3895 &
                        Wave == 2019,
                      "PreCOVID",
                      "Baseline"
                    )
                  ))%>% 
  dplyr::group_by(PrePostCovid0) %>% 
  filter(n() > 1) %>%
  ungroup() %>% # There is overlap between waves, we only want repeated measures
  dplyr::mutate(PrePostCovid =
                  ifelse(
                    TSCORE > 3895, "PostCovid",
                      "PreCovid"
                  ))%>% 
  dplyr::group_by(Id) %>% 
  dplyr::filter(n() == 2) %>%
  dplyr::ungroup(Id) %>%
  droplevels() %>%
  dplyr::select(
    TSCORE,
    WSCORE,
    Wave,
    Partner,
    Employed,
    Sat.Government,
    HLTH.ChildVaccination,
    Child.VaccinationActual,
    NZ.Business.Conditions,
    NZ.Economic.Situation,
    PrePostCovid,
    years,
    Id,
    Parent,
    SWB.SatPWI02, # your health
    Hours.Work,
    Hours.Exercise,
    KESSLER6,
    Hours.SocialMedia,
    Hours.Internet,
    KESSLER6sum,
    Age,
    Male,
    Relid,
    Pol.Orient,
    Urban,
    GenCohort,
    Edu,
    YearMeasured,
    Covid_Timeline,
    HLTH.SleepHours,
    HLTH.Fatigue,
    LIFESAT,
    PWI,
    EthnicCats,
    NZdep,
    Partner,
    Pol.Orient,
    Urban,
    Euro,
    Religious,
    NZdep,
    WSCORE,
    Religion.Church,
    Your.Future.Security, 
    Parent,
    PrePostCovid0
  ) %>%
  dplyr::mutate(
    Urban = (Urban),
    Euro = (Euro),
    Religious = as.factor(Religious),
    Your_Health = (SWB.SatPWI02),
    Your_Future_Security = Your.Future.Security,
    Covid_Timeline = as.factor(Covid_Timeline),
    PrePostCovid0
  )%>%
  dplyr::mutate(
    WSCORE = as.factor(WSCORE),
    #EduC = scale(as.numeric(Edu), scale = F, center = TRUE),
    Sat.Government = scale(Sat.Government),
   # AgeDecadeC = scale(Age, scale = F, center = T) / 10,
    Hours.Work10 = as.integer(Hours.Work) / 10,
    Hours.Sleep = as.integer(HLTH.SleepHours),
    Hours.Exercise = as.integer(Hours.Exercise),
    Fatigue = as.integer(HLTH.Fatigue),
    K6sum = as.integer(KESSLER6 * 6),
    KESSLER6SUM_S = scale(KESSLER6sum),
    NZdepS = scale(NZdep),
    PolOrientS = scale(Pol.Orient, scale = T, center = T),
    Conservative = Pol.Orient,
    logSM = log(Hours.SocialMedia + 1),
    logINT = log(Hours.Internet + 1),
    logEX = log(Hours.Exercise + 1),
    logWK= log(Hours.Work + 1),
    KESSLER6sum = as.integer(KESSLER6sum),
    Hours.Work = as.integer(Hours.Work),
    Hours.Exercise = as.integer(Hours.Exercise)
  ) %>%
  dplyr::mutate(Covid_Timeline = forcats::fct_relevel(Covid_Timeline, ord_dates_class)) %>%
  dplyr::mutate(PrePostCovid = forcats::fct_relevel(PrePostCovid, ord_cov)) %>%
  # dplyr::filter(
  #   Covid_Timeline == "Baseline" |
  #     Covid_Timeline == "EarlyMarch" |
  #     Covid_Timeline == "Lockdown" |
  #     Covid_Timeline == "PostLockdown"
  # ) %>% 
 # dplyr::group_by(Id) %>% filter(n() > 1) %>%
#  dplyr::filter(n() != 0) %>%
  droplevels()

#table((cv$Covid_Timeline)) # 8640
#length(unique(cv$Id))

# select only parents
cv1 <- cv %>%
  mutate(years0 = years - min(years)) # meaningful 0 for years

#length(unique(cv1$Id)) # 25566

count_waves_participants <- function(x){
  out<-dplyr::count(tally(group_by(x, Id), sort = TRUE, name="number_waves"), number_waves)
  print(out)
}

count_waves_participants(cv)
```




First we investigate population level change in a pre/post sample of New Zealanders who responded to the 


```{r cache=TRUE}
library(splines)
HLTH.ChildVaccination <- lmer(HLTH.ChildVaccination  ~   bs(years0) +  (1|Id),  cv1)
plot(ggeffects::ggpredict(HLTH.ChildVaccination, terms = "years0[all]"), add.data = TRUE, dot.alpha = .03) 

# library(ordinal)
# fm1 <- clmm2(as.factor(HLTH.ChildVaccination) ~ Covid_Timeline + years0, random=Id, data=cv1)

```

```{r}
equatiomatic::extract_eq(HLTH.ChildVaccination,
                         wrap = TRUE, 
                         terms_per_line = 1)
```




```{r cache = TRUE}
m1 <- brm(
  bf(HLTH.ChildVaccination  ~
       PrePostCovid  + (1 | Id)),
  family = cumulative(link = "logit"),
  data = cv1,
  file = here::here("models", "vax_1"),
  silent = FALSE
)

par_v1 <- parameters::model_parameters(m1)
par_v1
saveRDS(par_m1, here::("models","par_v1"))
plot(par_m1)

# Another approach
plot(ggeffects::ggpredict(m1, terms = "PrePostCovid")) 


```

Hre we can see that the log-odds of Fatigue dropped during Lockdown. But how exactly did Fatigue drop?

As with logistic regression, the coefficients here are not obvious. To interpret results, we should graph the predicted outcomes at specific values.

### Interpreting results of an ordinal model using graphical methods

To understand what is happening, we plot all the individual intercepts by setting `categorical = TRUE`. Following McElreath's Statistical Rethinking, we will predict outcomes using the .89 probability credible interval:

```{r}
plot(
  conditional_effects(
    m1,
    categorical = TRUE,
    prob = 0.89,
    re_formula = NA,
  ),   # WE cannot graph points when the points arg = TRUE
  points = TRUE,
  point_args = list(
    alpha = 0.1,
    width = .1,
    size = .2
  )
)[[1]] 


```



This is another method for graphing, where the individual facets denote our expected response thresholds:

```{r}
plot(ggeffects::ggpredict(
  m1, 
  effects = "PrePostCovid"),
  )
```



## ANother approach


```{r}

library(LMest)

# We investigate only pre-post covide responses
cv2 <- cv1 %>%
  dplyr::filter(
      Covid_Timeline == "Baseline" |
      Covid_Timeline == "EarlyMarch" |
      Covid_Timeline == "Lockdown" |
      Covid_Timeline == "PostLockdown"
  ) %>%
 dplyr::group_by(Id) %>% filter(n() > 1) %>%
  ungroup()
length(unique(cv2$Id))

widelong <-  cv2 %>%
  dplyr::select(Id,HLTH.ChildVaccination,PrePostCovid)




##THIS HANGS
#out <- with(relwidelong, long2matrices(id = Id, X = Age, Y = Religious))

wide<- spread(widelong,PrePostCovid,HLTH.ChildVaccination)
head(wide)

wide2<-wide[complete.cases(wide), ]



x_var_list<-names(wide2[,2:3])
x_var_list
library(lcsm)
plot_trajectories(data = wide2,
                 id_var = "Id", 
                 var_list = x_var_list,
                 xlab = "Condition", ylab = "Value",
                 connect_missing = F, 
                 random_sample_frac = 0.01, 
                 title_n = TRUE)  +
  facet_wrap(~Id)

#ldf.5$Pol.Orient

```



```{r}
library(TraMineR)
seq.m<-seqdef(wide[,2:3])

#seq.m
#head(seq.m)

# EXPLORATION
#seqiplot(seq.m, border = NA, with.legend = "top")
#seqfplot(seq.m, weighted = FALSE, border = NA, with.legend = FALSE, main = "Frequencies")
#seqmsplot(seq.m)
#seqmtplot(seq.m)
seqtab(seq.m)
seqIplot(seq.m)
sd <- seqstatd(seq.m)
plot(sd, type="d")
seqstatd(seq.m, weighted=FALSE)
seqdplot(seq.m)
seqrplot(seq.m)

seqtab(seq.m, idxs = 1:20)

ss<-seqtrate(seq.m)
ss
round(ss, 2)
dev.off()
## USE THESE PLOTS
sd<-seqtransn(seq.m)
sd
table(sd)
qplot(sd)
(seqdss(seq.m))
(seqdur(seq.m))
seqdur(seq.m)
```




```{r}
library(seqHMM)
sc_initmod_random <- build_hmm(observations = seq.m, n_states = 3)
                               
                             
sc_initmod_random

sc_initmod_random$initial_probs



sc_initmod <- build_hmm(observations = seq.m, 
                        initial_probs = sc_initmod_random$initial_probs, 
                        transition_probs = sc_initmod_random$transition_probs, 
                        emission_probs = sc_initmod_random$emission_probs, 
                        threads =4, 
                        seed = 123)



sc_fit <- fit_model(sc_initmod)

fm<-sc_fit$model
fm

names <- c("Med \n init = .39","Strong Pro Vax \n init = .5","Low \n init = .11")
summary(fm, conditional_se = FALSE)
library(igraph)
plot(sc_fit$model,
     layout = layout_nicely,
      main = "Hidden States Transitions Vaccination Attitudes",
      vertex.label = names,
      legend.prop =.1,
      ncol.legend = 3,
    # cex.edge.width = 0.8, 
    # edge.arrow.size = 1,
    vertex.label.dist = 1.1, 
    combine.slices = 0.02 ,
      loops = FALSE,
    # Remove edges with probability less than 0.01
  trim = 0.00001,
    combined.slice.label = "others (emission prob. < 0.02)"

)
#dev.off()

transprob<-as.matrix(fm$transition_probs)
transprob
```



## Appendix: Causal Inference 


Here we consider potential confounders in our model. We find that all backdoor paths are unconditionally closed, and furthermore, that there are no confounding colliders. 

We are therefore able to obtain an unbiased estimate for the causal effect of the covid-19 timeline on vaccination attitudes. 

```{r include = FALSE}
library(ggdag)

library(ggdag)
dg <- dagify(
  va ~ male + edu + eth + relig + covid + age + pol + U,
  edu ~ eth + age + U,
  relig ~ age + pol + eth + male,
  exposure =  "covid",
  outcome =   "va",
  latent = "U",
  labels = c(
    "va" = "Vaccination Attitudes",
    "male" = "male",
    "eth" = "ethnicity",
    "edu" = "education",
    "relig" = "religious identification",
    "age" = "age",
    "covid" = "covid timeline",
    "pol" = "political orientation",
    "U" = "Unmeasured"
  )
) %>%
  tidy_dagitty() 
#%>%
#  control_for("cs")

# dplot1 <-
#   ggdag::ggdag_collider(dg, use_labels = "label", text = FALSE) + theme_dag_blank() +
#   labs(title = "")
# dplot1


ggdag::ggdag_adjustment_set(dg, use_labels = "label", text = FALSE) + theme_dag_blank() +
  labs(title = "")
```


## Appendix: Missing cata


```{r}
naniar::vis_miss(cv1, warn_large_data = FALSE)
```



## Appendix: For more information

For more information about the NZAVS see: [here](https://www.psych.auckland.ac.nz/en/about/new-zealand-attitudes-and-values-study.html) and [here](https://go-bayes.github.io/reports/posts/nzavs/)

