---
title: "How did the Christchurch Mosque Attacks Affect Attitudes to Muslims in New Zealand?"
description: |
author:
  - name: Joseph Bulbulia
    url: https://josephbulbulia.netlify.app
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: 0000-0002-5861-2056
date: 2021-MAR-12
output:
  distill::distill_article:
    self_contained: false
    toc: true
    code_folding: true
bibliography: bib.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  layout = "l-body-outset",
  fig.width = 12,
  fig.height = 15,
  collapse = TRUE,
  R.options = list(width = 60
  )
)
```

```{r libs, include=FALSE}
library("tidyverse")
library("here")
library("equatiomatic")
library("lubridate")
library("ggplot2")
library("ggthemes") #themes
library("ggpubr")
library("viridis")
library("patchwork")
library("ggforce")
library("kableExtra")
library("lme4")
library("brms")
library("rstan")
library("rstanarm")
library("bayesplot")
library("easystats")
library("kableExtra")
library("broom")
library("tidybayes")
library("bmlm")
# rstan options
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores ())
theme_set(theme_classic())
```

```{r data, cache = TRUE}
#import data

df <- readRDS(here::here("data", "df"))
```

```{r dataprep, cache=TRUE}
# prepare data
dt <- df %>%
  dplyr::filter(YearMeasured == 1)  %>%
  dplyr::filter(
    Wave == 2019 |
      Wave == 2018 |
      Wave == 2017 |
      Wave == 2016 |
      Wave == 2015 |
      Wave == 2014 |
      Wave == 2013 |
      Wave == 2012
  ) %>%
  dplyr::group_by(Id) %>% filter(n() > 2) %>%
  dplyr::ungroup(Id)  %>%
  dplyr::select(Id, TSCORE, Warm.Muslims) %>%
  dplyr::filter(!is.na(Warm.Muslims)) %>%
  dplyr::mutate(
    wm_s = scale(Warm.Muslims),
    days = as.integer(TSCORE),
    yr_0 = ((days - min(days)) / 365),
    yrs = (days / 365),
    yr_a = 3545 / 365,
  ) %>%
  dplyr::mutate(Pre_PostATTACK = factor(ifelse(
    TSCORE >= 3545, "post_attack",
    "pre_attack"
  ))) %>%
  dplyr::mutate(Pre_PostATTACK = forcats::fct_relevel(Pre_PostATTACK, c("pre_attack", "post_attack")))


## below are dataframes used for the supplemental timelines in the appendix


# For Maori timline
dm <- df %>%
  dplyr::filter(YearMeasured == 1)  %>%
  dplyr::filter(
    Wave == 2019 |
      Wave == 2018 |
      Wave == 2017 |
      Wave == 2016 |
      Wave == 2015 |
      Wave == 2014 |
      Wave == 2013 |
      Wave == 2012
  ) %>%
  dplyr::group_by(Id) %>% filter(n() > 2) %>%
  dplyr::ungroup(Id)  %>%
  dplyr::select(Id, TSCORE, Warm.Maori) %>%
  dplyr::filter(!is.na(Warm.Maori)) %>%
  dplyr::mutate(
    wm_s = scale(Warm.Maori),
    days = as.integer(TSCORE),
    yr_0 = ((days - min(days)) / 365),
    yrs = (days / 365),
    yr_a = 3545 / 365,
  ) %>%
  dplyr::mutate(Pre_PostATTACK = factor(ifelse(
    TSCORE >= 3545, "post_attack",
    "pre_attack"
  ))) %>%
  dplyr::mutate(Pre_PostATTACK = forcats::fct_relevel(Pre_PostATTACK, c("pre_attack", "post_attack")))


# For Migrant timline
di <- df %>%
  dplyr::filter(YearMeasured == 1)  %>%
  dplyr::filter(
    Wave == 2019 |
      Wave == 2018 |
      Wave == 2017 |
      Wave == 2016 |
      Wave == 2015 |
      Wave == 2014 |
      Wave == 2013 |
      Wave == 2012
  ) %>%
  dplyr::group_by(Id) %>% filter(n() > 2) %>%
  dplyr::ungroup(Id)  %>%
  dplyr::select(Id, TSCORE, Warm.Immigrants) %>%
  dplyr::filter(!is.na(Warm.Immigrants)) %>%
  dplyr::mutate(
    wm_s = scale(Warm.Immigrants),
    days = as.integer(TSCORE),
    yr_0 = ((days - min(days)) / 365),
    yrs = (days / 365),
    yr_a = 3545 / 365,
  ) %>%
  dplyr::mutate(Pre_PostATTACK = factor(ifelse(
    TSCORE >= 3545, "post_attack",
    "pre_attack"
  ))) %>%
  dplyr::mutate(Pre_PostATTACK = forcats::fct_relevel(Pre_PostATTACK, c("pre_attack", "post_attack")))

dnz <- df %>%
  dplyr::filter(YearMeasured == 1)  %>%
  dplyr::filter(
    Wave == 2019 |
      Wave == 2018 |
      Wave == 2017 |
      Wave == 2016 |
      Wave == 2015 |
      Wave == 2014 |
      Wave == 2013 |
      Wave == 2012
  ) %>%
  dplyr::group_by(Id) %>% filter(n() > 2) %>%
  dplyr::ungroup(Id)  %>%
  dplyr::select(Id, TSCORE, Warm.NZEuro) %>%
  dplyr::filter(!is.na(Warm.NZEuro)) %>%
  dplyr::mutate(
    wm_s = scale(Warm.NZEuro),
    days = as.integer(TSCORE),
    yr_0 = ((days - min(days)) / 365),
    yrs = (days / 365),
    yr_a = 3545 / 365,
  ) %>%
  dplyr::mutate(Pre_PostATTACK = factor(ifelse(
    TSCORE >= 3545, "post_attack",
    "pre_attack"
  ))) %>%
  dplyr::mutate(Pre_PostATTACK = forcats::fct_relevel(Pre_PostATTACK, c("pre_attack", "post_attack")))


# For Refugee timline

drefugees <- df %>%
  dplyr::filter(YearMeasured == 1)  %>%
  dplyr::filter(
    Wave == 2019 |
      Wave == 2018 |
      Wave == 2017 |
      Wave == 2016 |
      Wave == 2015 |
      Wave == 2014 |
      Wave == 2013 |
      Wave == 2012
  ) %>%
  dplyr::group_by(Id) %>% filter(n() > 2) %>%
  dplyr::ungroup(Id)  %>%
  dplyr::select(Id, TSCORE, Warm.Refugees) %>%
  dplyr::filter(!is.na(Warm.Refugees)) %>%
  dplyr::mutate(
    wm_s = scale(Warm.Refugees),
    days = as.integer(TSCORE),
    yr_0 = ((days - min(days)) / 365),
    yrs = (days / 365),
    yr_a = 3545 / 365,
  ) %>%
  dplyr::mutate(Pre_PostATTACK = factor(ifelse(
    TSCORE >= 3545, "post_attack",
    "pre_attack"
  ))) %>%
  dplyr::mutate(Pre_PostATTACK = forcats::fct_relevel(Pre_PostATTACK, c("pre_attack", "post_attack")))


# For Chinese timline

dchinese <- df %>%
  dplyr::filter(YearMeasured == 1)  %>%
  dplyr::filter(
    Wave == 2019 |
      Wave == 2018 |
      Wave == 2017 |
      Wave == 2016 |
      Wave == 2015 |
      Wave == 2014 |
      Wave == 2013 |
      Wave == 2012
  ) %>%
  dplyr::group_by(Id) %>% filter(n() > 2) %>%
  dplyr::ungroup(Id)  %>%
  dplyr::select(Id, TSCORE, Warm.Chinese) %>%
  dplyr::filter(!is.na(Warm.Chinese)) %>%
  dplyr::mutate(
    wm_s = scale(Warm.Chinese),
    days = as.integer(TSCORE),
    yr_0 = ((days - min(days)) / 365),
    yrs = (days / 365),
    yr_a = 3545 / 365,
  ) %>%
  dplyr::mutate(Pre_PostATTACK = factor(ifelse(
    TSCORE >= 3545, "post_attack",
    "pre_attack"
  ))) %>%
  dplyr::mutate(Pre_PostATTACK = forcats::fct_relevel(Pre_PostATTACK, c("pre_attack", "post_attack")))


# For Indians timline


dindians <- df %>%
  dplyr::filter(YearMeasured == 1)  %>%
  dplyr::filter(
    Wave == 2019 |
      Wave == 2018 |
      Wave == 2017 |
      Wave == 2016 |
      Wave == 2015 |
      Wave == 2014 |
      Wave == 2013 |
      Wave == 2012
  ) %>%
  dplyr::group_by(Id) %>% filter(n() > 2) %>%
  dplyr::ungroup(Id)  %>%
  dplyr::select(Id, TSCORE, Warm.Indians) %>%
  dplyr::filter(!is.na(Warm.Indians)) %>%
  dplyr::mutate(
    wm_s = scale(Warm.Indians),
    days = as.integer(TSCORE),
    yr_0 = ((days - min(days)) / 365),
    yrs = (days / 365),
    yr_a = 3545 / 365,
  ) %>%
  dplyr::mutate(Pre_PostATTACK = factor(ifelse(
    TSCORE >= 3545, "post_attack",
    "pre_attack"
  ))) %>%
  dplyr::mutate(Pre_PostATTACK = forcats::fct_relevel(Pre_PostATTACK, c("pre_attack", "post_attack")))


# For Pacific Peoples timline

dpacific <- df %>%
  dplyr::filter(YearMeasured == 1)  %>%
  dplyr::filter(
    Wave == 2019 |
      Wave == 2018 |
      Wave == 2017 |
      Wave == 2016 |
      Wave == 2015 |
      Wave == 2014 |
      Wave == 2013 |
      Wave == 2012
  ) %>%
  dplyr::group_by(Id) %>% filter(n() > 2) %>%
  dplyr::ungroup(Id)  %>%
  dplyr::select(Id, TSCORE, Warm.Pacific) %>%
  dplyr::filter(!is.na(Warm.Pacific)) %>%
  dplyr::mutate(
    wm_s = scale(Warm.Pacific),
    days = as.integer(TSCORE),
    yr_0 = ((days - min(days)) / 365),
    yrs = (days / 365),
    yr_a = 3545 / 365,
  ) %>%
  dplyr::mutate(Pre_PostATTACK = factor(ifelse(
    TSCORE >= 3545, "post_attack",
    "pre_attack"
  ))) %>%
  dplyr::mutate(Pre_PostATTACK = forcats::fct_relevel(Pre_PostATTACK, c("pre_attack", "post_attack")))

drefugees <- df %>%
  dplyr::filter(YearMeasured == 1)  %>%
  dplyr::filter(
    Wave == 2019 |
      Wave == 2018 |
      Wave == 2017 |
      Wave == 2016 |
      Wave == 2015 |
      Wave == 2014 |
      Wave == 2013 |
      Wave == 2012
  ) %>%
  dplyr::group_by(Id) %>% filter(n() > 2) %>%
  dplyr::ungroup(Id)  %>%
  dplyr::select(Id, TSCORE, Warm.Refugees) %>%
  dplyr::filter(!is.na(Warm.Refugees)) %>%
  dplyr::mutate(
    wm_s = scale(Warm.Refugees),
    days = as.integer(TSCORE),
    yr_0 = ((days - min(days)) / 365),
    yrs = (days / 365),
    yr_a = 3545 / 365,
  ) %>%
  dplyr::mutate(Pre_PostATTACK = factor(ifelse(
    TSCORE >= 3545, "post_attack",
    "pre_attack"
  ))) %>%
  dplyr::mutate(Pre_PostATTACK = forcats::fct_relevel(Pre_PostATTACK, c("pre_attack", "post_attack")))

```

```{r danalysisdata, cache=TRUE}
 ord_attack <- c("bsline_w09","pre_w10", "pst_w10","pst_w11")

# dataset for models

km2 <- df %>%
  dplyr::select(
    Id,
    Age,
    TSCORE,
    EthnicCats,
    Warm.Overweight,
    Warm.Elderly,
    Warm.MentalIllness,
    Warm.Muslims,
    Warm.Immigrants,
    Warm.Asians,
    Warm.Refugees,
    Wave,
    Warm.Maori,
    Warm.NZEuro,
    Warm.Indians,
    Warm.Chinese,
    Warm.Refugees,
    Warm.Pacific,
    Muslim,
    Euro,
    Relid,
    Religious,
    Pol.Orient,
    TSCORE,
    WSCORE, 
    YearMeasured
  ) %>%
dplyr::filter(Wave == 2017 & YearMeasured == 1 |  Wave == 2018 & YearMeasured == 1| Wave == 2019 & YearMeasured == 1) %>%
   droplevels() %>%
  group_by(Id)%>%
  filter(n() == 3) %>%
  dplyr::mutate(Pre_PostATTACK = as.factor(ifelse(
    TSCORE >= 3545 & Wave == 2018,
    "pst_w10",
    ifelse(
      Wave == 2019,
      "pst_w11",
      ifelse(TSCORE < 3545 & Wave == 2018, "pre_w10",
             "bsline_w09") )
  ))) %>%
  dplyr::mutate(Attack = ifelse(TSCORE >= 3545, "post_attack", "before_attack"))%>%
  dplyr::mutate(days = as.integer(TSCORE),
                years = days / 365) %>%
 # dplyr::filter(Muslim == 0) %>%
  dplyr::group_by(Id) %>%
  dplyr::add_tally()%>%
  dplyr::ungroup()%>%
  filter(n == 3)%>%
  dplyr::mutate(
    cons_s = scale(Pol.Orient),
    r_s = scale(Relid),
    a_s = scale(Age),
    yearS = years - min(years) )%>%
  dplyr::mutate(Pre_PostATTACK = forcats::fct_relevel(Pre_PostATTACK, ord_attack))

#library(table1)  # make pretty tables quickly
#table1::table1(~Muslim|Wave, data = km, overall=F)# there are 31 muslims in 2017
```

```{r  dagpol, include = FALSE, eval = FALSE}
## Use DAG to determine indicators on which to condition on, for causal inference. 
## Note: for now, our focus is on prediction. 

library(ggdag)
dg2 <- dagify(
  wm ~ pp + cs + ml + news + U + yr + rel  + a + eth + ur,
  cs ~ ml + rel + a,
  rel ~ ml + rel + a + eth,
  pp ~ yr,
  a ~ yr,
  ur ~ eth + a + yr,
  rel ~ yr + ur,
  edu ~ ml + eth + ur,
  news ~ pp + yr,
  U ~ pp + cs + ml + news + yr  + rel + edu + a + ur,
  exposure =  "pp",
  outcome =   "wm",
  labels = c(
    "wm" = "Warmth Muslims",
    "a" = "age",
    "eth" = "ethnicity",
    "pp" = "pre/postattacks",
    "cs" = "political conservativism",
    "edu" = "education",
    "ur" = "urban",
    "yr" = "time",
    "rel" = "religion",
    "news" = "media",
    "ml" = "male",
    "U" = "Soc Networks"
  )
) %>%
  tidy_dagitty() 
#%>%
#  control_for("cs")

dplot1 <-
  ggdag::ggdag_collider(dg2, use_labels = "label", text = FALSE) + theme_dag_blank() +
  labs(title = "Causal analysis of Muslim Acceptance requires care to avoid confounding")
dplot1


ggdag::ggdag_adjustment_set(dg2, use_labels = "label", text = FALSE) + theme_dag_blank() +
  labs(title = "")

## BETTER
#(lds_0 + dplot1)/ lds2 /  lds3 / lds4  + plot_annotation(tag_levels = 'a')

#marsden_fig1v2 # 1750 x 2000

```

```{r models, cache=TRUE}
library(lme4)
library(mgcv)
library(splines)
library(ggeffects)
# Check model
#parameters::model_parameters(m1)
## 1.55 years to shooting
#parameters::model_parameters(m1)  estimate expected effect at day of shooting
#4.04 + .2 + .1*1.55


## models below

# muslims
m1 <- lmer(Warm.Muslims ~  Pre_PostATTACK +
             (1 | Id) ,
           data = km2)


p1 <- ggeffects::ggpredict(m1,
                           terms = "Pre_PostATTACK")

p1p <- plot(p1,
            add.data = TRUE,
            dot.alpha = .05,
            jitter = .8) +
  ylab("Warmth to Muslims (1-7)") + labs(title = "Warm Muslims") +
  geom_hline(yintercept = 4.395, color = "green") +
  # scale_y_continuous(limits = c(1, 7)) +
  scale_colour_viridis_d() + xlab("Attack timeline") +
  # geom_vline(xintercept = c(2.8), colour = "red", linetype = "dashed") +
  theme_classic()

## For intro
p1pp <- plot(p1,
            add.data = TRUE,
            dot.alpha = .05,
            jitter = .8) +
  ylab("Warmth to Muslims (1-7)") + labs(title = "Warm Muslims") +
  geom_hline(yintercept = 4.395, color = "green") +
  # scale_y_continuous(limits = c(1, 7)) +
  scale_colour_viridis_d() + xlab("Attack timeline") +
  # geom_vline(xintercept = c(2.8), colour = "red", linetype = "dashed") +
  theme_classic()


## euro
m2 <- lmer(Warm.NZEuro  ~    Pre_PostATTACK +
             (1 | Id) ,
           data = km2)

p2 <- ggeffects::ggpredict(m2,
                           terms = "Pre_PostATTACK")


p2p <- plot(p2,
            add.data = TRUE,
            dot.alpha = .05,
            jitter = .8) +
  ylab("Warmth to NZ Europeans (1-7)") + labs(title = "Warm NZ Europeans") +
  geom_hline(yintercept = 4.395, color = "green") +
  # scale_y_continuous(limits = c(1, 7)) +
  scale_colour_viridis_d() +
  xlab("Attack timeline") +
  # geom_vline(xintercept = c(2.8), colour = "red", linetype = "dashed") +
  theme_classic()


# maori
m3 <- lmer(Warm.Maori ~     Pre_PostATTACK  +
             (1 | Id) ,
           data = km2)
p3 <- ggeffects::ggpredict(m3,
                           terms = "Pre_PostATTACK")


p3p <- plot(p3,
            add.data = TRUE,
            dot.alpha = .05,
            jitter = .8) +
  ylab("Warmth to Māori (1-7)") + labs(title = "Warmth to Māori") +
  geom_hline(yintercept = 4.395, color = "green") +
  #  scale_y_continuous(limits = c(1, 7)) +
  scale_colour_viridis_d() + xlab("Attack timeline") +
  # geom_vline(xintercept = c(2.8), colour = "red", linetype = "dashed") +
  theme_classic()

# migrants

m4 <- lmer(Warm.Immigrants ~    Pre_PostATTACK  +
             (1 | Id) ,
           data = km2)

p4 <- ggeffects::ggpredict(m4,
                           terms = "Pre_PostATTACK")

p4p <- plot(p4,
            add.data = TRUE,
            dot.alpha = .05,
            jitter = .8) +
  ylab("Warmth to Immigrants (1-7)") + labs(title = "Warmth to Immigrants") +
  geom_hline(yintercept = 4.395, color = "green") +
  #  scale_y_continuous(limits = c(1, 7)) +
  scale_colour_viridis_d() + xlab("Attack timeline") +
  # geom_vline(xintercept = c(2.8), colour = "red", linetype = "dashed") +
  theme_classic()


# asians

m5 <- lmer(Warm.Asians ~ Pre_PostATTACK +
             (1 | Id) ,
           data = km2)

p5 <- ggeffects::ggpredict(m5,
                           terms = "Pre_PostATTACK")

p5p <- plot(p5,
            add.data = TRUE,
            dot.alpha = .05,
            jitter = .8) +
  ylab("Warmth to Asians (1-7)") + labs(title = "Warmth to Asians") +
  geom_hline(yintercept = 4.395, color = "green") +
  #  scale_y_continuous(limits = c(1, 7)) +
  scale_colour_viridis_d() + xlab("Attack timeline") +
  # geom_vline(xintercept = c(2.8), colour = "red", linetype = "dashed") +
  theme_classic()


# indians

m6 <- lmer(Warm.Indians ~ Pre_PostATTACK +
             (1 | Id) ,
           data = km2)

p6 <- ggeffects::ggpredict(m6,
                           terms = "Pre_PostATTACK")

p6p <- plot(p6,
            add.data = TRUE,
            dot.alpha = .05,
            jitter = .8) +
  ylab("Warmth to Indians (1-7)") + labs(title = "Warmth to Indians") +
  geom_hline(yintercept = 4.395, color = "green") +
  #  scale_y_continuous(limits = c(1, 7)) +
  scale_colour_viridis_d() + xlab("Attack timeline") +
  # geom_vline(xintercept = c(2.8), colour = "red", linetype = "dashed") +
  theme_classic()


# Chinese

m7 <- lmer(Warm.Chinese  ~  Pre_PostATTACK  +
             (1 | Id) ,
           data = km2)

p7 <- ggeffects::ggpredict(m7,
                           terms = "Pre_PostATTACK")

p7p <- plot(p7,
            add.data = TRUE,
            dot.alpha = .05,
            jitter = .8) +
  ylab("Warmth to Chinese (1-7)") + labs(title = "Warmth to Chinese") +
  geom_hline(yintercept = 4.395, color = "green") +
  #  scale_y_continuous(limits = c(1, 7)) +
  scale_colour_viridis_d() + xlab("Attack timeline") +
  # geom_vline(xintercept = c(2.8), colour = "red", linetype = "dashed") +
  theme_classic()


## pacific

m8 <- lmer(Warm.Pacific  ~  Pre_PostATTACK  +
             (1 | Id) ,
           data = km2)


p8 <- ggeffects::ggpredict(m8,
                           terms = "Pre_PostATTACK")

p8p <- plot(p8,
            add.data = TRUE,
            dot.alpha = .05,
            jitter = .8) +
  ylab("Warmth to Pacific (1-7)") + labs(title = "Warmth to Pacific Peoples") +
  geom_hline(yintercept = 4.395, color = "green") +
  #  scale_y_continuous(limits = c(1, 7)) +
  scale_colour_viridis_d() + xlab("Attack timeline") +
  # geom_vline(xintercept = c(2.8), colour = "red", linetype = "dashed") +
  theme_classic()


## Elderly (contrast)

m9 <- lmer(Warm.Elderly  ~  Pre_PostATTACK +
             (1 | Id),
           data = km2)


p9 <- ggeffects::ggpredict(m9,
                           terms = "Pre_PostATTACK")

p9p <- plot(p9,
            add.data = TRUE,
            dot.alpha = .05,
            jitter = .8) +
  ylab("Warmth to Elderly (1-7)") + labs(title = "Warmth to Elderly") +
  geom_hline(yintercept = 4.395, color = "green") +
  #  scale_y_continuous(limits = c(1, 7)) +
  scale_colour_viridis_d() + xlab("Attack timeline") +
  # geom_vline(xintercept = c(2.8), colour = "red", linetype = "dashed") +
  theme_classic()


## mental illness

m10 <- lmer(Warm.MentalIllness  ~  Pre_PostATTACK +
              (1 | Id) ,
            data = km2)

p10 <- ggeffects::ggpredict(m10,
                            terms = "Pre_PostATTACK")

p10p <- plot(p10,
             add.data = TRUE,
             dot.alpha = .05,
             jitter = .8) +
  ylab("Warmth to the Mentally ill (1-7)") + labs(title = "Warmth to the Mentally ill") +
  geom_hline(yintercept = 4.395, color = "green") +
  #  scale_y_continuous(limits = c(1, 7)) +
  scale_colour_viridis_d() + xlab("Attack timeline") +
  # geom_vline(xintercept = c(2.8), colour = "red", linetype = "dashed") +
  theme_classic()


### Overweight

m11 <- lmer(Warm.Overweight  ~ Pre_PostATTACK +
              (1 | Id) ,
            data = km2)


p11 <- ggeffects::ggpredict(m11,
                            terms = "Pre_PostATTACK")

p11p <- plot(p11,
             add.data = TRUE,
             dot.alpha = .05,
             jitter = .8) +
  ylab("Warmth to Overweight (1-7)") + labs(title = "Warmth to Overweight") +
  geom_hline(yintercept = 4.395, color = "green") +
  #  scale_y_continuous(limits = c(1, 7)) +
  scale_colour_viridis_d() + xlab("Attack timeline") +
  # geom_vline(xintercept = c(2.8), colour = "red", linetype = "dashed") +
  theme_classic()


## Refugees

m12 <- lmer(Warm.Refugees  ~  Pre_PostATTACK +
              (1 | Id) ,
            data = km2)

p12 <- ggeffects::ggpredict(m12,
                            terms = "Pre_PostATTACK")

p12p <- plot(p12,
             add.data = TRUE,
             dot.alpha = .05,
             jitter = .8) +
  ylab("Warmth to Refugees (1-7)") + labs(title = "Warmth to Refugees") +
  geom_hline(yintercept = 4.395, color = "green") +
  #  scale_y_continuous(limits = c(1, 7)) +
  scale_colour_viridis_d() + xlab("Attack timeline") +
  # geom_vline(xintercept = c(2.8), colour = "red", linetype = "dashed") +
  theme_classic()

## For graphs
desc <-
  'Large boost in Muslim acceptance following shootings; However Muslim acceptance still lags behind.'
p1a <-
  p1p #+   ggforce::geom_mark_ellipse(aes(label = 'Pre/Post Attack', description = desc), colour = "red") + theme_classic()
p2a <-
  p2p # +   ggforce::geom_mark_ellipse(aes(label = 'Pre/Post Attack')) + theme_classic()
p3a <-
  p3p # +   ggforce::geom_mark_ellipse(aes(label = 'Pre/Post Attack')) + theme_classic()
p4a <-
  p4p #+   ggforce::geom_mark_ellipse(aes(label = 'Pre/Post Attack')) + theme_classic()

p5a <-
  p5p #+   ggforce::geom_mark_ellipse(aes(label = 'Pre/Post Attack')) + theme_classic()


p6a <-
  p6p #+   ggforce::geom_mark_ellipse(aes(label = 'Pre/Post Attack')) + theme_classic()

p7a <-
  p7p #+   ggforce::geom_mark_ellipse(aes(label = 'Pre/Post Attack')) + theme_classic()


p8a <-
  p8p #+   ggforce::geom_mark_ellipse(aes(label = 'Pre/Post Attack')) + theme_classic()

p9a <-
  p9p #+   ggforce::geom_mark_ellipse(aes(label = 'Pre/Post Attack')) + theme_classic()

p10a <-
  p10p #+   ggforce::geom_mark_ellipse(aes(label = 'Pre/Post Attack')) + theme_classic()

p11a <-
  p11p #+   ggforce::geom_mark_ellipse(aes(label = 'Pre/Post Attack')) + theme_classic()

p12a <-
  p12p #+   ggforce::geom_mark_ellipse(aes(label = 'Pre/Post Attack')) + theme_classic()

lds3 <-
  (p1a +
     p4a +
     p5a +
     p6a +
     p7a +
     p12a) +
  plot_annotation(tag_levels = 'a',
                  title = "Attitudes to Muslims and Non-Pacific Minorities",
                  subtitle = "pre/post attacks") +
  plot_layout(guides = 'collect', ncol = 1) +
  theme_classic()

lds4 <-
  (p2a +
     p3a +
     p8a +
     p9a +
     p10a +
     p11a) + plot_annotation(tag_levels = 'a',
                             title = "Attitudes to contrast groups",
                             subtitle = "Pacific/Maori/non-Ethnic minorities: pre/post attacks") +  plot_layout(guides = 'collect', ncol = 1)


 
# RESULTS BELOW
# parameters::model_parameters(m1)
# parameters::model_parameters(m2)
# parameters::model_parameters(m2)
# parameters::model_parameters(m2)
# parameters::model_parameters(m2)
# parameters::model_parameters(m2)
# parameters::model_parameters(m2)
# parameters::model_parameters(m2)
# parameters::model_parameters(m2)
# parameters::model_parameters(m11)
# parameters::model_parameters(m10)
# parameters::model_parameters(m11)
```

## Summary

```{r fig.fullwidth = TRUE, layout="l-body-outset", cache=TRUE, fig.cap="\\label{fig:muslimboost} Change in acceptance of Muslims following the Christchurch Mosque attacks March 15, 2019.  Green horizonal line indicates peak acceptance of Muslims, which occurred following the attacks (N = 11272, Years = 2017-2020, Source = New Zealand Attitudes and Values Study)"}
p1pp
```


- Following the Christchurch Mosque attacks, warmth towards Muslim grew.
- Despite this growth, warmth to Muslims lags behind all other groups (except overweight people.)
- Following the mosque attacks non-Pacific/Māori minority groups with Muslims also received a boost in warmth.
- The Muslim acceptance gap remains large. 


## Introduction

We investigate warmth to Muslims before and after the 15 March 2019 mosque attacks in a nationally diverse longitudinal sample of New Zealanders (*N* = 11,272), and clarify how levels of warmth changed to Muslims and other groups.^[
The New Zealand Attitudes and Values Study (NZAVS) is a nationally representative panel study that Prof Chris Sibley started in 2009 [@nzavs2021], which has measured over 65,000 New Zealanders (see [NZAVS](https://www.psych.auckland.ac.nz/en/about/new-zealand-attitudes-and-values-study.html)]

<aside>
The NZAVS measures tolerance using validated "affective thermometers" See [@sibley2020prejudice].
</aside>

### Findings

  -   Following the attacks there was a substantial increase in warmth to Muslims (Figure \@ref(fig:graphsmodels)a)
  -   Following the attacks, there was also a small boost in warmth to Immigrants (Figure \@ref(fig:graphsmodels)b), Asians (Figure \@ref(fig:graphsmodels)c), Indians (Figure \@ref(fig:graphsmodels)d), Chinese people (Figure \@ref(fig:graphsmodels)e), and Refugees (Figure \@ref(fig:graphsmodels)f.)
  -  The boost in warmth was specific to Muslims and non-Pacific minorities  (Figure \@ref(fig:graphsmodels)a-f.)
  -  Despite the post-attack boost in warmth to Muslims, warmth to Muslims still lags behind warmth to other groups. (Figure \@ref(fig:graphsmodels)a-f).
  -  Whether the in boost to warmth to Muslims and ethnic groups associated with Muslims persists remains unclear. 
  

Muslims and groups non-Pacific ethnic minorities

```{r  graphsmodels, fig.height = 75, fig.fullwidth = TRUE, layout="l-body-outset", cache=TRUE, fig.cap="\\label{fig:graphsmodels} Increase in Warmth to Muslims After Shootings (red-dashed line), however, the acceptance of Muslims lags behind other minority groups. Green horizonal line indicates peak acceptance of Muslims, (N = 11272, Years = 2017-2020, Source = New Zealand Attitudes and Values Study)", echo = FALSE}
lds3
```


Contrast groups that are not associated with Muslims.

```{r graphsmodels2, fig.height = 75, fig.fullwidth = TRUE,  layout="l-body-outset", cache=TRUE, fig.cap="\\label{fig:graphsmodels2} There is no evidence for substantial change in prejudice pre-post shootings among groups that are not associated with Muslims.  Green horizonal line indicates peak acceptance of Muslims, which occurred following the attacks (N = 11272, Years = 2017-2020, Source = New Zealand Attitudes and Values Study)", echo = FALSE}
lds4
```




### Importance of findings

  -   Although the purpose of the Mosque attacks was to incite division, the attacks caused a strong boost in acceptance.
  -   The reasons for the boost in Muslim acceptance are unclear.
<aside>
Speculating, the government's response, media's response [@shaver2017news], and non-Muslim church responses [@Shaver2016-fs] likely played a role in boosting Muslim acceptance.
</aside>
  -   Whether growth in acceptance will be sustained remains unclear
  -   Whether acceptance reverts to pre-shooting levels remains unclear.



## Appendix 1: Design

Participants responded to waves 9, 10, and 11 of the New Zealand Attitudes and Values Study. In total there were `r length(unique(km2$Id))` participants who responded to all three waves. See Figure \@ref(fig:pptimeline), Table \@ref(tab:designtable)

```{r designtable,  tab.cap="\\label{tab:designtable}"}
km2 %>%
  select(Pre_PostATTACK) %>%
  group_by(Pre_PostATTACK) %>%
  summarise(n = n()) %>%
  kbl(caption = "Participant numbers divided by condition: baseline, wave 10 pre/shootings, wave 10 post-shooting, and wave 11") %>%
   kable_classic_2(c("striped", "hover"), full_width = TRUE)
```

```{r pptimeline, cache=TRUE, fig.fullwidth = TRUE,  layout="l-body-outset", fig.width=12, fig.height=12, fig.cap="\\label{fig:pptimeline} Within-participant repeated measures covering the years before and following the attacks allow precise estimates of attitudinal change within-people (N = 11,481)."}
## timeline
rarep<-df%>%
  dplyr::filter(YearMeasured == 1) %>%
  dplyr::filter(Wave == 2017 | Wave == 2018 | Wave == 2019) %>%
  dplyr::group_by(Id) %>% filter(n() == 3) %>%
  dplyr::filter(Wave == 2017 | Wave == 2018 | Wave == 2019) %>%
  droplevels() %>%
  dplyr::ungroup(Id) %>%
  dplyr::mutate(timeline = make_date(year = 2009, month = 6, day = 30)+ TSCORE)%>%
  dplyr:::count(day = floor_date(timeline, "day"))%>%
  dplyr::mutate(Condition = factor(ifelse(day < "2018-06-18", -1, 
                                          ifelse(day >="2018-06-18" & day < "2019-03-15", 0,
                                                 ifelse( day >="2019-03-15" & day < "2019-06-18",1 , 
                                                         2))),
                                                 labels= c("PRE-ATTACK Baseline wv9 N = 11,481","PRE-ATTACK CONTROL rep measure wv10: n = 8120","IMMEDIATE POST-ATTACK rep measure wv10: PostAttack n = 3361", "DELAY POST-ATTACK Repeated measure post attack 2019: N= 11,481")))%>%
  arrange(day)
#table(rarep$Condition)
# get data of change of baseline
dates_vline1<- as.Date("2018-06-18")

table(km2$Pre_PostATTACK)

# get attack date
dates_vline2<- as.Date("2019-03-15")
dates_vline3<- as.Date("2019-06-18")

# for line in a graph
dates_vline2b<-which(rarep$day %in% dates_vline2)
dates_vline1b<-which(rarep$day %in% dates_vline1)
dates_vline3b<-which(rarep$day %in% dates_vline3)

lds2 <- ggplot(rarep, aes(day, n)) + geom_col(aes(fill = Condition)) + scale_x_date(date_labels = "%b/%Y",
                                                                                    limits = c(as.Date("2017-08-25"), as.Date("2020-10-15")))  +
  scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
  geom_vline(xintercept = as.numeric(rarep$day[dates_vline2b]),
             col = "red",
             linetype = "dashed") +
  xlab("NZAVS Waves years 2017 - 2020 daily counts") + ylab("Count of Responses")+
  theme_classic() +
  annotate(
    "rect",
    xmin = as.Date("2017-08-25"),
    xmax = dates_vline1,
    ymin = 0,
    ymax = 900,
    alpha = 0
  ) +
  annotate(
    "rect",
    xmin = dates_vline2,
    xmax = dates_vline3,
    ymin = 0,
    ymax = 900,
    alpha = .3,
    fill = "darkred"
  ) +
  annotate(
    "rect",
    xmin = dates_vline1,
    xmax = dates_vline2,
    ymin = 0,
    ymax = 900,
    alpha = .3
  ) +
  annotate(
    "rect",
    xmin = dates_vline3,
    xmax = as.Date("2020-10-15"),
    ymin = 0,
    ymax = 900,
    alpha = .05,
    fill = "red"
  ) +
  annotate(
    "text",
    x = as.Date("2018-10-15"),
    y = 980,
    label = "Wave 10
           repeated pre-attacks"
  ) +
  annotate(
    "text",
    x = as.Date("2018-01-15"),
    y = 980,
    label = "Wave 9
           baseline (control)"
  ) +
  annotate(
    "text",
    x = as.Date("2019-04-30"),
    y = 980,
    label = "Wave 10
           repeated post attacks"
  ) +
  annotate(
    "text",
    x = as.Date("2020-02-15"),
    y = 980,
    label = "Wave 11
           repeated during the year following attacks"
  ) +
  annotate(
    geom = "curve",
    x = as.Date("2018-02-15"),
    y = 750,
    xend = as.Date("2018-10-15"),
    yend = 750,
    curvature = -.3,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(
    geom = "curve",
    x = as.Date("2018-02-15"),
    y = 750,
    xend = as.Date("2019-05-15"),
    yend = 750,
    curvature = -.3,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate("text",
           x = as.Date("2018-02-01"),
           y = 750,
           label = "0") +
  annotate("text",
           x = as.Date("2018-11-05"),
           y = 750,
           label = "+1") +
  annotate(
    geom = "curve",
    x = as.Date("2019-05-15"),
    y = 800,
    xend = as.Date("2020-05-15"),
    yend = 750,
    curvature = -.3,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate("text",
           x = as.Date("2019-06-05"),
           y = 750,
           label = "+1") +
  annotate("text",
           x = as.Date("2020-05-30"),
           y = 750,
           label = "+2") +
  annotate(
    geom = "curve",
    x = as.Date("2018-11-15"),
    y = 800,
    xend = as.Date("2020-05-15"),
    yend = 750,
    curvature = -.3,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  theme(
    legend.position = "top",
    legend.text = element_text(size = 6),
    legend.title = element_text(color = "Black", size = 8)
  ) +
  scale_fill_viridis_d(option = "plasma")

### USE GRAPH OF TIMELINE
lds2
```

## Appendix 2: Background


New Zealand ranks among the world's most tolerant societies [@Oecd2011-qv]. However, Muslims are New Zealand's least accepted minority group [@Shaver2016-fs; @shaver2017news; @hawi2019terrorism; @yogeeswaran2019exploring; @greaves2020comparative; @sibley2020prejudice; @highland2019attitudes; @hawi2019terrorism].

In the context of New Zealand history, the relatively high levels of prejudice against Muslim, as well as the confusion of Muslims with Arabs, might seem surprising.

First, New Zealand's cultural diversity exceeds that of Australia, the United Kingdom, France, Germany, the Netherlands, and Scandinavia. Muslims are only a small part of this diversity. In 2018, New Zealand's Muslim, just over 1.5% of the total population. The Islamic community has been present in New Zealand since at least 1874 (Shepard, 2006). The New Zealand Muslim community is of diverse ethnic and cultural origins --- of those that affiliated with Islam in 2013, 26.9% were born in Asia, 25.7% in New Zealand, 23.3% in the Middle East or Africa, and 21% in the Pacific Islands (Center, 2013). Thus, fewer than a quarter of New Zealand Muslims can be classified as 'Arab.'

<aside>
Colonial New Zealand state never adopted an official state religion, while principles of religious equality and the promotion of social harmony led to the formation of a secular state primary education system beginning in 1877. In such a setting where religious conflicts are few, anti-religious prejudice of any kind is anomalous.
</aside>

Another reason that anti-Muslim in New Zealand is puzzling is that New Zealand is one of the world's most socially progressive and tolerant societies [@Oecd2011-qv], which has a long tradition of religious tolerance and accommodation of religious diversity.

A final source of puzzlement about anti-Muslim prejudice in New Zealand is that there is no record of any extremist Muslim group in New Zealand, nor have there been any reported attacks of Muslims on non-Muslims By contrast many attacks against the Muslim minority were reported prior to 15 March 2019, when 51 Muslims were murdered at two mosques in a single day. Members of Islamic communities in New Zealand have long reported verbal and physical harassment, vandalism, negative media portrayal, and/or have faced difficulties in the labour market [\@ ](Shepard, 2012). Thus, while Muslims in New Zealand have a basis for concern about their experiences of anti-Muslim prejudice, there is no basis from in experience for anti-Muslim prejudice among the non-Muslim majority

### Sources of anti-Muslim prejudice

In previous research, we found that levels of media exposure predicted lower warmth towards Muslims; notably, this effect held at both the low and high end of the political conservativism scale [@shaver2017news]. Whether changes in media coverage of Muslims contributed to rising Muslim acceptance following the attacks is a question that our future research will consider.

 We also found that prior to the attacks, religiously identified New Zealanders were on average more accepting of Muslims [@Shaver2016-fs]. Whether this difference held after the attacks is another question that we will consider in future research.

## Appendix 3: Prejudice trends from 2012-2020 reveal a longstanding "Muslim Acceptance Gap"

Figure \@ref(fig:warmthtime) shows the longer term trend warmth towards Muslims, begining in 2012, when the NZAVS first included questions about about attitudes to Muslims. As evident in the figure, despite gradually increasing warmth towards Muslims, the group as a whole has experienced greater prejudice than other groups. Prejudice of any kind, towards Muslims or other groups, should be addressed because prejudice unfairly affects life experiences for those who are the targets of it. Experiences of unfairness conflict with New Zealand's aspirations to extend manaakitanga, and whanaungatanga to all New Zealanders.

For more analysis of prejudice trends in New Zealand see: [@sibley2020prejudice]

```{r include = FALSE, warmthtime, fig.width=12,  layout="l-body-outset", fig.height=12, fig.cap="\\label{fig:warmthtime} Within-person prejudice change pre/post attacks towards (a) Muslims, (b) Immigrants, (c) Māori, (d) NZ Europeans. Redline indicates mosque attacks. Greenline indicates maximum warmth to Muslims, which was strongly boosted post-attacks, yet lags behind other groups", cache = TRUE, fig.fullwidth = TRUE, include = TRUE}

ld <- ggplot(data = dt,
             aes(x = yrs,
                 y = Warm.Muslims))

lds_0 <-ld + geom_line(alpha = .005) +
  stat_summary(
    geom = "point",
    fun = mean,
    size = .1,
    alpha = .2
  ) +
  geom_smooth(method ="gam" ) +  theme_minimal() + labs("")   + theme(
    legend.position = "right",
    legend.text = element_text(size = 6),
    legend.title = element_text(color = "Black", size = 8)
  ) + scale_colour_viridis_d(option = "plasma") +   geom_vline(xintercept= 9.71, linetype="dashed", color = "red") +
  geom_hline(yintercept= 4.395, color = "green") +
  ylab("Warmth (1-7)") +
  labs(title="Warmth to Muslims") # +
#  xlab("Years 2011-2020, N = 22,254")

li <- ggplot(data = di,
             aes(x = yrs,
                 y = Warm.Immigrants))

li_0 <-li + geom_line(alpha = .005) +
  stat_summary(
    geom = "point",
    fun = mean,
    size = .1,
    alpha = .2
  ) +
  geom_smooth(method = "gam") +
  theme_minimal() + labs("")   + theme(
    legend.position = "right",
    legend.text = element_text(size = 6),
    legend.title = element_text(color = "Black", size = 8)
  ) + scale_colour_viridis_d(option = "plasma") +
  geom_vline(xintercept= 9.71, linetype="dashed", color = "red") +
  geom_hline(yintercept= 4.4, color = "green") +
  ylab("Warmth (1-7)") +
  labs(title="Warmth to Immigrants") #+
 # xlab("Years 2011-2020, N = 22,254")

## indians
lm <- ggplot(data = dindians,
             aes(x = yrs,
                 y = Warm.Indians))

lm_m <-lm + geom_line(alpha = .005) +
  stat_summary(
    geom = "point",
    fun = mean,
    size = .1,
    alpha = .2
  ) +
  geom_smooth( method = "gam" ) +
  theme_minimal() + labs("")   + theme(
    legend.position = "right",
    legend.text = element_text(size = 6),
    legend.title = element_text(color = "Black", size = 8)
  ) + scale_colour_viridis_d(option = "plasma") +
  geom_vline(xintercept= 9.71, linetype="dashed", color = "red") +
  geom_hline(yintercept= 4.4, color = "green") +
  ylab("Warmth (1-7)") +
  labs(title="Warmth to Indians")
  #+
 # xlab("Years 2011-2020, N = 22,254")

# Chinese
lnz <- ggplot(data = dchinese,
              aes(x = yrs,
                  y = Warm.Chinese))

lnz_0 <-lnz + geom_line(alpha = .005) +
  stat_summary(
    geom = "point",
    fun = mean,
    size = .1,
    alpha = .2
  ) +
  geom_smooth( method = "gam" ) +
  theme_classic() + labs("")   + theme(
    legend.position = "right",
    legend.text = element_text(size = 6),
    legend.title = element_text(color = "Black", size = 8)
  ) + scale_colour_viridis_d(option = "plasma") +
  geom_vline(xintercept= 9.71, linetype="dashed", color = "red") +
  geom_hline(yintercept= 4.4, color = "green") +
  ylab("Warmth (1-7)") +
  labs(title="Warmth to Chinese") +
  xlab("Years 2011-2020, N = 22,254")

lds_0 + li_0 + lm_m + lnz_0 +  plot_layout(guides = 'collect', nrow = 1, byrow = FALSE) +   plot_annotation(title = "Timeline of attitudes to different groups in New Zealand; years 2011-2020: Source: NZAVS, N = 22,254", subtitle = "Green line = maximum level of warmth for Muslims, red line = Mosque attacks; Alpha for points on graph were set to .02 to avoid overplotting; method for estimation", tag_levels = 'a')

```

```{r  modelspolitics,  cache = TRUE}

m6 <- lmer(Warm.Muslims ~  cons_s * Attack +  EthnicCats + 
             a_s +
             r_s + (1|Id) , # dependence owing to the week of response
           data=km2)

p6 <- plot(ggeffects::ggpredict(m6, terms = c("Attack [all]", "cons_s[all]"), ci = .89)) + xlab("Conservativism") + ylab("Warmth Muslims") +  scale_colour_viridis_d()

p7 <- plot(ggeffects::ggpredict(m6, terms = c("cons_s[all]","Attack [all]"), ci = .89), add.data = TRUE, dot.alpha = 0.02, jitter = .2 ) + scale_y_continuous(limits = c(.5,7.5)) +
  xlab("Political Conservativism (SD)") + ylab("Warmth Muslims (1-7") + 
  labs(title = "Warmth to Muslims") + scale_colour_viridis_d()   +
  theme(
    # Change legend background color
    # legend.background = element_rect(fill = "darkgray"),
    #  legend.key = element_rect(fill = "lightblue", color = NA),
    # Change legend key size and key width
    legend.key.size = unit(0.2, "cm"),
     legend.direction = "vertical",,
    legend.key.width = unit(0.2, "cm"),
  ) + 
  guides(size = 1.5)

desc <- "Post Shooting Difference"

p71<-p7 + annotate("rect", 
              xmin = 2., 
              xmax = 2.5, 
              ymin = 3.5, 
              ymax = 4.1,
              alpha = .2, 
              colour = "red") + 
  annotate(
    "rect",
    xmin = -2.,
    xmax = -1.5,
    ymin = 4.4,
    ymax = 4.8,
    alpha = .2,
    colour = "red"
  ) + 
  annotate(
    "text",
    x = 0,
    y = 7.2,
    label = " Greater relative growth in 
    acceptance among conservatives",
    colour = "brown3"
  ) + 
  annotate(
    geom = "curve",
    x = -1,
    y = 6.7,
    xend = -1.75,
    yend = 4.9,
    curvature = 0,
    arrow = arrow(length = unit(2, "mm")),
    colour = "red"
  ) +
   annotate(
    geom = "curve",
    x = 1,
    y = 6.7,
    xend = 2.25,
    yend = 4.2,
    curvature = 0,
    arrow = arrow(length = unit(2, "mm")),
    colour = "red"
  ) 

## Compare this to warmth to Maori
m8 <- lmer(Warm.Maori ~  cons_s * Attack +  EthnicCats + 
             a_s +
             r_s +(1|Id) , # dependence owing to the week of response
           data=km2)

p8 <- plot(ggeffects::ggpredict(m8, terms = c("cons_s[all]","Attack [all]"), ci = .89), 
          add.data = TRUE, dot.alpha = 0.02, jitter = .2 ) + scale_y_continuous(limits = c(.5,7.5)) +
  xlab("Political Conservativism (SD)") + ylab("Warmth Māori (1-7") + 
  labs(title = "Warmth to Māori") + scale_colour_viridis_d()+ 
    theme(
    # Change legend background color
    # legend.background = element_rect(fill = "darkgray"),
    #  legend.key = element_rect(fill = "lightblue", color = NA),
    # Change legend key size and key width
    legend.key.size = unit(0.2, "cm"),
    legend.direction = "vertical",
    legend.key.width = unit(0.2, "cm")
  )+ 
  guides(size = 1.5)

## Warmth to NZEuro
m9 <- lmer(Warm.NZEuro ~  cons_s * Attack +  EthnicCats + 
             a_s +
             r_s +(1|Id) , # dependence owing to the week of response
           data=km2)

p9 <- plot(ggeffects::ggpredict(m9, terms = c("cons_s[all]","Attack [all]"), ci = .89), 
          add.data = TRUE, dot.alpha = 0.02, jitter = .2 ) + scale_y_continuous(limits = c(.5,7.5)) +
  xlab("Political Conservativism (SD)") + ylab("Warmth NZ Europeans (1-7") + 
  labs(title = "Warmth to NZ Europeans") + scale_colour_viridis_d() + 
    theme(
    # Change legend background color
    # legend.background = element_rect(fill = "darkgray"),
    #  legend.key = element_rect(fill = "lightblue", color = NA),
    # Change legend key size and key width
    legend.key.size = unit(0.2, "cm"),
     legend.direction = "vertical",
    legend.key.width = unit(0.2, "cm")
  )+ 
  guides(size = 1.5)

m10 <- lmer(Warm.Immigrants ~  cons_s * Attack +  EthnicCats + 
             a_s +
             r_s +(1|Id) , # dependence owing to the week of response
           data=km2)

p10 <-
  plot(
    ggeffects::ggpredict(
      m10,
      terms = c("cons_s[all]", "Attack [all]"),
      ci = .89
    ),
    add.data = TRUE,
    dot.alpha = 0.02,
    jitter = .2
  ) + scale_y_continuous(limits = c(.5, 7.5)) +
  xlab("Political Conservativism (SD)") + ylab("Warmth Immigrants (1-7") +
  labs(title = "Warmth to Immigrants") + scale_colour_viridis_d()+
  theme(
    # Change legend background color
    # legend.background = element_rect(fill = "darkgray"),
    #  legend.key = element_rect(fill = "lightblue", color = NA),
    # Change legend key size and key width
    legend.key.size = unit(0.2, "cm"),
    legend.key.width = unit(0.2, "cm"),
    legend.direction = "vertical") +
  guides(size = 1.5) +
  annotate(
    "rect",
    xmin = 2.,
    xmax = 2.5,
    ymin = 4.2,
    ymax = 4.4,
    alpha = .2,
    colour = "red"
  ) + 
  annotate(
    "rect",
    xmin = -2.,
    xmax = -1.5,
    ymin = 4.75,
    ymax = 4.95,
    alpha = .2,
    colour = "red"
  ) + 
  annotate(
    "text",
    x = 0,
    y = 7.2,
    label = "Boost to Immigrant Warmth was linear across political conservativism",
    colour = "brown3"
  ) + 
  annotate(
    geom = "curve",
    x = -1,
    y = 6.7,
    xend = -1.75,
    yend = 4.95,
    curvature = 0,
    arrow = arrow(length = unit(2, "mm")),
    colour = "red"
  ) +
   annotate(
    geom = "curve",
    x = 1,
    y = 6.7,
    xend = 2.25,
    yend = 4.4,
    curvature = 0,
    arrow = arrow(length = unit(2, "mm")),
    colour = "red"
  ) 
```

## Appendix 4: Political conservatives also grew more accepting of Muslims after the 2019 Mosque attacks.

Generally, greater political conservativism predicts greater minority group prejudice. In absolute terms, however, growth in Muslim acceptance following the shootings was stronger at the conservative end of the scale (see Figure \@ref(fig:graphsmodelsPol). 

```{r  graphsmodelsPol, fig.fullwidth = TRUE,  layout="l-body-outset", fig.width=12, fig.height=25, cache = TRUE, fig.cap="\\label{fig:graphsmodelsPol} Warmth to Muslims (y-axis) and other groups by political conservativism (x-axis) pre/post shootings (the solid lines). The shift betweenand the purple/blue lines (pre-attacks) and the yellow/green lines (post-attacks) shows the magnitude of growth in minority group acceptance. Here we plot all expected values of the model as points. The darkness of the areas on the graph reflect densities of responses. This approach allows us to visualise the variance around average responses. Results reveal that the mosque attacks led to a greater increase in warmth towards Muslims among political conservatives. However, this population had more headroom for growth in warmth. Whether this boost in Muslim warmth is sustained remains to be seen: (N = 11272, Years = 2017-2020, Source = New Zealand Attitudes and Values Study)", eval=TRUE, echo = FALSE}
lds4 <-  p71 + p10 + p8 + p9 +  plot_annotation(tag_levels = 'a') +   plot_layout(ncol = 2,  byrow = FALSE)  +  plot_layout(guides = 'collect')
lds4 
```


## Appendix 5: Regression Discontinuity Analysis 


```{r}
glimpse(df)
df_rdd <- df %>%
  dplyr::select(
    Id,
    Age,
    TSCORE,
    EthnicCats,
    Warm.Overweight,
    Warm.Elderly,
    Warm.MentalIllness,
    Warm.Muslims,
    Warm.Immigrants,
    Warm.Asians,
    Warm.Refugees,
    Wave,
    Warm.Maori,
    Warm.NZEuro,
    Warm.Indians,
    Warm.Chinese,
    Warm.Refugees,
    Warm.Pacific,
    Muslim,
    Euro,
    Relid,
    Religious,
    Pol.Orient,
    TSCORE,
    WSCORE,
    Terrorism.Anxiety,
    KESSLER6sum,
    KESSLER6,
    BELONG,
    PWI,
    YearMeasured
  ) %>%
  dplyr::filter(TSCORE >= 3395 & TSCORE <= 3695
  )%>%
  dplyr::mutate(Pre_Post_attack = as.factor(ifelse(
    TSCORE >= 3545, "Post_Attack", "Pre_Attack"
  ))) %>%
  dplyr::mutate(Pre_Post_attack = forcats::fct_relevel(Pre_Post_attack, c("Pre_Attack", "Post_Attack"))) %>%
  dplyr::mutate(days = as.integer(TSCORE),
                years = days / 365) %>%
  dplyr::filter(Muslim == 0)


length(unique(df_rdd$Id))


#library(table1)  # make pretty tables quickly
#table1::table1(~Muslim|Wave, data = km, overall=F)# there are 31 muslims in 2017
```


```{r}
## RDD FULL SAMPLE

np <-
  ggplot(data = df_rdd,
         aes(
           x = days,
           y = KESSLER6,
           group = Pre_Post_attack,
           colour = Pre_Post_attack
         ))+ scale_fill_viridis_c(option = "plasma")
change_distress <- np +
  geom_point(alpha = .03) +
  geom_smooth() +
  theme_classic() + 
  scale_color_viridis_d(option = "plasma") +  
  labs(title = "Regression discontinuity attack shows little change in distress")  +   theme(
    legend.position = "right",
    legend.text = element_text(size = 6),
    legend.title = element_text(color = "Black", size = 8)) + 
  ylab("Kessler 6: scale 0-4")

cd <- change_distress + ggtitle("Regression Discontinuity Analysis of Kessler6 Distress", subtitle ="150 days prior to/following 15 March 2019 Mosque Shootings")
```

```{r}
## RDD FULL SAMPLE

np2 <-
  ggplot(data = df_rdd,
         aes(
           x = days,
           y = Terrorism.Anxiety,
           group = Pre_Post_attack,
           colour = Pre_Post_attack
         ))+ scale_fill_viridis_c(option = "plasma")
change_terror <- np2 +
  geom_point(alpha = .03) +
  geom_smooth() +
  theme_classic() + 
  scale_color_viridis_d(option = "plasma") +  
  labs(title = "Regression discontinuity attack shows greater change in terrorism anxiety")  +   theme(
    legend.position = "right",
    legend.text = element_text(size = 6),
    legend.title = element_text(color = "Black", size = 8))+ 
  ylab("Terrorism Anxiety: scale 1-7")

ct <-change_terror + ggtitle("Regression Discontinuity Analysis of Terrorism Anxiety", subtitle ="150 days prior to/following 15 March 2019 Mosque Shootings")


np3 <-
  ggplot(data = df_rdd,
         aes(
           x = days,
           y = BELONG,
           group = Pre_Post_attack,
           colour = Pre_Post_attack
         ))+ scale_fill_viridis_c(option = "plasma")
change_belong <- np3 +
  geom_point(alpha = .03) +
  geom_smooth() +
  theme_classic() + 
  scale_color_viridis_d(option = "plasma") +  
  labs(title = "Regression discontinuity attack shows greater change in community belonging")  +   theme(
    legend.position = "right",
    legend.text = element_text(size = 6),
    legend.title = element_text(color = "Black", size = 8))+ 
  ylab("Social Belonging: scale 1-7")

sb <-change_belong + ggtitle("Regression Discontinuity Analysis of Social Belonging", subtitle ="150 days prior to/following 15 March 2019 Mosque Shootings")


np4 <-
  ggplot(data = df_rdd,
         aes(
           x = days,
           y = PWI,
           group = Pre_Post_attack,
           colour = Pre_Post_attack
         ))+ scale_fill_viridis_c(option = "plasma")
change_pwi <- np4 +
  geom_point(alpha = .03) +
  geom_smooth() +
  theme_classic() + 
  scale_color_viridis_d(option = "plasma") +  
  labs(title = "Regression discontinuity attack shows greater change in Personal Wellbeing")  +   theme(
    legend.position = "right",
    legend.text = element_text(size = 6),
    legend.title = element_text(color = "Black", size = 8))+ 
  ylab("Personal Wellbeing: scale 1-7")

pwb <-change_belong + ggtitle("Regression Discontinuity Analysis of Personal Well-being", subtitle ="150 days prior to/following 15 March 2019 Mosque Shootings")

pwb

library(patchwork)

ct /cd /sb /pwb + plot_annotation(title= "Specificity of Wellbeing/Distress Response", subtitle = "Non-Muslims Distress Dimenisons Pre/Post Mosque Attacks,  n =  17407", tag_levels = "a")






```




