---
title: "What is the difference between a causal effect and a time trend?"
description: The case of religious change and environmental attitudes| 
author:
  - name: Joseph Bulbulia
    url: https://josephbulbulia.netlify.app
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: 0000-0002-5861-2056
date: 2022-FEB-10
output:
  distill::distill_article:
    self_contained: false
    toc: true
    code_folding: true
bibliography: bibliography.bib
editor_options: 
  chunk_output_type: console
---


```{r load_libraries, include=FALSE}
# setup
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  layout = "l-body-outset",
  fig.width = 16,
  fig.height = 9,
  collapse = TRUE,
  R.options = list(width = 60
)
  )


library("tidyverse")
library("easystats")
library("ggeffects")
library("geepack")
library("easystats")
library("lme4")

```


Causal estimate and an association 


```{r cache=TRUE, echo = FALSE}
# import data
df <- readRDS(here::here("data", "df"))

#USEFUL

sdf.0 <- df %>%
  mutate(Wave = as.numeric(as.character(Wave))) %>%
  arrange(Wave, Id) %>%
  group_by(Id) %>%
  mutate(first = {
    YearMeasured == 1
  } %>% {
    . * !duplicated(.)
  }) %>%
  mutate(
    value_tmp = if_else(first == 1, Wave, NA_real_),
    firstwave  = mean(value_tmp, na.rm = TRUE) # this is a hack, but works
  ) %>%
  mutate(state  = ifelse(
    YearMeasured == -1,
    "deceased",
    ifelse(
      YearMeasured == 0 & Wave < firstwave,
      "notyetmeasured",
      ifelse(YearMeasured == 0 &
               Wave > firstwave, "missing",
             "measured")
    )
  )) %>%
  dplyr::mutate(Wave = as.factor(Wave)) %>% # return Wave to a factor
  dplyr::select(Wave, Id, state, YearMeasured, SampleOriginYear) %>%
  dplyr::filter(state != "notyetmeasured") %>%
  droplevels() %>%
  arrange(Id, Wave)





tf <- df %>%
  dplyr::select(Id, Wave, TSCORE, Religious, Env.ClimateChgReal, YearMeasured, Male, GenCohort, Relid) %>%
  dplyr::filter(YearMeasured == 1) %>%
  dplyr::group_by(Id) %>% filter(n() > 2) %>%
    dplyr::mutate(
    days = as.integer(TSCORE),  # THIS GIVES DAY ZERO  THIS WON'T WORK
    # yr_0 = ((days - min(days)) / 365),
    # yrs = (days / 365),
    # yr_a = 3545 / 365,
    wave0 = as.numeric(as.character(Wave)) - min(as.numeric(as.character(Wave)))
  ) %>%   # THIS GIVES AN EVENT -- HERE THE MOSQUE SHOOTINGS
  ungroup() %>%
  # dplyr::mutate(Pre_PostATTACK = factor(ifelse(
  #   TSCORE >= 3545, "post_attack",
  #   "pre_attack"
  # ))) %>%
  dplyr::mutate(religious = as.numeric(Religious)-1) %>%
 # dplyr::mutate(Pre_PostATTACK = forcats::fct_relevel(Pre_PostATTACK, c("pre_attack", "post_attack"))) %>%
  dplyr::group_by(Id) %>% filter(n() > 1) %>%
  drop_na() %>%
  arrange(Id, wave0) %>%
   dplyr::mutate(across(
    c(religious,
      Env.ClimateChgReal, 
      Male, 
      Relid),
    list(lag = lag)
  )) %>% # get lag * 2
  dplyr::mutate(across( # sometimes useful
    c(religious_lag,
      Env.ClimateChgReal_lag,
      Male_lag,
      Relid),
    list(lag = lag)
  )) %>%
  dplyr::mutate(across(
    c(religious,
      Env.ClimateChgReal),
    list(lead = lead)
  )) %>%
  dplyr::ungroup(Id)  %>%
  droplevels() %>%
#  dplyr::group_by(Id) %>% filter(n() > 1) %>%
  dplyr::arrange(Id,wave0)
```


```{r cache=TRUE, echo = FALSE}
length(unique(tf$Id))
```

## Latent growth model

Everying is growing in environmental acceptance, religious people are growing more slowly

```{r cache=TRUE}
# This is one type of model 
library(lme4)

# Standard growth model
mod00 <- lmer(Env.ClimateChgReal ~ # outcome (after exposure)
               scale(yrs) * as.factor(religious) + #exposure 
               Male + # 
               GenCohort + # 
               (1|Id),  # dependencies from the repeated measures 
             data = tf)

mod00%>%
  parameters() %>%
  print_html()
```

Graph

```{r cache=TRUE}
plot(ggeffects::ggemmeans(mod00, terms=c("yrs","religious")), add.data=TRUE, dot.alpha =.005)
```

## Causal estimation

Here we attempt causal inference. 

```{r}
mod1 <- lmer(Env.ClimateChgReal_lead ~ # outcome (after exposure)
               religious + #exposure 
               religious_lag + # control for previous exposure + 
              # religious_lag_lag + 
               Env.ClimateChgReal_lag + #Control for previous outcome
              # Env.ClimateChgReal_lag_lag + 
               Male_lag_lag+ # baseline confounder control
               GenCohort + # baseline confounder control
               yrs + # year trend
               (1|Id),  # dependencies from the repeated measures 
             data = tf)
```

We find no causal effect 


```{r}
mod1%>%
  parameters() %>%
  print_html()

plot(ggeffects::ggemmeans(mod1, terms=c("religious")), add.data=TRUE, dot.alpha =.005)
```

# Target trial

We can emmulate a target trial...

```{r}
## CONDITIONS
tf1<- tf %>%
  arrange(Id,wave0) %>%
  group_by(Id) %>%
  mutate(always  = mean(religious, na.rm = TRUE) ) %>%# this is a hack, but works
  filter(!always == 1) %>% # Get rid of people who were always religious 
  mutate(convert = {
    religious == 1 & religious_lag ==0 & religious_lag_lag == 0 & religious_lead !=0
  } %>% {
    . * !duplicated(.)
  })%>%
  mutate(trt = ifelse(
    convert == 1,
    1,
     0))%>%
  dplyr::mutate(
                trt_lead2 = lead(trt,  n=2),
                trt_lag = lag(trt)) %>%
  dplyr::filter(!trt_lead2 == 1)  %>%
            ungroup() %>%
  arrange(Id, wave0)


#table(tf1$trt)
#sum(is.na(tf1$trt_lead2))

# how many Id's
#length(unique(tf1$Id))

# How many trt vs contols? 
#table(tf1$trt)

#   mixed effects
mod2 <- lmer(Env.ClimateChgReal_lead ~ # outcome (after exposure)
               trt + #exposure 
               # religious_lag + # control for previous exposure
               Env.ClimateChgReal_lag + #Control for previous outcome
               Male_lag + # baseline confounder control
               GenCohort + # baseline confounder control
               yrs + # year trend
               (1|Id),  # dependencies from the repeated measures 
             data = tf1)

# Table
mod2%>%
  parameters() %>%
  print_html()
```

No effect

```{r}
plot(ggeffects::ggemmeans(mod2, terms=c("trt")), add.data=TRUE, dot.alpha =.05) 
```




Similarly, we do not find an effect with a GEE model

```{r, eval=FALSE}
library(geepack)
# need to drop nas
ts<-tf1%>%
  drop_na()

## Nothing
m0 <- geeglm(
  Env.ClimateChgReal_lead ~ # outcome (after exposure)
               trt + #exposure 
               # religious_lag + # control for previous exposure
               Env.ClimateChgReal_lag + #Control for previous outcome
               Male_lag + # baseline confounder control
               GenCohort + # baseline confounder control
               yrs,
  data = ts,
  id = Id,
  family = "gaussian",
 # weights = ipw,
  waves = wave0,
  corstr = "ar1"
)

parameters(m0) %>%
  print_html()
```


## Does loss of religion improve environmental attitudes

Another target trial emulation

```{r}
tf2<- tf %>%
  arrange(Id,wave0) %>%
  group_by(Id) %>%
  mutate(always  = mean(religious, na.rm = TRUE) ) %>%# this is a hack, but works
  filter(!always == 0) %>% # Get rid of people who were always secular 
  mutate(deconvert = {
    religious == 0 & religious_lag ==1 & religious_lag_lag == 1 & religious_lead ==0
  } %>% {
    . * !duplicated(.)
  })%>%
  mutate(trt = ifelse(
    deconvert == 1,
    1,
     0))%>%
  dplyr::mutate(
                trt_lead2 = lead(trt,  n=2),
                trt_lag = lag(trt)) %>%
  dplyr::filter(!trt_lead2 == 1)  %>%

            ungroup() %>%
  arrange(Id, wave0)


#table(tf2$trt)
#sum(is.na(tf2$trt_lead2))

# how many Id's
#length(unique(tf2$Id))

# How many trt vs contols? 
#table(tf2$trt)
```

We do not find a preservative effect of deconversion on environmental attitudes. 

```{r}
modD<- lmer(Env.ClimateChgReal_lead ~ # outcome (after exposure)
               trt + #exposure 
               # religious_lag + # control for previous exposure
               Env.ClimateChgReal_lag + #Control for previous outcome
               Male_lag + # baseline confounder control
               GenCohort + # baseline confounder control
               yrs + # year trend
               (1|Id),  # dependencies from the repeated measures 
             data = tf2)

## Here we recover a stronger effect. 
modD%>%
  parameters() %>%
  print_html()
```

GEE: same result

```{r}
ts2<-tf2%>%
  drop_na()

## Nothing
m0d <- geeglm(
  Env.ClimateChgReal_lead ~ # outcome (after exposure)
               trt + #exposure 
               Env.ClimateChgReal_lag + #Control for previous outcome
               Male_lag + # baseline confounder control
               GenCohort + # baseline confounder control
               yrs,
  data = ts2,
  id = Id,
  family = "gaussian",
 # weights = ipw,
  waves = wave0,
  corstr = "exchangeable"
)
parameters(m0d) %>%
  print_html()
```


## Conclusion

There find no evidence that religion causally affects beliefs in the reality of climate change

Need to investigate the causal effects of religion on other environmental attitudes and behaviours.  

Warning to those who read causation from associations



