---
title: "National longitudinal study reveals durable shift in public acceptance following the 2019 New Zealand Mosque Attacks"
description: |
author:
  - name: Joseph Bulbulia
    url: https://josephbulbulia.netlify.app
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: 0000-0002-5861-2056
date: 2021-MAR-12
output:
  distill::distill_article:
    self_contained: false
    toc: true
    code_folding: true
bibliography: bib.bib
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  layout = "l-body-outset",
  fig.width = 12,
  fig.height = 15,
  collapse = TRUE,
  R.options = list(width = 60
  )
)
```

```{r libs, include=FALSE}
#libraries

library("tidyverse") # data wrangling
library("here") # file management
library("equatiomatic") # equations
library("lubridate") # working with dates
library("ggplot2") # graphs
library("ggthemes") #themes
library("ggpubr") # graphs
library("viridis") # colours
library("patchwork") # combine graphs
library("ggforce") # graphs
library("lme4") # multilevel estimation
library("geepack") # marginal models
library("easystats") # reporting
library("kableExtra") # tables
library("broom") # working with  models
library("broom.mixed") # mixed effects models
library("brms") # bayesian estimation
library("rstan") # backend brms
library("rstanarm") # graphing
library("cmdstanr") # backend brms
library("ipw") # inverse probability weighting
library("tidybayes") # workign with posterior probability distributions
library("bayesplot") # graphs
library("ggokabeito")   # color palette
library("gghalves")     #  half geoms
library("ggbeeswarm")   # Special distribution-shaped point jittering
library("emmeans") # estimate marginal means
library("table1") # tables /now with latex
library("kableExtra") # tables
# rstan options
rstan_options(auto_write = TRUE) # bayesian estimation
options(mc.cores = parallel::detectCores ()) # use all course
theme_set(theme_pubclean()) # nice theme
#theme_set(theme_classic())
```


```{}
cite_packages()
```


```{r data, cache = TRUE}
#import data
df <- readRDS(here::here("data", "df"))
```

We prepare data by selecting data from wave 2018 (years 2018-19) and wave 2019 (years 2019-20)


```{r danalysisdata, cache=TRUE}
# dataset for models

km <- df %>%
  dplyr::select(
    Id,
      Wave,
      Age,
      EthnicCats,
      Urban,
      Edu,
      Male,
      Pol.Orient,
      NZdep,
      GenCohort,
    TSCORE,
    # Warm.Overweight,
    # Warm.Elderly,
    # Warm.Mental-Illness,
    Warm.Muslims,
    # Warm.Immigrants,
    # Warm.Asians,
    # Warm.Refugees,
#     Warm.Maori,
#     Warm.NZEuro,
#     Warm.Indians,
#     Warm.Chinese,
#     Warm.Refugees,
#     Warm.Pacific,
#     Muslim,
    TSCORE,
    WSCORE, 
    YearMeasured,
    Religious
  ) %>%
#dplyr::filter( Wave == 2018 & YearMeasured ==1 | Wave == 2019 & YearMeasured ==1 ) %>%
  dplyr::filter( (Wave == 2018 & YearMeasured == 1 ) | Wave == 2019 )%>%  # Account for missingness
   droplevels() %>%
#  group_by(Id)%>%
#  filter(n() == 2) %>%
#  dplyr::add_tally() %>%
 # filter(n == 2 ) %>%
 # dplyr::ungroup() %>%
  dplyr::mutate(Attack = ifelse(TSCORE >= 3545, 1, 0)) %>%
  #dplyr::mutate(Attack2 = factor(ifelse(Attack == 1 & Wave ==2019, 3, Attack)))%>%
  # dplyr::mutate(daysAfter = as.integer(TSCORE - 3545),
  #               yearsAfter = daysAfter / 365) %>%
  dplyr::mutate(years = (TSCORE - min(TSCORE) / 365)) %>%
  #dplyr::mutate(mw_lead = lead(Warm.Muslims))%>%
  drop_na()
```

Number of participants
```{r}
length(unique(km$Id)) # 40785
```

How many 90 days after the attacks? 

<!-- ```{r} -->
<!-- # 3545 + 90 -->
<!-- ts<-df %>% -->
<!--   dplyr::filter(YearMeasured == 1)  %>% -->
<!--   dplyr::filter(Wave == 2018) %>% -->
<!--   dplyr::filter(TSCORE >= 3545) %>% -->
<!--   dplyr::filter(TSCORE <= 3635) %>% -->
<!--   dplyr::select(Id, TSCORE, Warm.Muslims) %>% -->
<!--   dplyr::filter(!is.na(Warm.Muslims))  -->

<!-- length(unique(ts$Id)) -->


<!-- # dplyr::mutate(Pre_PostATTACK = factor(ifelse( -->
<!--   #   TSCORE >= 3545, "post_attack", -->
<!--   #   "pre_attack" -->
<!--   # )))%>% -->
<!--   # dplyr::mutate(Pre_PostATTACK = forcats::fct_relevel(Pre_PostATTACK, c("pre_attack","post_attack")))%>% -->
<!-- ``` -->

<!-- Data preparation -->

<!-- ```{r} -->
<!-- dm <- df %>% -->
<!--   dplyr::filter(YearMeasured == 1)  %>% -->
<!--   dplyr::filter(Wave == 2019 | -->
<!--                   Wave == 2018 | -->
<!--                   Wave == 2017 | -->
<!--                   Wave == 2016 | -->
<!--                   Wave == 2015| -->
<!--                   Wave == 2014| -->
<!--                   Wave == 2013| -->
<!--                   Wave == 2012) %>% -->
<!--   dplyr::group_by(Id) %>% filter(n() > 2) %>% -->
<!--   dplyr::ungroup(Id)  %>% -->
<!--   dplyr::select(Id, TSCORE, Warm.Maori)%>% -->
<!--   dplyr::filter(!is.na(Warm.Maori)) %>% -->
<!--   dplyr::mutate( -->
<!--     wm_s = scale(Warm.Maori), -->
<!--     days = as.integer(TSCORE), -->
<!--     yr_0 = ((days - min(days)) / 365), -->
<!--     yrs = (days / 365), -->
<!--     yr_a = 3545/365, -->
<!--   )  -->
<!-- ``` -->



Participants

```{r}
km0<-km%>%
  mutate(Edu = as.numeric(Edu),
         Attack = as.factor(Attack))

levels(km0$Attack) <- c('Pre', 'Post')

km0$Warm.Muslims
x <- table1::table1(~ Warm.Muslims + Age + Male +Edu + EthnicCats  +  Religious + Pol.Orient + Urban + NZdep|Wave*Attack, data = km0)
x
t1kable(x, format ="latex")
```


```{r}
table1::table1(~Attack |Wave, data = km0)
```


```{r}
w_ipw <- ipwtm(
  exposure = Attack,
  family = "binomial",
  link = "logit",
  # Time invariant
  numerator =  ~ Male + GenCohort + Edu + EthnicCats,
  # Time invariant and non-invariant confounders
  denominator = ~ Male + GenCohort + Edu + EthnicCats + Religious + Pol.Orient + Urban + NZdep,
  id = Id,
  timevar = Wave,
  type = "first",
  data = as.data.frame(km)
)




<!-- #check no weights greater than 10 -->
max(w_ipw$ipw.weights) # max is 1.189481 -->
```


```{r}
## add weights to data frame.
km$Pol.Orient
library(tidyverse)
km <- km %>%
  mutate(ipw = w_ipw$ipw.weights,
  Pol.Orient_S = scale(Pol.Orient))

# make Attack a factor
km$Attack <- as.factor(km$Attack) # mack attack a factor
```

### Frequentist estimation


We can estimate the expected means under three exposure conditions:

This is the wrong way to estimate a causal effect 

The entire population never experiences an attack. 

```{r models, cache=TRUE}
m00 <- lmer(Warm.Muslims ~ Attack  + Wave + (1|Id), 
           weights = ipw,
           data = km)

parameters::model_parameters(m00)%>%
  print_html()
p0 <- ggeffects::ggemmeans(m00,
                           terms = c( "Attack[0,1]","Wave[2018,2019]"))

p0

# for graph 
pl0 <- plot(p0 ) +  scale_y_continuous(limits = c(3,6)) +
  labs(title = "Counterfactual Outcome:\nno attack exposure") + theme_pubclean()
pl0



estimate_contrasts(
  m00,
  contrast = c("Wave","Attack"),
  at = c("Pol.Orient_S = -2"),
  fixed = NULL,
  transform = "none",
  ci = 0.95,
  adjust = "holm",
)

```

2. The entire population experiences the attack. 

### Marginal structural model 

We next replicate this study using a marginal structural model, with no differences in the expectation. 

```{r models, cache=TRUE}
## GEE
library(geepack)
m0 <- geeglm(
  Warm.Muslims ~ Attack + Wave,
  data = km,
  id = Id,
  family = "gaussian",
  weights = ipw,
  waves = Wave,
  corstr = "ar1"
)
summary(m0)

estimate_contrasts(
  m0,
  contrast = c("Wave","Attack"),
  at = NULL,
  fixed = NULL,
  transform = "none",
  ci = 0.95,
  adjust = "holm",
)
%>%
  slice(c(2,6,7) 
```

Also wrong. 

```{r models, cache=TRUE}

p0 <- ggeffects::ggemmeans(m0,
                           terms = c("Wave[2018]","Attack[0]"))
p0 <- ggeffects::ggemmeans(m0,
                           terms = c("Wave[2018,2019]","Attack[0,1]"))

p0

# for graph 
pl0 <- plot(p0 ) +  scale_y_continuous(limits = c(4,5)) +
  labs(title = "Counterfactual Outcome:\nno attack exposure") + theme_pubclean()
pl0
```


## Bayesian

We next replicate the multi-level model using a bayesian estimation. 

```{r}
library(tidybayes)    # Manipulate Stan objects in a tidy way

m1 <-readRDS(here::here("_posts", "mus", "mods", "m1.rds"))
m1 <- brms::brm( 
  Warm.Muslims|weights(ipw) ~ Wave + Attack +  (1|Id), 
  data = km, 
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  backend = "cmdstanr",
  file = here::here("_posts", "mus", "mods", "m1.rds")
  )


```


Wrong way 

```{r}
summary(m1)
library(lazerhawk)


blh_tab <- brms_SummaryTable(m1, panderize=F)

blh_tab
blh_tab %>%
   kable(booktabs = T, "latex", caption =  "Parameter for effect of attack on warmth to Muslims") %>%
    print()

ec <- modelbased::estimate_contrasts(
  m1,
  contrast = c("Attack","Wave"),
  at = "Attack",
  #fixed = NA,
  transform = "none",
  ci = 0.95,
  adjust = "holm",
)
#ec
saveRDS(ec, here::here("_posts", "mus", "mods", "ec.rds"))
ec <- readRDS(here::here("_posts", "mus", "mods", "ec.rds"))

tc<- as.data.frame(ec)
library(dplyr)
tc
library(tidyverse)


tc%>%
  slice(c(1,3,5))
#%>%
#  select(Level1,Level2,Difference,CI_low,CI_high,pd)%>%
 # kbl(digits=3, booktabs=T, "latex")

pec<-readRDS( here::here("_posts", "mus", "mods", "ec.rds"))
```

```{r designtable,  tab.cap="\\label{tab:designtable}"}
km %>%
  group_by(Wave, Attack) %>%
  summarise(n = n()) %>%
  kbl(booktabs = T, "latex", caption = "Participant by exposure and wave") #%>%
  # kable_classic_2(c("striped", "hover"), full_width = TRUE) %>%


x <- table1::table1(~ Warm.Muslims + Age + Male + GenCohort + Edu + Employed + EthnicCats  +  Religious + Pol.Orient + NZdep + Urban|Wave*As, data = km4, overall=FALSE)
```


```{r eval=FALSE}
library(emmeans)
#d0 <-m1 %>% 
  emmeans(~ Wave,
          at = list(Attack = 0,
                    Wave = c("2018")),
          epred = TRUE,
          re_formulat = NA )
saveRDS(d0,  here::here("_posts", "mus", "mods", "d0.rds"))
d0 <- readRDS(here::here("_posts", "mus", "mods", "d0.rds"))
d0


#d1 <- m1 %>% emmeans(~ Wave,
          at = list(Attack = 1,
                    Wave = c("2018","2019")),
          epred = TRUE,
          re_formula = NA)

#saveRDS(d1,  here::here("_posts", "mus", "mods", "d1.rds"))
d1<- readRDS(here::here("_posts", "mus", "mods", "d1.rds"))
d1


d0 %>%
  contrast()

d1 %>%
  contrast()




# attack_effect_draws <- pred01 %>%
#   contrast() %>%
#   gather_emmeans_draws()
# attack_effect_draws


# graph
# ggplot(attack_effect_draws, aes(x = .value)) +
#   stat_halfeye(fill = palette_okabe_ito(order = 5)) +
#   labs(x = "Average marginal effect of attack", y = "Density") +
#   theme_clean() +
#   theme(legend.position = "bottom")

  
# parameters::parameters(
#   test = "pd",
#   priors = FALSE, 
#   effects = "all",
#   drop = TRUE,
#   group_level = FALSE,
#   diagnostic = "Rhat") %>%
#     mutate_if(is.numeric, ~ round(., 2)) %>%
#     mutate_all(funs(str_replace(., "b_", ""))) %>%
#     kable(booktabs = T, "latex", caption =  "Parameter estimates for model of Belief on Anxiety") %>%
#     print()

```


```{r}
#marg_eff_attack_0 <- m1 %>%
  epred_draws(newdata = expand.grid(Attack = c(0, 1),Wave = c("2018", "2019")),
              re_formula =NA)
           #   re_formula = NULL)  # or re_formula = ~ (1 | region)

#saveRDS(marg_eff_attack_0,  here::here("_posts", "mus", "mods", "marg_eff_attack_0.rds"))
marg_eff_attack_0 <- readRDS(here::here("_posts", "mus", "mods", "marg_eff_attack_0.rds"))


# Obtain contrasts
marg_eff_attack_0<- marg_eff_attack_0%>%
  filter(Attack == 1 & Wave ==2019| Attack == 1 & Wave ==2018|  Attack == 0 & Wave ==2018)
marg_eff_attack_0
plot_all <- ggplot(
  marg_eff_attack_0,
  aes(
    x = .epred,
    y = Wave,
    fill = as.factor(Attack)
  ) ) + 
#  scale_y_discrete(limits=rev) +
    stat_halfeye() +
    scale_fill_okabe_ito() +
    labs(
      x = "Predicted Warmth Response",
      y = NULL,
      fill = "Conterfactual Contrasts",
      subtitle = "Bayesian Posterior Simulations"
    ) +
    scale_x_continuous(limits=c(4.0,4.6)) +
    theme_pubclean() +
    theme(legend.position = "bottom"
    )
graph
#plot_all


grand_mean_ame <- m1 %>% 
  emmeans(~ Attack,
          epred = TRUE, re_formula = NA) %>% 
  contrast() %>% 
  gather_emmeans_draws()

#saveRDS(grand_mean_ame,  here::here("_posts", "mus", "mods", "grand_mean_ame.rds"))
grand_mean_ame <- readRDS(here::here("_posts", "mus", "mods", "grand_mean_ame.rds"))

# remove erro contrasts / 
grand_mean_ame_0 <- grand_mean_ame_0%>%
  filter(contrast != 0-0 |contrast != 1-0 )

grand_mean_ame_0

plot_all__ame <- ggplot(grand_mean_ame_0,
                                     aes(x = .value)) +
  stat_halfeye(slab_alpha = 0.75, fill = "grey") +
  scale_fill_okabe_ito(order = c(3, 4)) +
  labs(x = "Average marginal effect of attack on Warmth to Muslims",
       y = "Density") +
  #facet_wrap(vars(region)) +
  theme_classic() + 
  theme(legend.position = "bottom") + labs(title= "Average marginal effect of attack\non Warmth to Muslims")
plot_all__ame 
# Try
library(patchwork)
bayes_plots <- plot_all + plot_all__ame
bayes_plots

ggsave(
  bayes_plots,
  path = here::here(here::here("_posts", "mus", "figs")),
  width = 10,
  height = 5,
  units = "in",
  filename = "bayes_plots.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)
```




```{r pptimeline, cache=TRUE, fig.fullwidth = TRUE,  layout="l-body-outset", fig.width=12, fig.height=12, fig.cap="\\label{fig:pptimeline} Within-participant repeated measures covering the years before and following the attacks allow precise estimates of attitudinal change within-people (N = 11,481)."}
## timeline
rarep<-df%>%
  dplyr::filter(YearMeasured == 1) %>%
  dplyr::filter(Wave == 2018 | Wave == 2019) %>%
  dplyr::group_by(Id) %>% filter(n() == 2) %>%
  dplyr::filter(Wave == 2018 | Wave == 2019) %>%
  droplevels() %>%
  dplyr::ungroup(Id) %>%
  dplyr::mutate(timeline = make_date(year = 2009, month = 6, day = 30)+ TSCORE)%>%
  dplyr:::count(day = floor_date(timeline, "day"))%>%
  dplyr::mutate(Condition = factor(ifelse(day >="2018-06-18" & day < "2019-03-15", 0,
                                                 ifelse( day >="2019-03-15" & day < "2019-06-18",1 ,
                                                         2)),
                                                 labels= c("Control","Post-Attack", "Year following")))%>%
  arrange(day)
  #table(rarep$Condition)
# get data of change of baseline
#dates_vline1<- as.Date("2018-06-18")


# get attack date
dates_vline2<- as.Date("2019-03-15")
dates_vline3<- as.Date("2019-06-18")

# for line in a graph
dates_vline2b<-which(rarep$day %in% dates_vline2)
#dates_vline1b<-which(rarep$day %in% dates_vline1)
dates_vline3b<-which(rarep$day %in% dates_vline3)

lds2 <- ggplot(rarep, aes(day, n)) + geom_col(aes(fill = Condition)) + scale_x_date(date_labels = "%b/%Y",
                                                                                    limits = c(as.Date("2018-06-18"), as.Date("2020-10-15")))  +
  scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
  geom_vline(xintercept = as.numeric(rarep$day[dates_vline2b]),
             col = "red",
             linetype = "dashed") +
  xlab("NZAVS Waves years 2018 - 2020 daily counts by condition") + ylab("Count of Responses")+
  theme_classic() +
  # annotate(
  #   "rect",
  #   xmin = as.Date("2017-08-25"),
  #   xmax = dates_vline1,
  #   ymin = 0,
  #   ymax = 900,
  #   alpha = 0
  # ) +
  annotate(
    "rect",
    xmin = dates_vline2,
    xmax = dates_vline3,
    ymin = 0,
    ymax = 900,
    alpha = .3,
    fill = "darkred"
  ) +
  # annotate(
  #   "rect",
  #   xmin = dates_vline1,
  #   xmax = dates_vline2,
  #   ymin = 0,
  #   ymax = 900,
  #   alpha = .3
  # ) +
  annotate(
    "rect",
    xmin = dates_vline3,
    xmax = as.Date("2020-10-15"),
    ymin = 0,
    ymax = 900,
    alpha = .05,
    fill = "red"
  ) +
  annotate(
    "text",
    x = as.Date("2018-10-15"),
    y = 1500,
    label = "Wave 10\npre-attacks"
  ) +
  # annotate(
  #   "text",
  #   x = as.Date("2018-01-15"),
  #   y = 980,
  #   label = "Wave 9
  #          baseline (control)"
  # ) +
  annotate(
    "text",
    x = as.Date("2019-05-15"),
    y = 1500,
    label = "Wave 10\npost\nattacks"
  ) +
  annotate(
    "text",
    x = as.Date("2020-02-15"),
    y = 1500,
    label = "Wave 11\nrepeated"
  ) +
  annotate(
    geom = "curve",
    x = as.Date("2018-02-15"),
    y = 950,
    xend = as.Date("2018-10-15"),
    yend = 950,
    curvature = -.3,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(
    geom = "curve",
    x = as.Date("2018-02-15"),
    y = 950,
    xend = as.Date("2019-05-15"),
    yend = 950,
    curvature = -.3,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate("text",
           x = as.Date("2018-11-05"),
           y = 950,
           label = "Control") +
  annotate(
    geom = "curve",
    x = as.Date("2019-05-15"),
    y = 1000,
    xend = as.Date("2020-05-15"),
    yend = 1000,
    curvature = -.3,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate("text",
           x = as.Date("2019-06-05"),
           y = 950,
           label = "Attack") +
  annotate("text",
           x = as.Date("2020-07-30"),
           y = 1000,
           label = "Year\nFollowing") +
  annotate(
    geom = "curve",
    x = as.Date("2018-11-15"),
    y = 1000,
    xend = as.Date("2020-05-15"),
    yend = 1000,
    curvature = -.3,
    arrow = arrow(length = unit(2, "mm"))
  ) +
  theme(
    legend.position = "top",
    legend.text = element_text(size = 6),
    legend.title = element_text(color = "Black", size = 8)
  ) +
  scale_fill_viridis_d(option = "plasma")

### USE GRAPH OF TIMELINE
lds2


ggsave(
  lds2,
  path = here::here(here::here("_posts", "mus", "figs")),
  width = 10,
  height = 5,
  units = "in",
  filename = "timeline.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)
```

```{r}
## For intro
p1pp <- plot(p1,
            add.data = TRUE,
            dot.alpha = .05,
            jitter = .8) +
  ylab("Warmth to Muslims (1-7)") + labs(title = "Warm Muslims") +
  geom_hline(yintercept = 4.395, color = "green") +
  # scale_y_continuous(limits = c(1, 7)) +
  scale_colour_viridis_d() + xlab("Attack timeline") +
  # geom_vline(xintercept = c(2.8), colour = "red", linetype = "dashed") +
  theme_classic()
```


## Weights graph 

```{r}
kn <- km4
kn$attack <- as.numeric(km4$Attack)
kn$attack



imputed1<-imputed$imputations$imp1
im<- imputed1
im$attack <- as.numeric(im$As)-1
im$warmth <- as.numeric(im$Ys)
kn$warmth <- as.numeric(kn$Warm.Muslims)
im$attack

kn%>%
  filter(Wave ==2019 & As ==1) %>%
  select(Warm.Muslims) %>%
  count(is.na(.))

plot1 <- ggplot() + 
    geom_histogram(data = filter(im, attack == 1 & Wave == 2018), 
            #  bins = 10, 
              aes(x = warmth), 
                 fill = colorspace::lighten("chocolate", 0.55)) +  
  geom_histogram(data = filter(im, attack == 0 & Wave == 2018), 
                # bins = 10, 
                 aes(x = warmth, y = -..count..),
                  fill = colorspace::lighten("deepskyblue4", 0.55))  +
  geom_histogram(data = filter(kn, attack == 1& Wave == 2018), 
                 #bins = 10, 
                 aes(x = warmth), 
                 fill = colorspace::lighten("chocolate", 0.1))+ 
  geom_histogram(data = filter(kn, attack == 0 & Wave == 2018), 
                # bins = 10, 
                 aes(x = warmth, y = -..count..),
                 fill = colorspace::lighten("deepskyblue4", 0.1)) +
 annotate(geom = "label", x = 1.5, y = 2000, label = "Exposed\nobserved",
         fill = colorspace::lighten("chocolate",.1), color = "white", hjust = 1) +
 annotate(geom = "label", x = 3.5, y = 5000, label = "Exposed\nimputed",
           fill = colorspace::lighten("chocolate",.35), color = "white", hjust = 1)+
 annotate(geom = "label", x = 1.5, y = -4000, label = "Not Exposed\nobserved",
         fill = colorspace::lighten("deepskyblue4", 0.1), color = "white", hjust = 1) +
 annotate(geom = "label", x = 3.5, y = -10000, label = "Not Exposed\nimputed",
          fill = colorspace::lighten("deepskyblue4",  .35), color = "white", hjust = 1) +
 geom_hline(yintercept = 0, color = "white", size = 0.25) +
 scale_y_continuous(label = abs) + 
    scale_y_continuous(limits=c(-15000,15000)) +
 # coord_cartesian(xlim = c(0.1, 1)) +
  labs(x = "Warmth to Muslim", y = "Counts") + labs(title= "Wave 10")


plot1

length(unique(kn$Id))
length(unique(imputed1$Id))

plot2 <- ggplot() + 
    geom_histogram(data = filter(im, attack == 1 & Wave == 2019), 
             # bins = 10, 
              aes(x = warmth), 
                 fill = colorspace::lighten("chocolate", 0.55)) +  
  geom_histogram(data = filter(im, attack == 0 & Wave == 2019), 
                # bins = 10, 
                 aes(x = warmth, y = -..count..),
                  fill = colorspace::lighten("deepskyblue4", 0.55))  +
  geom_histogram(data = filter(kn, attack == 1 & Wave == 2019), 
                 #bins = 10, 
                 aes(x = warmth), 
                 fill = colorspace::lighten("chocolate", 0.1))+ 
  geom_histogram(data = filter(kn, attack == 0 & Wave == 2019), 
               #  bins = 10, 
                 aes(x = warmth, y = -..count..),
                 fill = colorspace::lighten("deepskyblue4", 0.1)) +
 annotate(geom = "label", x = 3.5, y = 8000, label = "Exposed\nobserved",
         fill = colorspace::lighten("chocolate",.1), color = "white", hjust = 1) +
 annotate(geom = "label", x = 3.5, y = 12000, label = "Exposed\nimputed",
           fill = colorspace::lighten("chocolate",.35), color = "white", hjust = 1)+
 annotate(geom = "label", x = 2.5, y = -4000, label = "Not Exposed is\nfully imputed",
          fill = colorspace::lighten("deepskyblue4",  .35), color = "white", hjust = 1) +
 geom_hline(yintercept = 0, color = "white", size = 0.25) +
 scale_y_continuous(label = abs) + 
 # coord_cartesian(xlim = c(0.1, 1)) +
  labs(x = "Warmth to Muslim", y = "Counts") + labs(title= "Wave 11") + 
  scale_y_continuous(limits=c(-15000,15000))
plot2
imp_frq<- plot1 + plot2 + plot_annotation(tag_levels = "a", title = "Comparison of multiply-imputed responses and observed\nresponse distributions in Wave 10 and Wave 11")


imp_frq


ggsave(
  imp_frq,
  path = here::here(here::here("_posts", "mus", "figs")),
  width = 12,
  height = 8,
  units = "in",
  filename = "imp_frq.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)



model_treatment_freq <- glm(attack ~    Male  + Edu + EthnicCats + Religious + Pol.Orient + Urban + NZdep + Religious,  data = kn,family = binomial(link = "logit"))


# Step 2: Use the treatment model to calculate propensity scores, and
# Step 3: Use the propensity scores to calculate inverse probability of treatment weights
km_with_weights <- augment(model_treatment_freq, kn,
                             type.predict = "response") %>%
  rename(propensity = .fitted) %>% 
  mutate(iptw = (attack / propensity) + ((1 - attack) / (1 - propensity)))


max(km_with_weights$iptw)


# Step 4: Use the IPTWs in a model that estimates the effect of treatment on outcome
model_outcome_freq <- lm(Warm.Muslims ~ Attack   ,
                         data = km_with_weights,
                         weights = iptw)

# Coefficient 
tidy(model_outcome_freq)




library(MetBrewer)
# ggplot() + 
#   geom_histogram(data = filter(km, Attack == 1), 
#                  bins = 50, aes(x = ipw), 
#                  fill = colorspace::lighten("darkorange", 0.5)) + 
#    geom_histogram(data = filter(km, Attack == 0), 
#                  bins = 50, aes(x = ipw, y = -..count..),
#                  fill = colorspace::lighten("darkgreen", 0.5)) +
#   geom_hline(yintercept = 0) + 
#   annotate(geom = "label", x = 0.8, y = 2000, label = "Treated", 
#            fill = colorspace::lighten("darkorange", 0.2), color = "white", hjust = 0) +
#   annotate(geom = "label", x = 0.8, y = -2000, label = "Untreated", 
#            fill = colorspace::lighten("darkgreen", 0.2), color = "white", hjust = 0) +
#   scale_y_continuous(label = abs) +
#  #coord_cartesian(xlim = c(0.1, 0.8), ylim = c(-10000, 10000)) +
#   labs(x = "Propensity", y = "Count") 


#  
imputed
ipwplot <- ggplot() + 
  geom_histogram(data = filter(km_with_weights, attack == 1), 
                 bins = 50, aes(x = propensity, weight = iptw), 
                 fill = colorspace::lighten("chocolate", 0.55)) + 
  geom_histogram(data = filter(km_with_weights, attack == 0), 
                 bins = 50, aes(x = propensity, weight = iptw, y = -..count..),
                  fill = colorspace::lighten("deepskyblue4", 0.55)) +
  geom_histogram(data = filter(km_with_weights, attack == 1), 
                 bins = 50, aes(x = propensity), 
                 fill = colorspace::lighten("chocolate", 0.1)) + 
  geom_histogram(data = filter(km_with_weights, attack == 0), 
                 bins = 50, aes(x = propensity, y = -..count..),
                 fill = colorspace::lighten("deepskyblue4", 0.1)) +
 annotate(geom = "label", x = 0.7, y = 1000, label = "Treated (actual)",
         fill = colorspace::lighten("chocolate",.1), color = "white", hjust = 1) +
 annotate(geom = "label", x = 0.7, y = 3000, label = "Treated (imputed\npseudo-population)",
           fill = colorspace::lighten("chocolate",.35), color = "white", hjust = .5)+
 annotate(geom = "label", x = 0.7, y = -1000, label = "Untreated (actual)",
         fill = colorspace::lighten("deepskyblue4", 0.1), color = "white", hjust = 1) +
 annotate(geom = "label", x = 0.7, y = -3000, label = "Untreated (imputed\npseudo-population)",
          fill = colorspace::lighten("deepskyblue4",  .35), color = "white", hjust = 1) +
 geom_hline(yintercept = 0, color = "white", size = 0.25) +
 scale_y_continuous(label = abs) + 
 # coord_cartesian(xlim = c(0.1, 1)) +
  labs(x = "Propensity", y = "Count") + labs(title= "Comparison of propensity score\nand original response distributions")
ipwplot



model_treatment_freq <- glm(attack ~  
                              Male  + Edu + EthnicCats + Religious + Pol.Orient + Urban + NZdep + Religious,
                            data = kp18,family = binomial(link = "logit"))


# Step 2: Use the treatment model to calculate propensity scores, and
# Step 3: Use the propensity scores to calculate inverse probability of treatment weights
km_with_weights <- augment(model_treatment_freq, kp18,
                             type.predict = "response") %>%
  rename(propensity = .fitted) %>% 
  mutate(iptw = (attack / propensity) + ((1 - attack) / (1 - propensity)))


max(km_with_weights$iptw)


# Step 4: Use the IPTWs in a model that estimates the effect of treatment on outcome
model_outcome_freq <- lm(Warm.Muslims ~ Attack ,
                         data = km_with_weights,
                         weights = iptw)

# Coefficient 
tidy(model_outcome_freq)




library(MetBrewer)
# ggplot() + 
#   geom_histogram(data = filter(km, Attack == 1), 
#                  bins = 50, aes(x = ipw), 
#                  fill = colorspace::lighten("darkorange", 0.5)) + 
#    geom_histogram(data = filter(km, Attack == 0), 
#                  bins = 50, aes(x = ipw, y = -..count..),
#                  fill = colorspace::lighten("darkgreen", 0.5)) +
#   geom_hline(yintercept = 0) + 
#   annotate(geom = "label", x = 0.8, y = 2000, label = "Treated", 
#            fill = colorspace::lighten("darkorange", 0.2), color = "white", hjust = 0) +
#   annotate(geom = "label", x = 0.8, y = -2000, label = "Untreated", 
#            fill = colorspace::lighten("darkgreen", 0.2), color = "white", hjust = 0) +
#   scale_y_continuous(label = abs) +
#  #coord_cartesian(xlim = c(0.1, 0.8), ylim = c(-10000, 10000)) +
#   labs(x = "Propensity", y = "Count") 


#  
imputed
ipwplot <- ggplot() + 
  geom_histogram(data = filter(km_with_weights, attack == 1), 
                 bins = 50, aes(x = propensity, weight = iptw), 
                 fill = colorspace::lighten("chocolate", 0.55)) + 
  geom_histogram(data = filter(km_with_weights, attack == 0), 
                 bins = 50, aes(x = propensity, weight = iptw, y = -..count..),
                  fill = colorspace::lighten("deepskyblue4", 0.55)) +
  geom_histogram(data = filter(km_with_weights, attack == 1), 
                 bins = 50, aes(x = propensity), 
                 fill = colorspace::lighten("chocolate", 0.1)) + 
  geom_histogram(data = filter(km_with_weights, attack == 0), 
                 bins = 50, aes(x = propensity, y = -..count..),
                 fill = colorspace::lighten("deepskyblue4", 0.1)) +
  # annotate(geom = "label", x = 0.7, y = 1000, label = "Treated (actual)", 
  #         fill = colorspace::lighten("chocolate",.1), color = "white", hjust = 1) +
  # annotate(geom = "label", x = 0.7, y = 3000, label = "Treated (imputed\npseudo-population)", 
  #           fill = colorspace::lighten("chocolate",.35), color = "white", hjust = .5)+
  # annotate(geom = "label", x = 0.7, y = -1000, label = "Untreated (actual)", 
  #         fill = colorspace::lighten("deepskyblue4", 0.1), color = "white", hjust = 1) +
  # annotate(geom = "label", x = 0.7, y = -3000, label = "Untreated (imputed\npseudo-population)", 
  #          fill = colorspace::lighten("deepskyblue4",  .35), color = "white", hjust = 1) +
  # geom_hline(yintercept = 0, color = "white", size = 0.25) +
  # scale_y_continuous(label = abs) +
 # coord_cartesian(xlim = c(0.1, 0.8), ylim = c(-80, 100)) +
  labs(x = "Propensity", y = "Count") + labs(title= "Comparison of propensity score\nand original response distributions")
ipwplot





model_treatment_freq <- glm(attack ~  
                              Male  + Edu + EthnicCats + Religious + Pol.Orient + Urban + NZdep + Religious,
                            data = kp19,family = binomial(link = "logit"))


# Step 2: Use the treatment model to calculate propensity scores, and
# Step 3: Use the propensity scores to calculate inverse probability of treatment weights
km_with_weights <- augment(model_treatment_freq, kp19,
                             type.predict = "response") %>%
  rename(propensity = .fitted) %>% 
  mutate(iptw = (attack / propensity) + ((1 - attack) / (1 - propensity)))


min(km_with_weights$iptw)


# Step 4: Use the IPTWs in a model that estimates the effect of treatment on outcome
model_outcome_freq <- lm(Warm.Muslims ~ Attack ,
                         data = km_with_weights,
                         weights = iptw)

# Coefficient 
tidy(model_outcome_freq)





ind <- imputed1
ind$propensity<- rep(1,nrow(ind))
ind$iptw<- rep(1,nrow(ind))
ind$attack <- ind$As

ipwplot <- ggplot() + 
  geom_histogram(data = filter(ind, attack == 1), 
                 bins = 50, aes(x = propensity, weight = iptw), 
                 fill = colorspace::lighten("chocolate", 0.55)) + 
  geom_histogram(data = filter(ind, attack == 0), 
                 bins = 50, aes(x = propensity, weight = iptw, y = -..count..),
                  fill = colorspace::lighten("deepskyblue4", 0.55)) +
  geom_histogram(data = filter(km_with_weights, attack == 1), 
                 bins = 50, aes(x = propensity), 
                 fill = colorspace::lighten("chocolate", 0.1)) + 
  geom_histogram(data = filter(km_with_weights, attack == 0), 
                 bins = 50, aes(x = propensity, y = -..count..),
                 fill = colorspace::lighten("deepskyblue4", 0.1)) +
 #  annotate(geom = "label", x = 0.7, y = 1000, label = "Treated (actual)", 
 #          fill = colorspace::lighten("chocolate",.1), color = "white", hjust = 1) +
 #  annotate(geom = "label", x = 0.7, y = 3000, label = "Treated (IPTW\npseudo-population)", 
 #            fill = colorspace::lighten("chocolate",.35), color = "white", hjust = 1)+
 #  annotate(geom = "label", x = 0.7, y = -1000, label = "Untreated (actual)", 
 #          fill = colorspace::lighten("deepskyblue4", 0.1), color = "white", hjust = 1) +
 #  annotate(geom = "label", x = 0.7, y = -3000, label = "Untreated (IPTW\npseudo-population)", 
 #           fill = colorspace::lighten("deepskyblue4",  .35), color = "white", hjust = 1) +
 #  geom_hline(yintercept = 0, color = "white", size = 0.25) +
 #  scale_y_continuous(label = abs) +
 # # coord_cartesian(xlim = c(0.1, 0.8), ylim = c(-80, 100)) +
   labs(x = "Propensity", y = "Count") + labs(title= "Comparison of propensity score\nand original response distributions")#+ scale_y_continuous(limits=c(-15000,15000))
ipwplot



ggsave(
  ipwplot,
  path = here::here(here::here("_posts", "mus", "figs")),
  width = 10,
  height = 5,
  units = "in",
  filename = "ipweightplot.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)


```




## 2017 as well

```{r danalysisdata, cache=TRUE}
ord_attack <- c("pre", "pst_w10","pst_w11")

 # table1::table1(~ Warm.Muslims|Wave, data = ts,transpose = TRUE)

  # dataset for models
km2 <- df %>%
  dplyr::select(
    Id,
    Age,
    Wave,
    EthnicCats,
    Urban,
    Edu,
    Male,
    Pol.Orient,
    NZdep,
    GenCohort,
    Urban,
    TSCORE,
    EthnicCats,
    # Warm.Overweight,
    # Warm.Elderly,
    # Warm.MentalIllness,
    Warm.Muslims,
    # Warm.Immigrants,
    # Warm.Asians,
    # Warm.Refugees,
    # Wave,
    # Warm.Maori,
    # Warm.NZEuro,
    # Warm.Indians,
    # Warm.Chinese,
    # Warm.Refugees,
    # Warm.Pacific,
    Muslim,
    TSCORE,
    WSCORE,
    YearMeasured,
    Religious
  ) %>%
  dplyr::filter(
      Wave == 2012 &
      YearMeasured == 1 |
      Wave == 2013 &
      YearMeasured == 1 |
      Wave == 2014 &
      YearMeasured == 1 |
      Wave == 2016 &
      YearMeasured == 1 |
      Wave == 2017 &
      YearMeasured == 1 |
      Wave == 2018 &
      YearMeasured == 1 |
      Wave == 2019 & 
        YearMeasured == 1
  ) %>% 
  droplevels() %>%
  arrange(Wave,Id) %>%
  group_by(Id) %>%
  dplyr::group_by(Id) %>% filter(n() > 6) %>%
  dplyr::add_tally() %>%
  filter(n == 7) %>%
  arrange(Wave,Id) %>%
  dplyr::mutate(Warm.Muslims_lag = lag(Warm.Muslims))%>%
  droplevels() %>%
  ungroup() %>%
  dplyr::mutate(Attack = ifelse(TSCORE >= 3545, 1, 0)) %>%
dplyr::mutate(Pre_PostATTACK = as.factor(ifelse(
  TSCORE >= 3545 & Wave == 2018,
  "pst_w10",
  ifelse(
    Wave == 2019,
    "pst_w11",
           "pre") )
)) %>%
dplyr::mutate(Pre_PostATTACK = forcats::fct_relevel(Pre_PostATTACK, ord_attack)) %>%
  dplyr::group_by(Id) %>% filter(n() > 5) %>% 
  ungroup()%>%
  dplyr::mutate(dys = (TSCORE - min(TSCORE)))%>% 
  dplyr::mutate(yrs =  (dys/365))%>% 
  arrange(Id,Wave) %>%
  drop_na() 

length(unique(km2$Id))

w_ipw <- ipwtm(
  exposure = yrs,
  family = "gaussian",
  # Time invariant 
  numerator =  ~ Male + GenCohort + Edu + EthnicCats,
  # Time invariant and non-invariant confounders
  denominator = ~ Male + GenCohort + Edu + EthnicCats + Religious + Pol.Orient + Urban+NZdep,
  id = Id,
  timevar = Wave,
  corstr = "exchangeable",
  type = "all",
  data = as.data.frame(km2)
)




#check no weights greater than 10
max(w_ipw$ipw.weights) # max is 1.189481

## add weights to data frame. 
km$Pol.Orient
library(tidyverse)
km2 <- km2 %>% 
  mutate(ipw = w_ipw$ipw.weights)


library(splines)

m00 <- lmer(Warm.Muslims ~   bs(yrs) + Warm.Muslims_lag +   (1|Id), weights=ipw,
           data = km2)

parameters::model_parameters(m00)%>%
  print_html()
p0 <- ggeffects::ggemmeans(m00,
                           terms = c("yrs[all]"))
p0

# 
# # for graph 
pl0 <- plot(p0) +  scale_y_continuous(limits = c(3,6)) +
  labs(title = "Marginal Trend in Muslim Acceptance") + theme_pubclean()  +
  geom_vline(xintercept = 6.48, linetype="dashed", 
                color = "red", size=.5)
  
pl0


library(geepack)

# No difference
# m0 <- lmer(
#   Warm.Muslims ~  bs(yrs) + (1|Id),
#   data = km3
#  # weights = ipw,
# )


m0 <- geeglm(
  Warm.Muslims ~  bs(yrs),
  data = km3,
  id = Id,
  family = "gaussian",
  weights = ipw,
  waves = Wave,
  corstr = "ar1"
)
summary(m0)

max(km3$yrs)
p0 <- ggeffects::ggemmeans(m0,terms = c("yrs[all]"))

length(unique(km3$Id))
#
# # for graph 
marginal_trend <- plot(p0) +  scale_y_continuous(limits = c(3,6)) +
  labs(title = "Marginal Trend in Muslim Acceptance", subtitle=
         "N = 7920") + theme_pubclean()  +
  geom_vline(xintercept = 5.49, linetype="dashed", 
                color = "red", size=.5) + 
    geom_vline(xintercept = 5.49,
             col = "red",
             linetype = "dashed") + xlab("Years before attack") + ylab("Warmth to Muslims")
marginal_trend

ggsave(
  marginal_trend,
  path = here::here(here::here("_posts", "mus", "figs")),
  width = 10,
  height = 5,
  units = "in",
  filename = "marginal_trend.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)


km3 <- df %>%
  dplyr::select(
    Id,
    Age,
    Wave,
    EthnicCats,
    Urban,
    Edu,
    Male,
    Pol.Orient,
    NZdep,
    GenCohort,
    Urban,
    TSCORE,
    EthnicCats,
    # Warm.Overweight,
    # Warm.Elderly,
    # Warm.MentalIllness,
    Warm.Muslims,
    # Warm.Immigrants,
    # Warm.Asians,
    # Warm.Refugees,
    # Wave,
    # Warm.Maori,
    # Warm.NZEuro,
    # Warm.Indians,
    # Warm.Chinese,
    # Warm.Refugees,
    # Warm.Pacific,
    Muslim,
    TSCORE,
    WSCORE,
    YearMeasured,
    Religious
  ) %>%
  dplyr::filter(
      # Wave == 2012 &
      # YearMeasured == 1 |
      Wave == 2013 &
      YearMeasured == 1 |
      Wave == 2014 &
      YearMeasured == 1 |
      Wave == 2016 &
      YearMeasured == 1 |
      Wave == 2017 &
      YearMeasured == 1 |
      Wave == 2018 &
      YearMeasured == 1 
  ) %>% 
  droplevels() %>%
  arrange(Wave,Id) %>%
  group_by(Id) %>%
  dplyr::group_by(Id) %>% filter(n() > 4) %>%
  dplyr::add_tally() %>%
  filter(n == 5)%>%
  arrange(Wave,Id) %>%
  dplyr::mutate(Warm.Muslims_lag = lag(Warm.Muslims))%>%
  droplevels() %>%
  ungroup() %>%
  dplyr::mutate(Attack = ifelse(TSCORE >= 3545, 1, 0)) %>%
  dplyr::filter(Attack == 0) %>%
  dplyr::mutate(dys = (TSCORE - min(TSCORE)))%>% 
  dplyr::mutate(yrs =  (dys/365))%>% 
  arrange(Id,Wave) %>%
  drop_na() 

length(unique(km3$Id))


w_ipw <- ipwtm(
  exposure = yrs,
  family = "gaussian",
  # Time invariant 
  numerator =  ~ Male + GenCohort + Edu + EthnicCats,
  # Time invariant and non-invariant confounders
  denominator = ~ Male + GenCohort + Edu + EthnicCats + Religious + Pol.Orient + Urban+ NZdep,
  id = Id,
  timevar = Wave,
  corstr = "exchangeable",
  type = "all",
  data = as.data.frame(km3)
)




#check no weights greater than 10
max(w_ipw$ipw.weights) # max is 1.189481

## add weights to data frame. 
km$Pol.Orient
library(tidyverse)
km3 <- km3 %>% 
  mutate(ipw = w_ipw$ipw.weights)


max(km3$yrs)


library(geepack)
m0 <- geeglm(
  Warm.Muslims ~ bs(yrs),
  data = km3,
  id = Id,
  family = "gaussian",
  waves = Wave,
  weights = ipw,
  corstr = "ar1"
)
summary(m0)


p0 <- ggeffects::ggemmeans(m0,
                           terms = c("yrs[all]"))
p0

# 
# # for graph 
pl0 <- plot(p0) +  scale_y_continuous(limits = c(3,6)) +
  labs(title = "Effect of Time on Muslim Acceptance") + theme_pubclean()  +
  geom_vline(xintercept = 5.49, linetype="dashed", 
                color = "red", size=.5)
pl0

model_parameters(m0)%>%
  kbl(booktabs = T, "latex", caption = "Marginal Structural Model (splines) of Year Trend on Muslim Warmth prior to Attacks") #%>%

# 3545-1540 # rescakled date = 2005
```



## Imputation 

## USE THIS DATASET 

```{r}
library(tidyverse)
km4 <- df %>%
  dplyr::select(
    Id,
    Age,
    Wave,
    EthnicCats,
    Employed,
    Urban,
    Edu,
    Male,
    Pol.Orient,
    NZdep,
    Religious,
    GenCohort,
    Urban,
    TSCORE,
    # Warm.Overweight,
    # Warm.Elderly,
    # Warm.MentalIllness,
    Warm.Muslims,
    # Warm.Immigrants,
    # Warm.Asians,
    # Warm.Refugees,
    # Wave,
    # Warm.Maori,
    # Warm.NZEuro,
    # Warm.Indians,
    # Warm.Chinese,
    # Warm.Refugees,
    # Warm.Pacific,
    YearMeasured
  ) %>%
  dplyr::filter(
      # Wave == 2012 &
      # YearMeasured == 1 |
      # Wave == 2013 &
      # YearMeasured == 1 |
      # Wave == 2014 &
      # YearMeasured == 1 |
      # Wave == 2016 &
      # YearMeasured == 1 |
      # Wave == 2017 &
      # YearMeasured == 1 |
      Wave == 2018 &
      YearMeasured == 1 |
      Wave == 2019 &
      YearMeasured == 1 
  )%>% 
  droplevels() %>%
  dplyr::mutate(Edu = as.numeric(Edu))%>%
  arrange(Wave,Id) %>%
  dplyr::group_by(Id) %>% filter(n() > 1) %>%
  dplyr::add_tally() %>%
  filter(n == 2)%>%
  # dplyr::mutate(Warm.Muslims_lag = lag(Warm.Muslims))%>%
  # dplyr::mutate(Attack_lead = lead(Attack)) %>%
  # dplyr::mutate(Attack_lag = lag(Attack))%>%
  ungroup() %>%
  arrange(Wave,Id) %>%
  dplyr::mutate(Attack = as.numeric((ifelse(TSCORE >= 3545, 1, 0)))) %>%
 # dplyr::filter(Attack == 0) %>%
  dplyr::mutate(dys = (TSCORE - min(TSCORE)))%>% 
  dplyr::mutate(Ys = Warm.Muslims, 
                As = Attack)%>%
  dplyr::mutate(yrs =  (dys/365))%>% 
  select(Id, Wave, yrs,Ys, As, Warm.Muslims,Attack, Age, EthnicCats, Edu, Employed, Urban, Male, GenCohort, Religious,Pol.Orient,Urban,NZdep)%>%
  arrange(Wave,Id) 

length(unique(km4$Id))
head(km4)

obtl<-table1::table1(~ Attack|Wave, data = km4, overall=FALSE)

obtl
t1kable(obtl, format ="latex", booktabs = TRUE)


x <- table1::table1(~ Warm.Muslims + Age + Male + GenCohort + Edu + Employed + EthnicCats  +  Religious + Pol.Orient + NZdep + Urban|Wave*As, data = km4, overall=FALSE)
x
t1kable(x, format ="latex")



### ALL

library(tidyverse)
km_all <- df %>%
  dplyr::select(
    Id,
    Age,
    Wave,
    EthnicCats,
    Employed,
    Urban,
    Edu,
    Male,
    Pol.Orient,
    NZdep,
    Religious,
    GenCohort,
    Urban,
    TSCORE,
    # Warm.Overweight,
    # Warm.Elderly,
    # Warm.MentalIllness,
    Warm.Muslims,
    # Warm.Immigrants,
    # Warm.Asians,
    # Warm.Refugees,
    # Wave,
    # Warm.Maori,
    # Warm.NZEuro,
    # Warm.Indians,
    # Warm.Chinese,
    # Warm.Refugees,
    # Warm.Pacific,
    YearMeasured
  ) %>%
  dplyr::filter(Wave == 2018 | Wave ==2019) %>%
  droplevels() %>%
  dplyr::mutate(org2018 =  ifelse(Wave == 2018 & YearMeasured ==1,1,0 ))%>%
  group_by(Id) %>%
  dplyr::mutate(hold = mean(org2018, na.rm = TRUE)) %>%  # Hack
  filter(hold>0) %>% # hack!
  dplyr::mutate(Edu = as.numeric(Edu))%>%
  arrange(Wave,Id) %>%
  dplyr::mutate(Attack = as.numeric((ifelse(TSCORE >= 3545|Wave ==2019, 1, 0)))) %>%
 # dplyr::filter(Attack == 0) %>%
  dplyr::mutate(dys = (TSCORE - min(TSCORE)))%>% 
  dplyr::mutate(Ys = Warm.Muslims, 
                As = Attack)%>%
  dplyr::mutate(yrs =  (dys/365))%>% 
  select(Id, Wave, yrs,Ys, As, Warm.Muslims,Attack, Age, EthnicCats, Edu, Employed, Urban, Male, GenCohort, Religious,Pol.Orient,Urban,NZdep)%>%
  arrange(Wave,Id) 

length(unique(km_all$Id))

table1::table1(~ Warm.Muslims|Wave*as.factor(Attack), data = km_all, overall=FALSE)


head(km_all)

obtl<-table1::table1(~ Attack|Wave, data = km_all, overall=FALSE)
kable(obtl, format ="latex", booktabs = TRUE)


x <- table1::table1(~ Warm.Muslims + Age + Male + GenCohort + Edu + Employed + EthnicCats  +  Religious + Pol.Orient + NZdep + Urban|Wave*As, data = km_all, overall=FALSE)
x
t1kable(x, format ="latex")



# # impute 
# library(Amelia)
# set.seed(1234)
# 
# km4<-as.data.frame(km4)
# imputed1 <- amelia(
#   km4, #dataset to impute
#   m = 10, # number of imputations
#   cs= c("Id"),
#   ts= c("yrs"),
#   noms = c(
#     "EthnicCats",
#     "Employed",
#     "Urban",
#     "Male",
#     "GenCohort",
#     "Religious"),
#  idvars=c("Wave"), # do not impute outcome
#   polytime = 3) #https://stackoverflow.com/questions/56218702/missing-data-warning-r
# #saveRDS(imputed,"imputed")



# create new data set
library(tidyverse)
kf  <-km_all %>%
  group_by(Id) %>%  # All ZEROS
 # mutate(Attack == as.numeric(Attack))%>%
  mutate(As = (ifelse(Wave==2018 & Attack == 1|Wave == 2019, 0, 
                     ifelse(Wave==2018 & Attack == 0, 1, Attack)))) %>%
  mutate(Ys = ifelse(Wave==2018 & Attack == 1|Wave ==2019, NA, 
                     ifelse(Wave==2018 & Attack == 0, NA, Warm.Muslims)))%>%
  ungroup() %>%
  arrange(Wave,Id) 


  
# Test
table1::table1(~Ys|Wave *as.factor(As), data =kf ,overall=F)

k0 <- km_all %>%
  arrange(Id,Wave) 

### ORDINARY TEST
library(Amelia)
k0<-as.data.frame(k0) 
k0$wave <-as.numeric(k0$Wave)-1
set.seed=1234

imputed_test<- amelia(
  k0, #dataset to impute
  m = 10, # number of imputations
  cs= c("Id"),
  ts= c("wave"),
  noms = c(
    "As",
    "EthnicCats",
    "Employed",
    "Pol.Orient",
    "Urban",
    "Male",
    "GenCohort",
    "Religious"),
 idvars=c("yrs","Wave")) #, # do not impute outcome
library(Amelia)
ka3<-as.data.frame(ka2)  







ka <- km_all %>%
bind_rows(kf)%>%
  arrange(Id,Wave) %>%
  mutate(As = as.factor(As)) %>%
  select(-c(Warm.Muslims,Attack))

head(ka)
ka
# Check 
table1::table1( ~Ys | Wave*As, data = ka)

# looks good
km_all%>%
  select(Id,Wave,As,Ys,yrs)

# impute missing data

# avoid collineraity
ka2<-ka%>%
  select(Id,Wave,As,Ys,Edu,EthnicCats,Employed,Urban,Male,GenCohort,Religious,Pol.Orient,NZdep, yrs)

library(Amelia)
ka2<-as.data.frame(ka2) 
ka2$wave<-as.numeric(ka2$Wave)-1
ka2$wave
set.seed=1234
imputed <- amelia(
  ka2, #dataset to impute
  m = 10, # number of imputations
  cs= c("Id"),
  ts= c("yrs"),
  noms = c(
    "As",
    "EthnicCats",
    "Employed",
    "Pol.Orient",
    "Urban",
    "Male",
    "GenCohort",
    "Religious"),
 idvars=c("Wave")) #, # do not impute outcome
library(Amelia)
ka3<-as.data.frame(ka2)     


### WITHOUT JOINT ASSUMPTION 
# filter only 0s and only 1s for the As
d0 <- ka3 %>%
  filter(As==0)

d1 <- ka3 %>%
  filter(As==1 )



#ka3$Wave<-as.numeric(ka3$Wave)


imputed_0<- amelia(
  set.seed=1234,
  d0, #dataset to impute
  m = 20, # number of imputations
 # cs= c("Id"),
#  ts= c("yrs"),
  noms = c(
    "EthnicCats",
    "Employed",
    "Urban",
    "Male",
   # "Ys",
    "GenCohort",
    "Religious"),
   idvars=c("Wave","As","Id","yrs","wave")) #, # do 



imputed_1<- amelia(
  d1, #dataset to impute
  m = 20, # number of imputations
  # cs= c("Id"),
  # ts= c("wave"),
  noms = c(
    "EthnicCats",
    "Employed",
    "Pol.Orient",
    "Urban",
    "Male",
    "GenCohort",
    "Religious"),
 idvars=c("As","yrs","Wave","Id")) #, # do not impute outcome



# imputed_19<- amelia(
#   set.seed=14321,
#   d1_19, #dataset to impute
#   m = 20, # number of imputations
#  # cs= c("Id"),
#  # ts= c("yrs"),
#   noms = c(
#     "EthnicCats",
#     "Employed",
#     "Urban",
#     "Male",
#    # "Ys",
#     "GenCohort",
#     "Religious"),
#    idvars=c("Wave","As","Id","yrs","wave")) #, # do 
# # function for combining dataframes
# 


m<-20
imps <-NULL
impsL <-NULL
for(i in 1:m) {
  imps$imputations$imp[[i]] <- dplyr::bind_rows(imputed_0$imputations[[i]], 
                                     imputed_1$imputations[[i]])
  imps$imputations$imp[[i]] <- imps$imputations$imp[[i]] %>% arrange(Wave,Id)
  impsL <- as.list
          
  
}


m<-20
imps<-NULL
for(i in 1:m) {
  imps$imputations$imp[[i]] <- dplyr::bind_rows(imputed_0$imputations[[i]], 
                                     imputed_1$imputations[[i]])
  imps$imputations$imp[[i]] <- imps$imputations$imp[[i]] %>% arrange(Wave,Id)
  
}

 
 
m<-20
impsL <-NULL
datlist <- NULL

for(i in 1:m) {
  impsL$imputations[[i]]<- as.data.frame(imps$imputations$imp[[i]])
}

# datlist <- impsL$imputations
# saveRDS(datlist, here::here("_posts", "mus", "mods", "datlist"))
# saveRDS(impsL, here::here("_posts", "mus", "mods", "imps"))
# saveRDS(imps, here::here("_posts", "mus", "mods", "imps"))


m<-20
models<-NULL
for(i in 1:m) {
  models[[i]] <- lmer(Ys ~ As * Wave  + (1|Id), data= imps$imputations$imp[[i]])
}

pool_parameters(models)

pred <- ggeffects::ggemmeans(models[[1]], terms = c("Wave","As"))
pred

plot(pred, facets = F) #  +  theme_classic() + ggtitle("") # title to be suppled

pool_parameters(models)




pred <- ggeffects::ggemmeans(models[[3]], terms = c("Wave","As"))
pred

plot(pred, facets = F) #  +  theme_classic() + ggtitle("") # title to be suppled



test <- lmer(Ys ~ As * Wave  + (1|Id), data=imp)
## Ordinal



ka3$wave<-as.numeric(ka3$Wave)
imputed_d<- amelia(
  ka3, #dataset to impute
  m = 20, # number of imputations
  cs= c("Id"),
  ts= c("yrs"),
  noms = c(
    "As",
    "EthnicCats",
    "Employed",
    "Urban",
    "Male",
    "GenCohort",
    "Religious"),
   idvars=c("Wave")) #, # do not impute outcome




#polytime = 3) #https://stackoverflow.com/questions/56218702/missing-data-warning-r
#saveRDS(imputed,here::here("_posts","mus","mods","imputed.rds"))
imputed<- readRDS(here::here("_posts","mus","mods","imputed.rds"))



tscsPlot(imputed, var = "Ys", cs =c(2,4,491,564,76,582), draws = 100, conf = 0.9, misscol = "red",
  obscol = "black")


imputed1<- imputed$imputations$imp1
imputed2<- imputed$imputations$imp2
imputed3<- imputed$imputations$imp3
imputed4<- imputed$imputations$imp4
imputed5<- imputed$imputations$imp5
imputed6<- imputed$imputations$imp6
imputed7<- imputed$imputations$imp7
imputed8<- imputed$imputations$imp8
imputed9<- imputed$imputations$imp9
imputed10<- imputed$imputations$imp10
str(imputed1)
hist(imputed1$Ys, col = "grey", border = "white")
hist(imputed2$Ys, col = "grey", border = "white")
hist(imputed3$Ys, col = "grey", border = "white")
hist(imputed4$Ys, col = "grey", border = "white")
hist(imputed5$Ys, col = "grey", border = "white")

table1::table1(~Ys| Wave*As, data = imputed1)
table1::table1(~Ys| Wave*As, data = imputed2)
table1::table1(~Ys| Wave*As, data = imputed3)
table1::table1(~Ys| Wave*As, data = imputed4)
table1::table1(~Ys| Wave*As, data = imputed5)


m<-10
models1<-NULL
for(i in 1:m) {
  models1[[i]] <- lmer(Ys ~ As * Wave  + (1|Id), data=imputed$imputations[[i]])
}

pool_parameters(models1)
pred1<- ggeffects::ggemmeans(models1[[2]], terms = c("Wave","As"))
pred1







ct<-table1::table1(~ As|Wave, data = imputed1, overall=FALSE)

ct<-table1::table1(~ Ys|As*Wave, data = imputed1, overall=FALSE)
ct2<-table1::table1(~ Ys|As*Wave, data = imputed2, overall=FALSE)


t1kable(out, format ="latex")

plot(imputed)


str(imputed)

??mi.meld
x<- mi.meld(imputed$imputations, se)

library(Amelia)
# see: https://www.andrewheiss.com/blog/2018/03/07/amelia-tidy-melding/, who writes:
# unclass() is necessary because bind_rows() will complain when dealing with
# lists with the "amelia" class, which is what amelia() returns



all_imputations <- bind_rows(unclass(imputed$imputations), .id = "m") %>%
  group_by(m) %>%
  nest()

all_imputations <- bind_rows(unclass(imps$imputations), .id = "m") %>%
  group_by(m) %>%
  nest()

unnest(all_imputations) %>%
  select(m, Wave, As,Ys )%>%
   arrange((m), Wave) %>%
   group_by(m,Wave,As) %>%
  rename( Dataset = m,
          Muslim_Warmth = Ys,
          Exposure = As) %>%
   summarise(mean = mean(Muslim_Warmth), sd = sd(Muslim_Warmth) )%>%
  pivot_wider(names_from = c("Exposure","Wave"), values_from = c(mean,sd))%>%
  mutate( across(where(is.numeric), round, 3)) 
%>%
   kbl("latex",booktabs =T, caption = "Imputed mean/sd for warmth to Muslims by condition and wave")
           
   
unnest(all_imputations) %>%
  select(m, Wave, As,Ys )%>%
   group_by(Wave,As) %>%
  rename( Dataset = m,
          Muslim_Warmth = Ys,
          Exposure = As) %>%
   summarise(n = n(), mean = mean(Muslim_Warmth), sd = sd(Muslim_Warmth) )%>%
  mutate( across(where(is.numeric), round, 3)) %>%
   kbl("latex",booktabs =T, caption = "Overall imputed mean/sd for warmth to Muslims by condition and wave")


# This doesn't work
# all_imputations_d <- bind_rows(unclass(imputed_d$imputations), .id = "m") %>%
#   group_by(m) %>%
#   nest()
# 
# unnest(all_imputations_d) %>%
#   select(m, Wave, As,Ys )%>%
#    group_by(Wave,As) %>%
#   rename( Dataset = m,
#           Muslim_Warmth = Ys,
#           Exposure = As) %>%
#    summarise(n = n(), mean = mean(Muslim_Warmth), sd = sd(Muslim_Warmth) )%>%
#   mutate( across(where(is.numeric), round, 3)) %>%
#    kbl("latex",booktabs =T, caption = "Overall imputed mean/sd for warmth to Muslims by condition and wave")

unnest(all_imputations_d) %>%
  select(m, Wave, As,Ys )%>%
   arrange((m), Wave) %>%
   group_by(m,Wave,As) %>%
  rename( Dataset = m,
          Muslim_Warmth = Ys,
          Exposure = As) %>%
   summarise(mean = mean(Muslim_Warmth), sd = sd(Muslim_Warmth) )%>%
  pivot_wider(names_from = c("Exposure","Wave"), values_from = c(mean,sd))%>%
  mutate( across(where(is.numeric), round, 3)) 
```

## FULL BAYES



```{r}
## FULL BAYES
m_direct <- brms::brm( 
  Ys ~ As +  Wave + (1|Id), 
  data = imputed1, 
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  backend = "cmdstanr",
  file = here::here("_posts", "mus", "mods", "m_direct.rds"))

lazerhawk::brms_SummaryTable(m_direct)
prior_summary(m_direct)
# Print Table
ouput <- tidy(m_direct)
str(ouput)
ouput
#output<- as.data.frame(ouput)


# ouput%>%
#   dplyr::select(-c("effect","component", "group"))


# t_results_m = m_direct %>% 
#   emmeans(~ As+Wave) %>% 
#   tidy(conf.int = TRUE) 
# 
# t_results_m
# t_results
# 
# saveRDS(t_results_m,  here::here("_posts", "mus", "mods", "t_results_m"))

t_results
saveRDS(t_results,  here::here("_posts", "mus", "mods", "t_results"))
library(lazerhawk)
brms_SummaryTable(m3a)

library(lazerhawk)
blh_tab <- brms_SummaryTable(m3a, panderize=F)
blh_tab
blh_tab %>%
   kable(booktabs = T, "latex", caption =  "Parameter for effect of attack on warmth to Muslims") %>%
    print()



## prior = c(prior(normal(0, 1), class = b)),

amelia.list <- list(imputed$imputations$imp1, 
                    imputed$imputations$imp2, 
                    imputed$imputations$imp3, 
                    imputed$imputations$imp4, 
                    imputed$imputations$imp5,
                    imputed$imputations$imp6, 
                    imputed$imputations$imp7, 
                    imputed$imputations$imp8, 
                    imputed$imputations$imp9, 
                    imputed$imputations$imp10)

#saveRDS(amelia.list,here::here("_posts","mus", "mods", "amelia.list"))
amelia.list<-readRDS(here::here("_posts","mus", "mods", "amelia.list"))

m3b <- brms::brm_multiple(
  Ys ~ As *  Wave + (1|Id), 
  seed = 1234,
  warmup = 500,
  iter = 1000,
  chains = 4,
  backend = "cmdstanr",
  data = amelia.list,
  file = here::here("_posts", "mus", "mods", "m3ab.rds"))

summary(m3a)
brms_SummaryTable(m3a)
```


### USE THIS

```{r}
#amelia.list<-readRDS(here::here("_posts","mus", "mods", "amelia.list"))

m_us <- brms::brms(
  Ys ~ As +  Wave + (1|Id), 
  prior = c(
    prior(student_t(3, 4.2, .25), class = Intercept),
    prior(normal(0, .5), class = b),
    prior(student_t(3, 0, 1), class = sd, group = Id),
    prior(student_t(3, 0, 1), class = sd, Intercept, group = Id)),
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  backend = "cmdstanr",
  data = amelia.list,
  file = here::here("_posts", "mus", "mods", "m_us.rds"))
prior_summary(m_us)
summary(m_us)
```


### BAYES 2

```{r}
#### BRMS MODELS


#iter=10^6, thin =10
### connection to self. 
# library(lme4)
# library(merTools)
# with( dwat.out.SC$imputations$imp2, CrossTable(EthnicIndian,HinduPlusPuja))
# 
# # rm(modList)
# modList <- lmerModList(ConWork~ Time * HinduPlusPuja  + Time * EmotionalClose  + Age.C.decade + EthnicIndian + Male + (1|Id), data = dwat.out.SC$imputations)

# summary(modList)
#   print(modList)
# plot_model(modList$imp1)
# tab_model(modList$imp1)
# tab_model(modList$imp2)
# tab_model(modList$imp3)
# tab_model(modList$imp4)
# tab_model(modList$imp5)ggplot2::labs(colour = "factor1 (centred and normalized)")
# <- "Close to Diwali Dancer"
# ts<-ggpredict(modList$imp1, c("Time","HinduPlusPuja")) 
# plot(ts, facet=T)  +  labs(title = "Predicted Happiness Decay", y="Connected to Self")
# 
# 
# )


### omni-model  ### 

marg_eff_attack_0a <- m_direct %>%
  epred_draws(newdata = expand.grid(As = c(0, 1),Wave = c("2018", "2019")),
              re_formula =NA)
           #   re_formula = NULL)  # or re_formula = ~ (1 | region)

#saveRDS(marg_eff_attack_0a,  here::here("_posts", "mus", "mods", "marg_eff_attack_0a.rds"))
marg_eff_attack_0a <- readRDS(here::here("_posts", "mus", "mods", "marg_eff_attack_0a.rds"))

marg_eff_attack_0a
# Obtain contrasts
# marg_eff_attack_0a<- marg_eff_attack_0a%>%
#   filter(As == 1 & Wave ==2019) #Attack == 1 & Wave ==2018|  Attack == 0 & Wave ==2018)

# marg_eff_attack_0
plot_all <- ggplot(
  marg_eff_attack_0a,
  aes(
    x = .epred,
    y = Wave,
    fill = as.factor(As)
  ) ) + 
#  scale_y_discrete(limits=rev) +
    stat_halfeye() +
    scale_fill_okabe_ito() +
    labs(
      x = "Predicted Warmth Response",
      y = "w2018(years 2018-2019); w2019 (years 2019-2020)",
      fill = "Conterfactual Contrasts",
      subtitle = "Bayesian posterior locations of potential outcomes"
    ) +
  #  scale_x_continuous(limits=c(4.0,4.6)) +
    theme_pubclean() +
    theme(legend.position = "bottom"
    )
plot_all
#plot_all


# not working
grand_mean_ame_a <- m3a %>%
  emmeans(~ As*Wave,
          epred = TRUE, re_formula = NA) %>%
  contrast() %>%
  gather_emmeans_draws() 

grand_mean_ame_a
#   filter(As == 1 & Wave ==2019) #Attack == 1 & Wave ==2018|  Attack == 0 & Wave ==2018)

#saveRDS(grand_mean_ame_a,  here::here("_posts", "mus", "mods", "grand_mean_ame_a.rds"))
#grand_mean_ame_a <- readRDS(here::here("_posts", "mus", "mods", "grand_mean_ame_a.rds"))

# remove erro contrasts / we don't observe 0 in year two 




plot_all__ame <- ggplot(grand_mean_ame_a,
                                     aes(x = .value)) +
  stat_halfeye(slab_alpha = 0.75, fill = "grey") +
  scale_fill_okabe_ito(order = c(3, 4)) +
  labs(x = "Average marginal effect of attack on warmth to Muslims",
       y = "Density") +
  #facet_wrap(vars(region)) +
  theme_classic() + 
  theme(legend.position = "bottom") + labs(title= "Marginal effect of attack on warmth to Muslims")
plot_all__ame 
# Try
library(patchwork)
bayes_plots_a <- plot_all + plot_all__ame + plot_annotation(tag_levels = 'a')
bayes_plots_a

ggsave(
  bayes_plots_a,
  path = here::here(here::here("_posts", "mus", "figs")),
  width = 10,
  height = 5,
  units = "in",
  filename = "bayes_plots_a.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)


# 
# blh_tab %>%
#    kable(booktabs = T, "latex", caption =  "Parameter for effect of attack on warmth to Muslims") %>%
#     print()
```

## MI Bayes

```{r}
## Run on my other mac, cmdstanr was ausing problems
gc()
m3ab <- readRDS(here::here("_posts", "mus", "mods", "m3ab.rds"))

summary(m3ab)

# Model was as below, called Rstand
# m3ab <- brms::brm_multiple(Ys ~ As *  Wave + (1|Id), 
#   seed = 1234,
#   warmup = 500,
#   iter = 1500,
#   chains = 4,
#  # backend = "cmdstanr",
#    data = imputed, 
#   file = here::here("_posts", "mus", "mods", "m3ab.rds"))



plot_bayes <- m3ab %>%
  emmeans( ~ As * Wave) %>%
  contrast(method = "pairwise") %>%
  gather_emmeans_draws() %>%
  ggplot(aes(x = .value, y = contrast)) +
  stat_halfeye()



marg_eff_attack_0ab <- m3ab %>%
  epred_draws(newdata = expand.grid(As = c(0, 1),Wave = c("2018", "2019")),
              re_formula =NA)

saveRDS(marg_eff_attack_0ab,  here::here("_posts", "mus", "mods", "marg_eff_attack_0ab.rds"))
#marg_eff_attack_0ab <- readRDS(here::here("_posts", "mus", "mods", "marg_eff_attack_0ab.rds"))


# Obtain contrasts

marg_eff_attack_0ab
plot_all <- ggplot(
  marg_eff_attack_0ab,
  aes(
    x = .epred,
    y = Wave,
    fill = as.factor(As)
  ) ) + 
#  scale_y_discrete(limits=rev) +
    stat_halfeye() +
    scale_fill_okabe_ito() +
    labs(
      x = "Predicted Warmth Response",
      y = "w2018(years 2018-2019); w2019 (years 2019-2020)",
      fill = "Conterfactual Contrasts",
      subtitle = "Bayesian posterior locations of potential outcomes"
    ) +
  #  scale_x_continuous(limits=c(4.0,4.6)) +
    theme_pubclean() +
    theme(legend.position = "bottom"
    )
plot_all
#plot_all


grand_mean_ame_ab <- m3ab %>% 
  emmeans(~ As*Wave,
          epred = TRUE, re_formula = NA) %>% 
  gather_emmeans_draws() 
   
grand_mean_ame_ab
grand_mean_ame_ab
saveRDS(grand_mean_ame_ab,  here::here("_posts", "mus", "mods", "grand_mean_ame_ab.rds"))
grand_mean_ame_ab <- readRDS(here::here("_posts", "mus", "mods", "grand_mean_ame_ab.rds"))
grand_mean_ame_ab%>%
  slice(10000)
# remove erro contrasts / we don't observe 0 in year two 
test <- grand_mean_ame_ab


plot_all__ame_ab <- ggplot(grand_mean_ame_ab,
                                     aes(x = .value)) +
  stat_halfeye(slab_alpha = 0.75, fill = "grey") +
  scale_fill_okabe_ito(order = c(3, 4)) +
  labs(x = "Average marginal effect of attack on warmth to Muslims",
       y = "Density") +
  #facet_wrap(vars(region)) +
  theme_classic() + 
  theme(legend.position = "bottom") + labs(title= "Marginal effect of attack on warmth to Muslims")
plot_all__ame_ab 
library(patchwork)
bayes_plots_a <- plot_all + plot_all__ame + plot_annotation(tag_levels = 'a')
bayes_plots_a

ggsave(
  bayes_plots_a,
  path = here::here(here::here("_posts", "mus", "figs")),
  width = 10,
  height = 5,
  units = "in",
  filename = "bayes_plots_a.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)

```



## Experimental

```{r}
path_m <- bf(
  yrs ~  As + Wave + (1 | c | Id)
  )
path_y <- bf(
  Ys|mi() ~ As + Wave + yrs + (1 | c | Id)
  )

med1 <- brm(
  path_m + path_y + set_rescor(FALSE)
  data = ka2,
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  backend = "cmdstanr",
  file = here::here("_posts", "mus", "mods", "med1")
)

summary(med1)
prior_summary(med1)
lazerhawk::brms_SummaryTable(med1, panderize=F)


## Correct model 
bm_c <- brm_multiple(
  Ys|mi() ~ As * Wave + (1 |  Id),
  prior = c(
    prior(student_t(3, 0, .5), class = Intercept),
    prior(student_t(3, 0, 1), class = "b")),
  data = datlist, # correct data
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  backend = "cmdstanr",
  file = here::here("_posts", "mus", "mods", "bm_c"))

#summary(bm_c)

lazerhawk::brms_SummaryTable(bm_c, panderize=F)
plot(bm_c)





```


```{r echo=FALSE, cache = FALSE}
post1F <- brms::posterior_samples(f1a)
post_marF <- post1F %>% 
  transmute(
    a = b_mF_xEarly_March_2020,
    b = b_y_mF_w,
    cp = b_y_xEarly_March_2020,
    me = a * b,
    c = cp + me#,
   # pme = me / c
  )
# posterior_summary(post_marF)
```
```{r}
mcmc_intervals(post_marF)
??mcmc_intervals
```

```




