---
title: "Does income affect psychological distress?"
description: |
author:
  - name: Joseph Bulbulia
    url: https://josephbulbulia.netlify.app
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: 0000-0002-5861-2056
date: 2021-DEC-02
output:
  distill::distill_article:
    self_contained: false
    toc: true
    code_folding: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  layout = "l-body-outset",
  fig.width = 12,
  fig.height = 15,
  collapse = TRUE,
  R.options = list(width = 60
  )
)
```

```{r libs, include=FALSE}
library("tidyverse")
library("easystats")
library("here")
library("equatiomatic")
library("lubridate")
library("ggplot2")
library("ggthemes") #themes
library("ggpubr")
library("viridis")
library("patchwork")
library("ggforce")
library("kableExtra")
library("lme4")
library("brms")
library("rstan")
library("rstanarm")
library("bayesplot")
library("kableExtra")
library("broom")
library("tidybayes")
library("bmlm")
library("gfoRmula")
library("ipw")
library("geepack")
# rstan options
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores ())
theme_set(theme_classic())
```

```{r data, cache = TRUE}
#import data
# long data
df <- readRDS(here::here("data", "df"))
```

Does money make people happy?


## Data preparation 

```{r dataprep, cache=TRUE}
# comparative analysis

# prepare data
# note, still need to do IPW and multiply impute missing data

dt <- df %>%
  dplyr::filter(YearMeasured == 1)  %>%
 dplyr::filter(Wave != 2009) %>% # no k6 measure
  dplyr::filter(!is.na(KESSLER6sum), !is.na(Household.INC),!is.na(EthnicCats),!is.na(Male),!is.na(Urban), !is.na(Employed)) %>%
  dplyr::select(
    Id,
    Household.INC,
    KESSLER6sum,
    NZdep,
    Wave,
    TSCORE,
    Age,
    Religion.Prayer,
    Religion.Scripture,
    Religion.Church,
    Male,
    Edu,
    EthnicCats,
    Urban,
    Wave,
    Employed,
    Partner
  ) %>%
  dplyr::mutate(
    k6 = as.numeric(KESSLER6sum),
    age = (Age),
    inc_l = log(Household.INC + 1),
    emp = as.numeric(Employed),
    age_c = scale(Age, scale = F),
  #  pray_l = log(Religion.Prayer + 1),
  #  script_l = log(Religion.Scripture + 1),
    church_l = log(Religion.Church + 1),
    edu = as.numeric(Edu),
    partner = as.numeric(Partner),
    male = as.factor(Male),
    eth = EthnicCats,
    nzdep = as.numeric(NZdep),
    urban = Urban
  ) %>%
  dplyr::group_by(Id) %>% filter(n() > 2) %>%
  dplyr::mutate(across(
    c(
      age_c,
      male,
      eth,
      emp,
      urban,
      k6,
      inc_l,
      edu,
      church_l,
      nzdep,
      partner
    ),
    list(lag = lag)
  )) %>%
  dplyr::mutate(k6_lag = as.numeric(k6_lag),
                inc_l_lag = as.numeric(inc_l_lag),
                church_l_lag = as.numeric(church_l_lag) ) %>%
  dplyr::ungroup(Id) %>%
  dplyr::filter(!is.na(k6_lag),
                !is.na(inc_l_lag),
                !is.na(urban_lag),
                !is.na(emp_lag),
                !is.na(nzdep),
                !is.na(partner_lag))%>%
  arrange(Wave,Id)
                
 #)%>%  # lots of missingness on edu, so might leave this out
    #   dplyr::mutate(across(c(male_lag, age_s_lag, eth_lag, urban_lag, # lage 2
    #                      church_l_lag), list(lag = lag))) %>%
    # dplyr::mutate(k6_s_lag = as.numeric(inc_l_lag),
    #             inc_s_lag = as.numeric(inc_s_lag) )%>%  # lots of missingness on edu, so might leave this out or better multiply impute


# cound id's
#length(unique(dt$Id))

# demean data to obtain within/between individual predictors
# we'll be looking at church attendance and scripture reading in other work 


# see https://easystats.github.io/datawizard/articles/demean.html
# we want to deal with *Heterogeneity bias *
dt <- cbind(dt,
            demean(
              dt,
              select = c("inc_l",
                         "k6",
                         "age",
                         "church_l"),
              group = "Id"
            )) %>%
  mutate(
    age_between_c = scale(age_between, scale = FALSE),
    inc_l_between_c = scale(inc_l_between, scale = FALSE)
  )



```


## Within and between person mixed effects regression: IPW

```{r}
# ip weights


dt_weights_1 <- ipw::ipwtm(
  exposure = k6,
  family = "gaussian",
  type = "all",
  corstr = "ar1",
  id = "Id",
  timevar = "Wave",
  numerator = ~ k6_lag  + inc_l_between  + age_within + age_between_c +
    male + emp + eth + emp_lag + nzdep + partner_lag + urban_lag,
  denominator = ~ k6_lag  + inc_l_within + inc_l_between  + age_within + age_between_c +
    male + emp + eth + emp_lag + nzdep + partner_lag + urban_lag ,
  data = as.data.frame(dt)
)

df_weights_use_1 <- dt %>%
  mutate(ipw = dt_weights_1$ipw.weights)



# possion because k6 behaves as a rate parameter. but takes too long to run for this simple demonstration
m1 <-
  lmer(
    k6  ~ k6_lag  + inc_l_within + inc_l_between  + age_within + age_between_c +
      male + eth + emp_lag + partner_lag  + nzdep_lag + urban_lag + (1 | Id),
    weights = df_weights_use_1$ipw,
    data = df_weights_use_1
    # family = "poisson"
  )


parameters::model_parameters(m1) %>%
  print_html()
```

We do not find reliable (or large)  within-person effects:

```{r}
# graph
p <- plot( ggeffects::ggpredict(m1, terms = "inc_l_within [0,15]"),  add.data = TRUE, dot.alpha = 0.05)   # 
p #+ scale_y_continuous(limits= c(0,15)) # nothing
```

There are between person associations between income and distress, although we do not estimate this as a causal effect. 

```{r}
p2 <-plot(ggeffects::ggpredict(m1, terms = "inc_l_between [0,15]"),  add.data = TRUE, dot.alpha = 0.05) # 
p2# + scale_y_continuous(limits= c(0,15)) # nothing
```

## Marginal Structural model approach: IPW

Here we will used lagged values of the exposure to adjust for confounders and IP weights.

```{r}

# calculate weights

dt_weights_2 <- ipw::ipwtm(
  exposure = k6,
  family = "gaussian",
  type = "all",
  corstr = "ar1",
  id = "Id",
  timevar = "Wave", 
  numerator = ~ k6_lag  + age_c +
    male + eth +  emp_lag + nzdep + partner_lag  +  urban_lag ,
  denominator = ~ k6_lag  + inc_l_lag  + age_c +
    male + eth + emp_lag + nzdep + partner_lag + urban_lag,
  data = as.data.frame(dt)
)
dt_weights_use_2 <- dt %>% 
  mutate(ipw = dt_weights_2$ipw.weights)



# 
m2 <- geeglm(
  k6  ~ k6_lag  + inc_l  + as.numeric(age_c) +
    male + eth + emp_lag + nzdep + partner_lag +  urban_lag ,
  data = dt_weights_use_2,
  id = Id,
  weights = ipw,
  waves = Wave,
  corstr = "ar1",
)

parameters::model_parameters(m2) %>%
  print_html()

p2 <- plot(ggeffects::ggpredict(m2, terms = "inc_l"),add.data = TRUE, dot.alpha = 0.1)    # 2 x standard deviations
p2 #+ scale_y_continuous(limits= c(0,15)) # nothing

```

Causal effect


##  What would happen if we did not use IPW? 

We find income very strongly related to Kessler 6 distress!

```{r}
m2_no_weights <- geeglm(
  k6  ~ k6_lag  + inc_l  + as.numeric(age_c) +
    male + eth + emp_lag  + nzdep + partner_lag +  urban_lag ,
  data = dt_weights_use_2,
  id = Id,
  waves = Wave,
  corstr = "ar1",
)


parameters::model_parameters(m2_no_weights) %>%
  print_html()


p2_n <-plot( ggeffects::ggpredict(m2_no_weights, terms = "inc_l"),add.data = TRUE, dot.alpha = 0.1) #
p2_n #+ scale_y_continuous(limits= c(0,15)) # 

```

Without IP weights the model estimates a stronger causal effect!

This suggests the importance of specifying correct IP weights.


## Mixed effects approach: IPW and GAMM

This recovers the same estimate

```{r}
library(gamm4)
library(splines)

m2_lmer <- lmer(
  k6  ~ k6_lag  + bs(inc_l)  + as.numeric(age_c) +
    male + eth +  emp_lag  + nzdep +  urban_lag + (1|Id),
  data = dt_weights_use_2,
  weights = dt_weights_use_2$ipw
)

parameters::model_parameters(m2_lmer) %>%
  print_html()

# unclear
p2m2_lmer <- plot( ggeffects::ggpredict(m2_lmer, terms = "inc_l [all]"),add.data = TRUE, dot.alpha = 0.1)   
p2m2_lmer # + scale_y_continuous(limits= c(0,15)) 
```

This reveals the possible problems in the distribution of values across the sample. Although pretheoretically we would expect the effect to be linear. 

## Mixed effects approach: Linear IPW

```{r}
m2_lmer2 <- lmer(
  k6  ~ k6_lag  + inc_l  + as.numeric(age_c) +
    male + eth + nzdep + partner_lag +  urban_lag + (1|Id),
  data = dt_weights_use_2,
  weights = dt_weights_use_2$ipw
)


parameters::model_parameters(m2_lmer2) %>%
  print_html()

# then it looks as though more income = lower distress. 
p3 <- plot( ggeffects::ggpredict(m2_lmer2, terms = "inc_l"), add.data = TRUE, dot.alpha = 0.1)     # 
p3
```

Here we find support for a linear relationship which is slightly stronger than the GEE estimate (with weights)

## Questions

The question arises, which model to prefer? I think probably GEE.

Key points:

  - Sensitivity to IP weighting = important.
  - Model specification = important.
  - Handling of zero income? 
  - Need to handle missingness! 
  - Need to include more confounders, probably.
  - Draw a DAG!
  - All sorts of reasons people change in househould income. 
  - Probably go with GEE. 

