---
title: "Does income affect psychological distress?"
description: |
author:
  - name: Joseph Bulbulia
    url: https://josephbulbulia.netlify.app
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: 0000-0002-5861-2056
date: 2021-DEC-02
output:
  distill::distill_article:
    self_contained: false
    toc: true
    code_folding: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  layout = "l-body-outset",
  fig.width = 12,
  fig.height = 15,
  collapse = TRUE,
  R.options = list(width = 60
  )
)
```

```{r libs, include=FALSE}
library("tidyverse")
library("easystats")
library("here")
library("equatiomatic")
library("lubridate")
library("ggplot2")
library("ggthemes") #themes
library("ggpubr")
library("viridis")
library("patchwork")
library("ggforce")
library("kableExtra")
library("lme4")
library("brms")
library("rstan")
library("rstanarm")
library("bayesplot")
library("kableExtra")
library("broom")
library("tidybayes")
library("bmlm")
library("gfoRmula")
library("ipw")
library("geepack")
library("gesttools")
library("lcsm")
library("patchwork")

# rstan options
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores ())
theme_set(theme_classic())
```

```{r data, cache = TRUE}
#import data
# long data
df <- readRDS(here::here("data", "df"))
```

Does money make people happy?


## Data preparation 

```{r dataprep, cache=TRUE}
# comparative analysis

# prepare data
# note, still need to do IPW and multiply impute missing data

dt <- df %>%
  dplyr::filter(YearMeasured == 1)  %>%
 dplyr::filter(Wave != 2009) %>% # no k6 measure
  dplyr::filter(!is.na(KESSLER6sum), !is.na(Household.INC),!is.na(EthnicCats),!is.na(Male),!is.na(Urban), !is.na(Employed)) %>%
  dplyr::select(
    Id,
    Household.INC,
    KESSLER6sum,
    NZdep,
    Wave,
    TSCORE,
    Age,
    Religious,
    Religion.Prayer,
    Religion.Scripture,
    Religion.Church,
    Male,
    Edu,
    EthnicCats,
    Urban,
    Wave,
    Employed,
    Partner
  ) %>%
  dplyr::mutate(
    k6 = as.numeric(KESSLER6sum),
    age = (Age),
    inc_l = log(Household.INC + 1),
    emp = as.numeric(Employed),
  #  pray_l = log(Religion.Prayer + 1),
  #  script_l = log(Religion.Scripture + 1),
    church_l = log(Religion.Church + 1),
    edu = as.numeric(Edu),
    religious = as.numeric(Religious),
    partner = as.numeric(Partner),
    male = as.factor(Male),
    eth = EthnicCats,
    nzdep = as.numeric(NZdep),
    urban = Urban,
   id = Id
  ) %>%
  dplyr::group_by(Id) %>% filter(n() > 2) %>%
  mutate(time0 = as.numeric(Wave))%>%
  mutate(time = time0 - min(time0) )%>%
  mutate(mxtime = max(time))%>%
  dplyr::mutate(across(
    c(
      age,
      male,
      eth,
      emp,
      urban,
      k6,
      inc_l,
      edu,
      church_l,
      nzdep,
      partner,
      religious
    ),
    list(lag = lag)
  )) %>%
   dplyr::mutate(across(c(age_lag, 
                        eth_lag, 
                        urban_lag,
                        male_lag, 
                        urban_lag,
                        edu_lag, 
                        church_l_lag, 
                        nzdep_lag, 
                        partner_lag,
                        religious_lag,
                        emp_lag,
                        k6), 
                 list(lag = lag)
                 ))%>%
  dplyr::ungroup(Id) %>%
  dplyr::select(id, k6, k6_lag, inc_l_lag, age_lag_lag, eth_lag_lag,urban_lag_lag,edu_lag_lag,
                church_l_lag_lag,nzdep_lag_lag,partner_lag_lag,emp_lag_lag,time,male_lag_lag,mxtime, inc_l, age_lag, emp_lag, partner_lag,male_lag, edu_lag, eth_lag, church_l_lag, urban_lag, religious_lag, nzdep_lag, Id) %>%
  drop_na() %>%
  dplyr::mutate(age_c_lag_lag = scale(age_lag_lag, scale = F)) %>%
    dplyr::arrange(id,time)

  
#dt<- dt %>%
 # mutate_all(~as.numeric(.))


dt<-as.data.frame(dt)

# cound id's
#length(unique(dt$Id))

# demean data to obtain within/between individual predictors
# we'll be looking at church attendance and scripture reading in other work 
# 
# 
```


<!--  ```{r} -->
<!-- # # ip weights -->
<!-- #  -->
<!-- # # possion because k6 behaves as a rate parameter. but takes too long to run for this simple demonstration -->
<!-- # m1 <- -->
<!-- #   lmer( -->
<!-- #     k6  ~ k6_lag  + inc_l_within + inc_l_between  + age_within + age_between_c + -->
<!-- #       male + eth + emp_lag + partner_lag  + nzdep_lag + urban_lag + (1 | Id), -->
<!-- #     data = df_weights_use_1 -->
<!-- #     # family = "poisson" -->
<!-- #   ) -->
<!-- #  -->
<!-- #  -->
<!-- # parameters::model_parameters(m1) %>% -->
<!-- #   print_html() -->
<!-- ``` -->




## Draw your assumptions


# Dag

We adjust for the effects of unmeasured confounders (U) by conditioning on the lag of the exposure, the lag of the outcome, and the lag2 of measured confounders (L):  

```{r}
# Create Dags
library(ggdag)
dg <- ggdag::dagify(
  k6  ~ k6_lag  + inc_lag  + L,
  inc_lag ~ L + U,
  k6_lag  ~   L + U,
  L ~ U,
  exposure = "inc_lag",
  outcome = "k6",
  latent = "U"
) %>%
  control_for("k6_lag")

#Check backdoor paths
#p1 <-ggdag(dg) + theme_dag_blank() + labs(title = "confounding control")
#p1
ggdag::ggdag_adjustment_set(dg) + theme_dag_blank()

```


## Descriptive graphs


Here we plot change in K6 by id over 10 waves. Hard to see what is happening. 

```{r}
df %>% 
  dplyr::filter(YearMeasured==1) %>%
  dplyr::group_by(Id) %>% filter(n() > 9) %>%
  ungroup()%>%
  ggplot(aes(x = TSCORE,
             y = KESSLER6sum)) +
  geom_point() +
  geom_line(aes(group = Id), 
            size = 1, 
            alpha = .1) +
 # geom_smooth(method = "lm") +
  theme_bw() +
  #facet_grid(.~ Employed) +
  labs(title = "Change in distress over time",
       subtitle = "NZAVS years: 2010-2020")
```


Here we plot distress trajectories witin a subset of individuals. This approach helps us to see the qualities of the data. 


```{r}
library(lcsm)
widelong <-  df %>%
  dplyr::filter(YearMeasured==1) %>%
  dplyr::filter(Wave!=2009) %>% # k6 not measured in wave 1
  dplyr::group_by(Id) %>% filter(n() > 9) %>%
  dplyr::select(Id, KESSLER6sum, Wave) # 

##THIS HANGS
#out <- with(relwidelong, long2matrices(id = Id, X = Age, Y = Religious))

wide <- spread(widelong, Wave, KESSLER6sum)

wide2 <- wide[complete.cases(wide),]


x_var_list <- names(wide2[, 2:11])



wide2 <- as.data.frame(wide2)
plot_trajectories(
  data = wide2,
  id_var = "Id",
  var_list = x_var_list,
  line_colour = "red",
  xlab = "Time",
  ylab = "Value",
  connect_missing = F,
  scale_x_num = T,
  scale_x_num_start = 1,
  random_sample_frac = 0.05,
  seed = 1234
  #title_n = T
)  +
  facet_wrap( ~ Id)



```

Next we can look at variation in income. Is this variable reliable? 

```{r}
widelong <-  df %>%
  dplyr::filter(YearMeasured==1) %>%
  dplyr::filter(Wave!=2009) %>% # 1
  dplyr::group_by(Id) %>% filter(n() > 9) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(Household.INC_log = log(Household.INC+1)) %>%
  dplyr::select(Id, Household.INC_log, Wave) # 

wide <- spread(widelong, Wave, Household.INC_log)

wide2 <- wide[complete.cases(wide),]


x_var_list <- names(wide2[, 2:11])
wide2 <- as.data.frame(wide2) # needs df

# graph
plot_trajectories(
  data = wide2,
  id_var = "Id",
  var_list = x_var_list,
  line_colour = "red",
  xlab = "Time",
  ylab = "Value",
  connect_missing = F,
  scale_x_num = T,
  scale_x_num_start = 1,
  random_sample_frac = 0.05,
  seed = 1234
  #title_n = T
)  +
  facet_wrap( ~ Id)

```


Consider NZdep. Is this variable reliable? Lots of movement. 

```{r}
widelong <-  df %>%
  dplyr::filter(YearMeasured==1) %>%
  dplyr::filter(Wave!=2009) %>% # 1
  dplyr::group_by(Id) %>% filter(n() > 9) %>%
  dplyr::ungroup() %>%
  dplyr::select(Id, NZdep, Wave) # 

wide <- spread(widelong, Wave, NZdep)


wide2 <- wide[complete.cases(wide),]


x_var_list <- names(wide2[, 2:11])



wide2 <- as.data.frame(wide2)
plot_trajectories(
  data = wide2,
  id_var = "Id",
  var_list = x_var_list,
  line_colour = "red",
  xlab = "Time",
  ylab = "NZdep",
  connect_missing = F,
  scale_x_num = T,
  scale_x_num_start = 1,
  random_sample_frac = 0.05,
  seed = 1234
  #title_n = T
)  +
  facet_wrap( ~ Id)

```


## So called "Fixed Effects Models"

Some worry about "heterogeneity bias."  Can separate within and between participant features of change? It seems that we should do so, for example, to avoid Simpson's Paradoxes. 

See: https://easystats.github.io/datawizard/articles/demean.html



```{r}
# see https://easystats.github.io/datawizard/articles/demean.html
# we want to deal with *Heterogeneity bias *
# prepare data
dt2 <- cbind(dt,
             demean(dt,
                    select = c("inc_l"),
                    group = "Id")) %>%
  mutate(
    inc_l_between_c = scale(inc_l_between, scale = FALSE)
  )



m1 <- lmer(
  k6 ~ 
    inc_l_within + 
    inc_l_between_c  +
    as.numeric(k6_lag) +
    as.numeric(age_lag) +
    male_lag +
    eth_lag +
    emp_lag +
    nzdep_lag +
    partner_lag +
    religious_lag + 
    church_l_lag + 
    urban_lag + (1 | Id),
  data = dt2
)


parameters::model_parameters(m1) %>%
  print_html()

library(ggeffects)
p0 <- plot(ggeffects::ggpredict(m1, terms = "inc_l_within[all]"), add.data = TRUE, dot.alpha = 0.1) + labs(title = "Within-person association of log income change on K6 distress")   

p1 <- plot(ggeffects::ggpredict(m1, terms = "inc_l_between_c[all]"), add.data = TRUE, dot.alpha = 0.1)    + labs(title = "Between-person association of log income on K6 distress")   # 2 x standard deviations

library(patchwork)
p0 + p1
```

We find no evidence for a within-person association with k6 

We find strong btween person association on income on k6. 

A causal interpretation does not seem legitimate here. The within and between person averages do not reflect a temporal ordering in which causes precede effects. Both the within-person and between person "effects" average over the entire time series.  To investigate within persona affects we perhaps want to assess gains in income during the previous year. However, there might be other ways to think about this. For example, perhaps the inference using "fixed" effects can view the world *sub species aeternitatis*.


## GEE

Here we will used lagged values of the exposure to adjust for confounders and IP weights.


First we calculate weights for the exposure 


```{r}
## Marginal Structural model approach: IPW


```{r}
# calculate weights
dt_weights_2 <- ipw::ipwtm(
  exposure = k6,
  family = "gaussian",
  type = "all",
  corstr = "ar1",
  id = "id",
  timevar = "time", 
  numerator = ~  k6_lag  + 
    age_c_lag_lag +
    male_lag_lag + 
    eth_lag_lag + 
    emp_lag_lag + 
    nzdep_lag_lag + 
    partner_lag_lag+  
    urban_lag_lag,
  denominator = ~ 
    k6_lag  + 
    inc_l_lag  + 
    age_c_lag_lag +
    male_lag_lag + 
    eth_lag_lag + 
    emp_lag_lag + 
    nzdep_lag_lag + 
    partner_lag_lag+  
    urban_lag_lag,
  data = as.data.frame(dt2)
)
dt_weights_use_2 <- dt2 %>% 
  mutate(ipw = dt_weights_2$ipw.weights)
```


Next we run a model, including lagged K6 and lagged confounders (unless time invariant). Note that we could take the lag of the exposure and the lag2 of the confounders.  Additionally, this model does not handle missing data. Finally, we would want a richer set of baseline confounders. That aside, we find: 

```{r}
str(dt)
m2 <- geeglm(
  k6  ~ k6_lag  + 
    inc_l_lag  + 
    as.numeric(age_c_lag_lag) +
    male_lag_lag + 
    eth_lag_lag + 
    emp_lag_lag + 
    nzdep_lag_lag + 
    partner_lag_lag+  
    urban_lag_lag,
  data = dt_weights_use_2,
  id = id,
  weights = ipw,
  waves = time,
  corstr = "ar1"
)

parameters::model_parameters(m2) %>%
  print_html()

library(ggeffects)
p2 <- plot(ggeffects::ggemmeans(m2, terms = "inc_l_lag[all]"), add.data = TRUE, dot.alpha = 0.1)    # 2 x standard deviations
p2 #+ scale_y_continuous(limits= c(0,15)) # nothing
```


## Weights within/between (No  difference)

We can try within/between model with weights. (We can, but we probably shouldn't)

```{r}
head(dt_weights_use_2)
m1b <- lmer(
  k6 ~ 
    inc_l_within + 
    inc_l_between_c  +
    as.numeric(k6_lag) +
    as.numeric(age_lag) +
    male_lag +
    eth_lag +
    emp_lag +
    nzdep_lag +
    partner_lag +
    religious_lag + 
    church_l_lag + 
    urban_lag + (1 | Id),
   weights = dt_weights_use_2$ipw,
   data =  dt_weights_use_2
)


parameters::model_parameters(m1b) %>%
  print_html()

library(ggeffects)
p0b <- plot(ggeffects::ggpredict(m1b, terms = "inc_l_within[sd]"), add.data = TRUE, dot.alpha = 0.1) + labs(title = "Within-person association of log income change on K6 distress (ipw)")   

p1b <- plot(ggeffects::ggpredict(m1b, terms = "inc_l_between_c[sd]"), add.data = TRUE, dot.alpha = 0.1)    + labs(title = "Between-person association of log income on K6 distress (ipw")   # 2 x standard deviations

library(patchwork)
p0b + p1b
```





So we do not find a causal effect.


##  What would happen if we did not use IPW? 

We find income more strongly related to Kessler 6 distress!

```{r}
library(effects)
# cannot plot without weights. so we add very small amount of noise
dt_weights_use_2$nullwts  <- rnorm(nrow(dt_weights_use_2), 1,.001)

library(splines)
m3 <- geeglm(
  k6  ~ k6_lag  +
    inc_l_lag  +
    as.numeric(age_c_lag_lag) +
    male_lag_lag +
    eth_lag_lag +
    emp_lag_lag +
    nzdep_lag_lag +
    partner_lag_lag +
    urban_lag_lag,
  data = dt_weights_use_2,
  id = id,
  waves = time,
  corstr = "ar1",
  weights = nullwts
)


parameters::model_parameters(m3) %>%
  print_html()

# cannot graph GEE with
plot(ggeffects::ggemmeans(m3, terms = "inc_l_lag[all]"), add.data = TRUE, dot.alpha = 0.1)    
```




## Mixed effects approach: IPW

What if we were to use a mixed effects model? 

```{r}
library(gamm4)
library(splines)

m2_lmer <- lmer(
  k6  ~ k6_lag  + 
    inc_l_lag  + 
    as.numeric(age_c_lag_lag) +
    male_lag_lag + 
    eth_lag_lag + 
    emp_lag_lag + 
    nzdep_lag_lag + 
    partner_lag_lag+  
    urban_lag_lag + (1 + time|id),
  data = dt_weights_use_2,
  weights = dt_weights_use_2$ipw
)

parameters::model_parameters(m2_lmer) %>%
  print_html()

# unclear
plot( ggeffects::ggpredict(m2_lmer, terms = "inc_l_lag [all]"), add.data = TRUE, dot.alpha = 0.1)
```

We do not find support for an income effect. 


## Mixed effects approach no IPW

```{r}
m2_lmer2 <- lmer(
  k6  ~  k6_lag  + 
    inc_l_lag  + 
    as.numeric(age_c_lag_lag) +
    male_lag_lag + 
    eth_lag_lag + 
    emp_lag_lag + 
    nzdep_lag_lag + 
    partner_lag_lag+  
    urban_lag_lag + (1 + time|id),
  data = dt_weights_use_2
)


# we find an effect
parameters::model_parameters(m2_lmer2) %>%
  print_html()

# then it looks as though more income = lower distress. 
plot( ggeffects::ggpredict(m2_lmer2, terms = "inc_l_lag"), add.data = TRUE, dot.alpha = 0.1)     # 

```

Here we find support for a linear relationship.




Finally, let us consider splines. 

```{r}
library(splines)

m2_lmer3 <- lmer(
  k6  ~  k6_lag  + 
    bs(inc_l_lag) + 
    as.numeric(age_c_lag_lag) +
    male_lag_lag + 
    eth_lag_lag + 
    emp_lag_lag + 
    nzdep_lag_lag + 
    partner_lag_lag+  
    urban_lag_lag  + (1|id),
  data = dt_weights_use_2
)
# we find an effect
parameters::model_parameters(m2_lmer3) %>%
  print_html()

# then it looks as though more income = lower distress. 
plot( ggeffects::ggpredict(m2_lmer3, terms = "inc_l_lag [all]"), add.data = TRUE, dot.alpha = 0.1)     # 

```

This suggests a linear decline in distress from income. The lower distress at the zero end of income might arise from situations in which there is wealt but no household income (Elon Musk, etc...)

## Questions

Key points:
  - need to multiply impute
  - Use GEE
  - Negative binomial? 
  - Sensitivity to IP weighting = important.
  - Model specification = important.
  - Handling of zero income? 
  - Need to handle missingness at the next iteration.
  - Need to adjust for more confounders at the next iteration.  
  - Sensitivity tests.





## G-estimation (just testing)

This is possibly not the right approach to our question. Notably, however, the model recovers a larger effect estimate. 

We must handle attrition. There is likely to be selection on those who remain in the study. 

Note: the model below won't run because time (k) needs to be ordered k...K+1 with no breaks.



```{r eval=FALSE}
# we do not evaluate this to save time

library(gesttools)
# must start at 1
dg <- df %>%
  dplyr::filter(YearMeasured == 1)  %>%
 dplyr::filter(Wave != 2009) %>% # no k6 measure
  dplyr::filter(!is.na(KESSLER6sum), !is.na(Household.INC),!is.na(EthnicCats),!is.na(Male),!is.na(Urban), !is.na(Employed)) %>%
  dplyr::select(
    Id,
    Household.INC,
    KESSLER6sum,
    NZdep,
    Wave,
   # TSCORE,
    Age,
  # Religion.Prayer,
  #  Religion.Scripture,
    Religion.Church,
    Male,
    Edu,
    EthnicCats,
    Urban,
    Wave,
    Employed,
    Partner,
    Religious,
    Parent,
    NZdep,
   YearMeasured
  ) %>%
  dplyr::mutate(
    k6 = as.numeric(KESSLER6sum),
    age = (Age),
    inc_l = log(Household.INC + 1),
    emp = as.numeric(Employed),
    age_c = scale(Age, scale = F),
    employed = as.numeric(Employed)-1,
    nzdep = as.numeric(NZdep),
  #  pray_l = log(Religion.Prayer + 1),
  #  script_l = log(Religion.Scripture + 1),
    church_l = log(Religion.Church + 1),
    edu = as.numeric(Edu),
    partner = as.numeric(Partner),
    male = as.numeric(Male),
    eth = EthnicCats,
    nzdep = as.numeric(NZdep),
    religious=as.numeric(Religious),
    urban = as.numeric(Urban),
    ym = as.numeric(YearMeasured)-1) %>%
  dplyr::group_by(Id) %>% filter(n() > 8) %>%
  ungroup()%>%
  arrange(Id,Wave)

# must start at 1
dg$time <- as.integer(dg$Wave)-1
length(unique(dg$Id)) # 2366

dg1 <- dg %>%
  select(Id, time, inc_l, k6, male, urban, employed, nzdep, religious) %>%
  group_by(Id) %>%
  mutate(time = time - min(time) + 1)%>%
  mutate(mxtime = max(time))%>%
  ungroup() %>%
  mutate(id = as.numeric(factor(Id)))%>%
  select(-Id) %>%
  drop_na()

dg2 <- as.data.frame(dg1)

head(dg2)
dgg <- FormatData(dg2, 
                  idvar="id",
                  timevar = "time", 
                  An = "inc_l",
                  Cn = "mxtime",
                  varying=c("k6","inc_l", "employed","religious","nzdep","urban","male"),
                  GenerateHistory=TRUE, GenerateHistoryMax=NA)

head(dgg$k6)
head(dg1)
str(dgg


test <- gestMultiple(
  dgg,
  idvar = "id",
  timevar = "time",
  Yn = "k6",
  An = "inc_l",
  Ybin = FALSE,
  Abin = FALSE,
  Acat = FALSE,
  Lny = c("employed", "religious", "nzdep", "urban", "male"),
  Lnp =c( "employed", "religious", "nzdep", "urban", "male"),
  type = 1 #,
 # Cn = "mxtime",
 # LnC =c("employed", "religious", "nzdep", "urban", "male"),
 # cutoff = "mxtime"
)
summary(test$psi)


#
test2 <- gestboot(
  gestMultiple,
  dgg,
  idvar = "id",
  timevar = "time",
  Yn = "k6",
  An = "inc_l",
  Ybin = FALSE,
  Abin = FALSE,
  Acat = FALSE,
  Lny = c("employed", "religious", "nzdep", "urban", "male"),
  Lnp =c( "employed", "religious", "nzdep", "urban", "male"),
  type = 1 ,#,
  alpha = .05,
  bn = 5,
  oneside = "twosided",
  seed = 123)
 # Cn = "mxtime",
 # LnC =c("employed", "religious", "nzdep", "urban", "male"),
 # cutoff = "mxtime"

#saveRDS(test2, here::here("models", "test2"))
```


```{r}
test2 <- readRDS(here::here("models","test2"))
test2
```

## Gformula

Experimental

```{r}

dgf <- df %>%
 dplyr::filter(Wave != 2009) %>% # no k6 measure
  droplevels() %>%
 dplyr::filter(YearMeasured == 1)  %>%
  dplyr::select(
    Id,
    Household.INC,
    KESSLER6sum,
    NZdep,
    Wave,
   # TSCORE,
    Age,
    Euro,
  # Religion.Prayer,
  #  Religion.Scripture,
    Religion.Church,
    Male,
    Edu,
    EthnicCats,
    Urban,
    Wave,
    Employed,
    Partner,
    Religious,
    Parent,
    NZdep,
   YearMeasured
  ) %>%
  dplyr::mutate(
    wave = as.numeric(Wave) -1, 
    k6 = as.numeric(KESSLER6sum),
    age = (Age),
    inc_l = log(Household.INC + 1),
    emp = as.numeric(Employed)-1,
    euro = as.numeric(Euro)-1,
    age_c = scale(Age, scale = F),
    employed = as.numeric(Employed)-1,
    nzdep = as.numeric(NZdep),
  #  pray_l = log(Religion.Prayer + 1),
  #  script_l = log(Religion.Scripture + 1),
    church_l = log(Religion.Church + 1),
    edu = as.numeric(Edu),
    partner = as.numeric(Partner),
    male = as.numeric(Male)-1,
    eth = EthnicCats,
    nzdep = as.numeric(NZdep),
    religious=as.numeric(Religious)-1,
    urban = as.numeric(Urban)-1) %>%
    dplyr::group_by(Id) %>% 
  select(Id, k6,  inc_l, age, wave, euro, employed, nzdep, partner, male, religious, urban) %>%
  #mutate_all(~as.numeric(.)) %>%
 # drop_na() %>%
  filter(n() == 10) %>%
  ungroup() %>%
  mutate(time = wave - min(wave))%>%
  mutate(mxtime = max(time))%>%
  mutate(id = as.numeric(factor(Id)))%>%
  mutate(k6_s = scale(k6)) %>%
  arrange(id,time)

max(dgf$id)



count_waves_participants <- function(x){
  out<-dplyr::count(tally(group_by(x, Id), sort = TRUE, name="number_waves"), number_waves)
  print(out)
}
count_waves_participants(dgf)
```

```{r, eval=FALSE}
library(gfoRmula)

#This isn't working

# "Error in error_catch(id = id, nsimul = nsimul, intvars = intvars, interventions = interventions,  : 
# Time variable in obs_data not correctly specified. For each individual time records should begin with 0 (or, optionally -i if using i lags) and increase in increments of 1, where no time records are skipped."
dgf<- dgf%>%
rename(t0= time,
       A = partner,
       L1 = "inc_l",
       Y = "k6_s")
dgf
id <- 'id'
time_name <- 't0'
time_points <-10
covnames <- c(
    "L1",
    "A"
  )
outcome_name <- 'Y'
outcome_type <- 'continuous_eof'
covtypes =  c(
    "normal", "binary"
  )

intvars <- list('A', 'A')

interventions <- list(list(c(static, rep(0, 10))),
                      list(c(static, rep(1, 10))))

int_descript <- c('Never treat', 'Always treat')
                      
histories <- list(lagged)

histvars = list(c("L1", "A"))

covparams <- list(
    covmodels = c(
      L1 ~ lag1_A   +  t0,    
      A ~ lag1_A + L1  + t0))
covnames

ymodel <- Y ~  L1 + lag1_A + lag1_L1 + t0

library(data.table)
dgf<- data.table(dgf)


head(dgf)
test3 <- gformula(
  obs_data = dgf,
  id = id, 
  time_name = time_name,
  time_points = time_points,
  covnames = covnames, 
  outcome_name = outcome_name,
  outcome_type = outcome_type, 
  covtypes = covtypes,
  covparams = covparams, 
  ymodel = ymodel,
  intvars = intvars,
  interventions = interventions,
  int_descript = int_descript,
  histories = histories, 
  histvars = histvars,
  #basecovs = c("male","euro"),
  nsimul = 10000,
  seed = 1234)
plot(test3)


```

```{r, eval=FALSE}
id <- 'id'
time_points <- 7
time_name <- 't0'
covnames <- c('L1', 'L2', 'A')
outcome_name <- 'Y'
outcome_type <- 'survival'
covtypes <- c('binary', 'bounded normal', 'binary')
histories <- c(lagged, lagavg)
histvars <- list(c('A', 'L1', 'L2'), c('L1', 'L2'))
covparams <- list(covmodels = c(L1 ~ lag1_A + lag_cumavg1_L1 + lag_cumavg1_L2 +
                                  L3 + t0,
                                L2 ~ lag1_A + L1 + lag_cumavg1_L1 +
                                  lag_cumavg1_L2 + L3 + t0,
                                A ~ lag1_A + L1 + L2 + lag_cumavg1_L1 +
                                  lag_cumavg1_L2 + L3 + t0))
ymodel <- Y ~ A + L1 + L2 + L3 + lag1_A + lag1_L1 + lag1_L2 + t0
intvars <- list('A', 'A')
interventions <- list(list(c(static, rep(0, time_points))),
                      list(c(static, rep(1, time_points))))
int_descript <- c('Never treat', 'Always treat')
nsimul <- 10000

gform_basic <- gformula(obs_data = basicdata_nocomp, id = id,
                        time_points = time_points,
                        time_name = time_name, covnames = covnames,
                        outcome_name = outcome_name,
                        outcome_type = outcome_type, covtypes = covtypes,
                        covparams = covparams, ymodel = ymodel,
                        intvars = intvars,
                        interventions = interventions,
                        int_descript = int_descript,
                        histories = histories, histvars = histvars,
                        basecovs = c('L3'), nsimul = nsimul,
                        seed = 1234)
gform_basic
plot(gform_basic)
```








