---
title: "Does income affect psychological distress?"
description: |
author:
  - name: Joseph Bulbulia
    url: https://josephbulbulia.netlify.app
    affiliation: Victoria University of Wellington
    affiliation_url: https://www.wgtn.ac.nz
    orcid_id: 0000-0002-5861-2056
date: 2021-DEC-02
output:
  distill::distill_article:
    self_contained: false
    toc: true
    code_folding: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  layout = "l-body-outset",
  fig.width = 12,
  fig.height = 15,
  collapse = TRUE,
  R.options = list(width = 60
  )
)
```

```{r libs, include=FALSE}
library("tidyverse")
library("easystats")
library("here")
library("equatiomatic")
library("lubridate")
library("ggplot2")
library("ggthemes") #themes
library("ggpubr")
library("viridis")
library("patchwork")
library("ggforce")
library("kableExtra")
library("lme4")
library("brms")
library("rstan")
library("rstanarm")
library("bayesplot")
library("kableExtra")
library("broom")
library("tidybayes")
library("bmlm")
library("gfoRmula")
library("ipw")
library("geepack")
library("gesttools")
library("lcsm")
library("patchwork")

# rstan options
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores ())
theme_set(theme_classic())
```

```{r data, cache = TRUE}
#import data
# long data
df <- readRDS(here::here("data", "df"))
```

Does money make people happy?


## Lingering Questions: 

- What is the target-trial that we are trying to emulate here? (cf Hernans...)
- Does the (k6 + t2) ~ (inc + t1)  + (k6 + t1) + lag_2 (t0_baseline confounders) emulate a target trial? 
- exposure/outcome confounding? 
- do we want to define a clear treatment (ordinal categories for income?), so that we can emulate a target trial (and obtain meaningful IPWs)?


## Data preparation 

```{r dataprep, cache=TRUE}
# comparative analysis

# prepare data
# note, still need to do IPW and multiply impute missing data
dt <- df %>%
  dplyr::filter(YearMeasured == 1)  %>%
 dplyr::filter(Wave != 2009) %>% # no k6 measure
  dplyr::filter(!is.na(KESSLER6sum), !is.na(Household.INC),!is.na(EthnicCats),!is.na(Male),!is.na(Urban), !is.na(Employed)) %>%
  dplyr::select(
    Id,
    Household.INC,
    KESSLER6sum,
    NZdep,
    Wave,
    TSCORE,
    Age,
    Religious,
    Religion.Prayer,
    Religion.Scripture,
    Religion.Church,
    Male,
    Edu,
    EthnicCats,
    Urban,
    Wave,
    Employed,
    Partner
  ) %>%
  dplyr::mutate(
    k6 = as.numeric(KESSLER6sum),
    age = (Age),
    inc_l = log(Household.INC + 1),
    emp = as.numeric(Employed),
  #  pray_l = log(Religion.Prayer + 1),
  #  script_l = log(Religion.Scripture + 1),
    church_l = log(Religion.Church + 1),
    edu = as.numeric(Edu),
    religious = as.numeric(Religious),
    partner = as.numeric(Partner),
    male = as.factor(Male),
    eth = EthnicCats,
    nzdep = as.numeric(NZdep),
    urban = Urban,
   id = Id
  ) %>%
  dplyr::group_by(Id) %>% filter(n() > 2) %>%
  mutate(time0 = as.numeric(Wave))%>%
  mutate(time = time0 - min(time0) )%>%
  mutate(mxtime = max(time))%>%
  dplyr::mutate(across(
    c(
      age,
      male,
      eth,
      emp,
      urban,
      k6,
      inc_l,
      edu,
      church_l,
      nzdep,
      partner,
      religious
    ),
    list(lag = lag)
  )) %>%
   dplyr::mutate(across(c(age_lag, 
                        eth_lag, 
                        urban_lag,
                        male_lag, 
                        urban_lag,
                        edu_lag, 
                        church_l_lag, 
                        nzdep_lag, 
                        partner_lag,
                        religious_lag,
                        emp_lag,
                        inc_l_lag,
                        k6), 
                 list(lag = lag)
                 ))%>%
  dplyr::ungroup(Id) %>%
  dplyr::select(id, k6, k6_lag, inc_l_lag, age_lag_lag, eth_lag_lag,urban_lag_lag,edu_lag_lag,
                church_l_lag_lag,nzdep_lag_lag,partner_lag_lag,emp_lag_lag,time,male_lag_lag,mxtime, inc_l, age_lag, emp_lag, partner_lag,male_lag, edu_lag, eth_lag, church_l_lag, urban_lag, religious_lag, nzdep_lag, inc_l_lag_lag, Id) %>%
  drop_na() %>%
  dplyr::mutate(age_c_lag_lag = scale(age_lag_lag, scale = F)) %>%
    dplyr::arrange(id,time)


  
#dt<- dt %>%
 # mutate_all(~as.numeric(.))


dt<-as.data.frame(dt)
```

Number of participants

```{r, cache=TRUE}
# cound id's
length(unique(dt$Id))
```


### Prepare data for within/between models

Some worry about "heterogeneity bias."  Can separate within and between participant features of change? It seems that we should do so, for example, to avoid Simpson's Paradoxes. 

See: https://easystats.github.io/datawizard/articles/demean.html


```{r}
# see https://easystats.github.io/datawizard/articles/demean.html
# we want to deal with *Heterogeneity bias *
# prepare data
dt2 <- cbind(dt,
             demean(dt,
                    select = c("inc_l"),
                    group = "Id")) %>%
  mutate(
    inc_l_between_c = scale(inc_l_between, scale = FALSE)
  )
```


### Prepare data for IP Weights


```{r}
## Marginal Structural model approach: IPW
# calculate weights: Note -- is this correct? 

dt_weights_2 <- ipw::ipwtm(
  exposure = inc_l_lag,
  family = "gaussian",
  type = "all",
  corstr = "ar1",
  id = "id",
  timevar = "time", 
  numerator = ~  inc_l_lag_lag  +  # lag treatment + confounders
    age_c_lag_lag +
    male_lag_lag + 
    eth_lag_lag + 
    emp_lag_lag + 
    nzdep_lag_lag + 
    partner_lag_lag+  
    urban_lag_lag,
  denominator = ~ # lag treatment + lag outcome +  confounders
    k6_lag  + 
    inc_l_lag_lag  + 
    age_c_lag_lag +
    male_lag_lag + 
    eth_lag_lag + 
    emp_lag_lag + 
    nzdep_lag_lag + 
    partner_lag_lag+  
    urban_lag_lag,
  data = as.data.frame(dt2)
)
dt_weights_use_2 <- dt2 %>% 
  mutate(ipw = dt_weights_2$ipw.weights)
```




## Draw your assumptions


# Dag

We adjust for the effects of unmeasured confounders (U) by conditioning on the lag of the exposure, the lag of the outcome, and the lag2 of measured confounders (L):  

```{r}
# Create Dags
library(ggdag)
dg <- ggdag::dagify(
  k6  ~ k6_lag  + inc_lag  + L,
  inc_lag ~ L + U,
  k6_lag  ~   L + U,
  L ~ U,
  exposure = "inc_lag",
  outcome = "k6",
  latent = "U"
) %>%
  control_for("k6_lag")

#Check backdoor paths
#p1 <-ggdag(dg) + theme_dag_blank() + labs(title = "confounding control")
#p1
ggdag::ggdag_adjustment_set(dg) + theme_dag_blank()

```


## Descriptive graphs


Here we plot change in K6 by id over 10 waves. Hard to see what is happening. 

```{r}
df %>% 
  dplyr::filter(YearMeasured==1) %>%
  dplyr::group_by(Id) %>% filter(n() > 9) %>%
  ungroup()%>%
  ggplot(aes(x = TSCORE,
             y = KESSLER6sum)) +
  geom_point() +
  geom_line(aes(group = Id), 
            size = 1, 
            alpha = .1) +
 # geom_smooth(method = "lm") +
  theme_bw() +
  #facet_grid(.~ Employed) +
  labs(title = "Change in distress over time",
       subtitle = "NZAVS years: 2010-2020")
```


Here we plot distress trajectories witin a subset of individuals. This approach helps us to see the qualities of the data. 


```{r}
library(lcsm)
widelong <-  df %>%
  dplyr::filter(YearMeasured==1) %>%
  dplyr::filter(Wave!=2009) %>% # k6 not measured in wave 1
  dplyr::group_by(Id) %>% filter(n() > 9) %>%
  dplyr::select(Id, KESSLER6sum, Wave) # 



wide <- spread(widelong, Wave, KESSLER6sum)

wide2 <- wide[complete.cases(wide),]


x_var_list <- names(wide2[, 2:11])



wide2 <- as.data.frame(wide2)
plot_trajectories(
  data = wide2,
  id_var = "Id",
  var_list = x_var_list,
  line_colour = "red",
  xlab = "Time",
  ylab = "Value",
  connect_missing = F,
  scale_x_num = T,
  scale_x_num_start = 1,
  random_sample_frac = 0.05,
  seed = 1234
  #title_n = T
)  +
  facet_wrap( ~ Id)



```

Next we can look at variation in income. Is this variable reliable? 

```{r}
widelong <-  df %>%
  dplyr::filter(YearMeasured==1) %>%
  dplyr::filter(Wave!=2009) %>% # 1
  dplyr::group_by(Id) %>% filter(n() > 9) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(Household.INC_log = log(Household.INC+1)) %>%
  dplyr::select(Id, Household.INC_log, Wave) # 

wide <- spread(widelong, Wave, Household.INC_log)

wide2 <- wide[complete.cases(wide),]


x_var_list <- names(wide2[, 2:11])
wide2 <- as.data.frame(wide2) # needs df

# graph
plot_trajectories(
  data = wide2,
  id_var = "Id",
  var_list = x_var_list,
  line_colour = "red",
  xlab = "Time",
  ylab = "Value",
  connect_missing = F,
  scale_x_num = T,
  scale_x_num_start = 1,
  random_sample_frac = 0.05,
  seed = 1234
  #title_n = T
)  +
  facet_wrap( ~ Id)

```


Consider NZdep. Is this variable reliable? Lots of movement. 

```{r}
widelong <-  df %>%
  dplyr::filter(YearMeasured==1) %>%
  dplyr::filter(Wave!=2009) %>% # 1
  dplyr::group_by(Id) %>% filter(n() > 9) %>%
  dplyr::ungroup() %>%
  dplyr::select(Id, NZdep, Wave) # 

wide <- spread(widelong, Wave, NZdep)


wide2 <- wide[complete.cases(wide),]


x_var_list <- names(wide2[, 2:11])



wide2 <- as.data.frame(wide2)
plot_trajectories(
  data = wide2,
  id_var = "Id",
  var_list = x_var_list,
  line_colour = "red",
  xlab = "Time",
  ylab = "NZdep",
  connect_missing = F,
  scale_x_num = T,
  scale_x_num_start = 1,
  random_sample_frac = 0.05,
  seed = 1234
  #title_n = T
)  +
  facet_wrap( ~ Id)

```


## Within/between mixed effects model (IPW)


```{r}
m1 <- lmer(
  k6 ~ 
    inc_l_within + 
    inc_l_between_c  +
    as.numeric(k6_lag) +
    as.numeric(age_lag) +
    male_lag +
    eth_lag +
    emp_lag +
    nzdep_lag +
    partner_lag +
    religious_lag + 
    church_l_lag + 
    urban_lag + (1 | Id),
  weights = dt_weights_use_2$ipw,
  data = dt_weights_use_2
)


parameters::model_parameters(m1) %>%
  print_html()

library(ggeffects)
p0 <- plot(ggeffects::ggpredict(m1, terms = "inc_l_within[all]"), add.data = TRUE, dot.alpha = 0.1) + labs(title = "Within-person association of log income change on K6 distress")   

p1 <- plot(ggeffects::ggpredict(m1, terms = "inc_l_between_c[all]"), add.data = TRUE, dot.alpha = 0.1)    + labs(title = "Between-person association of log income on K6 distress")   # 2 x standard deviations

library(patchwork)
p0 + p1
```

We find evidence for a within-person and between person effects of income on k6.


## No weights: within/between 

We can try within/between model without weights.

```{r}
m1b <- lmer(
  k6 ~
    inc_l_within +
    inc_l_between_c  +
    as.numeric(k6_lag) +
    as.numeric(age_lag) +
    male_lag +
    eth_lag +
    emp_lag +
    nzdep_lag +
    partner_lag +
    religious_lag +
    church_l_lag +
    urban_lag + (1 | Id),
  #weights = dt_weights_use_2$ipw,
  data =  dt_weights_use_2
)


parameters::model_parameters(m1b) %>%
  print_html()

library(ggeffects)
p0b <-
  plot(
    ggeffects::ggpredict(m1b, terms = "inc_l_within[all]"),
    add.data = TRUE,
    dot.alpha = 0.1
  ) + labs(title = "Within-person association of log income change on K6 distress (no ipw)")

p1b <-
  plot(
    ggeffects::ggpredict(m1b, terms = "inc_l_between_c[all]"),
    add.data = TRUE,
    dot.alpha = 0.1
  )    + labs(title = "Between-person association of log income on K6 distress (no ipw")   # 2 x standard deviations

library(patchwork)
p0b + p1b
```

Removing weights attenuates within-person effect.


## GEE

Here we will used lagged values of the exposure to adjust for confounders and IP weights.

```{r}
str(dt)
m2 <- geeglm(
  k6  ~  k6_lag  + 
    inc_l_lag + 
    as.numeric(age_c_lag_lag) +
    male_lag_lag + 
    eth_lag_lag + 
    emp_lag_lag + 
    nzdep_lag_lag + 
    partner_lag_lag+  
    urban_lag_lag,
  data = dt_weights_use_2,
  id = id,
  weights = ipw,
  waves = time,
  corstr = "ar1"
)

parameters::model_parameters(m2) %>%
  print_html()

library(ggeffects)
p2 <- plot(ggeffects::ggemmeans(m2, terms = "inc_l_lag[all]"), add.data = TRUE, dot.alpha = 0.1)    # 2 x standard deviations
p2 #+ scale_y_continuous(limits= c(0,15)) # nothing
```

Here we find an effect of income on K6. 


We find income more strongly related to Kessler 6 distress!

```{r}
library(effects)
# cannot plot without weights. so we add very small amount of noise
dt_weights_use_2$nullwts  <- rnorm(nrow(dt_weights_use_2), 1,.001)

library(splines)
m3 <- geeglm(
  k6  ~ k6_lag  +
    inc_l_lag  +
    as.numeric(age_c_lag_lag) +
    male_lag_lag +
    eth_lag_lag +
    emp_lag_lag +
    nzdep_lag_lag +
    partner_lag_lag +
    urban_lag_lag,
  data = dt_weights_use_2,
  id = id,
  waves = time,
  corstr = "ar1",
  weights = nullwts
)


parameters::model_parameters(m3) %>%
  print_html()

# cannot graph GEE with
plot(ggeffects::ggemmeans(m3, terms = "inc_l_lag[all]"), add.data = TRUE, dot.alpha = 0.1)    
```

Even without weights, we recover the effect. 


## Mixed effects approach: IPW

What if we were to use a mixed effects model? 

```{r}
library(gamm4)
library(splines)

# lmer
m2_lmer <- lmer(
  k6  ~ k6_lag  +
    inc_l_lag  +
    as.numeric(age_c_lag_lag) +
    male_lag_lag +
    eth_lag_lag +
    emp_lag_lag +
    nzdep_lag_lag +
    partner_lag_lag +
    urban_lag_lag + (1 + time | id),
  data = dt_weights_use_2,
  weights = dt_weights_use_2$ipw
)

parameters::model_parameters(m2_lmer) %>%
  print_html()

# graph
plot(
  ggeffects::ggpredict(m2_lmer, terms = "inc_l_lag [all]"),
  add.data = TRUE,
  dot.alpha = 0.1
)
```

We find support for an income effect. 


## Mixed effects approach (no IPW)

```{r}
m2_lmer2 <- lmer(
  k6  ~  k6_lag  + 
    inc_l_lag  + 
    as.numeric(age_c_lag_lag) +
    male_lag_lag + 
    eth_lag_lag + 
    emp_lag_lag + 
    nzdep_lag_lag + 
    partner_lag_lag+  
    urban_lag_lag + (1 + time|id),
  data = dt_weights_use_2
)


# we find an effect
parameters::model_parameters(m2_lmer2) %>%
  print_html()

# then it looks as though more income = lower distress. 
plot( ggeffects::ggpredict(m2_lmer2, terms = "inc_l_lag"), add.data = TRUE, dot.alpha = 0.1)     # 

```

Here we find support for a linear relationship.


## Mixed effects models with splines


Finally, let us consider splines. 

```{r}
library(splines)

m2_lmer3 <- lmer(
  k6  ~  k6_lag  + 
    bs(inc_l_lag) + 
    as.numeric(age_c_lag_lag) +
    male_lag_lag + 
    eth_lag_lag + 
    emp_lag_lag + 
    nzdep_lag_lag + 
    partner_lag_lag+  
    urban_lag_lag  + (1|id),
    weights = dt_weights_use_2$ipw,
  data = dt_weights_use_2
)
# we find an effect
parameters::model_parameters(m2_lmer3) %>%
  print_html()

# then it looks as though more income = lower distress. 
plot(
  ggeffects::ggpredict(m2_lmer3,
                       terms = "inc_l_lag [all]"),
  add.data = TRUE,
  dot.alpha = 0.1
)     

```

This suggests a linear decline in distress from income, at the high end of income.

### Within/between splines

Similar story. 

```{r}
m1bs <- lmer(
  k6 ~
    bs(inc_l_within) +
    bs(inc_l_between_c)  +
    as.numeric(k6_lag) +
    as.numeric(age_lag) +
    male_lag +
    eth_lag +
    emp_lag +
    nzdep_lag +
    partner_lag +
    religious_lag +
    church_l_lag +
    urban_lag + (1 | Id),
  weights = dt_weights_use_2$ipw,
  data =  dt_weights_use_2
)


parameters::model_parameters(m1bs) %>%
  print_html()

library(ggeffects)
p0bs <-
  plot(
    ggeffects::ggpredict(m1bs, terms = "inc_l_within [all]"),
    add.data = TRUE,
    dot.alpha = 0.1
  ) + labs(title = "Within-person association of log income change on K6 distress (no ipw)")

p1bs <-
  plot(
    ggeffects::ggpredict(m1bs, terms = "inc_l_between_c[all]"),
    add.data = TRUE,
    dot.alpha = 0.1
  )    + labs(title = "Between-person association of log income on K6 distress (no ipw")   # 2 x standard deviations

library(patchwork)
p0bs + p1bs
```

We cannot obtain confidence intervales here. The linear model would appear sufficient. Greater income causes lower psychological distress. 


## Questions

Key points:
  - need to multiply impute
  - Use GEE
  - IP weighting = important, but does it makes sense for continuous exposures? 
  - Model specification = important.
  - Handling of zero income? 
  - Need to adjust for more confounders at the next iteration.  
  - Sensitivity tests.


## G-estimation (just testing)

This is possibly not the right approach to our question. Notably, however, the model recovers a larger effect estimate. 

We must handle attrition. There is likely to be selection on those who remain in the study. 
Note: the model below won't run because time (k) needs to be ordered k...K+1 with no breaks.



```{r eval=FALSE}
# we do not evaluate this to save time

library(gesttools)
# must start at 1

dg <- df %>%
  dplyr::filter(YearMeasured == 1)  %>%
  dplyr::filter(Wave != 2009) %>% # no k6 measure
  dplyr::filter(
    !is.na(KESSLER6sum),
    !is.na(Household.INC),
    !is.na(EthnicCats),
    !is.na(Male),
    !is.na(Urban),
    !is.na(Employed)
  ) %>%
  dplyr::select(
    Id,
    Household.INC,
    KESSLER6sum,
    NZdep,
    Wave,
    # TSCORE,
    Age,
    # Religion.Prayer,
    #  Religion.Scripture,
    Religion.Church,
    Male,
    Edu,
    EthnicCats,
    Urban,
    Wave,
    Employed,
    Partner,
    Religious,
    Parent,
    NZdep,
    YearMeasured
  ) %>%
  dplyr::mutate(
    k6 = as.numeric(KESSLER6sum),
    age = (Age),
    inc_l = log(Household.INC + 1),
    emp = as.numeric(Employed),
    age_c = scale(Age, scale = F),
    employed = as.numeric(Employed) - 1,
    nzdep = as.numeric(NZdep),
    #  pray_l = log(Religion.Prayer + 1),
    #  script_l = log(Religion.Scripture + 1),
    church_l = log(Religion.Church + 1),
    edu = as.numeric(Edu),
    partner = as.numeric(Partner),
    male = as.numeric(Male),
    eth = EthnicCats,
    nzdep = as.numeric(NZdep),
    religious = as.numeric(Religious),
    urban = as.numeric(Urban),
    ym = as.numeric(YearMeasured) - 1
  ) %>%
  dplyr::group_by(Id) %>% filter(n() > 8) %>%
  ungroup() %>%
  arrange(Id, Wave)

# must start at 1
dg$time <- as.integer(dg$Wave) - 1
length(unique(dg$Id)) # 2366

dg1 <- dg %>%
  select(Id, time, inc_l, k6, male, urban, employed, nzdep, religious) %>%
  group_by(Id) %>%
  mutate(time = time - min(time) + 1) %>%
  mutate(mxtime = max(time)) %>%
  ungroup() %>%
  mutate(id = as.numeric(factor(Id))) %>%
  select(-Id) %>%
  drop_na()

dg2 <- as.data.frame(dg1)

head(dg2)
dgg <- FormatData(
  dg2,
  idvar = "id",
  timevar = "time",
  An = "inc_l",
  Cn = "mxtime",
  varying = c("k6", "inc_l", "employed", "religious", "nzdep", "urban", "male"),
  GenerateHistory = TRUE,
  GenerateHistoryMax = NA
)

head(dgg$k6)
head(dg1)
str(dgg

    
    
    
    test <- gestMultiple(
      dgg,
      idvar = "id",
      timevar = "time",
      Yn = "k6",
      An = "inc_l",
      Ybin = FALSE,
      Abin = FALSE,
      Acat = FALSE,
      Lny = c("employed", "religious", "nzdep", "urban", "male"),
      Lnp = c("employed", "religious", "nzdep", "urban", "male"),
      type = 1 #,
      # Cn = "mxtime",
      # LnC =c("employed", "religious", "nzdep", "urban", "male"),
      # cutoff = "mxtime"
    )
    summary(test$psi)
    
    
    #
    test2 <- gestboot(
      gestMultiple,
      dgg,
      idvar = "id",
      timevar = "time",
      Yn = "k6",
      An = "inc_l",
      Ybin = FALSE,
      Abin = FALSE,
      Acat = FALSE,
      Lny = c("employed", "religious", "nzdep", "urban", "male"),
      Lnp = c("employed", "religious", "nzdep", "urban", "male"),
      type = 1 ,
      #,
      alpha = .05,
      bn = 5,
      oneside = "twosided",
      seed = 123
    )
    # Cn = "mxtime",
    # LnC =c("employed", "religious", "nzdep", "urban", "male"),
    # cutoff = "mxtime"
    
#saveRDS(test2, here::here("models", "test2"))
```


```{r}
test2 <- readRDS(here::here("models","test2"))
test2
```

## Gformula

Experimental

```{r}
dgf <- df %>%
 dplyr::filter(Wave != 2009) %>% # no k6 measure
  droplevels() %>%
 dplyr::filter(YearMeasured == 1)  %>%
  dplyr::select(
    Id,
    Household.INC,
    KESSLER6sum,
    NZdep,
    Wave,
   # TSCORE,
    Age,
    Euro,
  # Religion.Prayer,
  #  Religion.Scripture,
    Religion.Church,
    Male,
    Edu,
    EthnicCats,
    Urban,
    Wave,
    Employed,
    Partner,
    Religious,
    Parent,
    NZdep,
   YearMeasured
  ) %>%
  dplyr::mutate(
    wave = as.numeric(Wave) -1, 
    k6 = as.numeric(KESSLER6sum),
    age = (Age),
    inc_l = log(Household.INC + 1),
    emp = as.numeric(Employed)-1,
    euro = as.numeric(Euro)-1,
    age_c = scale(Age, scale = F),
    employed = as.numeric(Employed)-1,
    nzdep = as.numeric(NZdep),
  #  pray_l = log(Religion.Prayer + 1),
  #  script_l = log(Religion.Scripture + 1),
    church_l = log(Religion.Church + 1),
    edu = as.numeric(Edu),
    partner = as.numeric(Partner),
    male = as.numeric(Male)-1,
    eth = EthnicCats,
    nzdep = as.numeric(NZdep),
    religious=as.numeric(Religious)-1,
    urban = as.numeric(Urban)-1) %>%
    dplyr::group_by(Id) %>% 
  select(Id, k6,  inc_l, age, wave, euro, employed, nzdep, partner, male, religious, urban) %>%
  #mutate_all(~as.numeric(.)) %>%
 # drop_na() %>%
  filter(n() == 10) %>%
  ungroup() %>%
  mutate(time = wave - min(wave))%>%
  mutate(mxtime = max(time))%>%
  mutate(id = as.numeric(factor(Id)))%>%
  mutate(k6_s = scale(k6)) %>%
  arrange(id,time)

max(dgf$id)



count_waves_participants <- function(x){
  out<-dplyr::count(tally(group_by(x, Id), sort = TRUE, name="number_waves"), number_waves)
  print(out)
}
#count_waves_participants(dgf)
```

```{r, eval=FALSE}
library(gfoRmula)

#This isn't working

# "Error in error_catch(id = id, nsimul = nsimul, intvars = intvars, interventions = interventions,  : 
# Time variable in obs_data not correctly specified. For each individual time records should begin with 0 (or, optionally -i if using i lags) and increase in increments of 1, where no time records are skipped."
dgf<- dgf%>%
rename(t0= time,
       A = partner,
       L1 = "inc_l",
       Y = "k6_s")
dgf
id <- 'id'
time_name <- 't0'
time_points <-10
covnames <- c(
    "L1",
    "A"
  )
outcome_name <- 'Y'
outcome_type <- 'continuous_eof'
covtypes =  c(
    "normal", "binary"
  )

intvars <- list('A', 'A')

interventions <- list(list(c(static, rep(0, 10))),
                      list(c(static, rep(1, 10))))

int_descript <- c('Never treat', 'Always treat')
                      
histories <- list(lagged)

histvars = list(c("L1", "A"))

covparams <- list(
    covmodels = c(
      L1 ~ lag1_A   +  t0,    
      A ~ lag1_A + L1  + t0))
covnames

ymodel <- Y ~  L1 + lag1_A + lag1_L1 + t0

library(data.table)
dgf<- data.table(dgf)

test3 <- gformula(
  obs_data = dgf,
  id = id, 
  time_name = time_name,
  time_points = time_points,
  covnames = covnames, 
  outcome_name = outcome_name,
  outcome_type = outcome_type, 
  covtypes = covtypes,
  covparams = covparams, 
  ymodel = ymodel,
  intvars = intvars,
  interventions = interventions,
  int_descript = int_descript,
  histories = histories, 
  histvars = histvars,
  #basecovs = c("male","euro"),
  nsimul = 10000,
  seed = 1234)
plot(test3)


```

```{r, eval=FALSE}
id <- 'id'
time_points <- 7
time_name <- 't0'
covnames <- c('L1', 'L2', 'A')
outcome_name <- 'Y'
outcome_type <- 'survival'
covtypes <- c('binary', 'bounded normal', 'binary')
histories <- c(lagged, lagavg)
histvars <- list(c('A', 'L1', 'L2'), c('L1', 'L2'))
covparams <- list(covmodels = c(L1 ~ lag1_A + lag_cumavg1_L1 + lag_cumavg1_L2 +
                                  L3 + t0,
                                L2 ~ lag1_A + L1 + lag_cumavg1_L1 +
                                  lag_cumavg1_L2 + L3 + t0,
                                A ~ lag1_A + L1 + L2 + lag_cumavg1_L1 +
                                  lag_cumavg1_L2 + L3 + t0))
ymodel <- Y ~ A + L1 + L2 + L3 + lag1_A + lag1_L1 + lag1_L2 + t0
intvars <- list('A', 'A')
interventions <- list(list(c(static, rep(0, time_points))),
                      list(c(static, rep(1, time_points))))
int_descript <- c('Never treat', 'Always treat')
nsimul <- 10000

gform_basic <- gformula(obs_data = basicdata_nocomp, id = id,
                        time_points = time_points,
                        time_name = time_name, covnames = covnames,
                        outcome_name = outcome_name,
                        outcome_type = outcome_type, covtypes = covtypes,
                        covparams = covparams, ymodel = ymodel,
                        intvars = intvars,
                        interventions = interventions,
                        int_descript = int_descript,
                        histories = histories, histvars = histvars,
                        basecovs = c('L3'), nsimul = nsimul,
                        seed = 1234)

plot(gform_basic)
```








